### 2016-09-09 notes.tex
Working notes

\documentclass{article}
\usepackage{graphics}
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{enumerate}
\newcommand{\coursenumber}{176}
\newcommand{\Rr}{\mathbb{R}}
\newcommand{\Cc}{\mathbb{C}}
\newcommand{\Zz}{\mathbb{Z}}
\newcommand{\Nn}{\mathbb{N}}
\newcommand{\Ff}{\mathbb{F}}
\newcommand{\Qq}{\mathbb{Q}}
\newcommand{\fix}{\text{fix }}
\newcommand{\cl}{\text{cl }}

\topmargin  18pt  	% 27pt
\headheight 12pt  	% 12pt
\headsep    35pt 	% 45pt
\textheight 8.0in
\textwidth  6.2in

\oddsidemargin   22pt      % Left margin on odd-numbered pages.
\evensidemargin  22pt      % Left margin on even-numbered pages.
\marginparwidth  72pt       % Width of marginal notes.
\marginparsep    11pt      % Horizontal space between outer margin and 
                           % marginal note

\pagestyle{fancy}
\lhead{Leo Selker }
\chead{}
\rhead{2016-2017}
\lfoot{}
\cfoot{\thepage}
\rfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

\begin{center}{\Large Thesis Notes}\\ \vspace{1 ex} \end{center}

\vspace{2 ex}
\noindent

Big idea: Magnitude of a metric space is large as $t$, some scale factor, gets large - $t$ scales the metric, and as points get farther apart, they are "counted separately." On the other hand, hierarchical clustering records fewer clusters as $r$, a scale factor, gets large. What is the relationship between these two "counts of number of clusters?" Is magnitude even such a count?

\end{document}

### 2016-09-10 Thesis_Comp/euclidean_space.py
Updated functionality

@@ -1,0 +1,39 @@
+from __future__ import division
+import numpy as np
+import numpy.linalg as linalg
+import sys
+from scipy.spatial import distance as dist
+import math
+
+
+class EuclideanSpace(object):
+    EPSILON = 10**8  # No real reason...
+
+    def __init__(self, data_array, scale_factor=1):
+        # Data should be row major - each row is a point. Should be a numpy array.
+        data_array = data_array * scale_factor
+        print data_array
+        (self.n_points, self.dimension) = data_array.shape
+
+        # Calculate the distance matrix (using scipy)
+        distance_matrix_compact = dist.pdist(data_array, 'euclidean')
+        distance_matrix = dist.squareform(distance_matrix_compact)
+        # Go through and exponentiate the distances
+        vector_inverse_exp = np.vectorize(lambda n: math.exp(-n))
+        self.distance_matrix = vector_inverse_exp(distance_matrix)
+
+
+    def magnitude(self):
+        if linalg.cond(self.distance_matrix) < 1 / self.EPSILON or True:
+            mobius_inversion = linalg.inv(self.distance_matrix)
+            return np.sum(mobius_inversion)
+        else:
+            return None
+
+if __name__ == '__main__':
+    test_array = np.array(
+        [[0, 0],
+         [0, 2],
+         [3, 2]]
+    )
+    print EuclideanSpace(test_array, scale_factor=10).magnitude()

### 2016-09-10 Thesis_Comp/euclidean_space.py
Bug fix

@@ -7,24 +7,26 @@ import math
 
 
 class EuclideanSpace(object):
-    EPSILON = 10**8  # No real reason...
+    EPSILON = 10**(-8)  # No real reason...
 
     def __init__(self, data_array, scale_factor=1):
         # Data should be row major - each row is a point. Should be a numpy array.
-        data_array = data_array * scale_factor
+        data_array *= scale_factor
         print data_array
         (self.n_points, self.dimension) = data_array.shape
 
         # Calculate the distance matrix (using scipy)
         distance_matrix_compact = dist.pdist(data_array, 'euclidean')
         distance_matrix = dist.squareform(distance_matrix_compact)
+
         # Go through and exponentiate the distances
         vector_inverse_exp = np.vectorize(lambda n: math.exp(-n))
         self.distance_matrix = vector_inverse_exp(distance_matrix)
 
-
     def magnitude(self):
-        if linalg.cond(self.distance_matrix) < 1 / self.EPSILON or True:
+        # Can't get condition number to work... but I think it uses svd anyway
+        singular_values = linalg.svd(self.distance_matrix, compute_uv=False)
+        if singular_values[0] / singular_values[-1] < 1 / self.EPSILON:
             mobius_inversion = linalg.inv(self.distance_matrix)
             return np.sum(mobius_inversion)
         else:
@@ -34,6 +36,6 @@ if __name__ == '__main__':
     test_array = np.array(
         [[0, 0],
          [0, 2],
-         [3, 2]]
+         [0, 4]]
     )
     print EuclideanSpace(test_array, scale_factor=10).magnitude()

### 2016-09-10 Thesis_Comp/euclidean.py
shebang

@@ -1,7 +1,7 @@
+#!/usr/bin/env python
 from __future__ import division
 import numpy as np
 import numpy.linalg as linalg
-import sys
 from scipy.spatial import distance as dist
 import math
 
@@ -26,7 +26,7 @@ class EuclideanSpace(object):
     def magnitude(self):
         # Can't get condition number to work... but I think it uses svd anyway
         singular_values = linalg.svd(self.distance_matrix, compute_uv=False)
-        if singular_values[0] / singular_values[-1] < 1 / self.EPSILON:
+        if singular_values[-1] / singular_values[0] > self.EPSILON:  # Check for singular matrix
             mobius_inversion = linalg.inv(self.distance_matrix)
             return np.sum(mobius_inversion)
         else:

### 2016-09-12 notes.tex
Fixing untracked files
shebang
Updates

@@
 \newcommand{\Qq}{\mathbb{Q}}
+\newcommand{\Aa}{\mathbb{A}}
 \newcommand{\fix}{\text{fix }}
 \newcommand{\cl}{\text{cl }}
+\DeclareMathOperator{\ob}{ob}
 
@@
 \renewcommand{\footrulewidth}{0pt}
+\newtheorem{cc}{cc} % basis for counter
+\newtheorem{sumMobiusWeighting}[cc]{Lemma}
+\theoremstyle{definition}
+\newtheorem{defCatMobius}[cc]{Definition}
+\newtheorem{defWeighting}[cc]{Definition}
 
@@
 
+Mobius inversion:
+\begin{align*}
+g(n) &= \sum_{d | n} f(d) \\
+\Rightarrow f(n) &= \sum_{d | n} \mu(\frac dn) g(n)
+\end{align*}
+
+\begin{defCatMobius}
+A category $\Aa$ has \textbf{Mobius Inversion} $\mu$ if $\mu$ satisfies
+\[
+\sum_b \mu(a,b)\zeta(b,c) = \delta(a,c) = \sum_b \zeta(a,b)\mu(b,c),
+\]
+with each equality implying the other by finite dimensionality (TODO: show)
+\end{defCatMobius}
+\begin{defWeighting}
+A \textbf{weighting} on a category $\Aa$ is a function $w_a$ on $\ob(\Aa)$ such that for all $a \in \Aa$,
+\[
+\sum_b \zeta(a,b)\omega_b = 1.
+\]
+\end{defWeighting}
+\begin{sumMobiusWeighting}
+If $\Aa$ has Mobius inversion, then $\omega_a = \sum_b \mu(a,b)$ is a weighting on $\Aa$.
+\end{sumMobiusWeighting}
+\begin{proof} For all $a \in \Aa$,
+\begin{align*}
+\sum_b \zeta(a,b)\omega_b &= \sum_b\left( \zeta(a,b)\sum_c \mu(b,c)\right)\\
+&=\sum_b\sum_c\zeta(a,b)\mu(b,c)\\
+&=\sum_c\left(\sum_b\zeta(a,b)\mu(b,c)\right)\\
+&=\sum_c \delta(a,c)\\
+&=1.
+\end{align*}
+\end{proof}
+
 \end{document}

### 2016-09-12 Thesis_Comp/euclidean.py

@@ -1,4 +1,5 @@
 #!/usr/bin/env python
+# Leo Selker, 2016
 from __future__ import division
 import numpy as np
 import numpy.linalg as linalg

### 2016-09-12 Thesis_Comp/euclidean.py
Added multiscale magnitude

@@ -12,26 +12,30 @@ class EuclideanSpace(object):
 
     def __init__(self, data_array, scale_factor=1):
         # Data should be row major - each row is a point. Should be a numpy array.
+        # We multiply early by the scale factor to give the option of permanently scaling the space
         data_array *= scale_factor
-        print data_array
         (self.n_points, self.dimension) = data_array.shape
 
         # Calculate the distance matrix (using scipy)
         distance_matrix_compact = dist.pdist(data_array, 'euclidean')
-        distance_matrix = dist.squareform(distance_matrix_compact)
+        self.distance_matrix = dist.squareform(distance_matrix_compact)
 
-        # Go through and exponentiate the distances
+    def magnitude(self, scale_factor=1):
+
+        # Scale then exponentiate the distances
         vector_inverse_exp = np.vectorize(lambda n: math.exp(-n))
-        self.distance_matrix = vector_inverse_exp(distance_matrix)
+        exp_distance_matrix = vector_inverse_exp(self.distance_matrix * scale_factor)
 
-    def magnitude(self):
-        # Can't get condition number to work... but I think it uses svd anyway
         singular_values = linalg.svd(self.distance_matrix, compute_uv=False)
         if singular_values[-1] / singular_values[0] > self.EPSILON:  # Check for singular matrix
-            mobius_inversion = linalg.inv(self.distance_matrix)
+            mobius_inversion = linalg.inv(exp_distance_matrix)
             return np.sum(mobius_inversion)
         else:
             return None
+
+    def multiscale_magnitude(self, scale_factor_iterable):
+        magnitude_list = map(self.magnitude, scale_factor_iterable)
+        return magnitude_list
 
 if __name__ == '__main__':
     test_array = np.array(
@@ -39,4 +43,5 @@ if __name__ == '__main__':
          [0, 2],
          [0, 4]]
     )
-    print EuclideanSpace(test_array, scale_factor=10).magnitude()
+    euclidean_space = EuclideanSpace(test_array)
+    print(euclidean_space.multiscale_magnitude((2, 3)))

### 2016-09-13 Thesis_Comp/category.py
added category and simplicial complex classes

@@ -1,0 +1,50 @@
+#!/usr/bin/env python
+# Leo Selker, 2016
+from __future__ import division
+import numpy as np
+import numpy.linalg as linalg
+
+
+class PartialCategory(object):
+    # Objects and # of morphisms. Does not keep track of or enforce composition.
+    EPSILON = 10**(-8)  # No real reason...
+
+    def __init__(self,  morphism_table):
+        """
+        :param morphism_table: nxn numpy array of # morphisms
+        """
+        self.morphism_table = morphism_table
+        (a, b) = morphism_table.shape
+        if a != b:
+            raise ValueError("Morphism table must be square")
+
+    def mobius_matrix(self):
+        singular_values = linalg.svd(self.morphism_table, compute_uv=False)
+        if singular_values[-1] / singular_values[0] > self.EPSILON:  # Check for singular matrix
+            return linalg.inv(self.morphism_table)
+        else:
+            return None
+
+    def weights(self):
+        mobius_matrix = self.mobius_matrix()
+        if mobius_matrix == None: return None
+        weights = []
+        for column in range(mobius_matrix.shape[1]):
+            weight = np.sum(mobius_matrix[:, column])
+            weights.append(weight)
+        return weights
+
+if __name__ == '__main__':
+    morphism_tables = (
+        np.array(
+            [[1,0,0,0,1,1],
+             [0,1,0,1,0,1],
+             [0,0,1,1,1,0],
+             [0,0,0,1,0,0],
+             [0,0,0,0,1,0],
+             [0,0,0,0,0,1]]
+    ),
+    )
+
+    p_cat = PartialCategory(morphism_tables[0])
+    print(p_cat.mobius_matrix())

### 2016-09-13 Thesis_Comp/euclidean.py

@@ -26,7 +26,7 @@ class EuclideanSpace(object):
         vector_inverse_exp = np.vectorize(lambda n: math.exp(-n))
         exp_distance_matrix = vector_inverse_exp(self.distance_matrix * scale_factor)
 
-        singular_values = linalg.svd(self.distance_matrix, compute_uv=False)
+        singular_values = linalg.svd(exp_distance_matrix, compute_uv=False)
         if singular_values[-1] / singular_values[0] > self.EPSILON:  # Check for singular matrix
             mobius_inversion = linalg.inv(exp_distance_matrix)
             return np.sum(mobius_inversion)

### 2016-09-13 Thesis_Comp/simplicial.py

@@ -1,0 +1,37 @@
+#!/usr/bin/env python
+# Leo Selker, 2016
+
+from __future__ import division
+import numpy as np
+import category as cat
+
+class SimplicialComplex(object):
+    # NOT as fast/good as it could be
+    def __init__(self, simplex_list):
+        """
+        :param maximal_simplex_list: A list of sets.
+        """
+        self.simplex_list = simplex_list
+        self.simplex_list.sort(key=lambda l:len(l))
+
+    def to_partial_category(self):
+        """
+
+        :return: A partial category corresponding to the simplicial complex.
+        """
+        n_simplices = len(self.simplex_list)
+        morphism_table = np.zeros((n_simplices, n_simplices))
+        for i, simplex in enumerate(self.simplex_list):
+            morphism_table[i,i] = 1
+            for j, other in enumerate(self.simplex_list[:i]):
+                if other.issubset(simplex):
+                    morphism_table[j, i] = 1
+        return cat.PartialCategory(morphism_table)
+
+
+if __name__ == '__main__':
+    # simplex_list = [{1},{2},{3},{1,2},{2,3},{3,1}]
+    simplex_list = [{1},{2},{3},{4},{1,2},{2,3},{3,4},{4,1},{2,4},{1,2,4}]
+    simplicial_complex = SimplicialComplex(simplex_list)
+    print simplicial_complex.simplex_list
+    print simplicial_complex.to_partial_category().weights()

### 2016-09-16 introduction.tex
Updates

\documentclass{article}
\input{leoheader}

\begin{document}
\begin{center}{\Large Thesis Topic}\\ \vspace{1 ex} \end{center}
A \textbf{metric space} is a set $X$ together with a function, $d: X \times X \rightarrow \Rr^+$, which must satisfy:
\begin{align*}
d(a,a) &= 0;\\
d(a,b) & > 0 \text{ if } a \neq bl\\
d(a,b) &= d(b,a);\\
d(a,b) &\leq d(a,c) + d(c,b)
\end{align*}
$ \forall a,b,c \in X$.

A simple example of a metric space is $\Rr^n$. In that case, the natural metric is the Euclidean metric: 
\[
d\left((a_1,..., a_n), (b_1,...,b_n)\right) = \sqrt{\sum_{i=1}^n (a_i-b_i)^2}.
\]
Multi-dimensional data can be represented as a finite subset of $\Rr^n$, with the Euclidean metric, where each point represents a data point, and each dimension represents a feature of the data. If two points are close together under this metric, they must vary a relatively small amount in every feature, so in some circumstances are likely to be similar in some way which we care about.

In that case, it can be useful to cluster the data, to see if any natural groups emerge. But it might not be immediately clear on what scale clustering makes sense. So we use \textbf{hierarchical clustering}: We consider the data on many scales, and cluster points which are close together under each scale. We take the information about which points are in which clusters for all scales at once and put it together to form a \textbf{persistent set}. This object holds information about the object at all scales.

We can also approach a finite metric space from an entirely different direction. Tom Leinster defines the Euler characteristic of what is called a \textbf{category}, which for the moment can be considered a generalization of metric spaces (not really a good way to look at it in general). Each finite metric $X$ space can be converted into a category, and we can then take that category's Euler characteristic, which gives us what we call the metric space's \textbf{magnitude} (denoted $|X|$). This is different from $\#(X)$, the cardinality or size of $X$. Let $X_k$ denote $X$ scaled by a non-negative real number $k$, meaning $X$ with all pairwise distances multiplied by $k$. Then as $k \rightarrow \infty, |X_k| \rightarrow \#(X_k) = \#(X)$. But if we scale $X$ down, the magnitude decreases (or may cease to be defined). In particular $|X_0| = 1$.

We wonder to what extent it is interesting to consider $|X_k|$ to be related to the number of clusters in $X$ viewed at some scale inversely related to $k$. We also wonder to what extent these two notions of clustering are related.
\end{document}

### 2016-09-16 Thesis_Comp/category.py

@@ -43,8 +43,22 @@ if __name__ == '__main__':
              [0,0,0,1,0,0],
              [0,0,0,0,1,0],
              [0,0,0,0,0,1]]
-    ),
+        ),
+        np.array(
+            [[1,1,1],
+             [0,1,1],
+             [0,0,1]]
+        ),
+        np.array(
+            [[1, 0, 0, 0, 1, 1, 0],
+             [0, 1, 0, 1, 0, 1, 0],
+             [0, 0, 1, 1, 1, 0, 0],
+             [0, 0, 0, 1, 0, 0, 1],
+             [0, 0, 0, 0, 1, 0, 1],
+             [0, 0, 0, 0, 0, 1, 1],
+             [0, 0, 0, 0, 0, 0, 1]]
+        )
     )
 
-    p_cat = PartialCategory(morphism_tables[0])
-    print(p_cat.mobius_matrix())
+    p_cat = PartialCategory(morphism_tables[2])
+    print(p_cat.mobius_matrix(), np.sum(p_cat.mobius_matrix()))

### 2016-09-16 Thesis_Comp/euclidean.py

@@ -5,6 +5,7 @@ import numpy as np
 import numpy.linalg as linalg
 from scipy.spatial import distance as dist
 import math
+from matplotlib import pyplot as plt
 
 
 class EuclideanSpace(object):
@@ -44,4 +45,7 @@ if __name__ == '__main__':
          [0, 4]]
     )
     euclidean_space = EuclideanSpace(test_array)
-    print(euclidean_space.multiscale_magnitude((2, 3)))
+    scale_factors = np.arange(0, 3, .2)
+    magnitudes = euclidean_space.multiscale_magnitude(scale_factors)
+    plt.plot(scale_factors, magnitudes)
+    plt.show()

### 2016-09-16 Thesis_Comp/simplicial.py

@@ -28,10 +28,11 @@ class SimplicialComplex(object):
                     morphism_table[j, i] = 1
         return cat.PartialCategory(morphism_table)
 
-
 if __name__ == '__main__':
-    # simplex_list = [{1},{2},{3},{1,2},{2,3},{3,1}]
-    simplex_list = [{1},{2},{3},{4},{1,2},{2,3},{3,4},{4,1},{2,4},{1,2,4}]
+    simplex_list = [{1},{2},{3},{1,2},{2,3},{3,1}, {1,2,3}]
+    # simplex_list = [{1},{2},{3},{4},{1,2},{2,3},{3,4},{4,1},{2,4},{1,2,4}]
     simplicial_complex = SimplicialComplex(simplex_list)
     print simplicial_complex.simplex_list
-    print simplicial_complex.to_partial_category().weights()
+    partial_category = simplicial_complex.to_partial_category()
+    print partial_category.morphism_table
+    print partial_category.mobius_matrix()

### 2016-10-04 annotated_bibliography.tex
Updates

\documentclass[]{article}
\input{commands_packages}
%opening
\title{Annotated Bibliography}
\author{Leo Selker}
\iffalse
A list—done in LATEX—of the relevant sources, preceded by
one or two paragraphs explaining which are the main sources and what you will be doing
with each. 
\fi

\begin{document}
\maketitle
Hierarchical clustering is a way of expressing structure at a variety of levels within data. We can keep track of that structure using a \textit{persistent set}\cite{Carl1}. We can define clusters however we want using some scale factor. Generally we use single linkage, i.e. we partition under the equivalence relation define by whether there's a path between points involving no jumps of too long a distance.

We can also define the magnitude of a finite metric space \cite{Lein2}. This definition captures the "effective number of points" in the space in some sense. This is based on the idea of the Euler characteristic of a metric space \cite{Lein1}. As we scale the space smaller, the magnitude approaches 1, and as we scale it larger it approaches the number of points in the space. In this sense, we have a "backwards" scale factor, where to zoom in we increase the factor. So in some ways it approximates hierarchical clustering results. We can say more in the case of positive definite metric spaces \cite{Meck1}. We'll investigate the possible connection(s) between these ideas.

So far, we've spent the most time on \cite{Lein1}. We've worked through the details of the Euler characteristic definitions and motivations. I've also used code to observe how the magnitude behaves in certain cases.

\bibliography{bib_7_30_16}{}
\bibliographystyle{plain}
\end{document}

### 2016-10-04 pres_1.tex
Updates

\documentclass{beamer}
\usetheme{Frankfurt}
\input{commands_packages}
\graphicspath{{Figures/}}
\newcommand{\Col}{\text{Col}}

\begin{document}
\title{Clustering and Metric Space Magnitude}   
\author{Leo Selker \\  Pomona College} 
\date{\today} %October 7th, 2016

\frame{\titlepage} 
\frame{\frametitle{Outline}\tableofcontents}

\section{Motivation}
\frame{\frametitle{Hierarchical Clustering}
\begin{itemize}
\item Points represent data in Euclidean space.
\item Idea: Capture structure at various scales
\end{itemize}
\vspace{1cm}
\[
\includegraphics[width = 0.7\paperwidth] {multiscale_structure.png}
\]
}
\frame{\frametitle{Plan}
\begin{itemize}
\item There are relatively intuitive ways of clustering: We could connect points within $k$ of each other and then scale $k$.
\item But that's boring!
\end{itemize}
}
\section{Metric Spaces}

\frame{\frametitle{Definition}
\begin{itemize}
\item
A \textbf{metric space} $(X,d)$ is a set $X$ along with a function $d:X \times X \rightarrow \Rr^{\geq 0}$, such that, $\forall x,y,z \in X$:\\
\begin{itemize}
\item $d(x,y) \geq 0$, with equality iff $x = y$;
\item $d(x,y) = d(y,x)$; and
\item $d(x,y) + d(y,x) \geq d(x,z)$.
\end{itemize} 
If $X$ is finite then we say $(X,d)$ is a \textbf{finite metric space}.\\
\item
Useful example: Finite set of points in $\Rr^2$.
\end{itemize}
}

\frame{\frametitle{Data as a Metric Space}
\begin{itemize}
\item Data consists of a finite set of samples over $n$ variables
\item Very common idea: Represent data as points in $\Rr^n$. 
\item Note: $\Rr^n$ has far more structure than we need. We only care about distance.
\end{itemize}
}

\section{Weights}
\frame{\frametitle{Intuition behind Weighting}
\begin{itemize}
\item We want to count the number of clusters in a data set. So we'll assign a \textbf{weighting} to the points.
\item We want each cluster's weight to sum to close to 1
\item Points near many other points will have smaller values
\item Points which are separated will have larger values
\item Then, we'll sum the weights to get the \textbf{magnitude}, i.e. number of clusters, in the data set.
\end{itemize}
}
\frame{\frametitle{Weighting and Magnitude}
\begin{itemize}
\item
A \textbf{weighting} on a finite metric space $X$ is a set of weights $\omega_x$ in $\Rr$ such that, for all $x \in X$:
\[
\sum_{y \in X}e^{-d(x,y)}\omega_y = 1
\]
Weights may be negative, but it's easier to think of them as nonnegative.
\item Then the \textbf{magnitude} of $X$, denoted $|X|$, is defined by:
\[
|X| = \sum_{x \in X}\omega_x.
\]
\item May be various weightings, but magnitude is unique
\item Scale-dependent - see examples to come
\end{itemize}
}
\section{Examples}
\frame{\frametitle{Two Points}
Consider the space of two points separated by distance $d$:\\

                        \[
\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
\node[circle, draw, fill=black,
                        inner sep=0pt, minimum width=4pt](1) at (0,0) {};
\node[circle, draw, fill=black,
                        inner sep=0pt, minimum width=4pt](2) at (4,0) {};

\draw (1) -- (2) node[midway, above] {\textit{d}};

\end{tikzpicture}\]
\begin{itemize}
\item If $d$ is small, we expect there to be one cluster, and if $d$ is large, 2 clusters.
\item In this case, the weight of each point is equal to 
\[\frac{1}{1+e^{-d}}\]
so the magnitude is
\[
\frac{2}{1+e^{-d}}.
\]
\end{itemize}
}
\frame{\frametitle{Two Points Plot}
The space's magnitude as we scale $d$:
}
\frame{\frametitle{Simple Examples}
Consider the space below:\\

                        \[
\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
\node[circle, draw, fill=black,
                        inner sep=0pt, minimum width=4pt](1) at (0,0) {};
\node[circle, draw, fill=black,
                        inner sep=0pt, minimum width=4pt](2) at (4,0) {};
\node[circle, draw, fill=black,
                        inner sep=0pt, minimum width=4pt](3) at (0,-1) {};
\node[circle, draw, fill=black,
                        inner sep=0pt, minimum width=4pt](4) at (4,-1) {};
\draw (1) -- (2) node[midway, above] {\textit{1,000}};
\draw (1) -- (3)node[midway, left] {\textit{1}};
\draw (2) -- (4);
\draw (3) -- (4);
\end{tikzpicture}\]
\begin{itemize}
\item If $d$ is small, we expect there to be one cluster, and if $d$ is large, 2 clusters.
\item In this case, the weight of each point is equal to 
\[\frac{1}{1+e^{-d}}.\]
\end{itemize}
}

\section{}

\frame{\frametitle{}
\begin{center} {\huge Thank you!}\end{center}
}

\end{document}

### 2016-10-04 Thesis_Comp/euclidean.py

@@ -48,15 +48,15 @@ if __name__ == '__main__':
     )
     euclidean_space = EuclideanSpace(test_arrays[0])
     two_space = EuclideanSpace(test_arrays[1])
-    scale_factors = np.arange(.05, 1000, .05)
+    scale_factors = np.arange(.05, 20, .05)
     magnitudes_euc = euclidean_space.multiscale_magnitude(scale_factors)
     magnitudes_two = two_space.multiscale_magnitude(scale_factors)
     scale_factors_log = map(lambda x: math.log(x, 10), scale_factors)
 
-    plt.subplot(211)
-    plt.plot(scale_factors_log, magnitudes_euc)
+    #plt.subplot(211)
+    #plt.plot(scale_factors_log, magnitudes_euc)
 
-    plt.subplot(212)
+    #plt.subplot(212)
     plt.plot(scale_factors_log, magnitudes_two)
 
     plt.show()

### 2016-10-11 pres_1.tex
updates

@@
 \newcommand{\Col}{\text{Col}}
+\usepackage[euler-digits]{eulervm}
+\usetikzlibrary{decorations.pathreplacing,angles,quotes}
 
@@
 \title{Clustering and Metric Space Magnitude}   
-\author{Leo Selker \\  Pomona College} 
+\author{Leo Selker \\ Advisor: Vin de Silva} 
 \date{\today} %October 7th, 2016
@@
 \frame{\frametitle{Hierarchical Clustering}
+Hierarchical clustering is a general approach to data analysis
 \begin{itemize}
-\item Points represent data in Euclidean space.
+\item Points represent data 
 \item Idea: Capture structure at various scales
@@
 \begin{itemize}
-\item There are relatively intuitive ways of clustering: We could connect points within $k$ of each other and then scale $k$.
-\item But that's boring!
+\item There are relatively intuitive ways of clustering: We could connect points within distance $k$ of each other and then scale $k$
+\item But we're exploring a weird approach
+\item Very common idea: We will represent data as a \textit{finite metric space}
 \end{itemize}
-}
+}2
 \section{Metric Spaces}
-
-\frame{\frametitle{Definition}
+\frame{\frametitle{Metric Spaces}
+A \textbf{metric space} is a set $X$ together with a function $d: X \times X \rightarrow \Rr^{\geq 0}$, such that for all $x, y, z \in X,$
 \begin{itemize}
-\item
-A \textbf{metric space} $(X,d)$ is a set $X$ along with a function $d:X \times X \rightarrow \Rr^{\geq 0}$, such that, $\forall x,y,z \in X$:\\
+\item $d(x, y) \geq 0$, with equality $\iff x = y$;
+\item $d(x,y) = d(y,x)$; and
+\item $d(x,y) + d(y,z) \geq d(x,z)$.
+\end{itemize}
+A metric space whose underlying set $X$ is finite is called a \textbf{finite metric space}.
 \begin{itemize}
-\item $d(x,y) \geq 0$, with equality iff $x = y$;
-\item $d(x,y) = d(y,x)$; and
-\item $d(x,y) + d(y,x) \geq d(x,z)$.
-\end{itemize} 
-If $X$ is finite then we say $(X,d)$ is a \textbf{finite metric space}.\\
-\item
-Useful example: Finite set of points in $\Rr^2$.
+\item Useful example: Finite set of points in $\Rr^n$ (or even $\Rr^2$)
 \end{itemize}
@@
 
+\iffalse
 \frame{\frametitle{Data as a Metric Space}
@@
 \item Very common idea: Represent data as points in $\Rr^n$. 
-\item Note: $\Rr^n$ has far more structure than we need. We only care about distance.
+\item Note: $\Rr^n$ has more structure than we need. We only care about distance. \begin{itemize}
+\item Any finite metric space would work
+\end{itemize}
+\item For any two points $x,y \in X$, let $d(x,y)$ denote the distance between $x$ and $y$. In $\Rr^n$, we'll have 
+\[
+d((x_1,...,x_n), (y_1,...,y_n)) = \sqrt{(x_1 - y_1)^2 + ... + (x_n - y_n)^2},
+\]
+which is the Euclidean distance between the two points.
 \end{itemize}
 }
-
+\fi
 \section{Weights}
-\frame{\frametitle{Intuition behind Weighting}
+\frame{\frametitle{Intuition Behind Weighting}
 \begin{itemize}
-\item We want to count the number of clusters in a data set. So we'll assign a \textbf{weighting} to the points.
+\item We want to count the number of clusters in a space. We'll do it in a weird way:
+\item[] \begin{itemize}
+\item Assign a \textbf{weighting} to the points, i.e. assign each point a real-valued "weight"
 \item We want each cluster's weight to sum to close to 1
@@
 \item Points which are separated will have larger values
+\end{itemize}
 \item Then, we'll sum the weights to get the \textbf{magnitude}, i.e. number of clusters, in the data set.
+\item Note: There is no "correct" or "actual" number of clusters in a space
 \end{itemize}
@@
 \]
-\item May be various weightings, but magnitude is unique
-\item Scale-dependent - see examples to come
+\item May be various weightings, but all lead to the same magnitude
+\item Scale-dependent, which is why it's useful - see examples to come
 \end{itemize}
@@
 \frame{\frametitle{Two Points}
+
 Consider the space of two points separated by distance $d$:\\
@@
 \begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
+
 \node[circle, draw, fill=black,
@@
 
-\draw (1) -- (2) node[midway, above] {\textit{d}};
+\draw[decoration={brace,raise=7pt},decorate] (1) -- (2) node[midway, above = 10pt] {\textit{d}};
 
@@
 \frame{\frametitle{Two Points Plot}
-The space's magnitude as we scale $d$:
+The space's magnitude as we scale $d$ (Note that the $x$-axis is the log of $d$):
+\centerline{
+\includegraphics[width = 1.2\textwidth]{2_point.png}
 }
-\frame{\frametitle{Simple Examples}
+}
+\frame{\frametitle{Another Example}
 Consider the space below:\\
@@
 \node[circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](2) at (4,0) {};
+                        inner sep=0pt, minimum width=4pt](2) at (5,0) {};
 \node[circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](3) at (0,-1) {};
+                        inner sep=0pt, minimum width=4pt](3) at (0,-.5) {};
 \node[circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](4) at (4,-1) {};
-\draw (1) -- (2) node[midway, above] {\textit{1,000}};
-\draw (1) -- (3)node[midway, left] {\textit{1}};
-\draw (2) -- (4);
-\draw (3) -- (4);
-\end{tikzpicture}\]
+                        inner sep=0pt, minimum width=4pt](4) at (5,-.5) {};
+\draw[decoration={brace,raise=7pt},decorate] (1) -- (2) node[midway, above = 10pt] {\textit{d}};
+\draw[decoration={brace, mirror, raise = 7pt},decorate] (1) -- (3) node[midway, left = 10pt] {\textit{$\frac{d}{1,000}$}};
+% \draw (2) -- (4);
+% \draw (3) -- (4);
+\end{tikzpicture}\]\\
 \begin{itemize}
-\item If $d$ is small, we expect there to be one cluster, and if $d$ is large, 2 clusters.
-\item In this case, the weight of each point is equal to 
-\[\frac{1}{1+e^{-d}}.\]
+\item As we increase $d$, we would expect this to have 1 cluster, then 2, then 4
 \end{itemize}
 }
-
+\frame{\frametitle{Four Points Plot}
+The magnitude plot:
+\centerline{
+\includegraphics[width = 1.2\textwidth]{4_point.png}
+}
+}
 \section{}

### 2016-10-11 Thesis_Comp/euclidean.py

@@ -1,64 +1,0 @@
-#!/usr/bin/env python
-# Leo Selker, 2016
-from __future__ import division
-import numpy as np
-from scipy.spatial import distance as dist
-import math
-from matplotlib import pyplot as plt
-import category as cat
-
-class EuclideanSpace(object):
-    EPSILON = 10**(-8)  # No real reason...
-
-    def __init__(self, data_array, scale_factor=1):
-        # Data should be row major - each row is a point. Should be a numpy array.
-        # We multiply early by the scale factor to give the option of permanently scaling the space
-        data_array *= scale_factor
-        (self.n_points, self.dimension) = data_array.shape
-
-        # Calculate the distance matrix (using scipy)
-        distance_matrix_compact = dist.pdist(data_array, 'euclidean')
-        self.distance_matrix = dist.squareform(distance_matrix_compact)
-
-    def magnitude(self, scale_factor=1):
-
-        # Scale then exponentiate the distances
-        vector_inverse_exp = np.vectorize(lambda n: math.exp(-n))
-        exp_distance_matrix = vector_inverse_exp(self.distance_matrix * scale_factor)
-
-        cat_rep = cat.PartialEnrichedCategory(exp_distance_matrix)
-        return np.sum(cat_rep.mobius_matrix())
-
-    def multiscale_magnitude(self, scale_factor_iterable):
-        magnitude_list = map(self.magnitude, scale_factor_iterable)
-        return magnitude_list
-
-if __name__ == '__main__':
-    test_arrays = (
-        np.array(
-            [[0, 0],
-             [0, .01],
-             [10, 0],
-             [10,.01]]
-        ),
-        np.array(
-            [[0, 0],
-            [10, 0]]
-        )
-    )
-    euclidean_space = EuclideanSpace(test_arrays[0])
-    two_space = EuclideanSpace(test_arrays[1])
-    scale_factors = np.arange(.05, 20, .05)
-    magnitudes_euc = euclidean_space.multiscale_magnitude(scale_factors)
-    magnitudes_two = two_space.multiscale_magnitude(scale_factors)
-    scale_factors_log = map(lambda x: math.log(x, 10), scale_factors)
-
-    #plt.subplot(211)
-    #plt.plot(scale_factors_log, magnitudes_euc)
-
-    #plt.subplot(212)
-    plt.plot(scale_factors_log, magnitudes_two)
-
-    plt.show()
-
-

### 2016-10-11 Thesis_Comp/metric.py

@@ -1,0 +1,125 @@
+#!/usr/bin/env python
+# Leo Selker, 2016
+from __future__ import division
+import numpy as np
+from scipy.spatial import distance as dist
+import math
+from matplotlib import pyplot as plt
+import category as cat
+
+EPSILON = 10**(-5)
+
+class MetricSpace(object):
+    EPSILON = 10**(-8)  # No real reason...
+    distance_matrix = None
+
+    def __init__(self, distance_matrix):
+        self.distance_matrix = distance_matrix
+
+    @staticmethod
+    def space(distance_matrix):
+        return MetricSpace(distance_matrix)
+
+    @staticmethod
+    def product_space(matrix_1, matrix_2):
+        # Slow
+        ((m, n), (p,q)) = (matrix_1.shape, matrix_2.shape)
+        distance_matrix = np.empty((m*p, n*q))
+        for r, row in enumerate(matrix_1):
+            for s, el in enumerate(row):
+                distance_matrix[p*r: p*(r+1), q*s: q*(s+1)] = matrix_2 + el
+        return MetricSpace(distance_matrix)
+
+    @staticmethod
+    def euclidean(data_array, scale_factor=1):
+        # Builds a metric space from euclidean coordinates
+        # Data should be row major - each row is a point. Should be a numpy array.
+        # We multiply early by the scale factor to give the option of permanently scaling the space
+        data_array *= scale_factor
+
+        # Calculate the distance matrix (using scipy)
+        distance_matrix_compact = dist.pdist(data_array, 'euclidean')
+        distance_matrix = dist.squareform(distance_matrix_compact)
+        return MetricSpace(distance_matrix)
+
+    def magnitude(self, scale_factor=1):
+
+        # Scale then exponentiate the distances
+        vector_inverse_exp = np.vectorize(lambda n: math.exp(-n))
+        exp_distance_matrix = vector_inverse_exp(self.distance_matrix * scale_factor)
+
+        cat_rep = cat.PartialEnrichedCategory(exp_distance_matrix)
+        return np.sum(cat_rep.mobius_matrix())
+
+    def multiscale_magnitude(self, scale_factor_iterable):
+        magnitude_list = map(self.magnitude, scale_factor_iterable)
+        return magnitude_list
+
+if __name__ == '__main__':
+    if False: # Euclidean tests for 2- and 4-point spaces
+        test_arrays_euclidean = (
[…]

### 2016-12-22 Drafts/Draft_12_2016.tex
Reorganization

\documentclass[12pt]{pom_thesis}
\input{commands_packages}
\author{Leo Selker}
\advisor{Vin de Silva}
\title{The Magnitude of a Metric Space: An Approach to Clustering}

\newcommand{\fix}{\text{fix }}
\newcommand{\cl}{\text{cl }}
\DeclareMathOperator{\cat}{cat}
\begin{document}

\maketitle

\begin{abstract}Clustering is an important application of topology. Here we explore a method of counting clusters at various scales. We build the necessary framework using the idea of a M\"obius inversion, and then we define the magnitude of a metric space\cite{Lein2}. We investigate behaviors of positive definite metric spaces, as well as how the magnitude acts under the product of spaces.
\end{abstract}

\pagenumbering{roman}
\tableofcontents

\newpage
\pagenumbering{arabic}
\begin{chapter}{Outline}
\section{Introduction}
We will be investigating the magnitude of metric spaces along with related/foundational ideas. We investigate M\"obius inversion, a way of calculating the magnitude of a metric space. We motivate and define magnitude of a metric space using the Euler characteristic of a category. We investigate positive definite metric spaces and tensor products. It's still slightly early to say what our "goal" is.
\section{M\"obius Inversion}
We will start with Mobius inversion on the positive integers, generalize to posets, and again generalize to categories\cite{Lein1}. At each step we will justify the way we choose to generalize.

Here we may also investigate the P\'olya Counting Formula/Burnside's Lemma. We're just starting on that, so we'll see where it goes.
\section{Euler Characteristic of a Category}
We define the Euler characteristic of a finite category as the sum of all values of its Mobius inversion\cite{Lein1}. We will justify this by showing that simplicial complexes behave well under this definition, and it coincides with the usual one in that case. We'll also investigate working the other way: Taking a poset and turning it into a simplicial complex of chains. Hopefully this will lead somewhere too.
\section{Magnitude, Properties, and Examples}
We will define the "induced category" of a metric space, and use it as a motivation for the definition of the \textbf{magnitude} of a finite metric space\cite{Lein2} (the magnitude is the Euler characteristic of the induces category). This definition captures the "effective number of points" in the space in some sense. As we scale the space smaller, the magnitude approaches 1, and as we scale it larger it approaches the number of points in the space. In this sense, we have a "backwards" scale factor, where to zoom in we increase the factor. 
In some ways magnitudes over scales approximate hierarchical clustering results. In fact, the magnitude of the tensor product of two finite spaces is the product of the spaces' magnitudes (we proved this, but it is likely known). We can also say more in the case of positive definite metric spaces\cite{Meck1}. We will investigate approximation theorems for "almost-product" spaces, and other situations which are well behaved.

Here we will also probably discuss results from code I am writing.
\section{Magnitude and Persistence}
Hierarchical clustering is a way of expressing structure at a variety of levels within data. We can keep track of that structure using a \textit{persistent set}\cite{Carl1}. We can define clusters however we want using some scale factor. Generally we use single linkage, i.e. we partition under the equivalence relation define by whether there's a path between points involving no jumps of too long a distance.

We will attempt to connect the magnitude of a space with its persistent set. Both offer scaled counts of the number of clusters in some sense - we have some basic connections but hope to find more.
\end{chapter}
\begin{chapter}{M\"obius Inversion}
M\"obius inversion is a general construct. The most basic definition of a M\"obius function is a function $\mu$ on the positive integers which satisfies the following for all functions $f,g$ on the integers:

\begin{align*}
g(n) &= \sum_{d | n} f(d) \iff f(n) = \sum_{d | n} \mu\left(\frac dn\right) g(n)
\end{align*}

We will formally develop this using a more general construction, and then generalize to more even more abstract structures. We start with several definitions:
\begin{defn}
A \emph{partially ordered set}, often called a \emph{poset}, is a set $X$ together with a relation, denoted $\leq$, such that, for all $a,b,c \in X$:
\begin{itemize}
\item $a \leq a$ (reflexive)
\item If $a \leq b$ and $b \leq a$ then $a = b$ (antisymmetric)
\item If $a \leq b$ and $b \leq c$ then $a \leq c$ (transitive).
\end{itemize}
\end{defn}
\begin{defn}
The \emph{incidence algebra} on a finite poset $X$ is over the set of functions from $X \times X$ to $\Rr$ which map $(a,b)$ to zero if $a \nleq b$. So the elements of the incidence algebra are 
\[\{f:X \times X \rightarrow \Rr:a \nleq b \Rightarrow f(a,b) = 0\}
\]
Scalar multiplication and addition are defined pointwise.  Multiplication is denoted by ``*'', and is defined:
\[(f* g)(a,b) = \sum_{a \leq c \leq b}f(a,c)g(c,b).\]
\end{defn}
Note that the bounds on the sum are not necessary, because all other terms will go to zero anyway by the condition on elements. But I use them for clarity. Omitting the bounds, we see that this is identical to matrix multiplication. It will be useful to formalize this:
\begin{lemma}\label{mat_eq}
Let $X$ be a finite poset, with $|X|=n$. Choose a total ordering on $X$ such that the partial order is respected - in other words, label the elements of $X$ from $x_1$ to $x_n$, such that if $x_i \leq x_j, i \leq j$. Let $f,g$ be elements of the incidence algebra on $X$. Let $F$ be the $n\times n$ square matrix where $F_{ij}=f(x_i, x_j)$. Define $G$ likewise. Then:
\begin{enumerate}[a)]
\item $F$ and $G$ are upper triangular; and
\item For any $i,j, (f * g)(x_i, x_j)=FG_{ij}$.
\end{enumerate}
\end{lemma}
\begin{proof}
\begin{enumerate}[a)]
\item If $i>j$, by how we defined $F$, $x_i \nleq x_j$. So $F_{ij} = f(x_i, x_j) = 0$. 
\item
The result follows directly from the definition of matrix multiplication. Let $i,j\leq n$ be given. Remember that we can omit the bounds from the sum in the definition of incidence algebra multiplication. Then:
\begin{align*}
(f * g)(x_i, x_j) &= \sum_{y \in X} f(x_i,y)g(y,x_j)\\
&=FG_{ij}
\end{align*}
\end{enumerate}
\end{proof}

There are several important functions, present in any incidence algebra, which we will need. 
The \textbf{identity function} $\delta$ is defined by 
\[\delta(a,b) = \begin{cases} 1 & a = b \\ 0 & else. \end{cases}
\]
This is equivalent to the identity matrix, with 1's along the main diagonal.

We also define another special function, $\zeta$ (the ``ones function''):
\[
\zeta(a,b) = \begin{cases} 1 & a \leq b \\ 0 & else. \end{cases}
\]

At this point, \ref{mat_eq} tells us several things about inverses. Since $\delta$ is equivalent to the identity matrix, inverses will coincide with the corresponding matrix inverses. This leads us to the following:
\begin{cor}\label{cor_inv}
Let $f,g$ be elements of the incidence algebra on $X$. Then:
\begin{enumerate}[a)]
\item $f*g = \delta \Rightarrow g*f = \delta$
\item If $\forall x \in X, f(x,x) \neq 0$, then $f$ is uniquely invertible - in other words, $\exists! f^{-1}$ such that $f*f^{-1} = \delta = f^{-1} * f$.
\end{enumerate}
\end{cor}
\begin{proof}
Part a) is true of all square matrices. Part b) is true of all upper triangular matrices, since the determinant of such matrices is the product of the main diagonal elements. We use \ref{mat_eq} to transfer the results to $f$ and $g$.
\end{proof}
We will refer to this unique inverse, if it exists, as $f^{-1}$. We are now ready to define the M\"obius function on partially ordered sets.
\begin{defn}\label{def_mob_pos}
Let $X$ be a finite poset. Let $\zeta$ be the ones function defined above. Let $\mu = \zeta^{-1}$. Then $\mu$ is the \emph{M\"obius function} on $X$.
\end{defn}
\begin{rmk}
This inverse exists by \ref{cor_inv} part b. 
\end{rmk}
\begin{rmk}
Another statement of the definition is that $\mu$ is the unique function such that, for all $x,y \in X$,
\[
\sum_{z \in X} \mu(x,z)\zeta(z,y) = \delta(x,z) = \sum_{z \in X} \zeta(x,z)\mu(z,y)
\]
\end{rmk}
Note: Here I will add a summary of how the integer divisibility case follows from this definition.

% % %
\begin{defn}
A category $\Aa$ has \emph{Mobius Inversion} $\mu$ if $\mu$ satisfies
\[
\sum_b \mu(a,b)\zeta(b,c) = \delta(a,c) = \sum_b \zeta(a,b)\mu(b,c),
\]
with each equality implying the other by finite dimensionality (this is the same argument as showing that one-sided square matrix inverses are two-sided).
\end{defn}

We now state a definition with no justification/explanation. This will be carefully developed in the chapter on magnitude - I'm not sure how I will end up choosing to organize it.
\begin{defn}
A \emph{weighting} on a category $\Aa$ is a function $w_a$ on $\ob(\Aa)$ such that for all $a \in \Aa$,
\[
\sum_b \zeta(a,b)\omega_b = 1.
\]
\end{defn}
\begin{lemma}
\label{mobius_is_weighting}
If $\Aa$ has Mobius inversion, then $\omega_a = \sum_b \mu(a,b)$ is a weighting on $\Aa$.
\end{lemma}
\begin{proof} For all $a \in \Aa$,
\begin{align*}
\sum_b \zeta(a,b)\omega_b &= \sum_b\left( \zeta(a,b)\sum_c \mu(b,c)\right)\\
&=\sum_b\sum_c\zeta(a,b)\mu(b,c)\\
&=\sum_c\left(\sum_b\zeta(a,b)\mu(b,c)\right)\\
&=\sum_c \delta(a,c)\\
&=1.
\end{align*}
\end{proof}

\begin{defn}
Let $\sigma$ be a simplicial complex. Then the \emph{category generated by $\sigma$}, or $\cat(\sigma)$, is the category whose objects are the cells of $\sigma$. If $\gamma$ and $\omega$ are cells of $\sigma$, then $|(\gamma, \omega)| = 1$ if $\gamma \subseteq \omega$ and 0 else.
\end{defn}
\begin{lemma}
\label{mu_lemma}
Suppose $\alpha \subseteq \beta$ are cells of a simplicial complex. Then $\mu(\cat(\alpha), \cat(\beta)) =(-1)^{|\beta - \alpha|} = (-1)^{|\alpha|} (-1)^{|\beta|}$.
\end{lemma}
\begin{proof}
We use induction. Base case: $\sigma = \beta$, \checkmark \\
For any simplex $\sigma$, let $\sigma'$ be $\sigma \cup \emptyset$. Suppose that $|\beta - \alpha| = k+1$. We know that \begin{align*}
\mu(\alpha, \beta) &=  - \sum_{\alpha \subseteq \sigma \subset \beta} \mu(\alpha, \sigma)\\
&= - \sum_{\gamma \subset (\beta - \alpha)'} \mu(\alpha, \gamma \cup \alpha) 
\end{align*}
Note that the above unions are always disjoint. So, by the inductive hypothesis, we can rewrite it:
\begin{align*}
\mu(\alpha, \beta) &= - \sum_{\gamma \subset (\beta - \alpha)'} (-1)^{|\gamma \cup \alpha| - |\alpha|} \\ %& \text{inductive hypothesis}\\
&= - \sum_{\gamma \subset (\beta - \alpha)'} (-1)^{|\gamma|}\\ % &\text{by disjointness}\\
&= - \sum_{\gamma \subseteq (\beta - \alpha)} (-1)^{|\gamma|} + (-1)^{|\beta - \alpha|} - (-1)^0 \\ %&\text{Removing the empty simplex and including $\gamma = \beta - \alpha$}\\
&= \chi(\beta - \alpha) + (-1)^{|\beta - \alpha|} - (-1)^0\\
&= 1-1+ (-1)^{|\beta - \alpha|}\\
&= (-1)^{|\beta - \alpha|}
\end{align*}

\end{proof}
\begin{thm}
\label{consistentEuler}
Let $\sigma$ be a simplicial complex. Then 
\[
\sum_{\gamma \subseteq \sigma} \sum_{\alpha \subseteq \gamma} \mu(\alpha, \gamma) = \chi(\sigma).
\]

\end{thm}
\begin{proof}
Then:
\begin{align*}
\sum_{\gamma \in \sigma} \sum_{\alpha \subseteq \gamma} \mu(\alpha, \gamma) &= \sum_{\gamma \in \sigma} \sum_{\emptyset \subset \alpha \subseteq \gamma} \mu(\alpha, \gamma)\\
&= \sum_{\gamma \in \sigma} \mu(\emptyset, \gamma)\\
&= \sum_{\gamma \in \sigma} (-1)^{|\gamma|} &\text{by \ref{mu_lemma}}\\
&= \chi(\sigma)
\end{align*}
\end{proof}
By \ref{mobius_is_weighting}, weightings are a generalization of Mo\"bius inversion. This fact motivates the following definition, due to \cite{Lein1}.
\begin{defn}
Let $\omega$ be a weighting on a finite category $A$. Then the \emph{Euler characteristic} of $A$, denoted (as usual) as $\chi(A)$, is defined by
\[
\chi(A) = \sum_{a \in A} \omega_a
\]
\end{defn}
Note that even if a category admits several weightings, they all lead to the same Euler characteristic by a simple sum rearrangement argument. Together with \ref{mobius_is_weighting}, this implies the following:
\begin{cor}
If a finite category $A$ has a M\"obius inversion $\mu$, then
\[\chi(A) = \sum_{a \subseteq A} \sum_{b \subseteq A} \mu(a, b).
\]
\end{cor}
This provides the main motivation for exploring M\"obius inversion here. It provides a way in which we can write down weightings on many metric spaces, since the similarity matrix $\zeta$ is invertible in most cases. We will investigate exactly which cases when we discuss positive semidefinite matrices.
\end{chapter}
\bibliographystyle{apalike}
\bibliography{bibliography.bib}

\end{document}

### 2016-12-22 Drafts/test_thesis.tex
Reorganization

\documentclass[12pt]{pom_thesis}

\author{Leo Selker}
\advisor{Vin de Silva}
\title{Absolutely Fascinating Thesis Title}
\iffalse
\theoremstyle{plain}{
\newtheorem{thm}{Theorem}[chapter]
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
}

\theoremstyle{definition}{
\newtheorem{defn}[thm]{Definition}
\newtheorem{examp}[thm]{Example}
\newtheorem{rmk}[thm]{Remark}
}\fi
\begin{document}

\maketitle

\begin{abstract}In this paper we don't really do much.  However, there are a lot of {\it real} theorems that still need to be proved. That is what you will probably do in your thesis.
\end{abstract}

\pagenumbering{roman}
\tableofcontents

\newpage
\pagenumbering{arabic}

% EXAMPLE STUFF
% this is how you begin a chapter:
% the label is so that you can refer to it later
\begin{chapter}{Boring Title for the First Chapter}
\label{Intro}

Let us do some math:
% to start a new line in math mode
% either write your equation inside $$ .... $$
$$ \Delta(h) = h_{(1)} \otimes h_{(2)} $$
% or inside \[ ... \]
\[ \Delta(h) = h_{(1)} \otimes h_{(2)} \]
% or:
\begin{equation*}
\Delta(h) = h_{(1)} \otimes h_{(2)}
\end{equation*}

Here is how you declare a theorem:

\begin{thm}{A Big Fat Theorem.} \label{thm:BigFat}
We assert that the following is true:
\begin{equation} \label{eqn:Stupid}
x = 1, y = 1 \Rightarrow x + y = 2
\end{equation}
\end{thm}

Let us first consider:
%Here is how you declare a lemma:
\begin{lemma}{A Small but Important Lemma.} \label{lemma:LittleLem}
If $x = a$, and $y = b$, then $x + y = a + b$.
\end{lemma}

We can then see that Lemma \ref{lemma:LittleLem} implies Theorem \ref{thm:BigFat} by letting $a = 1$ and $b = 1$ in Equation (\ref{eqn:Stupid}). See how we refer to a previously labeled item in the text?

\section{A delightful new section}

Some text for the section should go here. And let us look at footnotes.\footnote{This is one way to use a footnote.} \footnotemark

\footnotetext{Here is a second way to introduce a footnote}

\begin{thm}
hmmm
\end{thm}

Here is how you call the proof environment:

\begin{proof}
hmmmm
\end{proof}

% you should close a chapter before beginning a new one!
\end{chapter}

\begin{chapter}{Cooler Title for the Second Chapter} As we saw in Chapter \ref{Intro}, everything can be
made to be complicated. (See, for example,  Figure \ref{fig1}.) This is usually not a good idea unless you want to lose your audience.

\begin{figure}
\centering{
\includegraphics[height=5cm, width=6cm]{templatefig1}
}
\caption{Graphics can really snaz it up!}
\label{fig1} % label of the figure has to go after the caption to be accurate!
\end{figure}

Most importantly, \textcolor{red}{\bf NEVER DIVIDE BY ZERO} unless, of course, you are wearing your protective
divide-by-zero suit (See \cite{Ab80} for the terrible consequences which might result. And this is how you cite multiple references: \cite{Ab80, BlTaWe, Bo1}. And if you wanted to, you could refer to specific pages: \cite[pages 567--569]{Bo2}).

\section{Another fascinating section}

Some text needs to go here.

\subsection{And sometimes you will need subsections...}

More text goes here.
\end{chapter}
\end{document}

### 2016-12-22 Thesis_Comp/magnitude.py

@@ -1,0 +1,11 @@
+import numpy as np
+
+class EuclideanSpace(object):
+
+    def __init__(self, data_array):
+        self.data_array = data_array
+        (self.n_points, self.dimension) = data_array.shape
+
+
+    def compute_distance_matrix(self):
+        # Computes the distance matrix for the space

### 2017-01-01 Drafts/Draft.tex
Updates

--- 2016-12-22 Drafts/Draft_12_2016.tex
@@
 \end{chapter}
-\begin{chapter}{M\"obius Inversion}
+\begin{chapter}{Introduction to M\"obius Inversion}
+\section{Initial Example}
 M\"obius inversion is a general construct.
-The most basic definition of a M\"obius function is a function $\mu$ on the positive integers which satisfies the following for all functions $f,g$ on the integers:
+The most basic definition of a M\"obius function is a function $\mu$ on the positive integers which satisfies the following for functions $f,g$ on the positive integers:
 
-\begin{align*}
-g(n) &= \sum_{d | n} f(d) \iff f(n) = \sum_{d | n} \mu\left(\frac dn\right) g(n)
-\end{align*}
+\begin{equation}\label{init_mob} %TODO: Unify numbering
+g(n) = \sum_{d | n} f(d) \iff f(n) = \sum_{d | n} \mu\left(\frac dn\right) g(n)
+\end{equation}
 
-We will formally develop this using a more general construction, and then generalize to more even more abstract structures. We start with several definitions:
+We will formally develop this using a more general construction, and then generalize to more even more abstract structures. We start with several definitions.
+\section{Posets and Incidence Algebras}
 \begin{defn}
@@
 \begin{defn}
-The \emph{incidence algebra} on a finite poset $X$ is over the set of functions from $X \times X$ to $\Rr$ which map $(a,b)$ to zero if $a \nleq b$. So the elements of the incidence algebra are 
+A poset $X$ is \emph{locally finite} if, for any $a,b \in X$, the set $\{c \in X : a \leq c \leq b\}$ is finite.
+\end{defn}
+\begin{defn}
+The \emph{incidence algebra} on a locally finite poset $X$ is over the set of functions from $X \times X$ to $\Rr$ which map $(a,b)$ to zero if $a \nleq b$.
+So the elements of the incidence algebra are
 \[\{f:X \times X \rightarrow \Rr:a \nleq b \Rightarrow f(a,b) = 0\}
@@
 Scalar multiplication and addition are defined pointwise.  Multiplication is denoted by ``*'', and is defined:
-\[(f* g)(a,b) = \sum_{a \leq c \leq b}f(a,c)g(c,b).\]
+\[(f* g)(a,b) = \sum_{a \in X}f(a,c)g(c,b) = \sum_{a \leq c \leq b}f(a,c)g(c,b).\]
 \end{defn}
-Note that the bounds on the sum are not necessary, because all other terms will go to zero anyway by the condition on elements.
-But I use them for clarity.
-Omitting the bounds, we see that this is identical to matrix multiplication.
+\begin{rmk}
+The requirement that $X$ be locally finite ensures that the above sum has a finite number of terms.
+\end{rmk}
+\begin{rmk}
+We use $\Rr$ as the codomain of the functions in the incidence algebra. But this can be generalized to other commutative rings with identity.
+\end{rmk}
+I include the version with bounds for clarity, but they make no difference, because all other terms will go to zero anyway by the condition on elements.
+Considering the sum without th bounds, we see that this is identical to matrix multiplication.
 It will be useful to formalize this:
@@
 \end{proof}
-We will refer to this unique inverse, if it exists, as $f^{-1}$. We are now ready to define the M\"obius function on partially ordered sets.
+We will refer to this unique inverse, if it exists, as $f^{-1}$.
+
+\section{Definition of M\"obius Inversion}
+We are now ready to define the M\"obius function on partially ordered sets.
 \begin{defn}\label{def_mob_pos}
@@
 \end{rmk}
-Note: Here I will add a summary of how the integer divisibility case follows from this definition.
+\section{Integers with Divisibility Ordering}
+We are now able to justify the existence of, and find, the function $\mu$ from equation \ref{init_mob}.
+It is, of course, a type of M\"obius function.
+But the form in equation \ref{init_mob} uses functions of a single variable, while our construction uses functions of two variables.
+We must do some simple conversions to make the definitions line up.
 
+Let $X$ be the poset consisting of the positive integers, using $|$, or divisibility, as the ordering relation.
+Let $\zeta$, and therefore $\mu = \zeta^{-1}$, be defined as usual in the associated incidence algebra.
+%TODO: Finish this section (include intuition/direct proof)
+\end{chapter}
 % % %
@@
 \end{defn}
+\begin{chapter}{Groups and Orbits}
+\end{chapter}
 
-We now state a definition with no justification/explanation. This will be carefully developed in the chapter on magnitude - I'm not sure how I will end up choosing to organize it.
+\begin{chapter}{Metric Space Magnitude}
+\section{Motivation: Clustering}
+The \emph{magnitude} of a metric space is a notion introduced in \cite{Lein2}. %TODO: Finish introduction
+\section{Important Definitions}
+A metric space is a space with a notion of distance between pairs of points. 
+\begin{defn}
+A \textit{metric space} $(M,d)$ is a set $M$ together with a function  $d:M \times M \rightarrow \Rr$ (the \emph{metric}), such that the following are satisfied for all $a,b,c \in M$:
+\begin{itemize}
+\item $d(a,b) \geq 0$, with equality $\iff a = b$;
+\item $d(a,b) = d(b,a)$; and
+\item $d(a,b) + d(b,c) \geq d(a,c)$.
+\end{itemize}
+We sometimes write just $M$ if the metric is unambiguous.
+\end{defn}
+A category is an algebraic structure which generalizes ``objects" and ``maps" (or ``morphisms"), with composition.
+There are several equivalent definitions, all somewhat technical, but the construct itself is quite intuitive once you get used to it.
+\begin{defn}
+A \textit{category} $C$ consists of:
+\begin{itemize}
+\item A collection $C_0$ of \emph{objects};
+\item For each $a,b \in C_0$, a collection $C(a,b)$ of \emph{morphisms from $x$ to $y$};
+\item For each $a,b,c \in C_0$, a \emph{composition operator}: A function $\circ:C(a,b) \times C(b,c) \rightarrow C(a,c)$; and
+\item For each $a \in C_0$, an \emph{identity morphism} $1_a \in C(a,a)$,
+\end{itemize}
+such that the following axioms are satisfied:
+\begin{itemize}
+\item Composition is associative: If $a,b,c,d \in C_0$ and $f\in C(a,b), g \in C(b,c), h \in C(c,d)$, then $f \circ (g \circ h) = (f \circ g) \circ h$, and
+\item Composition respects identities: If $a,b \in C_0, f \in C(a,b)$, then $1_b \circ f = f = f \circ 1_a$.
+\end{itemize}
+
+\end{defn}
+\section{Euler Characteristic of a Category}
+\begin{defn}
+Let $\sigma$ be a simplicial complex.
+Then the \emph{category generated by $\sigma$}, or $\cat(\sigma)$, is the category whose objects are the cells of $\sigma$.
+If $\gamma$ and $\omega$ are cells of $\sigma$, then $|(\gamma, \omega)| = 1$ if $\gamma \subseteq \omega$ and 0 else.
+\end{defn}
+\section{Weightings}
 \begin{defn}
@@
 \end{proof}
-
-\begin{defn}
-Let $\sigma$ be a simplicial complex.
-Then the \emph{category generated by $\sigma$}, or $\cat(\sigma)$, is the category whose objects are the cells of $\sigma$.
-If $\gamma$ and $\omega$ are cells of $\sigma$, then $|(\gamma, \omega)| = 1$ if $\gamma \subseteq \omega$ and 0 else.
-\end{defn}
 \begin{lemma}

### 2017-01-03 Drafts/Draft.tex
Updates

@@
 \end{itemize}
+\end{defn}
+This is a definition of what is usually called a category, but here we will refer to it as an \emph{ordinary} category.
+This is because it will also be useful to mention a generalization of categories, called \emph{enriched categories}.
+The idea is that we replace the sets of morphisms with objects from an ordinary category of a certain type, and adapt the definition of composition accordingly.
 
+It's not necessary to fully understand how generalized metric spaces are categories - every space we consider here will be a bona fide metric space.
+Furthermore, the definitions and constructions we explore will be easy to apply directly to metric spaces.
+I point out that this construction is a type of category to justify dealing with them together with other categories in the next section.
+We will define the Euler characteristic of a category, and we will need to apply the definition to metric spaces by way of generalized metric spaces.
+This will make much more sense if we keep in mind that generalized metric spaces are categories.
+
+The full definition of enriched categories is complicated, technical, and not necessary here.
+For a full discussion of enriched categories, see \cite{Kelly1}.
+We will instead directly define a particular enriched category object called a \emph{generalized metric space}.
+\begin{defn}
+A \emph{generalized metric space} $C$ consists of:
+\begin{itemize}
+\item A collection $M$ of points (or objects); and
+\item For each $a,b \in M$, a non-negative real number $d(a,b)$, such
+\end{itemize}
+such that, for all $a,b \in M$,
+\[C(a,a) = 0,\hspace{1cm} C(a,b) + C(b,c) \geq C(a,c).
+\]
 \end{defn}
+Note that this is essentially the same as a metric space, but without the restriction that distinct points have nonzero distance, and without the requirement of symmetry.
+Relaxing these constraints allows us to cleanly express this as an enriched category.
+In keeping with the intuitive description of enriched categories which I gave earlier, this is a category where sets of morphisms are replaced by non-negative real numbers.
+The two axioms are enforced by details in the definition of an enriched category which I swept under the rug.
+
+For those who are interested in the details, what we are doing is letting $\mathcal{V}$ be the monoidal category whose set of objects is $\Rr^{\geq 0}$, with a single morphism from $a$ to $b$ if and only if $a \leq b$, and with addition (+) as the monoid operator.
+Then a generalized metric space is a category enriched with $\mathcal{V}$.
+
 \section{Euler Characteristic of a Category}
-\begin{defn}
-Let $\sigma$ be a simplicial complex.
-Then the \emph{category generated by $\sigma$}, or $\cat(\sigma)$, is the category whose objects are the cells of $\sigma$.
-If $\gamma$ and $\omega$ are cells of $\sigma$, then $|(\gamma, \omega)| = 1$ if $\gamma \subseteq \omega$ and 0 else.
-\end{defn}
-\section{Weightings}
+\subsection{Weightings and Definition}
+We now turn to a new construction: category weightings.
+This idea is fully explored in \cite{Lein2}.
+We will immediately connect this to M\"obius inversion.
+This will lead to the initial definition of the Euler characteristic of a category, which in turn will directly lead to the definition of the magnitude of a metric space.
+
+Throughout this section, objects declared as categories are implicitly allowed to be either ordinary categories or generalized metric spaces.
+
+We are interested in a notion of how close together things are - and it will need to measure closeness rather than distance, in the sense that it will increase for objects which are closer together.
+The reason for this will become clear soon.
+We will call this binary function $\zeta$, and define it on a category $C$ as follows: For $a,b \in C_0$, if $C$ is an ordinary category, then $\zeta(a,b) = |C(a,b)|$, or the size of the set of morphisms from $a$ to $b$.
+If $C$ is a generalized metric space, then $\zeta(a,b) = e^{-C(a,b)}$.
+The definition for ordinary categories is fairly natural.
+The more morphisms there are from $a$ to $b$, the closer together they are.
+In order to make sense of the definition for generalized metric spaces, consider three objects $a,b,c$ in an ordinary category:
+
+\begin{tikzpicture}
+\node[shape=circle,draw=black, fill=black] (a){a};
+\end{tikzpicture}
+
 \begin{defn}
@@
 \label{mobius_is_weighting}
-If $\Aa$ has Mobius inversion, then $\omega_a = \sum_b \mu(a,b)$ is a weighting on $\Aa$.
+If $\Aa$ has M\"obius inversion, then $\omega_a = \sum_b \mu(a,b)$ is a weighting on $\Aa$.
 \end{lemma}
@@
 \end{proof}
+
+The following definition is due to \cite{Lein1}.
+\begin{defn}
+Let $\omega$ be a weighting on a finite category $A$. Then the \emph{Euler characteristic} of $A$, denoted (as usual) as $\chi(A)$, is defined by
+\[
+\chi(A) = \sum_{a \in A} \omega_a
+\]
+\end{defn}
+Note that even if a category admits several weightings, they all lead to the same Euler characteristic by a simple sum rearrangement argument.
+Together with \ref{mobius_is_weighting}, this implies the following:
+\begin{cor}
+If a finite category $A$ has a M\"obius inversion $\mu$, then
+\[\chi(A) = \sum_{a \subseteq A} \sum_{b \subseteq A} \mu(a, b).
+\]
+\end{cor}
+This provides the main motivation for exploring M\"obius inversion here.
+It provides a way in which we can write down weightings on many metric spaces, since the similarity matrix $\zeta$ is invertible in most cases.
+We will investigate exactly which cases when we discuss positive semidefinite matrices.
+\subsection{Simplicial Complexes}
+This definition needs some intuitive justification. We will use a new construction, the simplicial complex, to show that calling this value an Euler characteristic is reasonable.
+
+\begin{defn}
+Let $\sigma$ be a simplicial complex.
+Then the \emph{category generated by $\sigma$}, or $\cat(\sigma)$, is the category whose objects are the cells of $\sigma$.
+If $\gamma$ and $\omega$ are cells of $\sigma$, then $|(\gamma, \omega)| = 1$ if $\gamma \subseteq \omega$ and 0 else.
+\end{defn}
 \begin{lemma}
@@
 \begin{proof}
-Then:
+
 \begin{align*}
@@
 \end{proof}
-By \ref{mobius_is_weighting}, weightings are a generalization of Mo\"bius inversion. This fact motivates the following definition, due to \cite{Lein1}.
-\begin{defn}
-Let $\omega$ be a weighting on a finite category $A$. Then the \emph{Euler characteristic} of $A$, denoted (as usual) as $\chi(A)$, is defined by
-\[
-\chi(A) = \sum_{a \in A} \omega_a
-\]
-\end{defn}
-Note that even if a category admits several weightings, they all lead to the same Euler characteristic by a simple sum rearrangement argument.
-Together with \ref{mobius_is_weighting}, this implies the following:
-\begin{cor}
-If a finite category $A$ has a M\"obius inversion $\mu$, then
-\[\chi(A) = \sum_{a \subseteq A} \sum_{b \subseteq A} \mu(a, b).
-\]
-\end{cor}
-This provides the main motivation for exploring M\"obius inversion here.
-It provides a way in which we can write down weightings on many metric spaces, since the similarity matrix $\zeta$ is invertible in most cases.
-We will investigate exactly which cases when we discuss positive semidefinite matrices.
 \end{chapter}

### 2017-01-27 Drafts/Draft.tex
update

@@
 \input{commands_packages}
+\usetikzlibrary{decorations.pathreplacing,angles,quotes}
 \author{Leo Selker}
@@
 \begin{defn}
-A \emph{partially ordered set}, often called a \emph{poset}, is a set $X$ together with a relation, denoted $\leq$, such that, for all $a,b,c \in X$:
+A \emph{partially ordered set}, often called a \emph{poset}, is a set $X$ together with a binary relation $\leq$, such that, for all $a,b,c \in X$:
 \begin{itemize}
@@
 
-We also define another special function, $\zeta$ (the ``ones function''):
+We also define another special function, $\zeta$ (the ``indicator function''):
 \[
@@
 \begin{defn}\label{def_mob_pos}
-Let $X$ be a finite poset. Let $\zeta$ be the ones function defined above. Let $\mu = \zeta^{-1}$. Then $\mu$ is the \emph{M\"obius function} on $X$.
+Let $X$ be a finite poset. Let $\zeta$ be the indicator function defined above. Let $\mu = \zeta^{-1}$. Then $\mu$ is the \emph{M\"obius function} on $X$.
 \end{defn}
@@
 \begin{chapter}{Groups and Orbits} 
+We want to apply M\"obius inversion to groups. So far, the most general construct to which we have applied M\"obius inversion is the partially ordered set (poset). Given a group $G$, 
+Suppose that a group $G$ acts on a set $\Omega$. 
 \end{chapter}
@@
 The \emph{magnitude} of a metric space is a notion introduced in \cite{Lein2}. %TODO: Finish introduction
-\section{Important Definitions}
+\section{Important Definitions} \label{mag_defs}
 A metric space is a space with a notion of distance between pairs of points. 
@@
 
+We will soon be interested in a notion of how close together things are - and it will need to measure closeness rather than distance, in the sense that it will increase for objects which are closer together.
+The reason for this will become clear soon.
+We will call this binary function $\zeta$, and define it on a category $C$ as follows: For $a,b \in C_0$, if $C$ is an ordinary category, then $\zeta(a,b) = |C(a,b)|$, or the size of the set of morphisms from $a$ to $b$.
+If $C$ is a generalized metric space, then $\zeta(a,b) = e^{-C(a,b)}$.
+
+The definition for ordinary categories is fairly natural.
+The version for generalized metric spaces is less intuitive, but the definitions are surprisingly consistent.
+Consider three objects $a,b,c$ in an ordinary category.
+The numbers above the arrows indicate the number of morphisms between adjacent objects:
+
+\[
+\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
+
+\node[label = below:{a}, circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](1) at (0,0) {};
+\node[label = below:{b}, circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](2) at (3,0) {};
+\node[label = below:{c}, circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](3) at (6,0) {};
+
+\draw[-latex] (1) -- (2) node[midway, above = 3pt] {\textit{k}};
+\draw[-latex] (2) -- (3) node[midway, above = 3pt] {\textit{l}};
+
+\end{tikzpicture}\]
+Then, as a result of the composition axioms, there must be a morphism $g \circ f$ from $a$ to $c$ for each pair of morphisms $f \in C(a,b), g \in C(b,c)$.
+This means that there are $kl$ morphisms from $a$ to $c$ which are implied by the morphisms shown above.
+So $\zeta(a,c) \geq \zeta(a,b)  \zeta(b,c)$.
+
+Now, consider the same situation in a generalized metric space. We know from one of the axioms that
+\[
+C(a,c) \leq C(a,b) + C(b,c).
+\]
+The inverse exponential function is monotonically decreasing. So we simply apply it to both sides and flip the inequality to get the same result, that $\zeta(a,c) \geq \zeta(a,b) \zeta(b,c)$.
+
+There is another way of looking at essentially the same property, which might make it slightly more clear why this works out.
+The reason the addition (+) operator appears in the second axiom in the generalized metric space definition is because addition is what is called the \textit{monoidal product} in the enriched category.
+The equivalent in an ordinary category is the tensor product, $\otimes$.
+In terms of number of morphisms, $\otimes$ behaves like multiplication.
+So it makes sense that we exponentiate in the generalized metric space case.
+Adding exponents becomes multiplication.
+\section{M\"obius Inversion on a Category}
+To define M\"obius inversion on a partially ordered set, we used an "indicator function" which was - not coincidentally - notated as $\zeta$.
+We will henceforth refer to this function as $\zeta'$, reserving $\zeta$ for the function we just defined on categories.
+Recall that for $a,b$ in a poset $X$, $\zeta'(a,b)$ was defined to be 1 if $a \leq b$, and 0 otherwise.
+We would like to generalize the construction of M\"obius inversion.
+The first step is to observe the following: Given a poset $X$, we can construct an "equivalent" category by letting $C_0=X$, and adding a single morphism from elements $a,b \in C_0$ if and only if $a \leq b \in X$.
+It is easily checked that this is in fact a category, and that for each triplet in $C_0$ there is only one possible composition operator (this is why we don't bother to explicitly define them).
+
+The key fact here is that for $a,b \in C_0 = X, \zeta(a,b) = \zeta'(a,b)$. This motivates the following definition:
+\begin{defn}\label{cat_mob} %TODO: Check uniqueness
+Let $C$ be a category. Let $\zeta$ be as defined above. Then the \emph{M\"obius function} on $C$, if it exists, is a function $\mu$ which, for all $x,y \in C$, satisfies
+\[
+\sum_{z \in X} \mu(x,z)\zeta(z,y) = \delta(x,z) = \sum_{z \in X} \zeta(x,z)\mu(z,y).
+\]
+If such a $\mu$ exists, $C$ is said to \emph{have M\"obius inversion}.
+\end{defn}
 \section{Euler Characteristic of a Category}
-\subsection{Weightings and Definition}
-We now turn to a new construction: category weightings.
-This idea is fully explored in \cite{Lein2}.
+\subsection{Definition}
+We are now ready to construct central definition of this section: the Euler characteristic of a category.
+The entire construction can be found in \cite{Lein1}, \cite{Lein2}, \cite{Lein4}.
 We will immediately connect this to M\"obius inversion.
@@
 Throughout this section, objects declared as categories are implicitly allowed to be either ordinary categories or generalized metric spaces.
-
-We are interested in a notion of how close together things are - and it will need to measure closeness rather than distance, in the sense that it will increase for objects which are closer together.
-The reason for this will become clear soon.
-We will call this binary function $\zeta$, and define it on a category $C$ as follows: For $a,b \in C_0$, if $C$ is an ordinary category, then $\zeta(a,b) = |C(a,b)|$, or the size of the set of morphisms from $a$ to $b$.
-If $C$ is a generalized metric space, then $\zeta(a,b) = e^{-C(a,b)}$.
-The definition for ordinary categories is fairly natural.
-The more morphisms there are from $a$ to $b$, the closer together they are.
-In order to make sense of the definition for generalized metric spaces, consider three objects $a,b,c$ in an ordinary category:
-
-\begin{tikzpicture}
-\node[shape=circle,draw=black, fill=black] (a){a};
-\end{tikzpicture}
+The definition of $\zeta$ from section \ref{mag_defs} will be assumed.
 
@@
 \end{cor}
-This provides the main motivation for exploring M\"obius inversion here.
-It provides a way in which we can write down weightings on many metric spaces, since the similarity matrix $\zeta$ is invertible in most cases.
+This is important.
+It provides a way in which we can write down weightings on metric spaces, since the similarity matrix $\zeta$ is invertible in many cases.
 We will investigate exactly which cases when we discuss positive semidefinite matrices.
@@
 \end{proof}
+\section{Metric Space Magnitude}
+
 \end{chapter}
-\bibliographystyle{apalike}
+\bibliographystyle{abbrv}
 \bibliography{bibliography.bib}

### 2017-02-10 Drafts/Draft.tex
Presentation

@@
 \usetikzlibrary{decorations.pathreplacing,angles,quotes}
+\usepackage{mathrsfs}
+% \usepackage[euler-digits]{eulervm} %TODO: Maybe change this
 \author{Leo Selker}
@@
 \DeclareMathOperator{\cat}{cat}
+\DeclareMathOperator{\ps}{\mathscr{P}}
 \begin{document}
@@
 Scalar multiplication and addition are defined pointwise.  Multiplication is denoted by ``*'', and is defined:
-\[(f* g)(a,b) = \sum_{a \in X}f(a,c)g(c,b) = \sum_{a \leq c \leq b}f(a,c)g(c,b).\]
+\[(f* g)(a,b) = \sum_{a \in X}f(a,c)g(c,b) \left( = \sum_{a \leq c \leq b}f(a,c)g(c,b)\right).\]
 \end{defn}
@@
 I include the version with bounds for clarity, but they make no difference, because all other terms will go to zero anyway by the condition on elements.
-Considering the sum without th bounds, we see that this is identical to matrix multiplication.
+Considering the sum without the bounds, we see that this is identical to matrix multiplication.
 It will be useful to formalize this:
@@
 \item
-The result follows directly from the definition of matrix multiplication.
-Let $i,j\leq n$ be given.
-Remember that we can omit the bounds from the sum in the definition of incidence algebra multiplication.
-Then:
+The result follows directly from the definition of matrix multiplication. Let $i,j\leq n$ be given. Then:
 \begin{align*}
@@
 \begin{cor}\label{cor_inv}
-Let $f,g$ be elements of the incidence algebra on $X$. Then:
+Let $f,g, h$ be elements of the incidence algebra on $X$. Then:
 \begin{enumerate}[a)]
+\item $(f*g)*h = f*(g*h)$, i.e. multiplication is associative
 \item $f*g = \delta \Rightarrow g*f = \delta$
@@
 \begin{proof}
-Part a) is true of all square matrices.
-Part b) is true of all upper triangular matrices, since the determinant of such matrices is the product of the main diagonal elements.
-We use \ref{mat_eq} to transfer the results to $f$ and $g$.
+Part a) is true of matrix multiplication in general.
+Part b) is true of all square matrices.
+Part c) is true of all upper triangular matrices, since the determinant of such matrices is the product of the main diagonal elements.
+We use \ref{mat_eq} to transfer all three results to $f$ and $g$.
 \end{proof}
@@
 \begin{rmk}
+Definition \ref{def_mob_pos} is a statement about incidence algebra multiplication, so is really about matrix multiplication.
 Another statement of the definition is that $\mu$ is the unique function such that, for all $x,y \in X$,
@@
 \end{rmk}
+
+This is the M\"obius function. To complete the definition of M\"obius inversion, we turn to the standard use of this function. 
+\begin{thm}[M\"obius Inversion]\label{mob_inv}
+Let $X$ be a finite poset. Let $f, g: X \times X \rightarrow \Rr$ be elements of the incidence algebra on $X$. Let $\zeta, \mu$ be defined as usual. Then:
+\begin{align*}
+g = f \zeta &\iff f = g \mu;\\
+g = \zeta f &\iff f = \mu g.
+\end{align*}
+Equivalently,
+\begin{align*}
+\forall x,y \in X, g(x,y) = \sum_{z \in X}f(x,z)\zeta(z,y) &\iff \forall x,y \in X, f(x,y) = \sum_{z \in X}g(x,z)\mu(z,y);\\
+\forall x,y \in X, g(x,y) = \sum_{z \in X}\zeta(x,z)f(z,y) &\iff \forall x,y \in X, f(x,y) = \sum_{z \in X}\mu(x,z)g(z,y).
+\end{align*}
+\begin{proof}
+All these results follow from the definition of $\mu$ and from facts about matrix/incidence algebra multiplication.
+\end{proof}
+\end{thm}
+This result seems quite straightforward based on how we defined $\zeta$ and $\mu$.
+However, it turns out to be extremely powerful.
+We will see many cases where values of $f$ from the theorem are readily attainable, but values of $g$ are what we really want.
+The M\"obius function allows us to obtain those values.
+This procedure - the use of the M\"obius function to reverse the process of summing terms as in theorem \ref{mob_inv} - is what is referred to as M\"obius inversion.
+
+With that in mind, we can also consider M\"obius inversion on functions in one variable (instead of two) on a poset.
+\begin{thm}
+Let $f,g:X \rightarrow \Rr$ be given. Let $\zeta, \mu$ be defined as usual. Then:
+\begin{align*}
+f = g \zeta & \iff g = f \mu;\\
+f = \zeta g & \iff g = \mu f.
+\end{align*}
+Equivalently,
+\begin{align*}
+\forall x \in X, f(x) = \sum_{y \in X} g(y)\zeta(y,x) &\iff \forall x \in X, g(x) = \sum_{y \in X} f(y)\mu(y,x);\\
+\forall x \in X, f(x) = \sum_{y \in X} \zeta(x,y)g(y) &\iff \forall x \in X, g(x) = \sum_{y \in X} \mu(x,y)g(y).
+\end{align*}
+\end{thm}
+We now have two equivalent definitions of the M\"obius function, one using matrices (or linear operators) and vectors, and one directly considering elements and sums.
+We will continue to move back and forth between these two approaches throughout this investigation.
+This is because although the two definitions are completely equivalent, they each have advantages.
+Working with sums and elements helps us see the details of what is going on, and reminds us of the structure of our poset.
+It is also often the perspective from which motivating problems arise.
+On the other hand, using matrices and vectors greatly simplifies the equations we have to deal with, makes the manipulations themselves easier, and allows us to keep the bigger picture - the idea of inversion - in mind more easily.
+
 \section{Integers with Divisibility Ordering}
@@
 \end{chapter}
-% % %
-\begin{defn}
-A category $\Aa$ has \emph{Mobius Inversion} $\mu$ if $\mu$ satisfies
-\[
-\sum_b \mu(a,b)\zeta(b,c) = \delta(a,c) = \sum_b \zeta(a,b)\mu(b,c),
-\]
-with each equality implying the other by finite dimensionality (this is the same argument as showing that one-sided square matrix inverses are two-sided).
-\end{defn}
+
 \begin{chapter}{Groups and Orbits} 
@@
 \]
-If such a $\mu$ exists, $C$ is said to \emph{have M\"obius inversion}.
+If such a $\mu$ exists, $C$ is said to \emph{have M\"obius inversion}. %TODO: Connect back, use matrix version
 \end{defn}
@@
 \section{Metric Space Magnitude}
+\end{chapter}
+\begin{chapter}{Inclusion-Exclusion}
+We start by introducing the desired end result, the \emph{inclusion-exclusion principle}:
+\begin{thm}[Inclusion-Exclusion]\label{iep}
+Let $S$ be a set. Let $A_i \subseteq S$ for each $i \in I$ where $I$ is finite. Let $K \subseteq I$ be given. Then
+\[
+\bigcup_{i \in K}A_i = \sum_{J \subseteq K}(-1)^{|J|}\bigcap_{i \in J}A_j
+.\]
+\end{thm}
+There are many proofs of this well-known fact.
+We will show it using M\"obius inversion.
+This means we will need a poset.
+Throughout this section, we will have the following setup: Let $S$ be a finite set.
+Let $I$ be a finite index set, and for all $i \in I$, let $A_i \subseteq S$.
+We will be manipulating functions on subsets of $I$, so this will be our poset.
 
+% % % OLD VERSION
+\iffalse
+\begin{definition}
+Let $S$ be a set. Then the \emph{power set} of $S$, denoted $\ps(S)$, is the set of subsets of $S$, $\{A \subseteq S\}$.
+\end{definition}
+We will be using the poset whose elements are from $\ps(S)$, where $A \leq B$ if $A \supseteq B$.
+However, for clarity, we won't use the $\leq$ notation for this poset - we will use inclusion notation directly, and define $\zeta$ and $\mu$ in terms of it.
+
+Recall that $\zeta$ is the indicator function on a poset. So we define $\zeta: \ps(S) \times \ps(S) \rightarrow \{0,1\}$:
+\[
+\zeta(A,B) = 
+\]
+\fi
 \end{chapter}
+
 \bibliographystyle{abbrv}

### 2017-03-21 Drafts/Draft.tex
before removing incidence algebras

@@
 \usepackage{mathrsfs}
-% \usepackage[euler-digits]{eulervm} %TODO: Maybe change this
+\usepackage[euler-digits]{eulervm} %TODO: Maybe change this
 \author{Leo Selker}
 \advisor{Vin de Silva}
-\title{The Magnitude of a Metric Space: An Approach to Clustering}
+\title{M\"obius Inversion: Construction and Applications}
 
@@
 \DeclareMathOperator{\ps}{\mathscr{P}}
+\DeclareMathOperator{\sub}{Sub}
+\DeclareMathOperator{\stab}{Stab}
+\DeclareMathOperator{\orb}{Orb}
+\DeclareMathOperator{\fixx}{fix}
+\DeclareMathOperator{\obj}{ob}
 \begin{document}
@@
 
-\begin{abstract}Clustering is an important application of topology.
-Here we explore a method of counting clusters at various scales.
-We build the necessary framework using the idea of a M\"obius inversion, and then we define the magnitude of a metric space\cite{Lein2}.
-We investigate behaviors of positive definite metric spaces, as well as how the magnitude acts under the product of spaces.
+\begin{abstract}M\"obius inversion is a general approach to reversing certain kinds of sums.
+In many situations, we know that a value we have access to is equal to the sum over a poset interval of values we want.
+M\"obius inversion is a tool which allows us to access those summed values.
+Here, we first develop the theory of M\"obius inversion on arbitrary posets.
+Then, we investigate its application in various counting examples, including the inclusion-exclusion principle and counting orbits of group actions.
+Finally, we explore an application of M\"obius inversion to data clustering.
 \end{abstract}
@@
 \pagenumbering{arabic}
-\begin{chapter}{Outline}
-\section{Introduction}
-We will be investigating the magnitude of metric spaces along with related/foundational ideas.
-We investigate M\"obius inversion, a way of calculating the magnitude of a metric space.
-We motivate and define magnitude of a metric space using the Euler characteristic of a category.
-We investigate positive definite metric spaces and tensor products.
-It's still slightly early to say what our "goal" is.
-\section{M\"obius Inversion}
-We will start with Mobius inversion on the positive integers, generalize to posets, and again generalize to categories\cite{Lein1}. At each step we will justify the way we choose to generalize.
-
-Here we may also investigate the P\'olya Counting Formula/Burnside's Lemma. We're just starting on that, so we'll see where it goes.
-\section{Euler Characteristic of a Category}
-We define the Euler characteristic of a finite category as the sum of all values of its Mobius inversion\cite{Lein1}.
-We will justify this by showing that simplicial complexes behave well under this definition, and it coincides with the usual one in that case.
-We'll also investigate working the other way: Taking a poset and turning it into a simplicial complex of chains.
-Hopefully this will lead somewhere too.
-\section{Magnitude, Properties, and Examples}
-We will define the "induced category" of a metric space, and use it as a motivation for the definition of the \textbf{magnitude} of a finite metric space\cite{Lein2} (the magnitude is the Euler characteristic of the induces category).
-This definition captures the "effective number of points" in the space in some sense.
-As we scale the space smaller, the magnitude approaches 1, and as we scale it larger it approaches the number of points in the space.
-In this sense, we have a "backwards" scale factor, where to zoom in we increase the factor.
-In some ways magnitudes over scales approximate hierarchical clustering results.
-In fact, the magnitude of the tensor product of two finite spaces is the product of the spaces' magnitudes (we proved this, but it is likely known).
-We can also say more in the case of positive definite metric spaces\cite{Meck1}.
-We will investigate approximation theorems for "almost-product" spaces, and other situations which are well behaved.
-
-Here we will also probably discuss results from code I am writing.
-\section{Magnitude and Persistence}
-Hierarchical clustering is a way of expressing structure at a variety of levels within data.
-We can keep track of that structure using a \textit{persistent set}\cite{Carl1}.
-We can define clusters however we want using some scale factor.
-Generally we use single linkage, i.e.
-we partition under the equivalence relation define by whether there's a path between points involving no jumps of too long a distance.
-
-We will attempt to connect the magnitude of a space with its persistent set. Both offer scaled counts of the number of clusters in some sense - we have some basic connections but hope to find more.
-\end{chapter}
-\begin{chapter}{Introduction to M\"obius Inversion}
+\begin{chapter}{Introduction to M\"obius Inversion}\label{chap_intro}
 \section{Initial Example}
@@
 \begin{equation}\label{init_mob} %TODO: Unify numbering
-g(n) = \sum_{d | n} f(d) \iff f(n) = \sum_{d | n} \mu\left(\frac dn\right) g(n)
+f(n) = \sum_{d | n} g(d) \iff g(n) = \sum_{d | n}  f(n)\mu\left(\frac dn\right)
 \end{equation}
 
-We will formally develop this using a more general construction, and then generalize to more even more abstract structures. We start with several definitions.
+Our first goal is to prove the existence of - and find - this function $\mu$.
+We will do this using a more general construction, and then generalize to more even more abstract structures.
+We start with several definitions.
 \section{Posets and Incidence Algebras}
@@
 \begin{defn}
-A poset $X$ is \emph{locally finite} if, for any $a,b \in X$, the set $\{c \in X : a \leq c \leq b\}$ is finite.
+A poset $X$ is \emph{lower finite} if, for any $a \in x$, the set $\{ c \in X: c \leq a\}$ is finite.
 \end{defn}
+\begin{rmk}
+A poset which is lower finite is also \emph{locally finite}: For any $a,b \in X$, the set $\{c \in X : a \leq c \leq b\}$ is finite.  
+\end{rmk}
+For many of the following definitions and theorems, it is enough for the poset to be locally finite. But we will assume our posets are lower finite, a stronger condition, to make certain steps easier.
 \begin{defn}
-The \emph{incidence algebra} on a locally finite poset $X$ is over the set of functions from $X \times X$ to $\Rr$ which map $(a,b)$ to zero if $a \nleq b$.
-So the elements of the incidence algebra are
+The \emph{incidence algebra} on a lower finite poset $X$ is over the set of functions from $X \times X$ to $\Rr$ which map $(a,b)$ to zero if $a \nleq b$. So the elements of the incidence algebra are 
 \[\{f:X \times X \rightarrow \Rr:a \nleq b \Rightarrow f(a,b) = 0\}
@@
 \begin{rmk}
-The requirement that $X$ be locally finite ensures that the above sum has a finite number of terms.
+The requirement that $X$ be lower finite ensures that the above sum has a finite number of nonzero terms, so is finite-valued.
 \end{rmk}
@@
 \begin{lemma}\label{mat_eq}
-Let $X$ be a finite poset, with $|X|=n$.
-Choose a total ordering on $X$ such that the partial order is respected - in other words, label the elements of $X$ from $x_1$ to $x_n$, such that if $x_i \leq x_j, i \leq j$.
+Let $X$ be a lower finite poset, with $|X|=n$.
+Choose a total ordering on $X$ such that the partial order is respected - in other words, label the elements with integers such that if $x_i \leq x_j, i \leq j$.
 Let $f,g$ be elements of the incidence algebra on $X$.
-Let $F$ be the $n\times n$ square matrix where $F_{ij}=f(x_i, x_j)$.
+Let $F$ be the (possibly infinite) square matrix where $F_{ij}=f(x_i, x_j)$.
 Define $G$ likewise.
@@
 \begin{cor}\label{cor_inv}
-Let $f,g, h$ be elements of the incidence algebra on $X$. Then:
+Let $X$ be a lower finite poset, and let $f,g, h$ be elements of the incidence algebra on $X$. Then:
 \begin{enumerate}[a)]
@@
 \begin{defn}\label{def_mob_pos}
-Let $X$ be a finite poset. Let $\zeta$ be the indicator function defined above. Let $\mu = \zeta^{-1}$. Then $\mu$ is the \emph{M\"obius function} on $X$.
+Let $X$ be a lower finite poset. Let $\zeta$ be the indicator function defined above. Let $\mu = \zeta^{-1}$. Then $\mu$ is the \emph{M\"obius function} on $X$.
 \end{defn}
@@
 \end{rmk}
-\begin{rmk}
+\begin{rmk}\label{sum_form}
 Definition \ref{def_mob_pos} is a statement about incidence algebra multiplication, so is really about matrix multiplication.
@@
 \begin{thm}[M\"obius Inversion]\label{mob_inv}
-Let $X$ be a finite poset. Let $f, g: X \times X \rightarrow \Rr$ be elements of the incidence algebra on $X$. Let $\zeta, \mu$ be defined as usual. Then:
+Let $X$ be a lower finite poset. Let $f, g: X \times X \rightarrow \Rr$ be elements of the incidence algebra on $X$. Let $\zeta, \mu$ be defined as usual. Then:
 \begin{align*}
-g = f \zeta &\iff f = g \mu;\\
-g = \zeta f &\iff f = \mu g.
+f = g * \zeta &\iff g = f *\mu;\\
+f = \zeta * g &\iff g = \mu * f.
 \end{align*}
@@
 \begin{align*}
-\forall x,y \in X, g(x,y) = \sum_{z \in X}f(x,z)\zeta(z,y) &\iff \forall x,y \in X, f(x,y) = \sum_{z \in X}g(x,z)\mu(z,y);\\
-\forall x,y \in X, g(x,y) = \sum_{z \in X}\zeta(x,z)f(z,y) &\iff \forall x,y \in X, f(x,y) = \sum_{z \in X}\mu(x,z)g(z,y).
+\forall x,y \in X, f(x,y) = \sum_{z \in X}g(x,z)\zeta(z,y) &\iff \forall x,y \in X, g(x,y) = \sum_{z \in X}f(x,z)\mu(z,y);\\
+\forall x,y \in X, f(x,y) = \sum_{z \in X}\zeta(x,z)g(z,y) &\iff \forall x,y \in X, g(x,y) = \sum_{z \in X}\mu(x,z)f(z,y).
 \end{align*}
@@
 With that in mind, we can also consider M\"obius inversion on functions in one variable (instead of two) on a poset.
-\begin{thm}
-Let $f,g:X \rightarrow \Rr$ be given. Let $\zeta, \mu$ be defined as usual. Then:
+\begin{thm}\label{1var_mob_inv}
+Let $X$ be a lower finite poset. Let $f,g:X \rightarrow \Rr$ be given. Let $\zeta, \mu$ be defined as usual. Then:
 \begin{align*}
-f = g \zeta & \iff g = f \mu;\\
-f = \zeta g & \iff g = \mu f.
+f = g *\zeta & \iff g = f *\mu;\\
+f = \zeta *g & \iff g = \mu *f.
 \end{align*}
@@
 \end{thm}
+\begin{proof}
+If we fix one argument of functions on two variables, this follows from \ref{mob_inv}.
+\end{proof}
 We now have two equivalent definitions of the M\"obius function, one using matrices (or linear operators) and vectors, and one directly considering elements and sums.
@@
 \section{Integers with Divisibility Ordering}
-We are now able to justify the existence of, and find, the function $\mu$ from equation \ref{init_mob}.
-It is, of course, a type of M\"obius function.
-But the form in equation \ref{init_mob} uses functions of a single variable, while our construction uses functions of two variables.
-We must do some simple conversions to make the definitions line up.
+We are now able to justify the existence of, and find, the function $\mu$ from equation \ref{init_mob}, with very little work.
 
-Let $X$ be the poset consisting of the positive integers, using $|$, or divisibility, as the ordering relation.
-Let $\zeta$, and therefore $\mu = \zeta^{-1}$, be defined as usual in the associated incidence algebra.
-%TODO: Finish this section (include intuition/direct proof)
+We will consider the set $\Nn$ as a poset ordered by divisibility.
+For our purposes, $0 \notin \Nn$.
+Note that this poset is lower finite: For any number $n$, the set $\{q \in \Nn: q|n\} \subseteq \{q \in \Nn: q \leq n\}$, and the latter set contains $n$ elements, which is finite.
+This means we are able to use M\"obius inversion.
+
+We go through the usual steps of M\"obius inversion and apply \ref{mob_inv}. We will use functions and sums rather than matrices and vectors to make it easier to see what is going on.
+\begin{itemize}
+\item Let $\zeta: \Nn \times \Nn \rightarrow \Nn$ be defined as follows. Note that $m|n$ means that $m$ divides $n$ without remainder.
+\[
+\zeta(m,n) = \begin{cases}1 & m|n \\ 0 & else \end{cases}
+\]
+\item Let $\mu = \zeta^{-1}$ (inverse in the incidence algebra)
+\end{itemize}
+Then \ref{1var_mob_inv} gives us:
+\[
+g(n) = \sum_{d | n} g(d) \iff g(n) = \sum_{d | n}  f(d)\mu(d,n)
+\]
+This is almost what we want, but not quite.
+Here $\mu$ is a function in two variables, while in \ref{init_mob} it is a function in a single variable.
+It turns out that values of $\mu(d,n)$ will only depend on $\frac nd$, which will gives us the desired form.
+To see that, we start by writing down a recursive form which works for any M\"obius function.
+
+\begin{lemma}\label{recurse}
+Let $X$ be a lower finite partially ordered set, and let $\zeta, \mu$ be defined as usual. Then for all $a, b \in X$,
+\[
+\mu(a,b) = 
+\begin{cases}
+0 & a \nleq b\\
+\delta(a,b)-\sum_{a \leq c < b}\mu(a,c) & else.
+\end{cases}
+\]
+\end{lemma}
+\begin{rmk}
+Note that the piecewise form is actually not necessary, because if $a \nleq b$ then the sum will be empty. So it is correct - albeit less clear- to just write
+\[
+\mu(a,b) = \delta(a,b)-\sum_{a \leq c < b}\mu(a,c).
+\]
+\end{rmk}
+\begin{proof}
+We fix $a,b$, and then rearrange terms starting from \ref{sum_form}:
+\begin{align*}
+\sum_{c \in X}\mu(a,c) \zeta(c,b) &= \delta(a,b)\\
+\sum_{a \leq c < b} \mu(a,c) + \mu(a,b) &= \delta(a,b)\\
+\mu(a,b) &= \delta(a,b) - \sum_{a \leq c < b} \mu(a,c) 
+\end{align*}
+\end{proof}
+We are now ready to write down $\mu$ in the context of the divisibility lattice poset.
+
+\begin{lemma}\label{nfact}
+Let $\zeta, \mu$ be defined as usual on $\Nn$ ordered by divisibility. Let $m,n \in \Nn$ be given.  Then:
+\[
+\mu(m,n) =
+\begin{cases}
+0 & m\nmid n\\
+0 & \exists p \in \Nn: p^2|(\frac nm )\\
+(-1)^{\#\{p \text{ prime}: p|\frac nm\}} & else
+\end{cases}
+\]
+\end{lemma}
+This lemma gives us what we need - a way of writing values of $\mu$ in terms of a single variable. We will prove it by induction on the number of prime factors of $\frac nm$.
+\begin{proof}
+If $n \nmid m$, then by \ref{recurse}, $\mu(m,n) = 0$. This is the first case.
+
+If $n = m$, then $\frac nm=1$ has zero prime factors. In that case, again by \ref{recurse}, $\mu(n,m) = 1$. This will be our base case for the second and third branches.
+
+Suppose that if $m|n$, and $\frac nm$ has $k$ prime factors (with multiplicity), then \ref{nfact} holds for $m$ and $n$.
+Suppose that $m_0|n_0$ and $\frac nm$ has $k+1$ prime factors.
+We now consider three cases.
+\begin{description}
+\item[Case 1:] Suppose that $\frac nm$ has no squared prime factors. 
+\end{description}
+\end{proof}
+
 \end{chapter}
@@
 \begin{chapter}{Groups and Orbits} 
-We want to apply M\"obius inversion to groups. So far, the most general construct to which we have applied M\"obius inversion is the partially ordered set (poset). Given a group $G$, 
-Suppose that a group $G$ acts on a set $\Omega$. 
+\section{Background}
+NOTE: Define groups, actions, orbits, subgroups, etc. (do I need to?)
+
+I will use $G(x)$ to denote $x$'s orbit under $G$, and $\orb(\Omega, G)$ to denote the set of orbits in $\Omega$ under $G$'s action on it. 
+\section{M\"obius Inversion on Poset of Subgroups}
+We want to apply M\"obius inversion to finite groups. This means we will need a poset. We will use the \emph{poset of subgroups} (or \emph{lattice of subgroups}):
+\begin{defn}
+Let $G$ be a finite group.
+Then let the \textit{poset of subgroups} of $G$, or $\sub(G)$, be the poset consisting of subgroups of $G$ \emph{reverse} ordered by inclusion.
+In other words, we say that $A \leq B$ if $A \supseteq B$.
+\end{defn}
+\begin{rmk}
+Because $G$ is finite, $\sub(G)$ is finite (so lower finite).
+\end{rmk}
+\begin{rmk}
+We are ordering the poset this way for reasons that will soon become clear.
+But to reduce confusion, we will continue to use inclusion notation to define $\zeta$, and so $\mu$, rather than using $\leq$.
+Also note that I will be using $\subseteq$ rather than $\leq$ to denote subgroups, also to reduce confusion with the poset relation.
+\end{rmk}
+This puts us in the position to apply M\"obius inversion. We will use the form of M\"obius inversion with matrices and vectors. So throughout this chapter:
+\begin{itemize}
+\item Given a group $G$, assume a total ordering of $\sub(G)$ which respects the partial ordering.
+Let $\zeta$ also denote the square matrix of size $|\sub(G)|$, with rows and columns labeled with elements of $\sub(G)$, such that
+\[
+\zeta_{A,B} = \begin{cases}
+1 & A \supseteq B\\
+0 & else
+\end{cases}
+\]
+\item Let $\mu = \zeta^{-1}$, which exists by \ref{cor_inv}.
+\end{itemize}
+Now, \ref{1var_mob_inv} tells us that, for any row vectors $f,g$ of length $|\sub{G}|$, 
+\[
+f = g\zeta \iff g = f\mu.
+\]
+\section{Counting Orbits}
+Throughout this section, let $G$ be a finite group acting on a set $\Omega$.
+
+We start by defining some vectors, each with entries corresponding with subgroups of $G$, which we will be using. Let:
+\begin{align*}
+f_A &= \#\{x \in \Sigma: \stab(x) \supseteq A\} = |\fix(A)|\\
+g_A &= \#\{x \in \Sigma: \stab(x) = A\}
+\sigma_A &= |A|
+\end{align*}
+
+What now?
+The goal is to count the orbits in $\Omega$ under the action by $G$ - in other words, to find $|\orb(\Omega, G)|$.
+We will start with the assumption that we are able to find $f$ and $\sigma$, which is true if we know the structure of $\sub(G)$ and know the group action.
+Then there are two steps we will follow:
+\begin{description}
+\item[Step 1:] Determine how to use $g$ and $\sigma$ to find $|\orb(\Omega, G)|$; and
+\item[Step 2:] Find $g$ from $g$.
+\end{description}
+
+Suppose we are handed $g$. In order to see how to find $|\orb(\Omega, G)|$, we recall a basic fact from group theory, which holds for any $x \in \Omega$:
+\begin{fact}
+\[|G| = |G(x)||\stab(x, G)|\]
+\end{fact}
+Because $G$ is finite, this implies that \[|G(x)| = \frac{|G|}{|\stab(x, G)|}.\]
+
+Starting from a trivial fact, we have:
+\begin{align*}
+|\orb(\Omega, G)| &= \sum_{O \in \orb(\Omega, G)}1\\
+&= \sum_{O \in \orb(\Omega, G)}\left(\sum_{x \in O}\frac{1}{|O|}\right)\\
+&= \sum_{x \in \Omega}\frac{1}{|G(x)|}
+\end{align*}
+
+Substituting, we now have the relationship:
+\[
+|\orb(\Omega, G)| = \frac{1}{|G|}\sum_{x \in \Omega}|\stab(x, G)|
+\]
+Each element of $\Omega$ has exactly one stabilizer in $G$. This means that we can partition the above sum as follows:
+\[
+|\orb(\Omega, G)| = \frac{1}{|G|}\sum_{A \in \sub(G)}\left(\sum_{x \in \Omega: \stab(x) = A}|A|\right)
+\]
+Using the definitions of $g$ and $\sigma$, we can rewrite to get the relationship we need:
+\begin{align*}
+|\orb(\Omega, G)| &= \frac{1}{|G|}\sum_{A \in \sub(G)}g_A|A|\\
+&= g \cdot \sigma
+\end{align*}
+
+On to Step 2.
+It is clear that $f_A = \sum_{B \supseteq A} g_A$.
+Another way of putting that is that $f = g\zeta$.
+As usual, this implies that $g = f\mu$.
+So M\"obius inversion makes this step trivial.
+Putting it all together:
+
+\[
+|\orb(\Omega, G)| = f\mu \cdot \sigma
+\]
+\section{Burnside's Lemma}
+A more familiar way of counting the orbits of a group is the following:
+\begin{thm}[Burnside's Lemma]\label{burnside}
+Let $G$ be a finite group acting on a finite set $\Omega$. Then:
+\[
+|\orb(\Omega, G) = \frac{1}{G}\sum_{g \in G}\fixx(g)
+\]
+\end{thm}
+
 \end{chapter}
 
+\begin{chapter}{Inclusion-Exclusion}
+\section{Introduction}
+We start by introducing the desired end result, the \emph{inclusion-exclusion principle}:
+\begin{thm}[Inclusion-Exclusion]\label{iep}
+Let $S$ be a set. Let $A_i \subseteq S$ for each $i \in I$ where $I$ is finite. Let $K \subseteq I$ be given. Then
+\[
+\bigcup_{i \in K}A_i = \sum_{J \subseteq K}(-1)^{|J|}\bigcap_{i \in J}A_j
+.\]
+\end{thm}
+\section{Proof using Mobius Inversion}
+There are many proofs of this well-known fact.
+We will show it using M\"obius inversion.
+This means we will need a poset.
+Throughout this section, we will have the following setup: Let $S$ be a finite set.
+Let $I$ be a finite index set, and for all $i \in I$, let $A_i \subseteq S$.
+We will be manipulating functions on subsets of $I$, so this will be our poset.
+\section{Generalizations}
+%TODO: Connect with integer divisibility
+
+\end{chapter}
 \begin{chapter}{Metric Space Magnitude}
@@
 The idea is that we replace the sets of morphisms with objects from an ordinary category of a certain type, and adapt the definition of composition accordingly.
+We will be using a particular kind of enriched category, called a \textit{generalized metric space}.
 
@@
 
-There is another way of looking at essentially the same property, which might make it slightly more clear why this works out.
+There is another way of looking at essentially the same property.
 The reason the addition (+) operator appears in the second axiom in the generalized metric space definition is because addition is what is called the \textit{monoidal product} in the enriched category.
@@
 In terms of number of morphisms, $\otimes$ behaves like multiplication.
-So it makes sense that we exponentiate in the generalized metric space case.
-Adding exponents becomes multiplication.
+We want a fact about addition to give us a fact about multiplication.
+Exponentiating is the most natural way to translate multiplication into addition, so we can apply the axiom.
 \section{M\"obius Inversion on a Category}
@@
 \subsection{Definition}
-We are now ready to construct central definition of this section: the Euler characteristic of a category.
-The entire construction can be found in \cite{Lein1}, \cite{Lein2}, \cite{Lein4}.
-We will immediately connect this to M\"obius inversion.
-This will lead to the initial definition of the Euler characteristic of a category, which in turn will directly lead to the definition of the magnitude of a metric space.
+We are now ready to construct central definition of this section: the Euler characteristic of a category. The entire construction can be found in \cite{Lein1, Lein2, Lein4}.
 
@@
 \begin{defn}
-A \emph{weighting} on a category $\Aa$ is a function $w_a$ on $\ob(\Aa)$ such that for all $a \in \Aa$,
+A \emph{weighting} on a category $\Aa$ is a function $w_a$ on $\obj(\Aa)$ such that for all $a \in \Aa$,
 \[
@@
 \end{defn}
+
 \begin{lemma}
@@
 
+This is important.
+It provides a way in which we can write down weightings on metric spaces, since the similarity matrix $\zeta$ is invertible in many cases.
+We will investigate exactly which cases when we discuss positive semidefinite matrices.
+
 The following definition is due to \cite{Lein1}.
 \begin{defn}
-Let $\omega$ be a weighting on a finite category $A$. Then the \emph{Euler characteristic} of $A$, denoted (as usual) as $\chi(A)$, is defined by
+Let $\omega$ be a weighting on a finite category $A$. Then the \emph{Euler characteristic} of $A$, denoted by $\chi(A)$, is defined by
 \[
@@
 \end{cor}
-This is important.
-It provides a way in which we can write down weightings on metric spaces, since the similarity matrix $\zeta$ is invertible in many cases.
-We will investigate exactly which cases when we discuss positive semidefinite matrices.
+
 \subsection{Simplicial Complexes}
-This definition needs some intuitive justification. We will use a new construction, the simplicial complex, to show that calling this value an Euler characteristic is reasonable.
+Calling a new construction an Euler characteristic needs some intuitive justification.
+We will a structure called a \textit{simplicial complex} to show that calling this value an Euler characteristic is reasonable.
+
+%TODO: Define simplicial complex
 
@@
 \end{proof}
+This implies the comforting fact that $\chi(\cat(\sigma)) = \chi(\sigma)$.
 \section{Metric Space Magnitude}
-\end{chapter}
-\begin{chapter}{Inclusion-Exclusion}
-We start by introducing the desired end result, the \emph{inclusion-exclusion principle}:
-\begin{thm}[Inclusion-Exclusion]\label{iep}
-Let $S$ be a set. Let $A_i \subseteq S$ for each $i \in I$ where $I$ is finite. Let $K \subseteq I$ be given. Then
-\[
-\bigcup_{i \in K}A_i = \sum_{J \subseteq K}(-1)^{|J|}\bigcap_{i \in J}A_j
-.\]
-\end{thm}
-There are many proofs of this well-known fact.
-We will show it using M\"obius inversion.
-This means we will need a poset.
-Throughout this section, we will have the following setup: Let $S$ be a finite set.
-Let $I$ be a finite index set, and for all $i \in I$, let $A_i \subseteq S$.
-We will be manipulating functions on subsets of $I$, so this will be our poset.
-
-% % % OLD VERSION
-\iffalse
-\begin{definition}
-Let $S$ be a set. Then the \emph{power set} of $S$, denoted $\ps(S)$, is the set of subsets of $S$, $\{A \subseteq S\}$.
-\end{definition}
-We will be using the poset whose elements are from $\ps(S)$, where $A \leq B$ if $A \supseteq B$.
-However, for clarity, we won't use the $\leq$ notation for this poset - we will use inclusion notation directly, and define $\zeta$ and $\mu$ in terms of it.
-
-Recall that $\zeta$ is the indicator function on a poset. So we define $\zeta: \ps(S) \times \ps(S) \rightarrow \{0,1\}$:
-\[
-\zeta(A,B) = 
-\]
-\fi
+\subsection{Motivation: Hierarchical Clustering}
+\subsection{Idea and Definition}
+\subsection{Product Spaces}
+\subsection{Examples}
 \end{chapter}

### 2017-03-21 Thesis_Comp/rooks.py

@@ -1,0 +1,58 @@
+#!/usr/bin/env python
+from __future__ import division
+import math
+import numpy as np
+"""
+Generate the min(p,q) x min(p,q) matrix to get g_k in terms of b_k
+"""
+
+def chars(m,n):
+    c = [[round(char(i,j)) for i in range(1,m)] for j in range(1,n)]
+    return np.round(np.array(c))
+
+
+#TODO: Support floats/complex numbers 
+def char(p,q):
+    A = np.abs(generate(p,q))
+    B = np.linalg.inv(A)
+    return np.round(np.sum(B),decimals=0)
+
+def generate(p,q):
+    # Packages the coefficients into matrix
+    n = min(p,q)
+
+    l = [
+        [coef(p,q,k,i) for i in range(n+1)]
+        for k in range(n+1)]
+
+    return np.array(l)
+
+def coef(p,q,k,i):
+    # Returns the k,i entry in the matrix for a pxq board
+    ordered = ((-1)**i * ch(k,i) * math.factorial(i) 
+               * falling(p-i, k-i) * falling(q-i, k-i))
+
+    return ordered // math.factorial(k)
+                
+
+def coef_(p,q,k,i):
+    # Returns the k,i entry in the matrix for a pxq board
+    ordered = ((-1)**(i+k) * ch(k,i) * math.factorial(i) 
+               * falling(p-i, k-i) * falling(q-i, k-i))
+
+    return ordered // math.factorial(k)
+                
+
+def ch(a,b):
+    # Choose
+    if a < b: return 0
+    else: return math.factorial(a) // (math.factorial(b)*math.factorial(a-b))
+
+def falling(a,b):
+    # Falling factorial
+    if a < b: return 0
+    total = 1
+    offset = a - b + 1
+    for i in range(b):
+        total *= (i + offset)
+    return total

### 2017-03-30 Drafts/Draft.tex
Update

@@
 \title{M\"obius Inversion: Construction and Applications}
-
+\renewcommand{\theequation}{\addtocounter{thm}{0}\thethm}
 \newcommand{\fix}{\text{fix }}
@@
 
-\begin{abstract}M\"obius inversion is a general approach to reversing certain kinds of sums.
+\begin{abstract} %TODO: Write a better abstract.
+M\"obius inversion is a general approach to reversing certain kinds of sums.
 In many situations, we know that a value we have access to is equal to the sum over a poset interval of values we want.
@@
 Then, we investigate its application in various counting examples, including the inclusion-exclusion principle and counting orbits of group actions.
-Finally, we explore an application of M\"obius inversion to data clustering.
+Finally, we explore an application of M\"obius inversion to data clustering.\
 \end{abstract}
@@
 \begin{chapter}{Introduction to M\"obius Inversion}\label{chap_intro}
-\section{Initial Example}
+\section{Introduction and Motivation}
+%TODO: Expand introduction with more explicit examples
+Suppose that we have the integer sequence $g$ of ones:
+\[
+g : 1, 1, 1, \cdots
+\]
+We can let $f$ be the sequence of cumulative sums of $g$. So $f_k = g_1 + \cdots + g_k$. We can write down the values:
+\[
+f: 1,2,3,\cdots
+\]
+In general, summing up values is easy. Finding values of $f$ from $g$ was not difficult.
+
+If we knew $f$ and wanted to find values of $g$, we would subtract adjacent values of $f$.
+So we would use the fact that $g_k = f_k - f_{k-1}$.
+It seems clear that, when we are talking about integer sequences, if for all integers $k$,
+\[
+\forall k f_k = \sum_{i = 1}^k g_i,
+\]
+then it is also true that
+\[\\
+g_k = f_k = f_{k-1}.
+\]
+This relationship is a result of the simple structure of the positive integers.
+However, it is possible to sum up values over more subsets of more complicated structures, such that this relationship isn't so obvious.
+For example, we could add up values of $g$ over a number's divisors, instead of over all numbers less than or equal to it:
+\[
+h_k = \sum_{l|k}g_l.
+\] 
+It is now much less clear how to obtain $g$ from $h$. In fact, we will see how to reverse this kind of sum soon.
+
+The goal of M\"obius inversion is to generalize the process of reversing sums over discrete, ordered structures called \emph{posets}.
+If sums like the above are a discrete analogue of integration (cumulatively summing over a region), then M\"obius inversion is discrete differentiation.
+In the same way that developing the theory of the derivative is useful for solving differential equations where functions are defined in terms of their integral, M\"obius inversion helps us extract values which are defined in terms of their cumulative sums.
+In addition to building the necessary machinery for M\"obius inversion, we will consider several applications of it, including a somewhat surprising one in data clustering.
+\section{Initial Example and Posets}
 M\"obius inversion is a general construct.
-The most basic definition of a M\"obius function is a function $\mu$ on the positive integers which satisfies the following for functions $f,g$ on the positive integers:
+The classical definition of a M\"obius function is a function $\mu$ on the positive integers which satisfies the following for functions $f,g$ on the positive integers:
 
-\begin{equation}\label{init_mob} %TODO: Unify numbering
-f(n) = \sum_{d | n} g(d) \iff g(n) = \sum_{d | n}  f(n)\mu\left(\frac dn\right)
+\begin{equation}\label{init_mob} 
+f(n) = \sum_{d | n} g(d) \iff g(n) = \sum_{d | n}  f(m)\mu\left(\frac dn\right)
 \end{equation}
 
-Our first goal is to prove the existence of - and find - this function $\mu$.
-We will do this using a more general construction, and then generalize to more even more abstract structures.
-We start with several definitions.
-\section{Posets and Incidence Algebras}
+Our first goal is to prove the existence of, and find, this function $\mu$. We will do this using by developing M\"obius inversion in general and then applying it. We start with several definitions.
+
 \begin{defn}
@@
 \end{defn}
+Note that, for completeness, a poset should be labeled with both its elements and its relations - e.g. $(X, \leq)$. But often we just write $X$ when the relation is implied.
 \begin{defn}
@@
 \end{defn}
-\begin{rmk}
-A poset which is lower finite is also \emph{locally finite}: For any $a,b \in X$, the set $\{c \in X : a \leq c \leq b\}$ is finite.  
-\end{rmk}
-For many of the following definitions and theorems, it is enough for the poset to be locally finite. But we will assume our posets are lower finite, a stronger condition, to make certain steps easier.
-\begin{defn}
-The \emph{incidence algebra} on a lower finite poset $X$ is over the set of functions from $X \times X$ to $\Rr$ which map $(a,b)$ to zero if $a \nleq b$. So the elements of the incidence algebra are 
-\[\{f:X \times X \rightarrow \Rr:a \nleq b \Rightarrow f(a,b) = 0\}
-\]
-Scalar multiplication and addition are defined pointwise.  Multiplication is denoted by ``*'', and is defined:
-\[(f* g)(a,b) = \sum_{a \in X}f(a,c)g(c,b) \left( = \sum_{a \leq c \leq b}f(a,c)g(c,b)\right).\]
-\end{defn}
-\begin{rmk}
-The requirement that $X$ be lower finite ensures that the above sum has a finite number of nonzero terms, so is finite-valued.
-\end{rmk}
-\begin{rmk}
-We use $\Rr$ as the codomain of the functions in the incidence algebra. But this can be generalized to other commutative rings with identity.
-\end{rmk}
-I include the version with bounds for clarity, but they make no difference, because all other terms will go to zero anyway by the condition on elements.
-Considering the sum without the bounds, we see that this is identical to matrix multiplication.
-It will be useful to formalize this:
-\begin{lemma}\label{mat_eq}
-Let $X$ be a lower finite poset, with $|X|=n$.
-Choose a total ordering on $X$ such that the partial order is respected - in other words, label the elements with integers such that if $x_i \leq x_j, i \leq j$.
-Let $f,g$ be elements of the incidence algebra on $X$.
-Let $F$ be the (possibly infinite) square matrix where $F_{ij}=f(x_i, x_j)$.
-Define $G$ likewise.
-Then:
-\begin{enumerate}[a)]
-\item $F$ and $G$ are upper triangular; and
-\item For any $i,j, (f * g)(x_i, x_j)=FG_{ij}$.
-\end{enumerate}
-\end{lemma}
-\begin{proof}
-\begin{enumerate}[a)]
-\item If $i>j$, by how we defined $F$, $x_i \nleq x_j$. So $F_{ij} = f(x_i, x_j) = 0$. 
-\item
-The result follows directly from the definition of matrix multiplication. Let $i,j\leq n$ be given. Then:
-\begin{align*}
-(f * g)(x_i, x_j) &= \sum_{y \in X} f(x_i,y)g(y,x_j)\\
-&=FG_{ij}
-\end{align*}
-\end{enumerate}
-\end{proof}
+This condition will be necessary for many of the following facts and theorems, to ensure that certain sums have a finite number of nonzero terms.
 
-There are several important functions, present in any incidence algebra, which we will need. 
-The \textbf{identity function} $\delta$ is defined by 
-\[\delta(a,b) = \begin{cases} 1 & a = b \\ 0 & else. \end{cases}
-\]
-This is equivalent to the identity matrix, with 1's along the main diagonal.
-
-We also define another special function, $\zeta$ (the ``indicator function''):
+Next, we define an important function on lower finite posets: $\zeta$ (the ``indicator function''), from $X \times X$ to $\Rr$:
 \[
@@
 
-At this point, \ref{mat_eq} tells us several things about inverses.
-Since $\delta$ is equivalent to the identity matrix, inverses will coincide with the corresponding matrix inverses.
-This leads us to the following:
-\begin{cor}\label{cor_inv}
-Let $X$ be a lower finite poset, and let $f,g, h$ be elements of the incidence algebra on $X$. Then:
-\begin{enumerate}[a)]
-\item $(f*g)*h = f*(g*h)$, i.e. multiplication is associative
-\item $f*g = \delta \Rightarrow g*f = \delta$
-\item If $\forall x \in X, f(x,x) \neq 0$, then $f$ is uniquely invertible - in other words, $\exists! f^{-1}$ such that $f*f^{-1} = \delta = f^{-1} * f$.
-\end{enumerate}
-\end{cor}
+M\"obius inversion is concerned with adding up values of functions.
+In particular, given a lower finite poset $X$ and a function $g:X \rightarrow \Rr$, we want to consider a function $f:X \rightarrow \Rr$ defined by
+
+\[
+f(a) = \sum_{b \leq a}g(b)
+\]
+
+Note that, because $X$ is lower finite, this sum has a finite number of terms, so is always finite-valued.
+Using the ``indicator" function $\zeta$ from above, we can rewrite the definition of $f$ to remove the need for the bound on the sum:
+\begin{equation}\label{sum_form_intro}
+f(a) = \sum_{b \in X}g(b)\zeta(b,a)
+\end{equation}
+Each value of $f$, therefore, takes on precisely the structure of a dot product. We will use this structure to leverage linear algebra: 
+\begin{itemize}
+\item Totally order $X$ such that the partial order is respected;
+\item Write $g$ as a row vector which contains the values $g$ takes on elements of $X$, with respect to the total ordering;
+\item Write $\zeta$ as a matrix whose $i,j$ entry is equal to $\zeta(a_i, a_j)$, where $a_i, a_j$ are the $i$'th and $j$'th elements of $X$ under the total ordering.
+\end{itemize}
+
+Going forward, we will not explicitly define the vector/matrix forms of functions in this way.
+Instead, when we refer to functions on one or two elements of a partially ordered set, we will implicitly think of them as (row) vectors and as matrices.
+We will also implicitly assume a total ordering, and identify an element $a$ of $X$ with its index in the total ordering.
+So if we write $g(a)$, we are referring to the function $g$ applied to $a$ and also to the element of the corresponding vector containing that value - they are equivalent.
+We will also use this perspective for function multiplication and inversion.
+Going forward, $g\zeta$ will refer to the vector/matrix product of $g$ and $\zeta$ rather than function composition, and $\zeta^{-1}$ will refer to the matrix inverse of $\zeta$ rather than the inverse function under composition.
+
+We now are able to define our desired function (or vector) $f$ more succinctly:
+\[
+f = g \zeta
+\]
+
+If the matrix multiplication is explicitly written out, what we get is identical to \ref{sum_form_intro}. %TODO: Fix this numbering
+
+The goal of M\"obius inversion is to obtain $g$ given $f$.
+If $\zeta$ were invertible, we would be able to do that.
+It turns out that $\zeta$ always is invertible.
+Because the total ordering respects the partial ordering, the matrix $\zeta$ is upper triangular and has ones on the diagonal.
+This implies the following straightforward but crucial fact:
+\begin{lemma}\label{inv_ex}
+Let $X$ be a lower finite poset. Fix a total order on $X$ which respects the partial order, and let $\zeta$ be the matrix where 
+\[
+\zeta(a,b) = \begin{cases}1 & a \leq b \\ 0 & else. \end{cases}
+\]
+Then $\zeta$ is invertible, and elements of $\zeta^{-1}$ are integers.
+\end{lemma}
 \begin{proof}
-Part a) is true of matrix multiplication in general.
-Part b) is true of all square matrices.
-Part c) is true of all upper triangular matrices, since the determinant of such matrices is the product of the main diagonal elements.
-We use \ref{mat_eq} to transfer all three results to $f$ and $g$.
+We have already observed that $\zeta$ is upper triangular and has ones on the main diagonal.
+This means that $\det(\zeta) = 1$, meaning that $\zeta$ is invertible.
+Together with the fact that elements of $\zeta$ are integers, this also implies that elements of $\zeta^{-1}$ are integers.
 \end{proof}
-We will refer to this unique inverse, if it exists, as $f^{-1}$.
+
+This means that we can let $\mu=\zeta^{-1}$, which we now know exists, and write down the central relationship of M\"obius inversion, which holds for any lower finite poset $X$ and pair of functions $f,g$ on it:
+\[
+g = g \zeta \iff g = f \mu.
+\]
+
+We will develop this further in the next section.
 
@@
 \begin{rmk}
-This inverse exists by \ref{cor_inv} part b. 
+Recall that $\zeta^{-1}$ is the matrix inverse rather than the functional inverse, and that it exists by \ref{inv_ex}.
 \end{rmk}
 \begin{rmk}\label{sum_form}
-Definition \ref{def_mob_pos} is a statement about incidence algebra multiplication, so is really about matrix multiplication.
-Another statement of the definition is that $\mu$ is the unique function such that, for all $x,y \in X$,
+We can unpack the linear algebra to get a definition analagous to \ref{sum_form_intro}: We can say that $\mu$ is the unique function from $X\times X$ to $\Rr$ such that, for all $x,y \in X$,
 \[
-\sum_{z \in X} \mu(x,z)\zeta(z,y) = \delta(x,z) = \sum_{z \in X} \zeta(x,z)\mu(z,y)
+\sum_{z \in X} \mu(x,z)\zeta(z,y) = \delta(x,z) = \sum_{z \in X} \zeta(x,z)\mu(z,y).
 \]
@@
 
-This is the M\"obius function. To complete the definition of M\"obius inversion, we turn to the standard use of this function. 
-\begin{thm}[M\"obius Inversion]\label{mob_inv}
-Let $X$ be a lower finite poset. Let $f, g: X \times X \rightarrow \Rr$ be elements of the incidence algebra on $X$. Let $\zeta, \mu$ be defined as usual. Then:
+To complete the definition of M\"obius inversion, we turn to the standard use of this function. 
+\begin{thm}[Single Variable M\"obius Inversion]\label{mob_inv}
+Let $X$ be a lower finite poset. Let $f,g:X \rightarrow \Rr$ be given. Let $\zeta:X \times X \rightarrow \Rr$ be defined as usual, and let $\mu = \zeta^{-1}$. Then:
 \begin{align*}
-f = g * \zeta &\iff g = f *\mu;\\
-f = \zeta * g &\iff g = \mu * f.
+f = g \zeta & \iff g = f \mu.
 \end{align*}
@@
 \begin{align*}
-\forall x,y \in X, f(x,y) = \sum_{z \in X}g(x,z)\zeta(z,y) &\iff \forall x,y \in X, g(x,y) = \sum_{z \in X}f(x,z)\mu(z,y);\\
-\forall x,y \in X, f(x,y) = \sum_{z \in X}\zeta(x,z)g(z,y) &\iff \forall x,y \in X, g(x,y) = \sum_{z \in X}\mu(x,z)f(z,y).
+\forall x \in X, f(x) = \sum_{y \in X} g(y)\zeta(y,x) &\iff \forall x \in X, g(x) = \sum_{y \in X} f(y)\mu(y,x).
 \end{align*}
+\end{thm}
 \begin{proof}
-All these results follow from the definition of $\mu$ and from facts about matrix/incidence algebra multiplication.
+Recall that by \ref{inv_ex}, $\mu = \zeta^{-1}$ exists. Given that, the result follows if we right-multiply both sides by $\mu$. The first statement becomes the second when the sums are made explicit.
 \end{proof}
-\end{thm}
-This result seems quite straightforward based on how we defined $\zeta$ and $\mu$.
-However, it turns out to be extremely powerful.
+
+This result is quite straightforward based on how we defined $\zeta$ and $\mu$.
+In fact, it feels strange that a supposedly central fact is just the inversion of a single matrix operation.
+In fact, the simplicity of the inversion step is the whole point of M\"obius inversion.
+The tricky part is formulating a given problem such that \ref{mob_inv} can be applied to it.
 We will see many cases where values of $f$ from the theorem are readily attainable, but values of $g$ are what we really want.
@@
 
-With that in mind, we can also consider M\"obius inversion on functions in one variable (instead of two) on a poset.
-\begin{thm}\label{1var_mob_inv}
-Let $X$ be a lower finite poset. Let $f,g:X \rightarrow \Rr$ be given. Let $\zeta, \mu$ be defined as usual. Then:
-\begin{align*}
-f = g *\zeta & \iff g = f *\mu;\\
-f = \zeta *g & \iff g = \mu *f.
-\end{align*}
-Equivalently,
-\begin{align*}
-\forall x \in X, f(x) = \sum_{y \in X} g(y)\zeta(y,x) &\iff \forall x \in X, g(x) = \sum_{y \in X} f(y)\mu(y,x);\\
-\forall x \in X, f(x) = \sum_{y \in X} \zeta(x,y)g(y) &\iff \forall x \in X, g(x) = \sum_{y \in X} \mu(x,y)g(y).
-\end{align*}
-\end{thm}
-\begin{proof}
-If we fix one argument of functions on two variables, this follows from \ref{mob_inv}.
-\end{proof}
 We now have two equivalent definitions of the M\"obius function, one using matrices (or linear operators) and vectors, and one directly considering elements and sums.
@@
 On the other hand, using matrices and vectors greatly simplifies the equations we have to deal with, makes the manipulations themselves easier, and allows us to keep the bigger picture - the idea of inversion - in mind more easily.
+\section{Integer Lattices}
+We now turn to a specific class of partially ordered sets, which will come up several times going forward.
+\begin{defn}\label{lattice}
+For any positive integer $n$, the \emph{integer lattice of dimension $n$}, which we denote $\Nn^n$, is the set of ordered $n$-tuples of non-negative integers.
+For any two elements $(a_1,...,a_n), (b_1,...,b_n) \in \Nn^n$, we say that $(a_1,...,a_n)\leq (b_1,...,b_n)$ if $a_i \leq b_i$ for each $i = 1,\cdots,n$.
+\end{defn}
+\begin{rmk}
+$(\Nn^n, \leq)$ is a poset for any positive integer $n$. The axioms are easily checked.
+\end{rmk}
+We turn to several examples.
+\begin{examp}
+Consider the $n$-dimensional unit cube in $\Rr^n$, placed such that one corner is at the origin and all vertices have non-negative coordinates.
+Let $S$ denote the set of vertices of the cube.
+Then we can think of the vertices of the cube as ordered $n$-tuples of zeros and ones.
+So $S \subseteq \Nn^{n}$.
 
-\section{Integers with Divisibility Ordering}
-We are now able to justify the existence of, and find, the function $\mu$ from equation \ref{init_mob}, with very little work.
+In this example, what is the interpretation of the poset relation?
+If $v_1, v_2 \subseteq S$, then $v_1 \leq v_2$ if $v_1$ has zeros in all of the coordinates where $v_2$ has zeros.
+So $v_1 \leq v_2$ if $v_1$ is part of a shortest path from $v_2$ to the origin along the edges of the cube.
+Equivalently, $v_1 \leq v_2$ if $v_1$ is the projection of $v_2$ onto some subset of the axes.
+%TODO: Make sure this is true
+\end{examp}
+\begin{examp}
+Each integer can be uniquely represented by its prime factorization.
+In particular, if we consider the set of integers whose factorizations only include the first $n$ primes, we can write those factorizations as ordered $n$-tuples, capturing each prime's multiplicity in the factorization.
+As a result, the integers whose factorizations only include the first $n$ primes form a copy of the $n$-dimensional integer lattice.
+
+In this case, if $\leq$ represents the poset relation from \ref{lattice}, then $m \leq n$ if, for each prime $p$, $m$'s factorization contains no more copies of $p$ than $n$'s factorization.
+This is the same as saying that $m|n$.
+So the poset relation becomes divisibility.
+We will explore this example more in the next sections.
+\end{examp}
+It turns out that several important posets have this lattice structure.
+So the goal is to determine the M\"obius function on certain subsets of the integer lattice, and then transfer those results to other partially ordered sets.
+To do so, we first need a lemma which applies to the M\"obius function on any poset.
+\begin{lemma}\label{recurse}
+Let $X$ be a lower finite partially ordered set, and let $\zeta, \mu$ be defined as usual. Then for all $a, b \in X$,
+\[
+\mu(a,b) = 
+\begin{cases}
+0 & a \nleq b\\
+\delta(a,b)-\sum_{a \leq c < b}\mu(a,c) & else.
+\end{cases}
+\]
+\end{lemma}
+\begin{rmk}
+Note that the piecewise form is actually not necessary, because if $a \nleq b$ then the sum will be empty. So it is correct - albeit less clear- to just write
+\[
+\mu(a,b) = \delta(a,b)-\sum_{a \leq c < b}\mu(a,c).
+\]
+\end{rmk}
+\begin{proof}
+We fix $a,b$, and then rearrange terms starting from \ref{sum_form}:
+\begin{align*}
+\sum_{c \in X}\mu(a,c) \zeta(c,b) &= \delta(a,b)\\
+\sum_{a \leq c < b} \mu(a,c) + \mu(a,b) &= \delta(a,b)\\
+\mu(a,b) &= \delta(a,b) - \sum_{a \leq c < b} \mu(a,c) 
+\end{align*}
+\end{proof}
+We are now ready to write down $\mu$ on certain subsets of the integer lattice. In order to ensure that the sums involved are predictable, we need an additional condition on the subsets we consider:
+
+\begin{lemma}\label{mu_lattice}
+Let $L$ be the $n$-dimensional integer lattice, with the usual poset relation.
+Let $X$ be a subset of $L$ such that if $x \in X, y \in L$, and $y \leq x$, then $y \in X$.
+Let $\zeta, \mu$ be defined as usual on $X$.
+Let $x=(x_1,...,x_n),y = (y_1,...,y_n)$ be elements of the lattice.
+Then:
+\[
+\mu(x,y) =
+\begin{cases}
+0 & x\nleq y\\
+0 & \exists i \in \Nn: y_i-x_i \geq 2\\
+(-1)^{\sum_{i=1}^ny_i-x_i} & \text{otherwise}
+\end{cases}
+\]
+\end{lemma}
+
+\begin{proof} %TODO: Prove for general integer lattice
+If $x \nleq y$, then by \ref{recurse}, $\mu(x,y) = 0$. This is the first case.
+
+We now proceed by induction on $\sum_{i=1}^ny_i-x_i$. If $x \leq y$ and $\sum_{i=1}^ny_i-x_i = 0$, then $x = y$. So by \ref{recurse}, $\mu(x,y) = 1$. This is the base case.
+
+Suppose that we have \ref{mu_lattice} for any $x \leq y$ where $\sum_{i=1}^ny_i-x_i \leq k-1$. Let $x \leq y$ be fixed such that $\sum_{i=1}^ny_i-x_i =k$. If $\exists i \in \Nn: y_i-x_i \geq 2$
+
+If $\frac{n_0}{d_0}$ is not divisible by a square, then $\frac{n_0}{d_0} = p_1p_2\cdots p_{k+1}$, where the $p_i$ are distinct primes. Then there is a direct correspondence:
+\begin{center}$\{k : d_0|k, k|n_0, k\neq n_0\} \leftrightarrow$ \{Nonempty subsets of $\{p_1,\cdots,p_{k+1}\}$\},\end{center}
+where $k$ is obtained by multiplying the remaining prime factors by $m_0$, and the omitted prime factors can be determined by factoring $k$.
+
+This means that we can index the sum from \ref{recurse} using those subsets:
+\[
+\mu(m_0, n_0) = -\sum_{P \subsetneq \{1,\cdots,k+1\}} \mu(d_0, m_0\cdot \prod_{i \in P}p_i )
+\]
+Because $\frac{d_0\cdot \prod_{i \in P}p_i}{d_0} = \prod_{i \in P}p_i$ has $|P| < k + 1$ prime factors, we can apply the inductive hypothesis, which tells us that 
+\[
+\mu(d_0, md_0\cdot \prod_{i \in P}p_i = (-1)^{|P|}.
+\]
+So we can write
+\begin{align*}
+\mu(d_0, n_0) &= -\sum_{P \subsetneq \{1,\cdots,k+1\}} (-1)^{|P|}\\
+&= -\sum_{i = 1}^{k}(-1)^i{k+1 \choose i}\\
+&= (-1)^{k+1}
+\end{align*}
+with the final equality following from the alternating-sum binomial identity
+\[
+\sum_{1=1}^{k+1}(-1)^i{k+1 \choose i} = 0.
+\]
+Finally, we consider the case where $\frac {d_0}{n_0}$ has a squared factor. So we can write 
+\[
+\frac {d_0}{n_0} = p^2q
+\]
+where $p$ is prime, and $q$ is some other integer.
+Note that we can no longer use the previous argument, because the factors of $\frac {d_0}{n_0} = p^2q$ form a set with multiplicity rather than a simple set, so the sum will no longer have standard binomial coefficients.
+
+Let $r$ divide $d_0q$ and be divisible by $d_0$.
+So $\mu(d_0, r)$ is a term in the sum from \ref{recurse}.
+Note also that $rp$ divides $d_0qp$, so $\mu(d_0, rp)$ is also a term in the sum.
+By the inductive hypothesis, $\mu(d_0, rp) = -\mu(d_0, r)$, so the terms cancel.
+We can pair terms in this way to eliminate all divisors of $d_0pq$.
+The only remaining terms are of the form $\mu(d_0, d_0p^2k)$.
+But because $\frac{d_0p^2k}{d_0}$ is divisible by $p^2$, by the inductive hypothesis, these terms are all zero.
+So all terms in \ref{recurse} cancel, meaning that $\mu(d_0, n_0) = 0$.
+\end{proof}
+
+\section{Integers with Divisibility Ordering} %TODO: Change \Nn to \Nn^+
+We are now able to justify the existence of, and find, the function $\mu$ from equation \ref{init_mob}, with little work.
 
@@
 For our purposes, $0 \notin \Nn$.
-Note that this poset is lower finite: For any number $n$, the set $\{q \in \Nn: q|n\} \subseteq \{q \in \Nn: q \leq n\}$, and the latter set contains $n$ elements, which is finite.
+Note that this poset is lower finite: For any number $n$, the set $\{q \in \Nn: q|n\} \subseteq \{q \in \Nn: q \leq n\}$, and the latter set contains $n$ elements, which is finite (note that $d|n$ means that $d$ divides $n$ without remainder).
 This means we are able to use M\"obius inversion.
 
-We go through the usual steps of M\"obius inversion and apply \ref{mob_inv}. We will use functions and sums rather than matrices and vectors to make it easier to see what is going on.
+We go through the usual steps of M\"obius inversion and apply \ref{mob_inv}:
 \begin{itemize}
-\item Let $\zeta: \Nn \times \Nn \rightarrow \Nn$ be defined as follows. Note that $m|n$ means that $m$ divides $n$ without remainder.
+\item Let $\zeta: \Nn \times \Nn \rightarrow \Nn$ be defined as follows.
 \[
-\zeta(m,n) = \begin{cases}1 & m|n \\ 0 & else \end{cases}
+\zeta(d,n) = \begin{cases}1 & d|n \\ 0 & else \end{cases}
 \]
-\item Let $\mu = \zeta^{-1}$ (inverse in the incidence algebra)
+\item Let $\mu = \zeta^{-1}$ 
 \end{itemize}
-Then \ref{1var_mob_inv} gives us:
+Then \ref{mob_inv} gives us:
 \[
@@
 \begin{lemma}\label{nfact}
-Let $\zeta, \mu$ be defined as usual on $\Nn$ ordered by divisibility. Let $m,n \in \Nn$ be given.  Then:
+Let $\zeta, \mu$ be defined as usual on $\Nn$ ordered by divisibility. Let $d,n \in \Nn$ be given.  Then:
 \[
-\mu(m,n) =
+\mu(d,n) =
 \begin{cases}
-0 & m\nmid n\\
-0 & \exists p \in \Nn: p^2|(\frac nm )\\
-(-1)^{\#\{p \text{ prime}: p|\frac nm\}} & else
+0 & d\nmid n\\
+0 & \exists p \in \Nn: p^2|(\frac nd )\\
+(-1)^{\#\{p \text{ prime}: p|\frac nd\}} & else
 \end{cases}
@@
 \end{lemma}
-This lemma gives us what we need - a way of writing values of $\mu$ in terms of a single variable. We will prove it by induction on the number of prime factors of $\frac nm$.
+This lemma gives us what we need - a way of writing values of $\mu$ in terms of a single variable. We will prove it by induction on the number of prime factors of $\frac nd$.
+\begin{proof} %TODO: Prove for general integer lattice
+If $d \nmid n$, then by \ref{recurse}, $\mu(d,n) = 0$. This is the first case.
+
+If $n = d$, then $\frac nd=1$ has zero prime factors. In that case, again by \ref{recurse}, $\mu(n,d) = 1$. This will be our base case for the second and third branches.
+
+Suppose that if $d|n$, and $\frac nd$ has $k$ prime factors (with multiplicity), then \ref{nfact} holds for $d$ and $n$.
+Suppose that $d_0|n_0$ and $\frac {n_0}{d_0}$ has $k+1$ prime factors.
+If $\frac{n_0}{d_0}$ is not divisible by a square, then $\frac{n_0}{d_0} = p_1p_2\cdots p_{k+1}$, where the $p_i$ are distinct primes.
+Then there is a direct correspondence:
+\begin{center}$\{k : d_0|k, k|n_0, k\neq n_0\} \leftrightarrow$ \{Nonempty subsets of $\{p_1,\cdots,p_{k+1}\}$\},\end{center}
+where $k$ is obtained by multiplying the remaining prime factors by $m_0$, and the omitted prime factors can be determined by factoring $k$.
+
+This means that we can index the sum from \ref{recurse} using those subsets:
+\[
+\mu(m_0, n_0) = -\sum_{P \subsetneq \{1,\cdots,k+1\}} \mu(d_0, m_0\cdot \prod_{i \in P}p_i )
+\]
+Because $\frac{d_0\cdot \prod_{i \in P}p_i}{d_0} = \prod_{i \in P}p_i$ has $|P| < k + 1$ prime factors, we can apply the inductive hypothesis, which tells us that 
+\[
+\mu(d_0, md_0\cdot \prod_{i \in P}p_i = (-1)^{|P|}.
+\]
+So we can write
+\begin{align*}
+\mu(d_0, n_0) &= -\sum_{P \subsetneq \{1,\cdots,k+1\}} (-1)^{|P|}\\
+&= -\sum_{i = 1}^{k}(-1)^i{k+1 \choose i}\\
+&= (-1)^{k+1}
+\end{align*}
+with the final equality following from the alternating-sum binomial identity
+\[
+\sum_{1=1}^{k+1}(-1)^i{k+1 \choose i} = 0.
+\]
+Finally, we consider the case where $\frac {d_0}{n_0}$ has a squared factor. So we can write 
+\[
+\frac {d_0}{n_0} = p^2q
+\]
+where $p$ is prime, and $q$ is some other integer.
+Note that we can no longer use the previous argument, because the factors of $\frac {d_0}{n_0} = p^2q$ form a set with multiplicity rather than a simple set, so the sum will no longer have standard binomial coefficients.
+
+Let $r$ divide $d_0q$ and be divisible by $d_0$.
+So $\mu(d_0, r)$ is a term in the sum from \ref{recurse}.
+Note also that $rp$ divides $d_0qp$, so $\mu(d_0, rp)$ is also a term in the sum.
+By the inductive hypothesis, $\mu(d_0, rp) = -\mu(d_0, r)$, so the terms cancel.
+We can pair terms in this way to eliminate all divisors of $d_0pq$.
+The only remaining terms are of the form $\mu(d_0, d_0p^2k)$.
+But because $\frac{d_0p^2k}{d_0}$ is divisible by $p^2$, by the inductive hypothesis, these terms are all zero.
+So all terms in \ref{recurse} cancel, meaning that $\mu(d_0, n_0) = 0$.
+\end{proof}
+Given \ref{nfact}, we can write $\mu(\frac nm)$ instead of $\mu(m,n)$. This allows us to use \ref{mob_inv} to arrive at \ref{init_mob}:
+\[
+f(n) = \sum_{m | n} g(m) \iff g(n) = \sum_{m | n}  f(m)\mu\left(\frac mn\right).
+\]
+\section{Euler's Totient}
+Euler's Totient is a famous function in number theory, which counts the how many numbers are relatively prime to a particular value.
+We denote the function by $\varphi : \Nn \rightarrow \Nn$, and its definition is:
+\[
+\varphi(n) = \#\{1 \leq m \leq n : (m,n) = 1\},
+\]
+where $(m,n)$ denotes the greatest common divisor of $m,n$.
+
+We wonder how we can write down the value of $\varphi(n)$ given a particular integer $n$.
+One approach would be to go through all the values from 1 to $n$, find each one's greatest common divisor with $n$, and then count how many are equal to 1.
+However, for large values of $n$, this could be computationally expensive.
+We will use the function $\mu$ from the previous part to arrive at a different, likely more efficient, approach.
+
+We start with an important fact:
+\begin{thm}[Gauss]\label{gauss}
+Let $n \in \Nn$ be given. Then 
+\[
+n = \sum_{d|n}\varphi(d).
+\]
+\end{thm}
+There are a variety of ways of proving this fact. Here we include a concise proof using group theory.
 \begin{proof}
-If $n \nmid m$, then by \ref{recurse}, $\mu(m,n) = 0$. This is the first case.
-
-If $n = m$, then $\frac nm=1$ has zero prime factors. In that case, again by \ref{recurse}, $\mu(n,m) = 1$. This will be our base case for the second and third branches.
-
-Suppose that if $m|n$, and $\frac nm$ has $k$ prime factors (with multiplicity), then \ref{nfact} holds for $m$ and $n$.
-Suppose that $m_0|n_0$ and $\frac nm$ has $k+1$ prime factors.
-We now consider three cases.
-\begin{description}
-\item[Case 1:] Suppose that $\frac nm$ has no squared prime factors. 
-\end{description}
+For any integer $d$, $\varphi(d)$ counts the generators of $C_d$.
+Each element of $C_n$ generates exactly one cyclic subgroup, so counting the total number of generators of cyclic subgroups of $C_n$ is equivalent to counting the elements of $C_n$.
+Also, $C_n$ has exactly one cyclic subgroup for each divisor of $n$ (and no others).
+So the sum indeed counts the number of elements of $C_n$, of which there are $n$.
 \end{proof}
-
+This sum gives us a value we have access to ($n$) in terms of a sum of values we want.
+This is a perfect situation to apply M\"obius inversion, and undo that sum.
+We apply \ref{init_mob}, which tells us
+\[
+\varphi(n) = \sum_{d|n} d\mu\left(\frac nd\right).
+\]
+Depending on what information we have access to, this might be much easier than just counting the number of values relatively prime to $n$.
+This is a straightforward example of how M\"obius inversion's ability to reverse a sum can be useful.
 \end{chapter}
@@
 \section{Background}
-NOTE: Define groups, actions, orbits, subgroups, etc. (do I need to?)
+Suppose that a group $G$ acts on a set $\Omega$.
 
@@
 \end{rmk}
-This puts us in the position to apply M\"obius inversion. We will use the form of M\"obius inversion with matrices and vectors. So throughout this chapter:
+This puts us in the position to apply M\"obius inversion. We first define the usual functions on $\sub(G) \times \sub(G)$:
 \begin{itemize}
-\item Given a group $G$, assume a total ordering of $\sub(G)$ which respects the partial ordering.
-Let $\zeta$ also denote the square matrix of size $|\sub(G)|$, with rows and columns labeled with elements of $\sub(G)$, such that
+\item Given a group $G$, let $\zeta:\sub(G) \times \sub(G) \rightarrow \Rr$ be defined by
 \[
-\zeta_{A,B} = \begin{cases}
+\zeta(a,b) = \begin{cases}
 1 & A \supseteq B\\
@@
 \]
-\item Let $\mu = \zeta^{-1}$, which exists by \ref{cor_inv}.
+\item Let $\mu = \zeta^{-1}$, which exists by \ref{inv_ex}.
 \end{itemize}
-Now, \ref{1var_mob_inv} tells us that, for any row vectors $f,g$ of length $|\sub{G}|$, 
+Recall that we manipulate $\zeta, \mu$ as if they were matrices.
+
+Now, \ref{mob_inv} tells us that, for any row vectors $f,g$ of length $|\sub{G}|$, 
 \[
@@
 \]
+Now, of course, the challenge is to determine how to formulate the problem such that inverting $\zeta$ will be useful.
 \section{Counting Orbits}
@@
 
-We start by defining some vectors, each with entries corresponding with subgroups of $G$, which we will be using. Let:
+We start by defining some functions/vectors, each with entries corresponding with subgroups of $G$, which we will be using. Let:
 \begin{align*}
-f_A &= \#\{x \in \Sigma: \stab(x) \supseteq A\} = |\fix(A)|\\
-g_A &= \#\{x \in \Sigma: \stab(x) = A\}
-\sigma_A &= |A|
+f(A) &= \#\{x \in \Sigma: \stab(x) \supseteq A\} = |\fix(A)|\\
+g(A) &= \#\{x \in \Sigma: \stab(x) = A\}
+\sigma(A) &= |A|
 \end{align*}
@@
 The goal is to count the orbits in $\Omega$ under the action by $G$ - in other words, to find $|\orb(\Omega, G)|$.
-We will start with the assumption that we are able to find $f$ and $\sigma$, which is true if we know the structure of $\sub(G)$ and know the group action.
+We will start with the assumption that we are able to find $\sigma$, which is true if we know the structure of $\sub(G)$.
+We will also assume that we are able to carry out the group action, thereby determining which elements of $\Omega$ are fixed by given subgroups of $G$.
+This gives us access to $f$.
 Then there are two steps we will follow:
@@
 \item[Step 1:] Determine how to use $g$ and $\sigma$ to find $|\orb(\Omega, G)|$; and
-\item[Step 2:] Find $g$ from $g$.
+\item[Step 2:] Find $g$ from $f$ using M\"obius inversion.
 \end{description}
@@
 \begin{align*}
-|\orb(\Omega, G)| &= \frac{1}{|G|}\sum_{A \in \sub(G)}g_A|A|\\
-&= g \cdot \sigma
+|\orb(\Omega, G)| &= \frac{1}{|G|}\sum_{A \in \sub(G)}g(A)|A|\\
+&= \frac {1}{|G|}g \cdot \sigma
 \end{align*}
@@
 \[
-|\orb(\Omega, G)| = f\mu \cdot \sigma
+|\orb(\Omega, G)| = \frac {1}{|G|}f\mu \cdot \sigma
 \]
+Recall that $\sigma$ and $\mu$ do not depend on the details of the group action, or on $\Omega$ at all.
+They only depend on $G$.
+So it is useful to rearrange this expression to isolate $f$, the only part which does depend on the action:
+\[
+|\orb(\Omega, G)| = \frac {1}{|G|}(\mu \cdot \sigma)^Tf^T
+\]
+
+By combining M\"obius inversion with basic group theory, we have a recipe for turning something readily obtainable (the function $f$) into something less obvious (the number of orbits of an action).
+\iffalse
 \section{Burnside's Lemma}
 A more familiar way of counting the orbits of a group is the following:
-\begin{thm}[Burnside's Lemma]\label{burnside}
+\begin{thm}[Burnside's Lemma]\label{burnside} %TODO: omit?
 Let $G$ be a finite group acting on a finite set $\Omega$. Then:
@@
 \end{thm}
-
+\fi
 \end{chapter}
@@
 \[
-\bigcup_{i \in K}A_i = \sum_{J \subseteq K}(-1)^{|J|}\bigcap_{i \in J}A_j
+\left|\bigcup_{i \in K}A_i\right| = \sum_{J \subseteq K}(-1)^{|J|}\left|\bigcap_{i \in J}A_j\right|
 .\]
@@
 We will be manipulating functions on subsets of $I$, so this will be our poset.
+We start by formalizing that:
+
+\begin{defn}
+For any set $I$, the \emph{power set} of $I$, denoted by $\ps(I)$, is the set of subsets of $I$. 
+\end{defn}
+\begin{rmk}\label{power_poset}
+Let $I$ be a finite set. Then $(\ps(I), \supseteq)$ is a partially ordered set.
+\end{rmk}
+Note that the poset from \ref{power_poset} is ordered by reverse inclusion rather than simple inclusion. The poset axioms are easily checked.
+
+The goal of the inclusion-exclusion principle is, given a subset $K$ of $I$, to find the size of the union of the sets $A_i$ for $i \in K$.
+The difficulty arises from counting elements multiple times.
+For example, if we knew that the $A_i$ were disjoint, we could say
+\[
+\left|\bigcup_{i \in K}A_i\right| = \sum_{i \in K}\left|A_i\right|.
+\]
+But, because intersections of the $A_i$ might be nonempty, this sum might count some elements multiple times.
+In order to solve this problem, we suppose that we have access to \emph{intersections} (but not unions) of the $A_i$ (it is apparent that this is required to use \ref{iep}).
+First, we define the following indicator function $\chi: s \rightarrow \ps(I)$ by:
+\[
+\chi(x) = \{i \in I : x \in A_i\}.
+\]
+So $\chi$ gives us the indices of the subsets of $S$ which contain $x$.  
+Next, we define some functions defined on our poset, $\ps(I)$.
+Let $J \subseteq I$ be given. Define $f,g,\hat{f}, \hat{g}:\ps(I) \rightarrow \Nn$ by
+
+\begin{align*}
+f(J) &= \left| \bigcap_{i \in J} A_i\right| &= |\{x \in S: \chi(x) \supseteq J\}|\\
+g(J) &= \left| \bigcap_{i \in J} A_i \cap \bigcap_{i \notin J} A_i^c\right| &= |\{x \in S: \chi(x) = J\}|\\
+\hat{f}(J) &= \left| \bigcap_{i \in J} A_i^c\right| &= |\{x \in S: \chi(x)^c \supseteq J\}|\\
+\hat{g}(J) &= \left|\bigcap_{i \in J} A_i^c \cap \bigcap_{i \notin J} A_i \right| &= |\{x \in S: \chi(x)^c = J\}|
+\end{align*}
+
+We can go through these functions to get a better handle on what they mean:
+\begin{itemize}
+\item The function $f$ counts the elements contained in $A_i$ for $i \in J$;
+\item The function $g$ counts the elements contained \emph{only} in the $A_i$ for $i \in J$;
+\item The function $\hat{f}$ counts the elements contained in none of the $A_i$ for $i \in J$; and
+\item The function $\hat{g}$ counts the elements contained in none of the $A_i$ for $i \in J$, but contained in all the other $A_i$.
+\end{itemize}
+Based on these definitions, we can observe certain relationships, which will start to point the way for using M\"obius inversion:
+\begin{align*}
+f(J) &= \sum_{K \supseteq J} g(K)\\
+\hat{f}(J) &= \sum_{K \supseteq J} \hat{g}(K)\\
+g(J) &= \hat{g}(J^c)
+\end{align*}
+
+Finally, we recall that our goal is to find the union of the $A_i$ for $i$ in some given $J$. To that end, we observe that
+\[
+\left| \bigcup_{i \in J} A_i \right| = |S| - \hat{f}(J).
+\]
+So if we are able to write down values of $\hat{f}$, we're done.
 \section{Generalizations}
@@
 \end{defn}
+%TODO: Add examples
 This is a definition of what is usually called a category, but here we will refer to it as an \emph{ordinary} category.
@@
 
+% % % Extra stuff/deleted portions
+\iffalse
+\iffalse
+We can replace the vectors $f,g$ with matrices to get the following generalization, which :
+\begin{thm}[Two Variable M\"obius Inversion]\label{mob_inv_old}
+Let $X$ be a lower finite poset.  Let $f,g:X \times X \rightarrow \Rr$ be given. Let $\zeta:X \times X \rightarrow \Rr$ be defined as usual, and let $\mu = \zeta^{-1}$. Then:
+\begin{align*}
+f = g \zeta &\iff g = f \mu;\\
+f = \zeta g &\iff g = \mu f.
+\end{align*}
+Equivalently,
+\begin{align*}
+\forall x,y \in X, f(x,y) = \sum_{z \in X}g(x,z)\zeta(z,y) &\iff \forall x,y \in X, g(x,y) = \sum_{z \in X}f(x,z)\mu(z,y);\\
+\forall x,y \in X, f(x,y) = \sum_{z \in X}\zeta(x,z)g(z,y) &\iff \forall x,y \in X, g(x,y) = \sum_{z \in X}\mu(x,z)f(z,y).
+\end{align*}
+\begin{proof}
+Again, the result is trivial when we treat $f,g,\zeta,\mu$ as matrices.
+\end{proof}
+\end{thm}
+\fi
+
+\begin{defn}
+The \emph{incidence algebra} on a lower finite poset $X$ is over the set of functions from $X \times X$ to $\Rr$ which map $(a,b)$ to zero if $a \nleq b$. So the elements of the incidence algebra are 
+\[\{f:X \times X \rightarrow \Rr:a \nleq b \Rightarrow f(a,b) = 0\}
+\]
+Scalar multiplication and addition are defined pointwise.  Multiplication is denoted by ``*'', and is defined:
+\[(f* g)(a,b) = \sum_{a \in X}f(a,c)g(c,b) \left( = \sum_{a \leq c \leq b}f(a,c)g(c,b)\right).\]
+\end{defn}
+\begin{rmk}
+The requirement that $X$ be lower finite ensures that the above sum has a finite number of nonzero terms, so is finite-valued.
+\end{rmk}
+\begin{rmk}
+We use $\Rr$ as the codomain of the functions in the incidence algebra. But this can be generalized to other commutative rings with identity.
+\end{rmk}
+I include the version with bounds for clarity, but they make no difference, because all other terms will go to zero anyway by the condition on elements.
+Considering the sum without the bounds, we see that this is identical to matrix multiplication.
+It will be useful to formalize this:
+\begin{lemma}\label{mat_eq}
+Let $X$ be a lower finite poset, with $|X|=n$.
+Choose a total ordering on $X$ such that the partial order is respected - in other words, label the elements with integers such that if $x_i \leq x_j, i \leq j$.
+Let $f,g$ be elements of the incidence algebra on $X$.
+Let $F$ be the (possibly infinite) square matrix where $F_{ij}=f(x_i, x_j)$.
+Define $G$ likewise.
+Then:
+\begin{enumerate}[a)]
+\item $F$ and $G$ are upper triangular; and
+\item For any $i,j, (f * g)(x_i, x_j)=FG_{ij}$.
+\end{enumerate}
+\end{lemma}
+\begin{proof}
+\begin{enumerate}[a)]
+\item If $i>j$, by how we defined $F$, $x_i \nleq x_j$. So $F_{ij} = f(x_i, x_j) = 0$. 
+\item
+The result follows directly from the definition of matrix multiplication. Let $i,j\leq n$ be given. Then:
+\begin{align*}
+(f * g)(x_i, x_j) &= \sum_{y \in X} f(x_i,y)g(y,x_j)\\
+&=FG_{ij}
+\end{align*}
+\end{enumerate}
+\end{proof}
+
+The \textbf{identity function} $\delta$ is defined by 
+\[\delta(a,b) = \begin{cases} 1 & a = b \\ 0 & else. \end{cases}
+\]
+\fi
 \end{document}

### 2017-04-06 Drafts/Draft.tex
Enriched categories etc

@@
 \documentclass[12pt]{pom_thesis}
+\usepackage[T1]{fontenc}
 \input{commands_packages}
@@
 \title{M\"obius Inversion: Construction and Applications}
-\renewcommand{\theequation}{\addtocounter{thm}{0}\thethm}
 \newcommand{\fix}{\text{fix }}
@@
 \DeclareMathOperator{\obj}{ob}
+\DeclareMathOperator{\im}{Im}
+\newcommand{\catname}[1]{\textbf{\textsc{#1}}}
+
+%\theoremstyle{plain}{
+%\newtheorem{thm}{Theorem}[chapter]
+%\newtheorem{lemma}[thm]{Lemma}
+%\newtheorem{prop}[thm]{Proposition}
+%\newtheorem{cor}[thm]{Corollary}
+%\newtheorem{conj}[thm]{Conjecture}
+%}
+
+%\theoremstyle{definition}{
+%\newtheorem{defn}[thm]{Definition}
+%\newtheorem{examp}[thm]{Example}
+%\newtheorem{rmk}[thm]{Remark}
+%\newtheorem{fact}[thm]{Fact}
+%}
 \begin{document}
@@
 The classical definition of a M\"obius function is a function $\mu$ on the positive integers which satisfies the following for functions $f,g$ on the positive integers:
-
 \begin{equation}\label{init_mob} 
-f(n) = \sum_{d | n} g(d) \iff g(n) = \sum_{d | n}  f(m)\mu\left(\frac dn\right)
+f(n) = \sum_{d | n} g(d) \iff g(n) = \sum_{d | n}  f(d)\mu\left(\frac dn\right)
 \end{equation}
@@
 Note that, for completeness, a poset should be labeled with both its elements and its relations - e.g. $(X, \leq)$. But often we just write $X$ when the relation is implied.
+\begin{rmk}
+Given $x_1, x_2$ in a poset $X$, we write $[x_1, x_2]$ to denote the set 
+\[
+\{y \in X: x_1 \leq y \leq x_2\}
+\]
+Replacing one of the square brackets with a parenthesis means we are omitting that element. So
+\begin{align*}
+[x_1, x_2) &= \{y \in X: x_1 \leq y < x_2\},\\
+(x_1, x_2] &= \{y \in X: x_1 < y \leq x_2\}.
+\end{align*}
+Note that if $x_1 \nleq x_2, [x_1, x_2] = [x_1, x_2) = (x_1, x_2]= \emptyset.$
+\end{rmk}
 \begin{defn}
@@
 This condition will be necessary for many of the following facts and theorems, to ensure that certain sums have a finite number of nonzero terms.
+Note that in a lower finite poset, $[x_1, x_2]$ is finite for any $x_1, x_2$.
 
@@
 Note that, because $X$ is lower finite, this sum has a finite number of terms, so is always finite-valued.
-Using the ``indicator" function $\zeta$ from above, we can rewrite the definition of $f$ to remove the need for the bound on the sum:
+Using the ``indicator'' function $\zeta$ from above, we can rewrite the definition of $f$ to remove the need for the bound on the sum:
 \begin{equation}\label{sum_form_intro}
@@
 
-If the matrix multiplication is explicitly written out, what we get is identical to \ref{sum_form_intro}. %TODO: Fix this numbering
+If the matrix multiplication is explicitly written out, what we get is identical to \eqref{sum_form_intro}.
 
@@
 \[
-g = g \zeta \iff g = f \mu.
+f = g \zeta \iff g = f \mu.
 \]
@@
 \begin{rmk}\label{sum_form}
-We can unpack the linear algebra to get a definition analagous to \ref{sum_form_intro}: We can say that $\mu$ is the unique function from $X\times X$ to $\Rr$ such that, for all $x,y \in X$,
-\[
-\sum_{z \in X} \mu(x,z)\zeta(z,y) = \delta(x,z) = \sum_{z \in X} \zeta(x,z)\mu(z,y).
+We can unpack the linear algebra to get a definition analagous to \eqref{sum_form_intro}: We can say that $\mu$ is the unique function from $X\times X$ to $\Rr$ such that, for all $x,y \in X$,
+\[
+\sum_{z \in X} \mu(x,z)\zeta(z,y) = \delta(x,y) = \sum_{z \in X} \zeta(x,z)\mu(z,y),
+\]
+or
+\[
+\sum_{z \leq y} \mu(x,z) = \delta(x,y) = \sum_{z \geq x} \mu(z,y).
 \]
@@
 For any positive integer $n$, the \emph{integer lattice of dimension $n$}, which we denote $\Nn^n$, is the set of ordered $n$-tuples of non-negative integers.
-For any two elements $(a_1,...,a_n), (b_1,...,b_n) \in \Nn^n$, we say that $(a_1,...,a_n)\leq (b_1,...,b_n)$ if $a_i \leq b_i$ for each $i = 1,\cdots,n$.
-\end{defn}
-\begin{rmk}
-$(\Nn^n, \leq)$ is a poset for any positive integer $n$. The axioms are easily checked.
-\end{rmk}
+For any two elements $(a_1,\dots,a_n), (b_1,\dots,b_n) \in \Nn^n$, we say that $(a_1,\dots,a_n)\leq (b_1,\dots,b_n)$ if $a_i \leq b_i$ for each $i = 1,\cdots,n$.
+\end{defn}
+\begin{lemma}
+$(\Nn^n, \leq)$ is a lower finite poset for any positive integer $n$. 
+\end{lemma}
+\begin{proof}
+The poset axioms are easily checked. We also observe that for any $x \in (\Nn^n, \leq)$,
+\[
+\#\{y \in (\Nn^n, \leq):y \leq x\} = \prod_{i =1}^n x_i.
+\]
+
+This is a finite product of integers, so is finite.
+\end{proof}
+
 We turn to several examples.
@@
 0 & a \nleq b\\
-\delta(a,b)-\sum_{a \leq c < b}\mu(a,c) & else.
+\delta(a,b)-\sum_{c \in [a,b)}\mu(a,c) & else.
 \end{cases}
@@
 \[
-\mu(a,b) = \delta(a,b)-\sum_{a \leq c < b}\mu(a,c).
+\mu(a,b) = \delta(a,b)-\sum_{c \in [a,b)}\mu(a,c).
 \]
@@
 \sum_{c \in X}\mu(a,c) \zeta(c,b) &= \delta(a,b)\\
-\sum_{a \leq c < b} \mu(a,c) + \mu(a,b) &= \delta(a,b)\\
-\mu(a,b) &= \delta(a,b) - \sum_{a \leq c < b} \mu(a,c) 
+\sum_{c \in [a,b)} \mu(a,c) + \mu(a,b) &= \delta(a,b)\\
+\mu(a,b) &= \delta(a,b) - \sum_{c \in [a,b)} \mu(a,c) 
 \end{align*}
@@
 
-\begin{lemma}\label{mu_lattice}
-Let $L$ be the $n$-dimensional integer lattice, with the usual poset relation.
-Let $X$ be a subset of $L$ such that if $x \in X, y \in L$, and $y \leq x$, then $y \in X$.
-Let $\zeta, \mu$ be defined as usual on $X$.
-Let $x=(x_1,...,x_n),y = (y_1,...,y_n)$ be elements of the lattice.
-Then:
+\begin{lemma}\label{int_lattice}
+Let $L$ be the $n$-dimensional integer lattice, with the usual poset relation. Let $\zeta, \mu$ be defined as usual on $L$. Let $x=(x_1,\dots,x_n),y = (y_1,\dots,y_n)$ be elements of $L$. Then:
 \[
@@
 
-\begin{proof} %TODO: Prove for general integer lattice
+\begin{proof}
 If $x \nleq y$, then by \ref{recurse}, $\mu(x,y) = 0$. This is the first case.
@@
 
-Suppose that we have \ref{mu_lattice} for any $x \leq y$ where $\sum_{i=1}^ny_i-x_i \leq k-1$. Let $x \leq y$ be fixed such that $\sum_{i=1}^ny_i-x_i =k$. If $\exists i \in \Nn: y_i-x_i \geq 2$
-
-If $\frac{n_0}{d_0}$ is not divisible by a square, then $\frac{n_0}{d_0} = p_1p_2\cdots p_{k+1}$, where the $p_i$ are distinct primes. Then there is a direct correspondence:
-\begin{center}$\{k : d_0|k, k|n_0, k\neq n_0\} \leftrightarrow$ \{Nonempty subsets of $\{p_1,\cdots,p_{k+1}\}$\},\end{center}
-where $k$ is obtained by multiplying the remaining prime factors by $m_0$, and the omitted prime factors can be determined by factoring $k$.
-
-This means that we can index the sum from \ref{recurse} using those subsets:
-\[
-\mu(m_0, n_0) = -\sum_{P \subsetneq \{1,\cdots,k+1\}} \mu(d_0, m_0\cdot \prod_{i \in P}p_i )
-\]
-Because $\frac{d_0\cdot \prod_{i \in P}p_i}{d_0} = \prod_{i \in P}p_i$ has $|P| < k + 1$ prime factors, we can apply the inductive hypothesis, which tells us that 
-\[
-\mu(d_0, md_0\cdot \prod_{i \in P}p_i = (-1)^{|P|}.
-\]
-So we can write
-\begin{align*}
-\mu(d_0, n_0) &= -\sum_{P \subsetneq \{1,\cdots,k+1\}} (-1)^{|P|}\\
-&= -\sum_{i = 1}^{k}(-1)^i{k+1 \choose i}\\
-&= (-1)^{k+1}
-\end{align*}
-with the final equality following from the alternating-sum binomial identity
-\[
-\sum_{1=1}^{k+1}(-1)^i{k+1 \choose i} = 0.
-\]
-Finally, we consider the case where $\frac {d_0}{n_0}$ has a squared factor. So we can write 
-\[
-\frac {d_0}{n_0} = p^2q
-\]
-where $p$ is prime, and $q$ is some other integer.
-Note that we can no longer use the previous argument, because the factors of $\frac {d_0}{n_0} = p^2q$ form a set with multiplicity rather than a simple set, so the sum will no longer have standard binomial coefficients.
-
-Let $r$ divide $d_0q$ and be divisible by $d_0$.
-So $\mu(d_0, r)$ is a term in the sum from \ref{recurse}.
-Note also that $rp$ divides $d_0qp$, so $\mu(d_0, rp)$ is also a term in the sum.
-By the inductive hypothesis, $\mu(d_0, rp) = -\mu(d_0, r)$, so the terms cancel.
-We can pair terms in this way to eliminate all divisors of $d_0pq$.
-The only remaining terms are of the form $\mu(d_0, d_0p^2k)$.
-But because $\frac{d_0p^2k}{d_0}$ is divisible by $p^2$, by the inductive hypothesis, these terms are all zero.
-So all terms in \ref{recurse} cancel, meaning that $\mu(d_0, n_0) = 0$.
-\end{proof}
-
-\section{Integers with Divisibility Ordering} %TODO: Change \Nn to \Nn^+
-We are now able to justify the existence of, and find, the function $\mu$ from equation \ref{init_mob}, with little work.
-
-We will consider the set $\Nn$ as a poset ordered by divisibility.
-For our purposes, $0 \notin \Nn$.
-Note that this poset is lower finite: For any number $n$, the set $\{q \in \Nn: q|n\} \subseteq \{q \in \Nn: q \leq n\}$, and the latter set contains $n$ elements, which is finite (note that $d|n$ means that $d$ divides $n$ without remainder).
+Suppose that we have \ref{int_lattice} for any $x \leq y$ where $\sum_{i=1}^ny_i-x_i \leq k-1$.
+Let $x \leq y$ be fixed such that $\sum_{i=1}^ny_i-x_i =k$.
+Suppose that for some $j \in \Nn, y_j-x_j \geq 2$.
+Let $y' = (y_1,\dots,y_j-1,\dots,y_n)$.
+Note that $x \leq y' < y$.
+So we can decompose the sum from $\ref{int_lattice}$.
+Let
+\begin{align*}
+\alpha &= \sum_{x \leq z \leq y'} \mu(x,z)\\
+\beta &= \sum_{y' < z < y}\mu(x,z).\\
+\end{align*}
+Then
+\begin{align*}
+\mu(x,y) &= -\sum_{x \leq z \leq y}\mu(x,z)\\
+&= -\sum_{x \leq z \leq y'} \mu(x,z) - \sum_{y' < z < y}\mu(x,z)\\
+&= -(\alpha + \beta).
+\end{align*}
+We note that
+\[\alpha = \sum_{z \in L} \mu(x,z)\zeta(z,y').
+\]
+So by \ref{sum_form}, $\alpha=0$.
+
+Recall that for all $i \neq j, y'_i = y_i$.
+This means that for any $z \in L$ where $z>y'$ and $y > z, z_j = y_j$.
+So $z_j-x_j \geq 2$.
+By the inductive hypothesis, this implies that $\mu(z,x)=0$.
+So all the terms of $\beta$ are zero, so $\beta=0$.
+This implies that \[\mu(z,y)=-(\alpha+\beta)=0.\]
+
+Finally, suppose that for all $i = 1,\dots,n, y_i-x_i \leq 1$.
+Because $\sum_{i=1}^ny_i-x_i =k$, there must be $k$ indices where $x$ and $y$ differ by one, while at the other $n-k$ indices they are equal.
+So for each $j = 0,\dots,k-1$, there are $k \choose j$ elements $z$ of $X$ where $x \leq z < y$ and $\sum_{i = 1}^n y_i-z_i = j$.
+For each of these, by the inductive hypothesis, $\mu(x,z) = (-1)^j$.
+So, using \ref{sum_form}, we can write
+\begin{align*}
+\mu(x,y)& = -\sum_{j = 1}^k {k \choose j} (-1)^j\\
+&= (-1)^k.
+\end{align*}
+\end{proof}
+This result will be powerful for determining values of $\mu$ on various posets whose structure is similar to an integer lattice. 
+\begin{thm}\label{mapping}
+Let $(X, \leq_X),(Y, \leq_Y)$ be lower finite posets. Let $x_1 \leq x_2 \in S$ be given. Suppose that there exists a bijective map
+\[
+\phi: [x_1, x_2] \leftrightarrow [\phi(x_1), \phi(x_2)]
+\]
+such that for all $z_1, z_2 \in [x_1, x_2]$,
+\[ 
+z_1 \leq_X z_2 \iff \phi(z_1) \leq_Y \phi(z_2).
+\] 
+Let $\mu_X, \mu_Y$ denote the M\"obius functions on $X$ and $Y$ respectively. Then:
+\[
+\mu_X(x_1, x_2) = \mu_Y(\phi(x_1), \phi(x_2)).
+\]
+\end{thm}
+This theorem tells us that if we can find a portion of a familiar poset which has identical structure to a portion of an unknown poset, we can transfer what we know about values of $\mu$ on that portion from one to the other.
+\begin{proof}
+We induct on $\#[x_1, x_2]$.
+Because $x_1 \leq x_2$, if $[x_1, x_2] = 1$, then $x_1 = x_2$.
+So by \ref{recurse}, $\mu_X(x_1, x_2) = 1$.
+Because $\phi(x_1) = \phi(x_2), \mu_Y(\phi(x_1), \phi(x)2) = 1$ also.
+
+Suppose the theorem is true if $\#[x_1, x_2] \leq k-1$ for some integer $k$. Fix $x_1, x_2$ such that $\#[x_1, x_2] = k$. Then by \ref{recurse},
+\[
+\mu_Y(\phi(x_1), \phi(x_2)) = -\sum_{y \in [\phi(x_1), \phi(x_2)]}\mu_Y(\phi(x_1), y)
+\]
+Because $\phi$ is an isomorphism which preserves $\leq$, we can rewrite this sum:
+\[
+\mu_Y(\phi(x_1), \phi(x_2)) = -\sum_{x \in [x_1, x_2]}\mu_Y(\phi(x_1), \phi(x))
+\]
+We can restrict $\phi$ to $[\phi(x_1), \phi(x)]$ to satisfy the hypotheses for all intermediate elements $x$. So we can apply the inductive hypothesis to all the terms of this sum:
+\begin{align*}
+\mu_Y(\phi(x_1), \phi(x_2)) &= -\sum_{x \in [x_1, x_2]}\mu_X(x_1, x)\\
+&= \mu_X(x_1, x_2)
+\end{align*}
+\end{proof}
+The following corollary follows immediately if we let $\phi$ be the inclusion map:
+\begin{cor}\label{subset}
+Let $X$ be a poset. Let $I$ be an interval in $X$. In other words, let $I = [z_1, z_2]$ for some $z_1, z_2 \in X$. Then
+\[
+\mu_I = \mu_X|_I.
+\]
+\end{cor}
+In the next section, we explore a poset where this fact will be extremely useful.
+
+\section{Integers with Divisibility Ordering}
+We are now able to justify the existence of, and find, the function $\mu$ from \eqref{init_mob}, with little work.
+
+We will consider the poset $(\Zz^{+}, |)$.
+This is the set of positive integers ordered by divisibility (recall that $d|n$ if $d$ divides $n$ without remainder).
+Note that this poset is lower finite: For any number $n$, the set $\{q \in \Zz^{+}: q|n\} \subseteq \{q \in \Zz^{+}: q \leq n\}$, and the latter set contains $n$ elements, which is finite (note that $d|n$ means that $d$ divides $n$ without remainder).
 This means we are able to use M\"obius inversion.
-
-We go through the usual steps of M\"obius inversion and apply \ref{mob_inv}:
-\begin{itemize}
-\item Let $\zeta: \Nn \times \Nn \rightarrow \Nn$ be defined as follows.
-\[
-\zeta(d,n) = \begin{cases}1 & d|n \\ 0 & else \end{cases}
-\]
-\item Let $\mu = \zeta^{-1}$ 
-\end{itemize}
-Then \ref{mob_inv} gives us:
-\[
-g(n) = \sum_{d | n} g(d) \iff g(n) = \sum_{d | n}  f(d)\mu(d,n)
-\]
-This is almost what we want, but not quite.
-Here $\mu$ is a function in two variables, while in \ref{init_mob} it is a function in a single variable.
-It turns out that values of $\mu(d,n)$ will only depend on $\frac nd$, which will gives us the desired form.
-To see that, we start by writing down a recursive form which works for any M\"obius function.
-
-\begin{lemma}\label{recurse}
-Let $X$ be a lower finite partially ordered set, and let $\zeta, \mu$ be defined as usual. Then for all $a, b \in X$,
-\[
-\mu(a,b) = 
-\begin{cases}
-0 & a \nleq b\\
-\delta(a,b)-\sum_{a \leq c < b}\mu(a,c) & else.
-\end{cases}
-\]
-\end{lemma}
-\begin{rmk}
-Note that the piecewise form is actually not necessary, because if $a \nleq b$ then the sum will be empty. So it is correct - albeit less clear- to just write
-\[
-\mu(a,b) = \delta(a,b)-\sum_{a \leq c < b}\mu(a,c).
-\]
-\end{rmk}
-\begin{proof}
-We fix $a,b$, and then rearrange terms starting from \ref{sum_form}:
-\begin{align*}
-\sum_{c \in X}\mu(a,c) \zeta(c,b) &= \delta(a,b)\\
-\sum_{a \leq c < b} \mu(a,c) + \mu(a,b) &= \delta(a,b)\\
-\mu(a,b) &= \delta(a,b) - \sum_{a \leq c < b} \mu(a,c) 
-\end{align*}
-\end{proof}
-We are now ready to write down $\mu$ in the context of the divisibility lattice poset.
-
-\begin{lemma}\label{nfact}
-Let $\zeta, \mu$ be defined as usual on $\Nn$ ordered by divisibility. Let $d,n \in \Nn$ be given.  Then:
+Rather than compute the M\"obius function directly, we can use \ref{int_lattice} and \ref{mapping} to reuse what we already know.
+
+\begin{thm}\label{mu_div}
+Let $\zeta, \mu$ be defined as usual on the poset $(\Zz^+, |)$. Then for all $d,n \in \Zz^+$,
 \[
@@
 \begin{cases}
-0 & d\nmid n\\
-0 & \exists p \in \Nn: p^2|(\frac nd )\\
-(-1)^{\#\{p \text{ prime}: p|\frac nd\}} & else
+0 & \nmid n \\
+0 & \exists p: p^2|\frac nd\\
+(-1)^{\#\{p|\frac nd : p \text{ prime}\}} & otherwise
 \end{cases}
 \]
-\end{lemma}
-This lemma gives us what we need - a way of writing values of $\mu$ in terms of a single variable. We will prove it by induction on the number of prime factors of $\frac nd$.
-\begin{proof} %TODO: Prove for general integer lattice
-If $d \nmid n$, then by \ref{recurse}, $\mu(d,n) = 0$. This is the first case.
-
-If $n = d$, then $\frac nd=1$ has zero prime factors. In that case, again by \ref{recurse}, $\mu(n,d) = 1$. This will be our base case for the second and third branches.
-
-Suppose that if $d|n$, and $\frac nd$ has $k$ prime factors (with multiplicity), then \ref{nfact} holds for $d$ and $n$.
-Suppose that $d_0|n_0$ and $\frac {n_0}{d_0}$ has $k+1$ prime factors.
-If $\frac{n_0}{d_0}$ is not divisible by a square, then $\frac{n_0}{d_0} = p_1p_2\cdots p_{k+1}$, where the $p_i$ are distinct primes.
-Then there is a direct correspondence:
-\begin{center}$\{k : d_0|k, k|n_0, k\neq n_0\} \leftrightarrow$ \{Nonempty subsets of $\{p_1,\cdots,p_{k+1}\}$\},\end{center}
-where $k$ is obtained by multiplying the remaining prime factors by $m_0$, and the omitted prime factors can be determined by factoring $k$.
-
-This means that we can index the sum from \ref{recurse} using those subsets:
-\[
-\mu(m_0, n_0) = -\sum_{P \subsetneq \{1,\cdots,k+1\}} \mu(d_0, m_0\cdot \prod_{i \in P}p_i )
-\]
-Because $\frac{d_0\cdot \prod_{i \in P}p_i}{d_0} = \prod_{i \in P}p_i$ has $|P| < k + 1$ prime factors, we can apply the inductive hypothesis, which tells us that 
-\[
-\mu(d_0, md_0\cdot \prod_{i \in P}p_i = (-1)^{|P|}.
-\]
-So we can write
-\begin{align*}
-\mu(d_0, n_0) &= -\sum_{P \subsetneq \{1,\cdots,k+1\}} (-1)^{|P|}\\
-&= -\sum_{i = 1}^{k}(-1)^i{k+1 \choose i}\\
-&= (-1)^{k+1}
-\end{align*}
-with the final equality following from the alternating-sum binomial identity
-\[
-\sum_{1=1}^{k+1}(-1)^i{k+1 \choose i} = 0.
-\]
-Finally, we consider the case where $\frac {d_0}{n_0}$ has a squared factor. So we can write 
-\[
-\frac {d_0}{n_0} = p^2q
-\]
-where $p$ is prime, and $q$ is some other integer.
-Note that we can no longer use the previous argument, because the factors of $\frac {d_0}{n_0} = p^2q$ form a set with multiplicity rather than a simple set, so the sum will no longer have standard binomial coefficients.
-
-Let $r$ divide $d_0q$ and be divisible by $d_0$.
-So $\mu(d_0, r)$ is a term in the sum from \ref{recurse}.
-Note also that $rp$ divides $d_0qp$, so $\mu(d_0, rp)$ is also a term in the sum.
-By the inductive hypothesis, $\mu(d_0, rp) = -\mu(d_0, r)$, so the terms cancel.
-We can pair terms in this way to eliminate all divisors of $d_0pq$.
-The only remaining terms are of the form $\mu(d_0, d_0p^2k)$.
-But because $\frac{d_0p^2k}{d_0}$ is divisible by $p^2$, by the inductive hypothesis, these terms are all zero.
-So all terms in \ref{recurse} cancel, meaning that $\mu(d_0, n_0) = 0$.
-\end{proof}
-Given \ref{nfact}, we can write $\mu(\frac nm)$ instead of $\mu(m,n)$. This allows us to use \ref{mob_inv} to arrive at \ref{init_mob}:
-\[
-f(n) = \sum_{m | n} g(m) \iff g(n) = \sum_{m | n}  f(m)\mu\left(\frac mn\right).
-\]
-\section{Euler's Totient}
+\end{thm}
+
+\begin{proof}
+Let $d,n \in \Zz^+$ be given.
+We set up the isomorphism required for \ref{mapping}: Index the primes $p_1, p_2, \dots$.
+So $p_1=2, p_2=3$, and so on.
+Let $k$ be the index of the largest prime which divides either $d$ or $n$.
+Then let $\phi : [d,n] \rightarrow \Nn^k$ be defined by
+\[
+ p_1^{x_1}p_2^{x_2}\cdots p_k^{x_k} \mapsto (x_1, \cdots, x_k).
+\]
+We claim that $\phi$ is a bijection from $[d,n]$ to $\im(\phi)$.
+
+Because prime factorizations are unique, this map is well-defined and injective.
+Let $m_1, m_2 \in [d,n]$ be given.
+Then $m_1|m_2$ if and only if the multiplicity of each prime $p_i$ in the factorization of $m_1$ is equal to or smaller than $p_i$'s multiplicity in the factorization of $m_2$.
+This is equivalent to checking whether or not $\phi(m_1)_i \leq \phi(m_2)_i$, which is the definition of $\leq$ on $\Nn^k$.
+So this map preserves $\leq$.
+This implies that $\im(\phi) \subseteq [\phi(d), \phi(n)]$, which allows us to check the final condition, surjectivity.
+
+Let $x = (x_1,...,x_k) \in [\phi(d), \phi(n)]$ be given.
+Then $\phi(p_1^{x_1}\cdots p_k^{x_k}) = x$.
+By above, because $\phi$ preserves $\leq$, $p_1^{x_1}\cdots p_k^{x_k} \in [d,n]$.
+So $x \in \im(\phi)$.
+
+So $\phi:[d,n] \leftrightarrow [\phi(d), \phi(n)]$ is a bijection.
+
+This allows us to use \ref{mapping}, and the result immediately follows.
+\end{proof}
+
+This definition of $\mu$ depends only on $\frac nd$, which means that we can abuse notation to write $\mu(\frac nd)$ instead of $\mu(d,n)$.
+This allows us to use \ref{mob_inv} to arrive at \eqref{init_mob}:
+\[
+f(n) = \sum_{d | n} g(d) \iff g(n) = \sum_{d | n}  f(d)\mu\left(\frac nd\right).
+\]
+\section{Euler's Totient} %TODO: Fix \Zz^+
 Euler's Totient is a famous function in number theory, which counts the how many numbers are relatively prime to a particular value.
@@
 \end{proof}
-This sum gives us a value we have access to ($n$) in terms of a sum of values we want.
+This sum gives us a value we have access to ($n$) in terms of a sum of values we want (values of $\varphi$).
 This is a perfect situation to apply M\"obius inversion, and undo that sum.
-We apply \ref{init_mob}, which tells us
+We apply \eqref{init_mob}, which tells us
 \[
@@
 \]
+Recall that \ref{mu_div} tells us how to write down values of $\mu$.
 Depending on what information we have access to, this might be much easier than just counting the number of values relatively prime to $n$.
@@
 \[
-\left|\bigcup_{i \in K}A_i\right| = \sum_{J \subseteq K}(-1)^{|J|}\left|\bigcap_{i \in J}A_j\right|
+\left|\bigcup_{i \in K}A_i\right| = \sum_{\emptyset \neq J \subseteq K}(-1)^{|J| + 1}\left|\bigcap_{i \in J}A_j\right|
 .\]
 \end{thm}
-\section{Proof using Mobius Inversion}
-There are many proofs of this well-known fact.
-We will show it using M\"obius inversion.
-This means we will need a poset.
+\section{Proof using M\"obius Inversion} %TODO: Motivate
+There are many proofs of this well-known fact. We will show it using M\"obius inversion. This means we will need a poset.
+
+\begin{defn}
+For any set $X$, the \emph{power set} of $X$, denoted by $\ps(X)$, is the set of subsets of $X$. 
+\end{defn}
+\begin{rmk}\label{power_poset}
+Let $I$ be a finite set. Then $(\ps(X), \supseteq)$ is a lower finite partially ordered set.
+\end{rmk}
+Note that the poset from \ref{power_poset} is ordered by reverse inclusion rather than simple inclusion. The poset axioms are easily checked.
+
 Throughout this section, we will have the following setup: Let $S$ be a finite set.
 Let $I$ be a finite index set, and for all $i \in I$, let $A_i \subseteq S$.
-We will be manipulating functions on subsets of $I$, so this will be our poset.
-We start by formalizing that:
-
-\begin{defn}
-For any set $I$, the \emph{power set} of $I$, denoted by $\ps(I)$, is the set of subsets of $I$. 
-\end{defn}
-\begin{rmk}\label{power_poset}
-Let $I$ be a finite set. Then $(\ps(I), \supseteq)$ is a partially ordered set.
-\end{rmk}
-Note that the poset from \ref{power_poset} is ordered by reverse inclusion rather than simple inclusion. The poset axioms are easily checked.
+We will be manipulating functions on $(\ps(I), \supseteq)$, so this will be our poset.
 
@@
 The difficulty arises from counting elements multiple times.
-For example, if we knew that the $A_i$ were disjoint, we could say
-\[
-\left|\bigcup_{i \in K}A_i\right| = \sum_{i \in K}\left|A_i\right|.
+For example, if we knew that the $A_i$ were disjoint, we could just consider
+\[
+\sum_{i \in K}\left|A_i\right|.
 \]
 But, because intersections of the $A_i$ might be nonempty, this sum might count some elements multiple times.
-In order to solve this problem, we suppose that we have access to \emph{intersections} (but not unions) of the $A_i$ (it is apparent that this is required to use \ref{iep}).
+We must approach the problem more carefully.
 First, we define the following indicator function $\chi: s \rightarrow \ps(I)$ by:
@@
 \end{itemize}
-Based on these definitions, we can observe certain relationships, which will start to point the way for using M\"obius inversion:
+Finally, we recall that our goal is to find the union of the $A_i$ for $i$ in some given $K$. To that end, we observe that
+\[
+\left| \bigcup_{i \in J=K} A_i \right| = |S| - \hat{f}(K).
+\]
+
+In order to find $\hat{f}$, we suppose that we have access to \emph{intersections} (but not unions) of the $A_i$ (it is apparent that this is required to use \ref{iep}).
+This means that we have access to $f$.
+
+We can observe certain relationships, which will start to point the way for using M\"obius inversion:
 \begin{align*}
@@
 \end{align*}
-
-Finally, we recall that our goal is to find the union of the $A_i$ for $i$ in some given $J$. To that end, we observe that
-\[
-\left| \bigcup_{i \in J} A_i \right| = |S| - \hat{f}(J).
-\]
-So if we are able to write down values of $\hat{f}$, we're done.
+Using these relationships, we can:
+\begin{enumerate}
+\item Use $f$ to find $g$ by using M\"obius inversion to invert the sum;
+\item Translate from $g$ to $\hat{g}$; and
+\item Use $\hat{g}$ to determine $\hat{f}$.
+\end{enumerate}
+
+Let $\zeta$ be defined as usual on $(\ps(I), \supseteq)$. So let $\zeta:\ps(I) \times \ps(I) \rightarrow \Rr$ be defined by
+\[
+\zeta(J,K) = \begin{cases} 1 & J \supseteq K \\ 0 & \text{otherwise}. \end{cases}
+\]
+
+Also, we define the \emph{complement} function/matrix $c$ as follows:
+\[
+c(J,K) = \begin{cases} 1 & J = K^c \\ 0 & \text{otherwise}. \end{cases}
+\]
+Note that by definition, $c(J,K) = c(K,J)$. So $c$ is symmetric. We also observe that $c^2 = I$, so $c$ is self-inverse.
+
+Using $\zeta$ and $c$, we can rewrite the relationships between the functions:
+\begin{align*}
+f &= g\zeta\\
+\hat{f} &= \hat{g}\zeta\\
+g &= \hat{g}c\\
+\hat{g} &= gc
+\end{align*}
+The complement matrix is readily accessible and self-inverse, so we are able to move easily between $g$ and $\hat{g}$.
+It is also straightforward to determine $\hat{f}$ from $\hat{g}$ using $\zeta$.
+The only remaining step is to determine $g$ using $f$.
+As usual, we use M\"obius inversion to reverse multiplication by $\zeta$.
+
+Let $\mu = \zeta^{-1}$ (as usual, we mean the matrix inverse). Then we can add the following important fact, using \ref{mob_inv}:
+\[
+g = f\mu.
+\]
+Putting it all together, we can write $\hat{f}$ in terms of $f$ step-by-step:
+\begin{align*}
+\hat{f} &= \hat{g}\zeta\\
+&= gc\zeta\\
+&= f\mu c\zeta.
+\end{align*}
+In a sense, we are done.
+We have determined how to find unions of sets of $A_i$ using $\hat{f}$, and we have written $\hat{f}$ in terms of values we have access to.
+But with a bit more work, we can show that what we have derived is really the inclusion-exclusion principle.
+The first step is to interpret values of $\mu$.
+We will again use \ref{int_lattice} and \ref{mapping}.
+
+\begin{thm}
+Let $\mu$ be defined as above. Then for all $J, K \in \ps(I)$,
+\[
+\mu(J,K) = 
+\begin{cases}
+0 & J \not\supseteq K\\
+(-1)^{|K|-|J|} & \text{otherwise}.
+\end{cases}
+\]
+\end{thm}
+The idea is that $\ps(I)$ can be viewed as a subset of the $|I|$-dimensional integer lattice, where all the coordinates are either ones or zeros, with a one corresponding to an element being present in a subset and a zero corresponding with that element being absent.
+This is the idea behind the bijection we will set up.
+\begin{proof}
+Label the elements of $I$, so that $I = \{\iota_1, \dots, \iota_{|I|}\}$.
+Let $\Nn^{|I|}$ be the integer lattice of dimension $|I|$.
+Let $X$ be the subset of $\Nn^{|I|}$ consisting of the points with all coordinates either zero or one.
+Let $\phi:X \rightarrow \ps(I)$ be defined as follows:
+\[
+\phi(x_1, \dots, x_{|I|}) = \{\iota_w : x_w = 0\}
+\]
+There are a variety of things we must check to use \ref{mapping}.
+\begin{itemize}
+\item $X = [(0,\dots,0), (1,\dots,1)] \subset \Nn^{|I|}$, so $X$ is an interval, as required.
+\item Let $J \subseteq I$ be given. Then we can construct an element of $X$ which maps to $J$ by setting the appropriate elements to zeros and ones. So $\phi$ is surjective on $\ps(I)$. 
+\item Distinct elements of $X$ map to distinct subsets of $I$. So $\phi$ is injective. 
+\item It is straightforward to check that $\phi(x) \leq_{\ps(I)} \phi(y) \iff x \leq_{\Nn^{|I|}} y$.
+\end{itemize}
+This means that \begin{align*}
+\mu_{\ps(I)}(J,K) &= \mu_{\Nn^{|I|}}(\phi(J), \phi(K)) \\
+&= \begin{cases}
+0 & J \not\supseteq K\\
+(-1)^{|K|-|J|} & \text{otherwise}
+\end{cases}
+\end{align*}
+\end{proof}
+This allows us to determine values of $\mu$. Given that we know $f, c$, and $\zeta$, we are now ready to determine $\hat{f}$.
+
+Recall that our goal is to determine 
+\[
+\left| \bigcup_{i \in J} A_i \right|,
+\]
+and that earlier we observed that
+\begin{align*}
+\left| \bigcup_{i \in J} A_i \right| &= |S| - \hat{f}(J)\\
+&= |S| - (f\mu c\zeta)(J).
+\end{align*}
+We consider the $J,K$ entry of $\mu c \zeta$.
+First we take the dot product of row $J$ of $\mu$ with column $K$ of $c$.
+Recall that column $K$ of $c$ is zero everywhere except in the row corresponding to $K^c$.
+So $(\mu c)(J,K) = \mu(J, K^c)$.
+
+Now we must consider the dot product of row $J$ of $(\mu c)$ and column $K$ of $\zeta$.
+Recall that $\zeta(L,K)$ is equal to one if and only if $L \supseteq K$, and zero otherwise.
+So, putting it all together:
+\begin{align*}
+(\mu c \zeta)(J,K) &= \sum_{L \supseteq K} \mu(J, L^c)\\
+&= \sum_{L \subseteq K^c} \mu(J, L) &\text{re-indexing the sum}\\
+\end{align*}
+Finally, we would like to multiply this on the left by $f$ to obtain $\hat{f} = f\mu c\zeta$. Expanding the dot product and rearranging, we have
+\begin{align*}
+f\mu c\zeta(K) &= \sum_{J \in \ps(I)} f(J) \sum_{L \subseteq K^c} \mu(J,L)\\
+&= \sum_{J \supseteq L} \sum_{L \subseteq K^c} (-1)^{|J|-|L|} f(J)\\
+&= \sum_{J \in \ps(I)}\left( \sum_{L \subseteq K^c \cap J}(-1)^{|J| - |L|} \right) f(J)\\
+&= \sum_{J \in \ps(I)}\left( \sum_{L \subseteq K^c \cap J}\mu(\emptyset, L)\right) (-1)^{|J|}f(J)
+\end{align*}
+We now apply \ref{sum_form} to simplify the inner sum and insert the definition of $f$:
+\begin{align*}
+\hat{f}(K) &= f\mu c\zeta(K) \\
+&=  \sum_{J \in \ps(I)}(\delta(\emptyset, K^c \cap J)(-1)^{|J|} )f(J)\\
+&= \sum_{J \subseteq K}(-1)^{|J|}f(J)\\
+&= \sum_{J \subseteq K}(-1)^{|J|}\left| \bigcap_{i \in J} A_i\right|\\
+\end{align*}
+Recall that 
+\[
+\left| \bigcup_{i \in K} A_i \right| = |S| - \hat{f}(K).
+\]
+So we can arrive at \ref{iep}:
+\begin{align*}
+\left| \bigcup_{i \in K} A_i \right| &= |S| - \sum_{J \subseteq K}(-1)^{|J|}\left| \bigcap_{i \in J} A_i\right|\\
+&= \sum_{\emptyset \neq J \subseteq K}(-1)^{|J| + 1}\left|\bigcap_{i \in J}A_j\right|.
+\end{align*}
 \section{Generalizations}
-%TODO: Connect with integer divisibility
 
 \end{chapter}
-\begin{chapter}{Metric Space Magnitude}
-\section{Motivation: Clustering}
-The \emph{magnitude} of a metric space is a notion introduced in \cite{Lein2}. %TODO: Finish introduction
-\section{Important Definitions} \label{mag_defs}
+\begin{chapter}{Euler Characteristic of a Category}\label{chap_euler}
+\section{Introduction to Categories} \label{cat_defs}
+
+A category is an algebraic structure which generalizes ``objects'' and ``maps'' (or ``morphisms''), with composition.
+There are several equivalent definitions, all somewhat technical, but the construct itself is quite intuitive once you get used to it.
+\begin{defn}
+A \textit{category} $C$ consists of:
+\begin{itemize}
+\item A collection $C_0$ of \emph{objects};
+\item For each $a,b \in C_0$, a collection $C(a,b)$ of \emph{morphisms from $x$ to $y$};
+\item For each $a,b,c \in C_0$, a \emph{composition operator}: A function $\circ_{abc} :C(a,b) \times C(b,c) \rightarrow C(a,c)$ (note that we usually omit the subscript, because they can be inferred); and
+\item For each $a \in C_0$, an \emph{identity morphism} $1_a \in C(a,a)$,
+\end{itemize}
+such that the following axioms are satisfied:
+\begin{itemize}
+\item Composition is associative: If $a,b,c,d \in C_0$ and $f\in C(a,b), g \in C(b,c), h \in C(c,d)$, then $f \circ (g \circ h) = (f \circ g) \circ h$, and
+\item Composition respects identities: If $a,b \in C_0, f \in C(a,b)$, then $1_b \circ f = f = f \circ 1_a$.
+\end{itemize}
+\end{defn}
+Note that we sometimes use function notation to write morphisms.
+So if $f \in C(a,b)$, we might right $f:a \rightarrow b$.
+We also often write $x \in C$ rather than $x \in C_0$ for an object $x$ of $C$, although technically $C$ is the entire category while $C_0$ is the set of objects.
+
+Categories are extremely general constructions.
+Note that we did not even insist that the collection of objects in a category is a set, which allows us consider ``larger'' categories such as the category of sets.
+We consider that example here:
+\begin{examp}
+If $f:X \rightarrow Y, g:Y\rightarrow Z$ are functions, then $g \circ f$ exists, and function composition is associative.
+So we can let \catname{set} be the category of all sets, with a morphism between sets $X,Y$ for each map $X \rightarrow Y$.
+\end{examp}
+A \emph{small} category is a category whose collection of objects is a set.
+
+We present several examples.
+\begin{examp}
+Let $G$ be a group. Then we can represent $G$ as a category $C$ as follows: 
+\begin{itemize}
+\item Let $C_0 = \{*\}$, a single object
+\item Let $C(*, *) = G$. In other words, let the set of morphisms from $*$ to $*$ be equal to the set of group elements. 
+\item Use the group operation for multiplication. In other words, if $g,h \in C(*,*)$, then, because $g,h \in G$, we can write $gh$. So let $g \circ h = gh$. 
+\end{itemize}
+It is straightforward to check that $C$ is indeed a category. 
+\end{examp}
+
+\section{M\"obius Inversion on a Category}
+
+To define M\"obius inversion on a partially ordered set, we used an ``indicator function'' which was notated as $\zeta$.
+We will henceforth refer to this function as $\zeta'$, reserving $\zeta$ for a function we are about to define on categories.
+Recall that for $a,b$ in a poset $X$, $\zeta'(a,b)$ was defined to be 1 if $a \leq b$, and 0 otherwise.
+We would like to define something similar on categories.
+It turns out that categories are generalizations of partially ordered sets - any poset can be represented using a category.
+
+Given a poset $X$, we can construct a category by letting $C_0=X$, and adding a single morphism from elements $a,b \in C_0$ if and only if $a \leq b \in X$. We formalize this:
+
+\begin{defn}\label{cat_poset}
+Let $(X, \leq)$ be a poset.
+Let $C$ be the category whose objects are elements of $X$, and where for any pair of elements $a,b \in X$, the set $C(a,b)$ contains one morphism if $a \leq b$, and zero otherwise.
+Then $C$ is the \emph{poset category of $X$}, which we will refer to as $\cat(X)$.
+\end{defn}
+Then $\cat(X)$ is a category for any poset $X$.
+The identity requirement follows from reflexivity of posets, and because pairs of elements have at most one morphism between them, we do not need to specify the composition operators.
+
+To do M\"obius inversion, we need a function/matrix $\zeta$.
+We would like the $\zeta$ arising from $\cat(X)$ to be the same as the one arising from $X$.
+Motivated by that intuition, we define $\zeta$ as follows.
+Note that it is not clear what a ``lower finite'' category would look like, so we restrict ourselves to finite categories.
+
+\begin{defn}
+Let $C$ be a finite category. Then define $\zeta : C \times C \rightarrow \Rr$ by 
+\[
+\zeta(a,b) = |C(a,b)|.
+\]
+\end{defn}
+So $\zeta$ simply counts the number of morphism from $a$ to $b$.
+In $\cat(X)$, there is one morphism if $a \leq b \in X$ and zero otherwise.
+So $\zeta(a,b) = \zeta'(a,b)$ (note that here $a,b \in C$ and also $a,b \in X$).
+
+What is unclear at this point is what the purpose is of doing M\"obius inversion on a category.
+It is not clear what kind of sum we are attempting to reverse - unlike the poset case, we don't know why we would want to reverse the operation of multiplying by $\zeta$.
+It turns out that inverting $\zeta$ (if we are able to) will allow us to calculate what is called the \emph{Euler-Leinster characteristic} of a category, which is the analog of an Euler characteristic on other structures.
+We will explore this over the next few sections.
+First, we finish the definition of the M\"obius function on categories.
+
+\begin{defn}\label{cat_mob} 
+Let $C$ be a finite category. Let $\zeta$ be as defined above. Then the \emph{M\"obius function} $\mu$ on $C$, if it exists, is defined by 
+\[
+\mu = \zeta^{-1}.
+\]
+Equivalently, $\mu$ is the function which, for all $x,y \in C$, satisfies
+\[
+\sum_{z \in X} \mu(x,z)\zeta(z,y) = \delta(x,z) = \sum_{z \in X} \zeta(x,z)\mu(z,y).
+\]
+If such a $\mu$ exists, $C$ is said to \emph{have M\"obius inversion} or to \emph{admit M\"obius inversion}.
+\end{defn}
+Note that $\mu$ may not exist. Unlike in the poset case, we have no way of ensuring that $\zeta$ is upper triangular or invertible. For example:
+\begin{examp}
+Let $C$ be the category with two objects $a$ and $b$, with exactly one morphism going each direction between $a$ and $b$, and with no other morphisms except the required identity morphisms.
+We can draw this category:
+\[
+\includegraphics{../Figures/cat_2.pdf}
+\]
+Note that whenever we draw a category, we omit the identity morphisms.
+They are implied, and serve only to clutter the diagram.
+We also omit implied compositions of morphisms.
+In this case, because the identity morphisms are the only elements of $C(a,a)$ and $C(b,b)$, it must be that the two drawn morphisms compose to the identity morphisms.
+
+We observe $\zeta$ defined on $C$ is
+\[\begin{bmatrix}1 & 1 \\ 1 & 1 \end{bmatrix}.\]
+This is not an invertible matrix. So this simple category does not admit M\"obius inversion.
+\end{examp}
+
+\section{Euler-Leinster Characteristic of a Category}
+We are now ready to construct central definition of this section: the Euler-Leinster characteristic (or just Euler characteristic) of a category.
+The entire construction can be found in \cite{Lein1, Lein2, Lein4}.
+
+Throughout this section, objects declared as categories are implicitly allowed to be either ordinary categories or generalized metric spaces.
+The definition of $\zeta$ from section \ref{cat_defs} will be assumed.
+
+\begin{defn}
+A \emph{weighting} on a category $\Aa$ is a function $w_a$ on $\obj(\Aa)$ such that for all $a \in \Aa$,
+\[
+\sum_b \zeta(a,b)\omega_b = 1.
+\]
+\end{defn}
+
+\begin{lemma}
+\label{mobius_is_weighting}
+If $\Aa$ has M\"obius inversion, then $\omega_a = \sum_b \mu(a,b)$ is a weighting on $\Aa$.
+\end{lemma}
+\begin{proof} For all $a \in \Aa$,
+\begin{align*}
+\sum_b \zeta(a,b)\omega_b &= \sum_b\left( \zeta(a,b)\sum_c \mu(b,c)\right)\\
+&=\sum_b\sum_c\zeta(a,b)\mu(b,c)\\
+&=\sum_c\left(\sum_b\zeta(a,b)\mu(b,c)\right)\\
+&=\sum_c \delta(a,c)\\
+&=1.
+\end{align*}
+\end{proof}
+
+This is important.
+It provides a way in which we can write down weightings on metric spaces, since the similarity matrix $\zeta$ is invertible in many cases.
+We will investigate exactly which cases when we discuss positive semidefinite matrices.
+
+The following definition is due to \cite{Lein1}.
+\begin{defn}\label{cat_euler}
+Let $\omega$ be a weighting on a finite category $A$. Then the \emph{Euler-Leinster characteristic}, or just the \emph{Euler characteristic}, of $A$, denoted by $\chi(A)$, is defined by
+\[
+\chi(A) = \sum_{a \in A} \omega_a
+\]
+\end{defn}
+Note that even if a category admits several weightings, they all lead to the same Euler characteristic by a simple sum rearrangement argument.
+Together with \ref{mobius_is_weighting}, this implies the following:
+\begin{cor}\label{euler_mu}
+If a finite category $A$ has a M\"obius inversion $\mu$, then
+\[\chi(A) = \sum_{a \subseteq A} \sum_{b \subseteq A} \mu(a, b).
+\]
+\end{cor}
+
+\section{Simplicial Complexes}
+Calling a new construction an Euler characteristic needs some intuitive justification.
+We will introduce a structure called a \textit{simplicial complex} to show that calling this value an Euler characteristic is reasonable.
+
+The most elementary form of an Euler characteristic is the version defined on polyhedrons: Vertices minus edges plus faces.
+As a result, it is common to think of the Euler characteristic as a value defined on geometric objects.
+A simplicial complex is a generalization of a polyhedron into higher dimensions.
+We use this construction because it has a natural notion of an Euler characteristic, which is consistent with the common one, and yet also is easily connected with categories.
+We start with the definition:
+
+\begin{defn}
+Let $V$ be a set.
+A \emph{simplicial complex} $\sigma$ over $V$ is a set of finite, non-empty subsets of $V$, called \emph{simplices} or \emph{cells}, such that, if $\alpha \in \sigma$ and $\emptyset \neq \beta \subset \alpha$, then $\beta \in \sigma$.
+\end{defn}
+
+Put another way, a simplicial complex over $V$  is a set of subsets of $V$ which is closed under taking subsets, with the exception of the empty subset.
+
+If a set in a simplicial complex $\sigma$ has $k$ elements, we call it a \emph{$k-1$-simplex} or a \emph{$k-1$-cell}.
+We think of 0-cells as vertices, 1-cells as edges, 2-cells as faces, etc.
+This will become much clearer with some examples.
+\begin{examp}
+Let $V=\{a,b\}, \sigma_2 = \{\{a\},\{b\}, \{a,b\}\}$. Then $\sigma_2$ is a simplicial complex over $V$. We visualize $\sigma_2$ as follows:
+\[
+\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
+
+\node[label = above:{$\{a\}$}, circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](1) at (0,0) {};
+\node[label = above:{$\{b\}$}, circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](2) at (3,0) {};
+
+\draw[-latex] (1) -- (2) node[midway, above = 3pt] {$\{a,b\}$};
+
+\end{tikzpicture}\]
+Because $\{a\} \subseteq \{a,b\}$, the vertex $\{a\}$ is an endpoint of the line $\{a,b\}$.
+Because $\sigma_2$ is closed under taking subsets, as all simplicial complexes must be, the line has both its endpoints.
+\end{examp}
+Going forward, when writing down simplicial complexes, we will not explicitly write down the set $V$ - it will implicitly be the set of all elements used in the simplicies.
+We will also omit the braces around the subsets to reduce clutter.
+So we would write $\sigma_2 = \{a,b,ab\}$.
+
+We saw in the previous example why it is that lines always have both their endpoints in the geometric representation of a simplicial complex.
+For the same reason, faces have all three edges.
+But the converse is not necessarily true - the outline of a triangle, for example, might exists without the triangle being filled.
+\begin{examp}
+Let $\sigma = \{a, b, c, d, ab, ac, bc, bd, cd, abc\}$. Then we draw $\sigma$ as follows:
+\[
+\includegraphics[scale = 1.3]{../Figures/simp_1.pdf}
+\]
+\end{examp}
+As these examples illustrate, a $k$-simplex, or a simplex with $k+1$ elements, is considered to be a $k$-dimensional feature.
+
+The goal of this construction was to justify our definition of the Euler characteristic of a category. To do that, we need to define the Euler characteristic of a simplicial complex.
+\begin{defn}
+Let $\sigma$ be a simplicial complex. Then the \emph{Euler characteristic} of $\sigma$, denoted by $\chi(\sigma)$, is equal to
+\[
+\sum_{\tau \in \sigma}(-1)^{|\tau|}.
+\]
+\end{defn}
+Note that this is a distinct (although related) definition to \ref{cat_euler}, yet we use $\chi$ for both. Which we mean will be determined by what kind of object we are applying $\chi$ to.
+
+This definition is consistent with the definition of the Euler characteristic of a polyhedron: If the largest cells of a simplicial complex are 2-cells, or two-dimensional faces, then the definitions are identical.
+
+It turns out that there is a straightforward way of converting a simplicial complex into a category.
+We will find that the Euler-Leinster characteristic of the resulting category will be the same as the Euler characteristic of the simplicial complex.
+\begin{defn}
+Let $\sigma$ be a simplicial complex.
+Then the \emph{category generated by $\sigma$}, or $\cat(\sigma)$, is the category whose objects are the cells of $\sigma$.
+If $\gamma$ and $\omega$ are cells of $\sigma$, then $|(\gamma, \omega)| = 1$ if $\gamma \subseteq \omega$ and 0 else.
+\end{defn}
+Note that a simplicial complex can be converted into a poset, where the cells are ordered by inclusion.
+Recall that we also defined $\cat(X)$ for a poset $X$ in \ref{cat_poset}.
+If $\sigma$ is a simplicial complex, and $X$ is the corresponding poset, then $\cat(\sigma) = \cat(X)$.
+
+The notation for $\cat(\sigma)$ is a little tricky.
+If $\sigma$ is a simplicial complex, and $\alpha \in \sigma$ is a simplex, then we write $\cat(\alpha)$ to denote the object in $\cat(\sigma)$ corresponding with the simplex $\alpha \in \sigma$.
+We consider an example.
+\begin{examp}
+Let $\sigma = \{a, b, ab\}$. Then we can draw $\sigma, \cat(\sigma)$:
+\[
+\includegraphics{../Figures/simp_cat.pdf}
+\]
+\end{examp}
+Recall that we omit identity morphisms when drawing a category.
+
+To prove that this operation preserves the Euler characteristic, we start with two lemmas about $\mu$, the M\"obius function on a category.
+First, recall that categories do not necessarily admit M\"obius inversion.
+So $\mu$, a priori, might not exist on a given category.
+However, the following lemma will rule this possibility out in the case of the category generated by a simplicial complex.
+\begin{lemma}\label{mu_exists}
+Let $\sigma$ be a simplicial complex. Then $\cat(\sigma)$ admits M\"obius inversion.
+\end{lemma}
+\begin{proof}
+Totally order the simplices of $\sigma$ respecting the partial order of number of elements (so if $\alpha, \beta \in \sigma$ and $|\alpha| < |\beta|$, then $\alpha < \beta$ in the total order).
+Write down the matrix $\zeta$ with the rows and columns in that order.
+Then $\zeta$ will be upper triangular, so it will be invertible.
+So $\mu = \zeta^{-1}$ exists.
+\end{proof}
+Now that we know $\mu$ exists, we can inductively determine its value, similarly to how we have done so in previous sections with M\"obius functions on partially ordered sets.
+\begin{lemma}
+\label{mu_lemma}
+Suppose $\sigma$ is a simplicial complex, and $\alpha \subseteq \beta$ are simplices in $\sigma$.
+Let $\mu$ denote the M\"obius function on $\cat(\sigma)$.
+Then $\mu(\cat(\alpha), \cat(\beta)) =(-1)^{|\beta - \alpha|} = (-1)^{|\alpha|} (-1)^{|\beta|}$ (note that $|\alpha|$ simply denotes the size of $\alpha$ as a set).
+\end{lemma}
+\begin{proof}
+We use induction. Base case: $\alpha = \beta$, and $\mu(\alpha, \beta)=1$.
+
+For the inductive step, suppose that if $|\beta-\alpha| \leq k$, the result is true.
+
+Suppose that $|\beta - \alpha| = k+1$. We know by \ref{cat_mob} that, because $\alpha \neq \beta$,
+ \begin{align*}
+\sum_{\alpha \subseteq \sigma \subseteq \beta} \mu(\alpha, \sigma)&= 0\\
+\mu(\alpha, \beta) &=  - \sum_{\alpha \subseteq \sigma \subset \beta} \mu(\alpha, \sigma)\\
+&= - \sum_{\gamma \subset (\beta - \alpha)} \mu(\alpha, \gamma \cup \alpha) 
+\end{align*}
+Note that the above unions are always disjoint. So, by the inductive hypothesis, we can rewrite it:
+\begin{align*}
+\mu(\alpha, \beta) &= - \sum_{\gamma \subset (\beta - \alpha)'} (-1)^{|\gamma \cup \alpha - \alpha|} \\ %& \text{inductive hypothesis}\\
+&= - \sum_{\gamma \subset (\beta - \alpha)'} (-1)^{|\gamma|}\\ % &\text{by disjointness}\\
+\end{align*}
+We can add and subtract $(-1)^{|\beta - \alpha|}$ and apply a binomial identity to finish the proof:
+\begin{align*}
+\mu(\alpha, \beta) &= - \sum_{\gamma \subseteq (\beta - \alpha)} (-1)^{|\gamma|} + (-1)^{|\beta - \alpha|} \\ 
+&= (-1)^{|\beta - \alpha|} -  \sum_{i = 0}^{|\beta - \alpha|}(-1)^i{|\beta- \alpha| \choose i}\\ 
+&= (-1)^{|\beta - \alpha|} \\ 
+\end{align*}
+\end{proof}
+We are now ready to prove that the two definitions of the Euler characteristic coincide.
+\begin{thm}
+\label{consistentEuler}
+Let $\sigma$ be a simplicial complex. Then 
+\[
+\chi(\cat(\sigma)) = \chi(\sigma).
+\]
+
+\end{thm}
+\begin{proof}
+Recall that by \ref{cat_euler}, 
+\[
+\chi(\cat(\sigma)) = \sum_{\gamma \in \sigma} \sum_{\alpha \in \sigma} \mu(\cat(\alpha), \cat(\gamma)).
+\]
+We know that if $\alpha \not \subseteq \gamma, \mu(\alpha, \gamma) = 0$. So
+\[
+\chi(\cat(\sigma)) = \sum_{\gamma \in \sigma} \sum_{\emptyset \neq \alpha \subseteq \gamma}\mu(\cat(\alpha), \cat(\gamma)).
+\]
+So we have
+\begin{align*}
+\chi(\cat(\sigma)) &= \sum_{\gamma \in \sigma} \sum_{\emptyset \neq \alpha \subseteq \gamma}\mu(\cat(\alpha), \cat(\gamma))\\
+&= \sum_{\gamma \in \sigma} \sum_{\emptyset \neq \alpha \subseteq \gamma}(-1)^{|\gamma| - |\alpha|} &\text{by \ref{mu_lemma}}\\
+&= \sum_{\gamma \in \sigma}(-1)^{|\gamma|} \sum_{i = 1}^{|\gamma|} (-1)^i{|\gamma| \choose i}\\
+&= \sum_{\gamma \in \sigma} (-1)^{|\gamma|} \\
+&= \chi(\sigma)
+\end{align*}
+\end{proof}
+The fact that $\chi(\cat(\sigma)) = \chi(\sigma)$ is comforting. It justifies calling using $\chi$ in \ref{cat_euler}, and calling this construction a type of Euler characteristic.
+
+\section{Euler-Leinster Characteristic Examples}
+
+\end{chapter}
+\begin{chapter}{Metric Space Magnitude}\label{chap_magnitude}
+\section{Motivation: Hierarchical Clustering}
+A common task in data analysis is clustering.
+Given a set of data points, it is often desirable to decide how many ``groups'' those data points fall into.
+Of course, there is usually no clear-cut definition of which points are in groups and which are not.
+
+The most straightforward way to cluster points is based on some notion of distance between them.
+If we assign a distance to each pair of points, then we can cluster points which are close together.
+But there is often no clear threshold for which points are and aren't close enough together to be in the same cluster.
+It all depends on the scale of structure we are looking for.
+One common technique for avoiding choosing a scale is what is called \emph{hierarchical clustering}.
+
+The idea of hierarchical clustering is that instead of choosing a scale, we capture the data's structure at a variety of scales:
+
+\[
+\includegraphics[width = 0.5\paperwidth] {../Figures/multiscale_structure.png}
+\]
+
+We can see that here that as we ``zoom out'', the structure of this data changes.
+First the data has first eight clusters of one point each, then four clusters of two points, and finally two clusters of four points.
+If we kept going, we would end up with a single cluster containing all of the points.
+
+There are many methods of hierarchal clustering.
+In the above example, explicit clusters are formed by grouping points which are near each other.
+We will explore an alternate method of clustering, which does not actually construct clusters, but instead estimates the number of clusters using a real, rather than integer, value.
+We will use a generalization of the Euler-Leinster characteristic from chapter \ref{chap_euler}.
+We start by building some important definitions.
+
 A metric space is a space with a notion of distance between pairs of points. 
@@
 \end{defn}
-A category is an algebraic structure which generalizes ``objects" and ``maps" (or ``morphisms"), with composition.
-There are several equivalent definitions, all somewhat technical, but the construct itself is quite intuitive once you get used to it.
-\begin{defn}
-A \textit{category} $C$ consists of:
-\begin{itemize}
-\item A collection $C_0$ of \emph{objects};
-\item For each $a,b \in C_0$, a collection $C(a,b)$ of \emph{morphisms from $x$ to $y$};
-\item For each $a,b,c \in C_0$, a \emph{composition operator}: A function $\circ:C(a,b) \times C(b,c) \rightarrow C(a,c)$; and
-\item For each $a \in C_0$, an \emph{identity morphism} $1_a \in C(a,a)$,
-\end{itemize}
-such that the following axioms are satisfied:
-\begin{itemize}
-\item Composition is associative: If $a,b,c,d \in C_0$ and $f\in C(a,b), g \in C(b,c), h \in C(c,d)$, then $f \circ (g \circ h) = (f \circ g) \circ h$, and
-\item Composition respects identities: If $a,b \in C_0, f \in C(a,b)$, then $1_b \circ f = f = f \circ 1_a$.
-\end{itemize}
-\end{defn}
-%TODO: Add examples
-This is a definition of what is usually called a category, but here we will refer to it as an \emph{ordinary} category.
-This is because it will also be useful to mention a generalization of categories, called \emph{enriched categories}.
+
+In almost all forms of hierarchical clustering, we represent data as a metric space.
+Here, we will actually define a slightly different structure which will be quite similar to a metric space, and use that instead.
+However, it's useful to keep in mind this more fundamental definition of a set with distance.
+
+In the next section, we expand the Euler-Leinster characteristic to a generalization of categories called \emph{enriched categories}.
+We will connect this back to data and metric spaces in subsequent sections.
+\section{Enriched Categories}
+In chapter \ref{chap_euler}, we defined a structure called a category.
+It turns out that this construction - which we will now call an \emph{ordinary} category - can be generalized further, to become an \emph{enriched} category.
 The idea is that we replace the sets of morphisms with objects from an ordinary category of a certain type, and adapt the definition of composition accordingly.
-We will be using a particular kind of enriched category, called a \textit{generalized metric space}.
-
-It's not necessary to fully understand how generalized metric spaces are categories - every space we consider here will be a bona fide metric space.
-Furthermore, the definitions and constructions we explore will be easy to apply directly to metric spaces.
+
+%TODO: Fix Furthermore, the definitions and constructions we explore will be easy to apply directly to metric spaces.
 I point out that this construction is a type of category to justify dealing with them together with other categories in the next section.
@@
 
-The full definition of enriched categories is complicated, technical, and not necessary here.
-For a full discussion of enriched categories, see \cite{Kelly1}.
-We will instead directly define a particular enriched category object called a \emph{generalized metric space}.
+In order to define the next construction, we need to define a notion of isomorphism between objects in a category.
 \begin{defn}
-A \emph{generalized metric space} $C$ consists of:
+Let $C$ be an ordinary category. Let $x,y \in C$ be two of $C$'s objects. Suppose that $f \in C(a,b), g \in C(b,a)$ are morphisms such that $g \circ f = 1_x, f \circ g = 1_y$. Then we say
 \begin{itemize}
-\item A collection $M$ of points (or objects); and
-\item For each $a,b \in M$, a non-negative real number $d(a,b)$, such
+\item $f = g^{-1}, g = f^{-1}$
+\item $f$ and $g$ are \emph{inverses} of each other
+\item $f$ and $g$ are both \emph{isomorphisms}
+\item $f \cong g$
+\item $a$ and $b$ are \emph{isomorphic}.
 \end{itemize}
-such that, for all $a,b \in M$,
-\[C(a,a) = 0,\hspace{1cm} C(a,b) + C(b,c) \geq C(a,c).
-\]
-\end{defn}
-Note that this is essentially the same as a metric space, but without the restriction that distinct points have nonzero distance, and without the requirement of symmetry.
+\end{defn}
+
+If two objects $a$ and $b$ are isomorphic, then for any morphism to or from either $a$ or $b$, we can use the isomorphisms to construct an ``equivalent'' map to or from the other object.
+As a result, $a$ and $b$ are equivalent in nearly every way.
+The next several definitions will replace requirements for - for example - associativity with requiring associativity up to isomorphism.
+This is common in category theory, and makes definitions more versatile, although it also makes them seem much more complicated at first.
+
+\begin{defn}
+A \emph{monoidal category} is an ordinary category $A$, together with
+\begin{itemize}
+\item A \emph{monoidal product} $\otimes : A \times A \rightarrow A$;
+\item A \emph{unit object} $u \in A$;
+\end{itemize}
+such that
+\begin{itemize}
+\item For each ordered triple of objects $x,y,z \in A$, $(x \otimes y) \otimes z \cong x \otimes (y \otimes z)$
+\item For each $x \in A$, $u \otimes x \cong x \cong x \otimes u$,
+\end{itemize} 
+and all the isomorphisms commute appropriately.
+\end{defn}
+There are a variety of commutation requirements which we are not considering in detail here. For a full account, see \cite{Kelly1}.
+
+We turn to several examples of monoidal categories.
+\begin{examp}
+The category $\catname{set}$ is the prototypical example of a monoidal category.
+In that case, the monoidal product $\otimes$ is the tensor product on sets (hence the notation $\otimes$ for the monoidal product), and $u = \{*\}$, some set with a single element.
+
+Here, we can consider what the required isomorphisms look like.
+It's required that for any set $X \in \catname{set}, \{*\} \otimes X \cong X$.
+Elements of $\{*\} \otimes X$ are of the form $(*, x)$ for $x \in X$.
+Also recall that an isomorphism is an invertible morphism, and that in \catname{set}, morphisms are just maps.
+So, because $|X| = |\{*\} \otimes X|$, the two sets are isomorphic in \catname{set}.
+The associativity isomorphisms are similar.
+\end{examp}
+\begin{examp}\label{cat_real}
+A monoidal category which will be very important here is $\Rr^{\geq 0}$, where there is exactly one morphism $f \in \Rr(a,b)$ if $a \geq b$.
+The monoidal product is addition, and the unit object is 0.
+The requirements are easily checked.
+We will refer to this category as $D$, because soon it will be used to represent distances.
+
+In this case, there are no need for isomorphisms, because for any $a,b,c \in \Rr^{\geq 0}, (a + b) + c = a + (b + c)$, and $0 + a = a = a + 0$.
+A monoidal category like this, where all the associativity and identity isomorphisms are the identity, is called a \emph{strict} monoidal category.
+In fact, in $D$, no two distinct elements are isomorphic.
+\end{examp}
+We are now ready to partially define an important generalization on ordinary categories.
+This definition is highly technical, and a full understanding of it is not necessary for this investigation.
+So we will not spend much time exploring examples or intuition beyond the specific applications we need.
+\begin{defn}\label{en_cat}
+Let $M$ be a monoidal category. Then a \emph{category enriched by $M$} consists of
+\begin{itemize}
+\item A set $C_0$ of objects;
+\item For each $a,b \in C_0$, an \emph{object of morphisms} $C(a,b) \in M$;
+\item For each $a,b,c \in C_0$, a \emph{composition morphism} $\circ_{abc}:  (C(b,c) \otimes  C(a,b)) \rightarrow  C(a,c)$;
+\item For each $a \in C_0$, an \emph{identity element morphism} $i_a : u \rightarrow C(a,a)$, where $u$ is the unit object in $M$,
+\end{itemize}
+such that all the $i_1, \circ_{abc}$ commute appropriately.
+\end{defn}
+As with ordinary categories, we usually will omit the subscripts on the composition morphisms. They will be implied by context.
+\begin{rmk}
+For a full discussion of enriched categories, including a complete description of the commutation requirements, see \cite{Kelly1}. 
+\end{rmk}
+
+\section{Norms and Magnitude}
+
+\begin{defn}\label{gen_met}
+Let $D$ be the monoidal category of non-negative real numbers defined in example \ref{cat_real}. Let $C$ be a category enriched over $D$. Then we call $C$ a \emph{generalized metric space}.
+\end{defn}
+It can be difficult to untangle the definitions involved in enriched categories.
+Luckily, because of the simplicity of $D$, we can simplify the definition of a generalized metric space to one which does not depend on the definition of an enriched category.
+\begin{thm}\label{direct_def}
+A generalized metric space $C$ can be defined equivalently by the following:
+\begin{itemize}
+\item A collection $C_0$ of points (or objects); and
+\item For each ordered pair $a,b \in C_0$, a non-negative real number $C(a,b)$
+\end{itemize}
+such that, for all $a,b \in C_0$,
+\[C(a,a) = 0,
+\]
+\[\hspace{1cm} C(a,b) + C(b,c) \geq C(a,c).
+\]
+\end{thm}
+\begin{proof}
+We will start with the definition from \ref{gen_met}, and argue that it is equivalent to the above.
+As defined originally, a generalized metric space consists of a set of objects $C_0$, with a non-negative real number $C(a,b)$ between any ordered pair of elements $a,b \in C_0$.
+So what remains is to show that the composition requirements from \ref{en_cat} are equivalent to the conditions in \ref{direct_def}.
+
+Let $C$ be a generalized metric space as defined in \ref{gen_met}.
+Then \ref{en_cat} requires that there be a morphism $i_a:0 \rightarrow C(a,a)$ for any $a \in C$.
+This exists if and only if $C(a,a) \leq 0$, which is equivalent to saying that $C(a,a)=0$.
+So the existence of $i_a$ for all $a$ is equivalent to the first requirement above.
+
+It is also required that for any $a,b,c \in C$, there is a map $\circ_{abc}: C(b,c) + C(a,b) \rightarrow C(a,c)$.
+This is equivalent to saying that $C(b,c) + C(a,b) \geq C(a,c)$, which is the second requirement.
+So the definitions are indeed identical.
+\end{proof}
+
+This makes it clear why we call this construction a generalized metric space.
+It is a metric space, but without the restriction that distinct points have nonzero distance, and without the requirement of symmetry.
 Relaxing these constraints allows us to cleanly express this as an enriched category.
-In keeping with the intuitive description of enriched categories which I gave earlier, this is a category where sets of morphisms are replaced by non-negative real numbers.
-The two axioms are enforced by details in the definition of an enriched category which I swept under the rug.
-
-For those who are interested in the details, what we are doing is letting $\mathcal{V}$ be the monoidal category whose set of objects is $\Rr^{\geq 0}$, with a single morphism from $a$ to $b$ if and only if $a \leq b$, and with addition (+) as the monoid operator.
-Then a generalized metric space is a category enriched with $\mathcal{V}$.
-
-We will soon be interested in a notion of how close together things are - and it will need to measure closeness rather than distance, in the sense that it will increase for objects which are closer together.
+
+%TODO: Probably remove
+We are interested in a notion of how close together things are - and it will need to measure closeness rather than distance, in the sense that it will increase for objects which are closer together.
 The reason for this will become clear soon.
-We will call this binary function $\zeta$, and define it on a category $C$ as follows: For $a,b \in C_0$, if $C$ is an ordinary category, then $\zeta(a,b) = |C(a,b)|$, or the size of the set of morphisms from $a$ to $b$.
-If $C$ is a generalized metric space, then $\zeta(a,b) = e^{-C(a,b)}$.
+We do this by defining $\zeta$ appropriately: If $C$ is a generalized metric space, then $\zeta(a,b) = e^{-C(a,b)}$.
 
@@
 Exponentiating is the most natural way to translate multiplication into addition, so we can apply the axiom.
-\section{M\"obius Inversion on a Category}
-To define M\"obius inversion on a partially ordered set, we used an "indicator function" which was - not coincidentally - notated as $\zeta$.
-We will henceforth refer to this function as $\zeta'$, reserving $\zeta$ for the function we just defined on categories.
-Recall that for $a,b$ in a poset $X$, $\zeta'(a,b)$ was defined to be 1 if $a \leq b$, and 0 otherwise.
-We would like to generalize the construction of M\"obius inversion.
-The first step is to observe the following: Given a poset $X$, we can construct an "equivalent" category by letting $C_0=X$, and adding a single morphism from elements $a,b \in C_0$ if and only if $a \leq b \in X$.
-It is easily checked that this is in fact a category, and that for each triplet in $C_0$ there is only one possible composition operator (this is why we don't bother to explicitly define them).
-
-The key fact here is that for $a,b \in C_0 = X, \zeta(a,b) = \zeta'(a,b)$. This motivates the following definition:
-\begin{defn}\label{cat_mob} %TODO: Check uniqueness
-Let $C$ be a category. Let $\zeta$ be as defined above. Then the \emph{M\"obius function} on $C$, if it exists, is a function $\mu$ which, for all $x,y \in C$, satisfies
-\[
-\sum_{z \in X} \mu(x,z)\zeta(z,y) = \delta(x,z) = \sum_{z \in X} \zeta(x,z)\mu(z,y).
-\]
-If such a $\mu$ exists, $C$ is said to \emph{have M\"obius inversion}. %TODO: Connect back, use matrix version
-\end{defn}
-\section{Euler Characteristic of a Category}
-\subsection{Definition}
-We are now ready to construct central definition of this section: the Euler characteristic of a category. The entire construction can be found in \cite{Lein1, Lein2, Lein4}.
-
-Throughout this section, objects declared as categories are implicitly allowed to be either ordinary categories or generalized metric spaces.
-The definition of $\zeta$ from section \ref{mag_defs} will be assumed.
-
-\begin{defn}
-A \emph{weighting} on a category $\Aa$ is a function $w_a$ on $\obj(\Aa)$ such that for all $a \in \Aa$,
-\[
-\sum_b \zeta(a,b)\omega_b = 1.
-\]
-\end{defn}
-
-\begin{lemma}
-\label{mobius_is_weighting}
-If $\Aa$ has M\"obius inversion, then $\omega_a = \sum_b \mu(a,b)$ is a weighting on $\Aa$.
-\end{lemma}
-\begin{proof} For all $a \in \Aa$,
-\begin{align*}
-\sum_b \zeta(a,b)\omega_b &= \sum_b\left( \zeta(a,b)\sum_c \mu(b,c)\right)\\
-&=\sum_b\sum_c\zeta(a,b)\mu(b,c)\\
-&=\sum_c\left(\sum_b\zeta(a,b)\mu(b,c)\right)\\
-&=\sum_c \delta(a,c)\\
-&=1.
-\end{align*}
-\end{proof}
-
-This is important.
-It provides a way in which we can write down weightings on metric spaces, since the similarity matrix $\zeta$ is invertible in many cases.
-We will investigate exactly which cases when we discuss positive semidefinite matrices.
-
-The following definition is due to \cite{Lein1}.
-\begin{defn}
-Let $\omega$ be a weighting on a finite category $A$. Then the \emph{Euler characteristic} of $A$, denoted by $\chi(A)$, is defined by
-\[
-\chi(A) = \sum_{a \in A} \omega_a
-\]
-\end{defn}
-Note that even if a category admits several weightings, they all lead to the same Euler characteristic by a simple sum rearrangement argument.
-Together with \ref{mobius_is_weighting}, this implies the following:
-\begin{cor}
-If a finite category $A$ has a M\"obius inversion $\mu$, then
-\[\chi(A) = \sum_{a \subseteq A} \sum_{b \subseteq A} \mu(a, b).
-\]
-\end{cor}
-
-\subsection{Simplicial Complexes}
-Calling a new construction an Euler characteristic needs some intuitive justification.
-We will a structure called a \textit{simplicial complex} to show that calling this value an Euler characteristic is reasonable.
-
-%TODO: Define simplicial complex
-
-\begin{defn}
-Let $\sigma$ be a simplicial complex.
-Then the \emph{category generated by $\sigma$}, or $\cat(\sigma)$, is the category whose objects are the cells of $\sigma$.
-If $\gamma$ and $\omega$ are cells of $\sigma$, then $|(\gamma, \omega)| = 1$ if $\gamma \subseteq \omega$ and 0 else.
-\end{defn}
-\begin{lemma}
-\label{mu_lemma}
-Suppose $\alpha \subseteq \beta$ are cells of a simplicial complex. Then $\mu(\cat(\alpha), \cat(\beta)) =(-1)^{|\beta - \alpha|} = (-1)^{|\alpha|} (-1)^{|\beta|}$.
-\end{lemma}
-\begin{proof}
-We use induction. Base case: $\sigma = \beta$, \checkmark \\
-For any simplex $\sigma$, let $\sigma'$ be $\sigma \cup \emptyset$. Suppose that $|\beta - \alpha| = k+1$. We know that \begin{align*}
-\mu(\alpha, \beta) &=  - \sum_{\alpha \subseteq \sigma \subset \beta} \mu(\alpha, \sigma)\\
-&= - \sum_{\gamma \subset (\beta - \alpha)'} \mu(\alpha, \gamma \cup \alpha) 
-\end{align*}
-Note that the above unions are always disjoint. So, by the inductive hypothesis, we can rewrite it:
-\begin{align*}
-\mu(\alpha, \beta) &= - \sum_{\gamma \subset (\beta - \alpha)'} (-1)^{|\gamma \cup \alpha| - |\alpha|} \\ %& \text{inductive hypothesis}\\
-&= - \sum_{\gamma \subset (\beta - \alpha)'} (-1)^{|\gamma|}\\ % &\text{by disjointness}\\
-&= - \sum_{\gamma \subseteq (\beta - \alpha)} (-1)^{|\gamma|} + (-1)^{|\beta - \alpha|} - (-1)^0 \\ %&\text{Removing the empty simplex and including $\gamma = \beta - \alpha$}\\
-&= \chi(\beta - \alpha) + (-1)^{|\beta - \alpha|} - (-1)^0\\
-&= 1-1+ (-1)^{|\beta - \alpha|}\\
-&= (-1)^{|\beta - \alpha|}
-\end{align*}
-
-\end{proof}
-\begin{thm}
-\label{consistentEuler}
-Let $\sigma$ be a simplicial complex. Then 
-\[
-\sum_{\gamma \subseteq \sigma} \sum_{\alpha \subseteq \gamma} \mu(\alpha, \gamma) = \chi(\sigma).
-\]
-
-\end{thm}
-\begin{proof}
-
-\begin{align*}
-\sum_{\gamma \in \sigma} \sum_{\alpha \subseteq \gamma} \mu(\alpha, \gamma) &= \sum_{\gamma \in \sigma} \sum_{\emptyset \subset \alpha \subseteq \gamma} \mu(\alpha, \gamma)\\
-&= \sum_{\gamma \in \sigma} \mu(\emptyset, \gamma)\\
-&= \sum_{\gamma \in \sigma} (-1)^{|\gamma|} &\text{by \ref{mu_lemma}}\\
-&= \chi(\sigma)
-\end{align*}
-\end{proof}
-This implies the comforting fact that $\chi(\cat(\sigma)) = \chi(\sigma)$.
-\section{Metric Space Magnitude}
-\subsection{Motivation: Hierarchical Clustering}
-\subsection{Idea and Definition}
-\subsection{Product Spaces}
-\subsection{Examples}
+\section{Product Spaces and Approximations}
+\section{Examples}
 \end{chapter}

### 2017-04-07 Drafts/Draft.tex
magnitude

@@
 \begin{defn}
-Let $C$ be a finite category. Then define $\zeta : C \times C \rightarrow \Rr$ by 
+Let $C$ be a finite category. Then define the \emph{similarity matrix} or \emph{similarity function} $\zeta : C \times C \rightarrow \Rr$ by 
 \[
@@
 \begin{defn}\label{cat_mob} 
-Let $C$ be a finite category. Let $\zeta$ be as defined above. Then the \emph{M\"obius function} $\mu$ on $C$, if it exists, is defined by 
+Let $C$ be a finite category. Let $\zeta$ be the similarity matrix defined above. Then the \emph{M\"obius function} $\mu$ on $C$, if it exists, is defined by 
 \[
@@
 Note that $\mu$ may not exist. Unlike in the poset case, we have no way of ensuring that $\zeta$ is upper triangular or invertible. For example:
-\begin{examp}
+\begin{examp}\label{2_pt}
 Let $C$ be the category with two objects $a$ and $b$, with exactly one morphism going each direction between $a$ and $b$, and with no other morphisms except the required identity morphisms.
@@
 
-Throughout this section, objects declared as categories are implicitly allowed to be either ordinary categories or generalized metric spaces.
-The definition of $\zeta$ from section \ref{cat_defs} will be assumed.
-
-\begin{defn}
-A \emph{weighting} on a category $\Aa$ is a function $w_a$ on $\obj(\Aa)$ such that for all $a \in \Aa$,
-\[
-\sum_b \zeta(a,b)\omega_b = 1.
-\]
-\end{defn}
+\begin{defn}\label{def_weighting}
+A \emph{weighting} on a category $\Aa$ is a function $\omega$ on $\obj(\Aa)$ such that for all $a \in \Aa$,
+\[
+\sum_{b \in C}|C(a,b)|\omega(b) = 1,
+\]
+or, equivalently, if
+\[
+\sum_{b \in C}\zeta(a,b)\omega(b) = 1.
+\]
+\end{defn}
+
+One of the first questions we ask when we see this definition is how we can write find valid weightings.
+Luckily, this definition looks familiar.
+We have a value we know (1) expressed as the sum of function we are seeking ($\omega$).
+So we can use M\"obius inversion!
+The situation is slightly more complicated, because we don't know for sure that $\zeta$ is invertible.
+We formalize that:
 
@@
 \label{mobius_is_weighting}
-If $\Aa$ has M\"obius inversion, then $\omega_a = \sum_b \mu(a,b)$ is a weighting on $\Aa$.
+If $C$ has M\"obius inversion, then the weighting $\omega_\mu$ defined by $\omega_\mu(a) = \sum_b \mu(a,b)$ is a weighting on $C$.
 \end{lemma}
-\begin{proof} For all $a \in \Aa$,
-\begin{align*}
-\sum_b \zeta(a,b)\omega_b &= \sum_b\left( \zeta(a,b)\sum_c \mu(b,c)\right)\\
+\begin{proof} For all $a \in C$,
+\begin{align*}
+\sum_b \zeta(a,b)\omega_\mu(b) &= \sum_b\left( \zeta(a,b)\sum_c \mu(b,c)\right)\\
 &=\sum_b\sum_c\zeta(a,b)\mu(b,c)\\
@@
 
+Note that even if $C$ does not admit M\"obius inversion, it might admit a weighting.
+For example, the category in example \ref{2_pt} admits the weighting $\omega(a) = \omega(b) = 0.5$, even though it does not admit M\"obius inversion.
+
 This is important.
@@
 \[
-\chi(A) = \sum_{a \in A} \omega_a
+\chi(A) = \sum_{a \in A} \omega(a)
 \]
@@
 Then the \emph{category generated by $\sigma$}, or $\cat(\sigma)$, is the category whose objects are the cells of $\sigma$.
-If $\gamma$ and $\omega$ are cells of $\sigma$, then $|(\gamma, \omega)| = 1$ if $\gamma \subseteq \omega$ and 0 else.
+If $\alpha$ and $\beta$ are cells of $\sigma$, then $|(\alpha, \beta)| = 1$ if $\alpha \subseteq \beta$ and 0 else.
 \end{defn}
@@
 \[
-\includegraphics[width = 0.5\paperwidth] {../Figures/multiscale_structure.png}
+\includegraphics[width = 0.4\paperwidth] {../Figures/multiscale_structure.png}
 \]
@@
 
-\section{Norms and Magnitude}
-
+\section{Norms and the Euler-Leinster Characteristic}
+The following constructions can be found in \cite{Lein4}.
+
+We would like to generalize the weightings and Euler-Leinster characteristic from chapter \ref{chap_euler} so we can use them on enriched categories.
+Recall that in \ref{def_weighting}, we used the function $\zeta$ to require that for $\omega$ to be a weighting on a category $C$, for all $a \in C$,
+\[
+\sum_{b \in C}|C(a,b)|\omega(b) = 1.
+\]
+
+The problem is that given an enriched category over some monoidal category $M$, for a pair $a,b$, $C(a,b)$ is no longer a set but an element of $M$.
+So it is no longer possible to use the function $|\cdot|$ as defined on sets.
+Instead, we must define our own \emph{norm} function on $M$.
+We define this as follows:
+\begin{defn}
+Let $(M,\otimes)$ be a monoidal category. Then the function $| \cdot |: M \rightarrow \Rr$ is a \emph{norm} on $M$ if, for any $a,b\in M$, and if $u$ is the unit object of $M$, it satisfies
+\[
+|a \otimes b| = |a||b|,
+\]
+\[
+|u| = 1.
+\]
+\end{defn}
+
+The usual cardinality function on the monoidal category \catname{set} does satisfy these requirements - for any two finite sets $A,B, |A \otimes B| = |A||B|$, and $|\{*\}|=1$.
+
+It's not clear why we require that the norm function be multiplicative. %TODO: If I get into products, discuss. Add more examples of norms
+
+We can consider some examples of norms.
+\begin{examp}
+Let $D$ be the monoidal category of non-negative real numbers defined in example \ref{cat_real}. Then, for all $t \in \Rr$, the function $|\cdot|:D \rightarrow \Rr$ defined by 
+\[
+|x| = e^{-tx}
+\]
+is a norm on $D$.
+
+We will explore this norm in detail shortly.
+\end{examp}
+
+Now that we know how to replace the norm function on sets, we can redefine the $\zeta$ function, M\"obius inversion, weightings, and the Euler-Leinster characteristic on enriched categories.
+We go through these definitions, and then we will explore their ramifications.
+\begin{defn}
+Let $C$ be a finite category enriched over a monoidal category $M$. Suppose that $|\cdot|$ is a norm on $M$. Then we define the similarity matrix $\zeta$ on $C$ by
+\[
+\zeta_{|\cdot|}(a,b) = |C(a,b)|.
+\]
+\end{defn}
+
+\begin{defn}
+Let $C$ be a finite category enriched over a monoidal category $M$.
+Let $|\cdot|$ be a norm on $M$, and let $\zeta_{|\cdot|}$ be the similarity matrix defined above.
+Then the M\"obius function on $C$, denoted $\mu_{|\cdot|}$, is defined by
+\[
+\mu_{|\cdot|} = \zeta_{|\cdot|},
+\]
+if $\zeta$ is invertible. If $\mu$ exists, we say that $C$ admits M\"obius inversion.
+\end{defn}
+
+\begin{defn}
+Let $C$ be a finite category enriched over a monoidal category $M$, with a specificed norm $|\cdot|$. Then $\omega$ is a \emph{weighting} on $C$ if, for all $a \in C$, 
+\[
+\sum_{b \in C}|C(a,b)|\omega(b) = 1,
+\]
+or, equivalently, if
+\[
+\sum_{b \in C}\zeta_{|\cdot|}(a,b)\omega(b) = 1.
+\]
+\end{defn}
+
+\begin{defn}
+Let $C$ be a finite category enriched over a monoidal category $M$, with a specified norm $|\cdot|$.
+Let $\omega$ be a weighting on $C$.
+Then the \emph{Euler-Leinster characteristic} of $C$, denoted $\chi_{|\cdot|}(C)$, is defined by
+\[
+\chi_{|\cdot|}(C) = \sum_{a \in c} \omega(a).
+\]
+\end{defn}
+In the notation just introduced, we will sometimes omit the subscripts specifying the norm, if the norm is implied.
+\begin{rmk}
+When $C$ is an enriched category, $\chi(C)$ is sometimes called the \emph{magnitude} of $C$ (for example, in \cite{Lein4}).
+We reserve that terminology for a particular class of enriched categories which we will soon introduce, and continue to refer to the general construction as the Euler-Leinster characteristic or the Euler characteristic of $C$.
+\end{rmk}
+\begin{rmk}
+As before, it is easy to show by rearranging terms that the value of $\chi_{|\cdot|}(C)$ is independent of the specific weighting chosen.
+However, it does depend on the norm we choose.
+This will become very important later.
+\end{rmk}
+%TODO: Examples of euler characteristics of non-metric space enriched categories
+
+\section{Magnitude}
+Recall that the motivation for this section was data clustering.
+So we would like to use the technology from the previous section to process data in the form of a metric space.
+We will use a particular enriched category for that purpose, called a \emph{generalized metric space}.
+This is a category enriched over a monoidal category whose objects are non-negative real numbers, allowing us to preserve a notion of distance.
 \begin{defn}\label{gen_met}
@@
 \end{defn}
-It can be difficult to untangle the definitions involved in enriched categories.
+There is a lot of technology buried in that definition, and it can be difficult to untangle the definitions involved in enriched categories.
 Luckily, because of the simplicity of $D$, we can simplify the definition of a generalized metric space to one which does not depend on the definition of an enriched category.
@@
 
-%TODO: Probably remove
+Generalized metric spaces are, of course, more general than ordinary metric spaces.
+So we can always express a metric space as a generalized metric space.
+This allows us to find the Euler-Leinster characteristic of a finite set of data points in a metric space.
+But first we must decide on the norm we will use on $D$, our monoidal category, and to do that, we take a step back and consider why we are doing this.
+
 We are interested in a notion of how close together things are - and it will need to measure closeness rather than distance, in the sense that it will increase for objects which are closer together.

### 2017-04-08 Drafts/Draft.tex
figures

@@
 \item A collection $C_0$ of \emph{objects};
-\item For each $a,b \in C_0$, a collection $C(a,b)$ of \emph{morphisms from $x$ to $y$};
+\item For each $a,b \in C_0$, a set $C(a,b)$ of \emph{morphisms from $x$ to $y$}, sometimes called the \emph{hom-set} of $(a,b)$;
 \item For each $a,b,c \in C_0$, a \emph{composition operator}: A function $\circ_{abc} :C(a,b) \times C(b,c) \rightarrow C(a,c)$ (note that we usually omit the subscript, because they can be inferred); and
@@
 \end{cor}
-
+%TODO: Think of category w/ no euler char
 \section{Simplicial Complexes}
@@
 
-\begin{defn}
+\begin{defn}\label{def_monoid}
 A \emph{monoidal category} is an ordinary category $A$, together with
@@
 \item For each $x \in A$, $u \otimes x \cong x \cong x \otimes u$,
+\item The function $\otimes$ is \emph{functorial}.
+This essentially means that if $x_1, x_2, y_1, y_2 \in M, f \in C(x_1, x_2), g \in C(y_1, y_2)$, then there exists a corresponding morphism in $C(x_1 \otimes y_1, x_2 \otimes y_2)$.
+We call that morphism $f \otimes g$, and require that it behave as we would expect (e.g.
+if $f,g$ are both isomorphisms, $f \otimes g$ also is).
 \end{itemize} 
-and all the isomorphisms commute appropriately.
-\end{defn}
-There are a variety of commutation requirements which we are not considering in detail here. For a full account, see \cite{Kelly1}.
+\end{defn}
+There are a variety of commutation requirements which we are not considering in detail here. The property of being functorial is also more involved. For a full account, see \cite{Kelly1}.
 
@@
 We can consider some examples of norms.
-\begin{examp}
+\begin{examp}\label{exp_norm}
 Let $D$ be the monoidal category of non-negative real numbers defined in example \ref{cat_real}. Then, for all $t \in \Rr$, the function $|\cdot|:D \rightarrow \Rr$ defined by 
@@
 \]
-is a norm on $D$.
-
+is a norm on $D$. We can see that it satisfies the requirements:
+\[|0| = 1
+\]
+\[|x + y| = e^{-tx + ty} = |x||y|.
+\]
 We will explore this norm in detail shortly.
@@
 
-We are interested in a notion of how close together things are - and it will need to measure closeness rather than distance, in the sense that it will increase for objects which are closer together.
-The reason for this will become clear soon.
-We do this by defining $\zeta$ appropriately: If $C$ is a generalized metric space, then $\zeta(a,b) = e^{-C(a,b)}$.
-
-The definition for ordinary categories is fairly natural.
-The version for generalized metric spaces is less intuitive, but the definitions are surprisingly consistent.
-Consider three objects $a,b,c$ in an ordinary category.
-The numbers above the arrows indicate the number of morphisms between adjacent objects:
-
-\[
-\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
-
-\node[label = below:{a}, circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](1) at (0,0) {};
-\node[label = below:{b}, circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](2) at (3,0) {};
-\node[label = below:{c}, circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](3) at (6,0) {};
-
-\draw[-latex] (1) -- (2) node[midway, above = 3pt] {\textit{k}};
-\draw[-latex] (2) -- (3) node[midway, above = 3pt] {\textit{l}};
-
-\end{tikzpicture}\]
-Then, as a result of the composition axioms, there must be a morphism $g \circ f$ from $a$ to $c$ for each pair of morphisms $f \in C(a,b), g \in C(b,c)$.
-This means that there are $kl$ morphisms from $a$ to $c$ which are implied by the morphisms shown above.
-So $\zeta(a,c) \geq \zeta(a,b)  \zeta(b,c)$.
-
-Now, consider the same situation in a generalized metric space. We know from one of the axioms that
-\[
-C(a,c) \leq C(a,b) + C(b,c).
-\]
-The inverse exponential function is monotonically decreasing. So we simply apply it to both sides and flip the inequality to get the same result, that $\zeta(a,c) \geq \zeta(a,b) \zeta(b,c)$.
-
-There is another way of looking at essentially the same property.
-The reason the addition (+) operator appears in the second axiom in the generalized metric space definition is because addition is what is called the \textit{monoidal product} in the enriched category.
-The equivalent in an ordinary category is the tensor product, $\otimes$.
-In terms of number of morphisms, $\otimes$ behaves like multiplication.
-We want a fact about addition to give us a fact about multiplication.
-Exponentiating is the most natural way to translate multiplication into addition, so we can apply the axiom.
+%TODO: Sports crowd analogy
+
+So we would like a norm on $D$, the monoidal category of real numbers, which decreases as its argument get large.
+Recall that in example \ref{exp_norm}, we observed that the function $|x|=e^{-tx}$ is a norm on $D$.
+For any positive $t$, this is a decreasing function.
+In fact, we wills see that if we use this family of norms, we can view $t$ as a ``zooming'' parameter, which allows us to consider the data at different scales.
+
+We have a special name for the Euler characteristic of a generalized metric space which results from this particular norm:
+\begin{defn}
+Let $M$ be a generalized metric space. Let $|\cdot|_t:D \rightarrow \Rr$ be defined by
+\[
+|x|_t = e^{-tx}.
+\]
+If it exists, let $\chi_t(M)$ be the Euler characteristic resulting from $|\cdot|$.
+Then $\chi_t(M)$ is called the \emph{$t$-magnitude} (or just \emph{magnitude} if $t=1$) of $M$, denoted $\magn_t(M)$ or just $\magn(M)$.
+\end{defn}
+%TODO: Small examples w/ graphs
 \section{Product Spaces and Approximations}
+
+Consider the following set of points $A$ in two-dimensional space:
+
+\[
+\includegraphics{../Figures/4x3.pdf}
+\]
+
+Let $M$ be this set:
+\[
+\includegraphics{../Figures/3.pdf}
+\]
+
+and $N$ this set:
+\[
+\includegraphics{../Figures/4.pdf}
+\]
+
+The set $A$ is what you would get if you replaced each point in $M$ with the set $N$. Suppose we choose a scale, and somehow count the number of clusters in $N$ and in $M$.
+
+If the scale is very small -- if we ``zoom in'' so that points must be very close together before they are considered to be in the same cluster -- then every point will be in its own cluster.
+So $N$ will have four clusters, $M$ three, and $A$ will have 12.
+
+If we choose a middle scale, then it might be that the points in $N$ are clustered together, but $M$ remains discrete.
+Then $N$ has one cluster, $M$ has three, and $A$ has four, as each copy of $N$ forms a cluster.
+
+Finally, if our scale is large enough that $M$ is grouped into a single cluster, all three sets of points will have a single cluster.
+
+In all three cases, the number of clusters in $A$ is the product of the number of clusters in $M$ and in $N$. It appears that this remains the case as we change our scale.
+
+$A$ is an approximation of what is called a \emph{tensor product category}.
+In this section, we define the construction formally, and explore how the Euler-Leinster characteristic behaves when two categories are combined in this way.
+In particular, we would like for the magnitude of a product space to be the product of the magnitudes of the original spaces - this is how the number of clusters seems like it should behave when we look at examples like $A$ above.
+
+Not all enriched categories can be used to construct product spaces. We first must define a restriction on the definition of a monoidal category.
+
+\begin{defn}
+Let $M$ be a monoidal category with monoidal product $\otimes$. Suppose that for all $a,b \in M, a \otimes b \cong b \otimes a$. Then $M$ is a \emph{symmetric monoidal category}.
+\end{defn}
+
+We add this restriction to allow us to prove the following lemma:
+
+\begin{lemma}
+Let $M$ be a symmetric monoidal category. Let $P,Q,R,S,T,U$ in $M$ be given. Suppose that we have morphisms
+\begin{align*}
+f&:(P \otimes Q) \rightarrow T\\
+g&:(R \otimes S) \rightarrow U.
+\end{align*}
+Then, if $f \otimes g$ is the morphism required by the functoriality requirement of definition \ref{def_monoid}, we have
+\[
+(f \otimes g):(P \otimes Q) \otimes (R \otimes S) \rightarrow T \otimes U.
+\]
+\end{lemma}
+\begin{proof}\label{prod_morph}
+Using the symmetry of $\otimes$, we can rearrange:
+\[
+(P \otimes Q) \otimes (R \otimes S) \cong (P \otimes R) \otimes (Q \otimes S).
+\]
+Then definition \ref{def_monoid} tells us that the desired morphism exists.
+\end{proof}
+This extra requirement is necessary for the product of two enriched categories to exist.
+In particular, the composition maps do not necessarily exist if the monoidal category is not symmetric.
+We can now define that:
+
+\begin{defn}
+Let $A,B$ be categories both enriched over a symmetric monoidal category $M$.
+Fix a norm on $M$.
+Then the \emph{tensor product} of $A$ and $B$, denoted $A \times B$, is the category enriched over $M$ defined as follows:
+\begin{itemize}
+\item The set of objects, $(A \times B)_0$, is $\{(a,b):a \in A_0, b \in  B_0\}$
+\item For $(a,b), (c,d) \in A_0, C((a,b), (c,d)) = C(a,b) \otimes C(c,d)$.
+\item The unit object is $u_A \otimes u_B$, where $u_A, u_B$ are the units of $A,B$ respectively
+\item The composition and identity morphisms are defined using Lemma \ref{prod_morph} (the details are not important for this discussion, but they are straightforward).
+\end{itemize}
+\begin{rmk}
+The tensor product of two categories enriched over $M$ is indeed a category enriched over $M$. There are many requirements to check, and we do not go through all of them here.
+\end{rmk}
+\end{defn}
+
+We consider some examples of simple product categories. Note that \catname{set} is a symmetric monoidal category, so ordinary categories are eligible to be used as factors of product categories. 
+\begin{examp}
+Let $A$ be the following category:
+\[
+\includegraphics{../Figures/cat_2_directed.pdf}
+\]
+Recall that we omit the identity morphisms when we draw categories. So $A$ has two points and three morphisms. Then $A \times A$ looks like this:
+\[
+\includegraphics{../Figures/cat_2_prod.pdf}
+\]
+To see why, recall that the monoidal product on \catname{set} is the direct product.
+So consider, for example, $(a,a)$ and $(a,b)$.
+There is one morphism from $a$ to $a$ and one from $a$ to $b$.
+So the direct product of the hom-sets also has one element, which is why there is one arrow from $(a,a)$ to $(a,b)$.
+On the other hand, because there is no morphism $b$ to $a$, there is also no morphism from $(a,b)$ to $(a,a)$.
+\end{examp}
+\begin{examp}\label{met_prod_ex}
+We will be focusing on products of generalized metric spaces. So we consider an example of that. Let $A, B$ be the following:
+\[
+\includegraphics{../Figures/gen_met_small.pdf}
+\]
+So each space has two points, with $A(a_1, a_2) = 1, B(b_1, b_2) = 2$. Then the tensor product category $A \times B$ looks like this:
+\[
+\includegraphics[width=.4\paperwidth]{../Figures/gen_met_small_prod}
+\]
+It is impossible to draw this product space to scale because of the way distances behave.
+
+We can observe the same behavior here as in the initial example.
+Suppose we used some clustering scheme where points within a threshold distance $t$ of each other were put into the same cluster.
+This is not how magnitude works, of course, but it is easier to visualize.
+Then we have three cases:
+\begin{description}
+\item[$t < 1$:] $A$ has two clusters, $B$ has two clusters, and $A \times B$ has four clusters.
+\item[$1 \leq t < 2$:] $A$ has one cluster, $B$ has two clusters, and $A \times B$ has two clusters.
+\item[$t \geq 2$:] $A, B$, and $A \times B$ each have just one cluster (note that $(a_1, b_2)$ and $(a_2, b_1)$ are in the same cluster in $A \times B$ even though their distance is 3, because both are in the same cluster as $(a_1, b_1)$).
+\end{description}
+So in all cases, the number of clusters in $A \times B$ is the product of the numbers of clusters in $A$ and $B$. We will see that this isn't a coincidence.
+\end{examp}
+
+Magnitude is obtained using $\zeta$, the similarity matrix.
+So we are interested in how the similarity matrix behaves under the tensor product.
+It turns out that the similarity matrix of a product category is obtained using the matrix \emph{Kronecker product}, not coincidentally (but confusingly) written using $\otimes$.
+\begin{defn}
+Let $A$ be an $m \times n$ matrix and $B$ be a $q \times r$ matrix.
+Then the \emph{Kronecker product} of $A$ and $B$, denoted $A \otimes B$, is the $mq \times nr$ matrix defined by the following block matrix:
+\[
+A \otimes B = 
+\begin{bmatrix}
+A_{11}B & A_{12}B & \cdots & A_{1n}B \\
+A_{21}B & A_{22}B & \cdots & A_{2n}B \\
+\vdots & \vdots & \ddots & \vdots \\
+A_{m1}B & A_{m2}B & \cdots & A_{mn}B
+\end{bmatrix}.
+\]
+\end{defn}
+We show that this definition makes sense by connecting it immediately to the tensor product of categories.
+
+\begin{lemma}\label{tensor_kron}
+Let $A, B$ be categories both enriched over a monoidal category $M$.
+Fix some norm on $M$.
+Let $\zeta_A, \zeta_B$ be the similarity matrices of $A,B$ under the chosen norm.
+If $a_1,\dots,a_m$ and $b_1,\dots,b_n$ are the orders chosen for the objects of $A$ and $B$ when constructing $\zeta_A, \zeta_B$, then fix the order \[a_1b_1, a_1b_2, \dots, a_1b_n, a_2b_1, \dots, a_mb_n\] for $A \times B$.
+Then
+\[
+\zeta_{A \times B} = \zeta_A \otimes \zeta_B.
+\]
+\end{lemma}
+\begin{proof}
+%TODO: Prove
+\end{proof}
+\begin{thm}
+Let $A, B$ be categories both enriched over a monoidal category $M$ . Fix some norm on $M$. Then, if $\chi(A), \chi(B)$ both exist,
+\[
+\chi(A \times B) = \chi(A)\chi(B).
+\]
+\end{thm}
+\begin{proof}
+Let $\zeta_A, \zeta_B$ be the similarity matrices of $A,B$. Then, by theorem \ref{tensor_kron}, the similarity matrix of $A \times B$ is $\zeta_A \otimes \zeta_B$.
+
+Because both Euler characteristics exist, there must exist a valid weighting on each category.
+Let $\omega_A, \omega_B$ be weightings on $A, B$ respectively.
+Let $1^{|A|}, 1^{|B|}$ be the ones vectors of lengths $|A|$ and $|B|$.
+Then, using facts about the Kronecker product, we have
+\begin{align*}
+1^{|A|}&= \zeta_A\omega_A \\
+1^{|B|}&= \zeta_B\omega_A \\
+1^{|A||B|} &= \zeta_A\omega_A \otimes \zeta_B\omega_B\\
+&= (\zeta_A \otimes \zeta_B)(\omega_A \otimes \omega_B)
+\end{align*}
+So the vector $\omega_A \otimes \omega_B$ is a weighting on $A \otimes B$. We have:
+\begin{align*}
+\chi(A \times B) &= \sum_{\alpha \in A \otimes B}(\omega_A \otimes \omega_B)(\alpha) \\
+&= \sum_{a \in A, b \in B} \omega_A(a)\omega_B(b) \\
+&= \left(\sum_{a \in A}\omega_A(a)\right)\left(\sum_{b \in B}\omega_B(b)\right) \\
+&= \chi(A)\chi(B).
+\end{align*}
+\end{proof}
 \section{Examples}
+%TODO: Necessary to be its own section?
 \end{chapter}
@@
 \iffalse
-\iffalse
+
 We can replace the vectors $f,g$ with matrices to get the following generalization, which :
@@
 \end{thm}
-\fi
 
@@
 \]
+
+The definition for ordinary categories is fairly natural.
+The version for generalized metric spaces is less intuitive, but the definitions are surprisingly consistent.
+Consider three objects $a,b,c$ in an ordinary category.
+The numbers above the arrows indicate the number of morphisms between adjacent objects:
+
+\[
+\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
+
+\node[label = below:{a}, circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](1) at (0,0) {};
+\node[label = below:{b}, circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](2) at (3,0) {};
+\node[label = below:{c}, circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](3) at (6,0) {};
+
+\draw[-latex] (1) -- (2) node[midway, above = 3pt] {\textit{k}};
+\draw[-latex] (2) -- (3) node[midway, above = 3pt] {\textit{l}};
+
+\end{tikzpicture}\]
+Then, as a result of the composition axioms, there must be a morphism $g \circ f$ from $a$ to $c$ for each pair of morphisms $f \in C(a,b), g \in C(b,c)$.
+This means that there are $kl$ morphisms from $a$ to $c$ which are implied by the morphisms shown above.
+So $\zeta(a,c) \geq \zeta(a,b)  \zeta(b,c)$.
+
+Now, consider the same situation in a generalized metric space. We know from one of the axioms that
+\[
+C(a,c) \leq C(a,b) + C(b,c).
+\]
+The inverse exponential function is monotonically decreasing. So we simply apply it to both sides and flip the inequality to get the same result, that $\zeta(a,c) \geq \zeta(a,b) \zeta(b,c)$.
+
+There is another way of looking at essentially the same property.
+The reason the addition (+) operator appears in the second axiom in the generalized metric space definition is because addition is what is called the \textit{monoidal product} in the enriched category.
+The equivalent in an ordinary category is the tensor product, $\otimes$.
+In terms of number of morphisms, $\otimes$ behaves like multiplication.
+We want a fact about addition to give us a fact about multiplication.
+Exponentiating is the most natural way to translate multiplication into addition, so we can apply the axiom.
 \fi

### 2017-04-10 Drafts/Draft.tex
Figures

@@
 \usepackage{mathrsfs}
-\usepackage[euler-digits]{eulervm} %TODO: Maybe change this
+\usepackage[euler-digits]{eulervm} 
+\usepackage[font={small}]{caption}
+\usepackage{float}
 \author{Leo Selker}
@@
 \title{M\"obius Inversion: Construction and Applications}
-\newcommand{\fix}{\text{fix }}
-\newcommand{\cl}{\text{cl }}
+\newcommand{\kron}{\boldsymbol{\otimes}}
+\DeclareMathOperator{\fix}{Fix}
 \DeclareMathOperator{\cat}{cat}
@@
 \DeclareMathOperator{\stab}{Stab}
-\DeclareMathOperator{\orb}{Orb}
+\DeclareMathOperator{\orb}{\mathcal{O}}
 \DeclareMathOperator{\fixx}{fix}
@@
 \section{Introduction and Motivation}
+%TODO: Capitalize "theorem, lemma,..."
 %TODO: Expand introduction with more explicit examples
@@
 \begin{rmk}
-Recall that $\zeta^{-1}$ is the matrix inverse rather than the functional inverse, and that it exists by \ref{inv_ex}.
+Recall that $\zeta^{-1}$ is the matrix inverse rather than the functional inverse, and that it exists by Lemma \ref{inv_ex}.
 \end{rmk}
@@
 \begin{proof}
-Recall that by \ref{inv_ex}, $\mu = \zeta^{-1}$ exists. Given that, the result follows if we right-multiply both sides by $\mu$. The first statement becomes the second when the sums are made explicit.
+Recall that by Lemma \ref{inv_ex}, $\mu = \zeta^{-1}$ exists.
+Given that, the result follows if we right-multiply both sides by $\mu$.
+The first statement becomes the second when the sums are made explicit.
 \end{proof}
@@
 In fact, the simplicity of the inversion step is the whole point of M\"obius inversion.
-The tricky part is formulating a given problem such that \ref{mob_inv} can be applied to it.
+The tricky part is formulating a given problem such that Theorem \ref{mob_inv} can be applied to it.
 We will see many cases where values of $f$ from the theorem are readily attainable, but values of $g$ are what we really want.
 The M\"obius function allows us to obtain those values.
-This procedure - the use of the M\"obius function to reverse the process of summing terms as in theorem \ref{mob_inv} - is what is referred to as M\"obius inversion.
+This procedure - the use of the M\"obius function to reverse the process of summing terms as in theorem Theorem \ref{mob_inv} - is what is referred to as M\"obius inversion.
 
@@
 
-In this case, if $\leq$ represents the poset relation from \ref{lattice}, then $m \leq n$ if, for each prime $p$, $m$'s factorization contains no more copies of $p$ than $n$'s factorization.
+In this case, if $\leq$ represents the poset relation from Definition \ref{lattice}, then $m \leq n$ if, for each prime $p$, $m$'s factorization contains no more copies of $p$ than $n$'s factorization.
 This is the same as saying that $m|n$.
@@
 \begin{proof}
-We fix $a,b$, and then rearrange terms starting from \ref{sum_form}:
+We fix $a,b$, and then rearrange terms starting from Remark \ref{sum_form}:
 \begin{align*}
@@
 \end{proof}
-We are now ready to write down $\mu$ on certain subsets of the integer lattice. In order to ensure that the sums involved are predictable, we need an additional condition on the subsets we consider:
-
-\begin{lemma}\label{int_lattice}
+We are now ready to write down $\mu$ on the integer lattice.
+\begin{thm}\label{int_lattice}
 Let $L$ be the $n$-dimensional integer lattice, with the usual poset relation. Let $\zeta, \mu$ be defined as usual on $L$. Let $x=(x_1,\dots,x_n),y = (y_1,\dots,y_n)$ be elements of $L$. Then:
@@
 \]
-\end{lemma}
+\end{thm}
 
 \begin{proof}
-If $x \nleq y$, then by \ref{recurse}, $\mu(x,y) = 0$. This is the first case.
-
-We now proceed by induction on $\sum_{i=1}^ny_i-x_i$. If $x \leq y$ and $\sum_{i=1}^ny_i-x_i = 0$, then $x = y$. So by \ref{recurse}, $\mu(x,y) = 1$. This is the base case.
-
-Suppose that we have \ref{int_lattice} for any $x \leq y$ where $\sum_{i=1}^ny_i-x_i \leq k-1$.
+If $x \nleq y$, then by Lemma \ref{recurse}, $\mu(x,y) = 0$. This is the first case.
+
+We now proceed by induction on $\sum_{i=1}^ny_i-x_i$. If $x \leq y$ and $\sum_{i=1}^ny_i-x_i = 0$, then $x = y$. So by Lemma \ref{recurse}, $\mu(x,y) = 1$. This is the base case.
+
+Suppose that we have Lemma \ref{int_lattice} for any $x \leq y$ where $\sum_{i=1}^ny_i-x_i \leq k-1$.
 Let $x \leq y$ be fixed such that $\sum_{i=1}^ny_i-x_i =k$.
@@
 Note that $x \leq y' < y$.
-So we can decompose the sum from $\ref{int_lattice}$.
+So we can decompose the sum from Lemma $\ref{recurse}$.
 Let
@@
 \]
-So by \ref{sum_form}, $\alpha=0$.
+So by Remark \ref{sum_form}, $\alpha=0$.
 
@@
 For each of these, by the inductive hypothesis, $\mu(x,z) = (-1)^j$.
-So, using \ref{sum_form}, we can write
+So, using Remark \ref{sum_form}, we can write
 \begin{align*}
@@
 Because $x_1 \leq x_2$, if $[x_1, x_2] = 1$, then $x_1 = x_2$.
-So by \ref{recurse}, $\mu_X(x_1, x_2) = 1$.
+So by Lemma \ref{recurse}, $\mu_X(x_1, x_2) = 1$.
 Because $\phi(x_1) = \phi(x_2), \mu_Y(\phi(x_1), \phi(x)2) = 1$ also.
 
-Suppose the theorem is true if $\#[x_1, x_2] \leq k-1$ for some integer $k$. Fix $x_1, x_2$ such that $\#[x_1, x_2] = k$. Then by \ref{recurse},
+Suppose the theorem is true if $\#[x_1, x_2] \leq k-1$ for some integer $k$. Fix $x_1, x_2$ such that $\#[x_1, x_2] = k$. Then by Lemma \ref{recurse},
 \[
@@
 This means we are able to use M\"obius inversion.
-Rather than compute the M\"obius function directly, we can use \ref{int_lattice} and \ref{mapping} to reuse what we already know.
+Rather than compute the M\"obius function directly, we can use Theorems \ref{int_lattice} and \ref{mapping} to reuse what we already know.
 
@@
 Let $d,n \in \Zz^+$ be given.
-We set up the isomorphism required for \ref{mapping}: Index the primes $p_1, p_2, \dots$.
+We set up the isomorphism required for Theorem \ref{mapping}: Index the primes $p_1, p_2, \dots$.
 So $p_1=2, p_2=3$, and so on.
@@
 
-This allows us to use \ref{mapping}, and the result immediately follows.
+This allows us to use Theorem \ref{mapping}, and the result immediately follows.
 \end{proof}
@@
 This definition of $\mu$ depends only on $\frac nd$, which means that we can abuse notation to write $\mu(\frac nd)$ instead of $\mu(d,n)$.
-This allows us to use \ref{mob_inv} to arrive at \eqref{init_mob}:
+This allows us to use Theorem \ref{mob_inv} to arrive at \eqref{init_mob}:
 \[
@@
 \]
-Recall that \ref{mu_div} tells us how to write down values of $\mu$.
+Recall that Theorem \ref{mu_div} tells us how to write down values of $\mu$.
 Depending on what information we have access to, this might be much easier than just counting the number of values relatively prime to $n$.
@@
 
-\begin{chapter}{Groups and Orbits} 
+\begin{chapter}{Groups and Orbits} \label{chap_groups}
 \section{Background}
-Suppose that a group $G$ acts on a set $\Omega$.
-
-I will use $G(x)$ to denote $x$'s orbit under $G$, and $\orb(\Omega, G)$ to denote the set of orbits in $\Omega$ under $G$'s action on it. 
-\section{M\"obius Inversion on Poset of Subgroups}
+For this chapter, it is necessary to be familiar with a simple structure called a \emph{group}.
+In this section, we will define it and briefly establish the machinery we need without going into too much detail, omitting proofs.
+More detail on elementary group theory can be found in an abstract algebra textbook.
+Knowledge of groups is not needed for any other chapters in this investigation.
+
+\begin{defn}
+A \emph{group} is a set $G$ together with a group operation (denoted with the empty operator) $G \times G \rightarrow G$. This operation must satisfy three requirements.
+\begin{itemize}
+\item For all $a,b,c \in G, (ab)c = a(bc)$
+\item There exists an element $e \in G$, such that $ea=a=ae$ for all $a \in G$
+\item For each $a \in G$, there exists an $a^{-1} \in G$ such that $aa^{-1} = e = a^{-1}a$.
+\end{itemize} 
+\end{defn}
+\begin{defn}
+Let $G$ be a group. Then $H \subseteq G$ is a \emph{subgroup} of $G$ if $H$ is itself a group, with the same group operation as $G$. If $H$ is a subgroup of $G$, we write $H \leq G$.
+\end{defn}
+\begin{defn}
+Let $G$ be a group and let $\Omega$ be a set. Then an \emph{action} of $G$ on $\Omega$ is a map $\cdot:G \times \Omega \rightarrow \Omega$ which satisfies the following properties:
+\begin{itemize}
+\item $e \cdot x = x$ for all $x \in \Omega$
+\item $g \cdot (h \cdot x) = (gh) \cdot x$ for all $g,h \in G, x \in \Omega$.
+\end{itemize} 
+\end{defn}
+\begin{defn}
+Let a group $G$ act on a set $\Omega$. Let $x \in \Omega$ be given. Then the \emph{orbit of $x$ under $G$}, denoted by $\orb_G(x)$ or $Gx$, is defined by
+\[
+\orb_G(x) = \{ y \in G : \exists g \in G \text{ where } g\cdot x = y\}
+\]
+or, equivalently,
+\[
+\orb_G(x) = \{g\cdot x : g \in G\}.
+\]
+\end{defn}
+
+\begin{defn}
+Let a group $G$ act on a set $\Omega$. Let $x \in \Omega$ be given. Then the \emph{stabilizer of $x$ under $G$}, denoted by $\stab_G(x)$, is defined by
+\[
+\stab_G(x) = \{g \in G:g \cdot x = x\}.
+\]
+\end{defn}
+\begin{thm}
+Let a group $G$ act on a set $\Omega$. Then for every $x \in \Omega, \stab_G(x)$ is a subgroup of $G$.
+\end{thm}
+\begin{proof}
+This is easily checked.
+\end{proof}
+\begin{thm}
+Let a group $G$ act on a set $\Omega$. Then the orbits of $\Omega$ under $G$ partition $\Omega$.
+\end{thm}
+\begin{proof}
+Omitted, but straightforward.
+\end{proof}
+\begin{thm}[Fundamental Counting Principle]\label{fcp}
+Let a \textbf{finite} group $G$ act on a set $\Omega$. Let $x \in \Omega$ be given. Then
+\[
+|\stab_G(x)||\orb_G(x)| = |G|.
+\]
+\end{thm}
+\begin{proof}
+Omitted - requires technology we don't have here.
+\end{proof}
+\begin{defn}
+Let a group $G$ act on a set $\Omega$. Then $\Omega/G$ denotes the set of orbits in $\Omega$ under $G$.
+\end{defn}
+\begin{defn}
+Let a group $G$ act on a set $\Omega$. Let $A \leq G$. Then the \emph{fixed set} of $A$, or $\fix_A(\Omega)$, is equal to
+\[
+\{x \in \Omega : \forall g \in A, g \cdot x = x\}.
+\]
+We can also speak of the fixed set of a group element $g \in G$. In that case, we say
+\[
+\fix_g(\Omega) = \{x \in \Omega : g \cdot x = x \}.
+\]
+\end{defn}
+
+\section{M\"obius Inversion on the Poset of Subgroups}
 We want to apply M\"obius inversion to finite groups. This means we will need a poset. We will use the \emph{poset of subgroups} (or \emph{lattice of subgroups}):
@@
 \end{rmk}
+\begin{examp}
+Consider the group $S_3$, the symmetric group of order 6. Then we can draw its lattice of subgroups:
+
+\begin{figure}[h]
+\[
+\includegraphics{../Figures/s3_lattice.pdf}
+\]
+\caption{The lattice of subgroups of $S_3$.}
+\end{figure}
+So, for example, $\langle (1,2) \rangle \leq \langle e \rangle$, because $\langle (1,2) \rangle \supseteq \langle e \rangle$. 
+\end{examp}
+\begin{rmk}
+We are ordering the poset this way for reasons that will soon become clear.
+But to reduce confusion, we will continue to use inclusion notation to define $\zeta$, and so $\mu$, rather than using $\leq$.
+I will be using $\subseteq$ rather than $\leq$ to denote subgroups, also to reduce confusion with the poset relation.
+\end{rmk}
 This puts us in the position to apply M\"obius inversion. We first define the usual functions on $\sub(G) \times \sub(G)$:
@@
 \]
-\item Let $\mu = \zeta^{-1}$, which exists by \ref{inv_ex}.
+\item Let $\mu = \zeta^{-1}$, which exists by Lemma \ref{inv_ex}.
 \end{itemize}
-Recall that we manipulate $\zeta, \mu$ as if they were matrices.
-
-Now, \ref{mob_inv} tells us that, for any row vectors $f,g$ of length $|\sub{G}|$, 
+Recall that we manipulate $\zeta, \mu$ as matrices.
+
+Now, Theorem \ref{mob_inv} tells us that, for any row vectors $f,g$ of length $|\sub{G}|$, 
 \[
@@
 
+The goal is to count the orbits in $\Omega$ under the action by $G$ - in other words, to find $|\Omega/G|$.
+We will do that by finding a weighted sum of elements of $\Omega$.
+If we were to simply count the elements of $\Omega$, we would almost certainly overestimate the number of orbits.
+We would prefer it if each orbit could ``send a representative.'' If that were possible, counting those representatives would be the same as counting the number of orbits.
+But there is no clear way of accomplishing this -- how would we choose one element exactly from each orbit?
+It seems like this would require prior knowledge of the orbit structure of $\Omega$ under $G$, which is exactly what we are seeking.
+
+So we have to change our perspective.
+Suppose that every element of $\Omega$ were able to provide information telling us the size of its orbit.
+So suppose that given $x \in \Omega$, we had access to $|\orb_G(x)|$.
+
+Now suppose that we are counting orbits by checking elements of $\Omega$ one at a time.
+Each time we see an element $x \in \Omega$, we ask it for the size of its orbit, and then add $\frac 1 {|\orb_G(x)|}$ to a running total.
+Let $O$ be a single orbit of $\Omega$ under $G$ where $|O|=n$.
+Then we will see $n$ elements of $\Omega$ which belong to $O$, and for each of them, we will add $\frac 1n$ to our running total.
+This means we add exactly 1 for $O$.
+The same is true of all the orbits in $\Omega$.
+So our final total will be the size of $G/X$.
+
+To formalize this, we have the following relationship:
+
+\begin{equation}\label{eq_counting}
+|G/X| = \sum_{x \in \Omega}\frac 1 {|\orb_G(x)|}.
+\end{equation}
+
+This is the central idea: We want to group elements of $\Omega$ by the size of their orbits.
+We will use the \emph{Fundamental Counting Principle}, Theorem \ref{fcp}, together with M\"obius inversion, to do this.
+Although we already justified \eqref{eq_counting}, we will prove it formally as well.
+
 We start by defining some functions/vectors, each with entries corresponding with subgroups of $G$, which we will be using. Let:
@@
 f(A) &= \#\{x \in \Sigma: \stab(x) \supseteq A\} = |\fix(A)|\\
-g(A) &= \#\{x \in \Sigma: \stab(x) = A\}
+g(A) &= \#\{x \in \Sigma: \stab(x) = A\}\\
 \sigma(A) &= |A|
@@
 
-What now?
-The goal is to count the orbits in $\Omega$ under the action by $G$ - in other words, to find $|\orb(\Omega, G)|$.
-We will start with the assumption that we are able to find $\sigma$, which is true if we know the structure of $\sub(G)$.
+We will operate with the assumption that we are able to find $\sigma$, which is true if we know the structure of $\sub(G)$.
 We will also assume that we are able to carry out the group action, thereby determining which elements of $\Omega$ are fixed by given subgroups of $G$.
@@
 
-Suppose we are handed $g$. In order to see how to find $|\orb(\Omega, G)|$, we recall a basic fact from group theory, which holds for any $x \in \Omega$:
-\begin{fact}
-\[|G| = |G(x)||\stab(x, G)|\]
-\end{fact}
+Suppose we are handed $g$. In order to see how to find $|\orb(\Omega, G)|$, we recall Theorem \ref{fcp}:
+
+\[|G| = |G(x)||\stab(x, G)|.\]
+
 Because $G$ is finite, this implies that \[|G(x)| = \frac{|G|}{|\stab(x, G)|}.\]
@@
 
-\[
-|\orb(\Omega, G)| = \frac {1}{|G|}f\mu \cdot \sigma
-\]
+\[|\orb(\Omega, G)| = \frac {1}{|G|}f\mu \cdot \sigma.\]
+
 Recall that $\sigma$ and $\mu$ do not depend on the details of the group action, or on $\Omega$ at all.
 They only depend on $G$.
-So it is useful to rearrange this expression to isolate $f$, the only part which does depend on the action:
+So it is useful to rearrange this expression to isolate $f$, the only part which does depend on the action.
+This gives us the central result of this chapter:
+\begin{thm}\label{orbit_count}
+Let $G$ act on a set $\Omega$. Let $f, \mu, \sigma$ be defined as above. Then
 \[
@@
 \]
+\end{thm}
 
 By combining M\"obius inversion with basic group theory, we have a recipe for turning something readily obtainable (the function $f$) into something less obvious (the number of orbits of an action).
-\iffalse
-\section{Burnside's Lemma}
-A more familiar way of counting the orbits of a group is the following:
-\begin{thm}[Burnside's Lemma]\label{burnside} %TODO: omit?
-Let $G$ be a finite group acting on a finite set $\Omega$. Then:
-\[
-|\orb(\Omega, G) = \frac{1}{G}\sum_{g \in G}\fixx(g)
-\]
-\end{thm}
-\fi
+
+The reason Theorem \ref{orbit_count} is powerful is that we can do almost all of the work knowing only the structure of the group, before we know anything about the set or the action.
+If we are handed a group $G$, we can define the vector $\lambda$ by
+\begin{equation}\label{eq:lambda}
+\lambda = \frac {1}{|G|}(\mu \cdot \sigma)^T.
+\end{equation}
+Then, for any action of $G$ onto any set $\omega$, all we need to do is compute $f$, and then Theorem \ref{orbit_count} tells us that
+\[
+|\Omega/G| = \lambda f^T.
+\]
+In the next example, we will walk through all the steps involved in counting the orbits of a simple action.
+\begin{examp}\label{ex:2x2}
+Let $G = C_4 = \{e, \alpha, \alpha^2, \alpha^3\}$, the cyclic group of order 4.  
+\begin{figure}[h]
+\[
+\includegraphics{../Figures/c4_lattice.pdf}
+\]
+\caption{The lattice of subgroups of $C_4$}
+\label{fig:c4_lattice}
+\end{figure}We first compute $\lambda$ using the formula from \eqref{eq:lambda}.
+We start by finding the M\"obius function.
+$C_4$ has three subgroups: All of $C_4$, the subgroup generated by $\alpha^2$, and the identity.
+So $\zeta$ will be a $3 \times 3$ matrix.
+Because each subgroup contains the next, there is only one admissible total ordering we can use to construct our vectors:
+\[
+C_4 < \langle \alpha^2 \rangle < \langle e \rangle.
+\]
+We can go through all the pairs of subgroups to determine that
+\[
+\zeta = \begin{bmatrix} 1 & 1 & 1 \\ 0 & 1 & 1 \\ 0 & 0 & 1 \end{bmatrix}.
+\]
+For example, because the first subgroup, $C_4$ contains the second, $\langle \alpha^2 \rangle$, the 1, 2 entry of $\zeta$ is equal to 1.
+
+This implies that
+\[
+\mu = \zeta^{-1} = \begin{bmatrix} 1 & -1 & 0\\ 0 & 1 & -1 \\ 0 & 0 & 1 \end{bmatrix}.
+\]
+Next, we find $\sigma$. Recall that $\sigma$ is the vector of subgroup sizes. So 
+\[
+\sigma = [4, 2, 1].
+\]
+Finally, note that $|C_4|=4$. So
+\begin{align*}
+\lambda &= \frac 14 \mu \sigma^T\\
+&= \frac 14 
+\begin{bmatrix} 1 & -1 & 0\\ 0 & 1 & -1 \\ 0 & 0 & 1 \end{bmatrix}
+\begin{bmatrix} 4 \\ 2 \\ 1 \end{bmatrix}\\
+&= \frac 14 \begin{bmatrix} 2 \\ 1 \\ 1\end{bmatrix}
+\end{align*}
+This $\lambda$ is independent of any set $G$ might act on.
+So let's try an example.
+Suppose we have a $2 \times 2$ chessboard, and we want to place some number of rooks on the board such that none of them attack one another.
+If one configuration can be obtained from the other by rotating the board (ignoring light and dark squares), then we wish to count them as the same configuration.
+The goal is to count how many distinct configurations there are, which cannot be obtained from each other by rotation.
+
+We can first solve this problem by inspection, or by "brute force," by just enumerating the possibilities:
+\begin{description}
+\item[Zero rooks:] There is one option with zero rooks: The empty board.
+\[
+\includegraphics{../Figures/zero_rooks.pdf}
+\]
+\item[One rook:] We can put one rook on any of the four squares. However, we can rotate the board to obtain any of these from the others. So there is just one distinct configuration. \\
+\[
+\makebox[\textwidth][c]{\includegraphics{../Figures/one_rook.pdf}}
+\]
+\item[Two rooks:] We can put rooks on opposite corners. There are two such pairs, but we can rotate the board and obtain either pair from the other. So, again, there is only one distinct possibility.
+\[
+\makebox[\textwidth][c]{\includegraphics{../Figures/two_rooks.pdf}}
+\]
+\end{description}
+So there are a total of three distinct arrangements of rooks. Now we can try to solve this problem using $\lambda$.
+
+Let $\Omega$ be the set of possible rook arrangements without regard for rotational equivalence.
+So putting a rook in the upper left hand corner and putting one in the lower left hand corner would be considered to be different arrangements.
+Now let $C_4$ act on $\Omega$ by rotating the board.
+So $\alpha$ rotates the board $90^\circ$ counterclockwise, $\alpha^2$ rotates it twice, etc.
+Then each distinct arrangement of rooks corresponds exactly with an orbit of $C_4$'s action on $\Omega$.
+
+Luckily, we know how to count orbits. All we have to do is find $f$. We go through the subgroups of $C_4$.
+\begin{itemize}
+\item $C_4$ only fixes the empty board. Any other arrangement can be changed by a rotation. So $f(1) = 1$.
+\item The subgroup $\langle \alpha^2 \rangle$ contains the identity element as well as the $180^\circ$ rotation.
+This subgroup fixes both arrangements with two rooks, as well as the empty board.
+So $f(2) = 3$.
+\item The subgroup $\langle e \rangle$ fixes all the arrangements. There are 2 ways to place two rooks, 4 ways to place one rook, and 1 way to place zero rooks. So $f(2) = 7$.
+\end{itemize}
+Then all we have to do is compute $\lambda f^T$.
+\begin{align*}
+\lambda f^T &= \frac 14 [2, 1, 1] \begin{bmatrix} 1 \\ 3 \\ 7\end{bmatrix} \\
+&= \frac 14 12\\
+&=3
+\end{align*}
+So we indeed find the correct answer. 
+\end{examp}
+
+In this example, it's not clear that using $\lambda$ actually saved work - in fact, it seemed to take longer.
+But if we were to increase $n$, we could still determine the number of distinct arrangements relatively easily, because $\lambda$ wouldn't change.
+Furthermore, in many situations (including this one) it is much easier to determine how many \emph{total} arrangements are fixed by a subgroup that it is to find the number of \emph{distinct} arrangements.
+As an example of that, we can look at another example, which is more difficult to solve by hand.
+\begin{examp}
+Suppose we have a $4 \times 4$ board, and we would like to color each square one of $k$ colors.
+We would like to consider colorings identical if one can be obtained from the other by rotating the board.
+The goal is to count the number of distinct colorings.
+
+As in Example \ref{ex:2x2}, we let $C_4$ act on the total set of colorings, and count the orbits.
+This problem is different from the previous one, but because the group which is acting is the same, we can re-use $\lambda$ from the last example.
+This is one reason this method is powerful.
+All we have to do is find $f$ by finding the fixed set of each subgroup of $C_4$.
+
+\begin{description}
+\item[$C_4$:] We want the number of colorings which are fixed under any rotation.
+This means that all four quadrants must be symmetrically colored.
+So we color one quadrant, and then use symmetry to determine how to color the rest.
+There are four squares in each quadrant, so this subgroup fixes $k^4$ colorings.
+\item[$\langle \alpha^2 \rangle$:] We use a similar approach: We color half the board, and then determine the coloring on the other half using symmetry.
+This means we are coloring 8 squares however we want.
+So there are $k^8$ colorings.
+\item[$\langle e \rangle$:] The identity subgroup always fixes all elements. We have 16 squares, so the fixed set has size $k^{16}$.
+\end{description}
+So the number of distinct colorings is
+\begin{align*}
+\lambda f &= \frac 14 [2,1,1]\begin{bmatrix} k^4 \\ k^8 \\ k^{16}\end{bmatrix}\\
+&= \frac 14 (2k^4 + k^8 + k^{16}).
+\end{align*}
+\end{examp}
+It's not clear how we would have solved this problem by brute force, and we were able to solve it very quickly, reusing $\lambda$ to save even more work.
 \end{chapter}
@@
 \begin{thm}[Inclusion-Exclusion]\label{iep}
-Let $S$ be a set. Let $A_i \subseteq S$ for each $i \in I$ where $I$ is finite. Let $K \subseteq I$ be given. Then
+Let $S$ be a finite set. Let $A_i \subseteq S$ for each $i \in I$ where $I$ is finite. Let $K \subseteq I$ be given. Then
 \[
@@
 \end{thm}
-\section{Proof using M\"obius Inversion} %TODO: Motivate
-There are many proofs of this well-known fact. We will show it using M\"obius inversion. This means we will need a poset.
-
-\begin{defn}
-For any set $X$, the \emph{power set} of $X$, denoted by $\ps(X)$, is the set of subsets of $X$. 
+This is a well-known fact.
+It allows us to find the size of unions of overlapping sets if we have information about intersections of those sets.
+There are many ways of proving the Inclusion-Exclusion Principle.
+%TODO: Explain why proving it with Mobius inversion is worthwhile
+
+\section{Proof using M\"obius Inversion} 
+We will need a poset.
+
+\begin{defn}
+For any set $I$, the \emph{power set} of $I$, denoted by $\ps(I)$, is the set of subsets of $I$. 
 \end{defn}
 \begin{rmk}\label{power_poset}
-Let $I$ be a finite set. Then $(\ps(X), \supseteq)$ is a lower finite partially ordered set.
+Let $I$ be a finite set. Then $(\ps(I), \supseteq)$ is a lower finite partially ordered set.
 \end{rmk}
-Note that the poset from \ref{power_poset} is ordered by reverse inclusion rather than simple inclusion. The poset axioms are easily checked.
+Note that the poset from Remark \ref{power_poset} is ordered by reverse inclusion rather than simple inclusion. The poset axioms are easily checked.
 
@@
 We will be manipulating functions on $(\ps(I), \supseteq)$, so this will be our poset.
+
+There are two sets of subsets here, and it can be hard to keep them straight.
+$S$ is a set of elements, and for each $i$, $A_i$ is a subset of $S$.
+On the other hand, $I$ is our index set, and our partially ordered set consists of subsets of $I$.
+We will perform M\"obius inversion on subsets of $I$ in order to determine sizes of unions of subsets of $S$.
 
@@
 
-In order to find $\hat{f}$, we suppose that we have access to \emph{intersections} (but not unions) of the $A_i$ (it is apparent that this is required to use \ref{iep}).
+In order to find $\hat{f}$, we suppose that we have access to \emph{intersections} (but not unions) of the $A_i$ (it is apparent that this is required to use Theorem \ref{iep}).
 This means that we have access to $f$.
@@
 
-Also, we define the \emph{complement} function/matrix $c$ as follows:
+Also, we define the \emph{complement} function/matrix $c$ as follows: %TODO: Change variable name
 \[
@@
 
-Let $\mu = \zeta^{-1}$ (as usual, we mean the matrix inverse). Then we can add the following important fact, using \ref{mob_inv}:
+Let $\mu = \zeta^{-1}$ (as usual, we mean the matrix inverse). Then we can add the following important fact, using Theorem \ref{mob_inv}:
 \[
@@
 We have determined how to find unions of sets of $A_i$ using $\hat{f}$, and we have written $\hat{f}$ in terms of values we have access to.
-But with a bit more work, we can show that what we have derived is really the inclusion-exclusion principle.
+But with a bit more work, we can show that what we have derived is really the Inclusion-Exclusion Principle.
 The first step is to interpret values of $\mu$.
-We will again use \ref{int_lattice} and \ref{mapping}.
+We will again use Theorems \ref{int_lattice} and \ref{mapping}.
 
@@
 \]
-There are a variety of things we must check to use \ref{mapping}.
+There are a variety of things we must check to use Theorem \ref{mapping}.
 \begin{itemize}
@@
 \end{itemize}
-This means that \begin{align*}
+This means that, if $\mu_{\Nn^{|I|}}$ is the M\"obius function on $\Nn^{|I|}$, \begin{align*}
 \mu_{\ps(I)}(J,K) &= \mu_{\Nn^{|I|}}(\phi(J), \phi(K)) \\
@@
 \end{align*}
+We can walk through the matrix algebra.
 We consider the $J,K$ entry of $\mu c \zeta$.
@@
 \end{align*}
-We now apply \ref{sum_form} to simplify the inner sum and insert the definition of $f$:
+We now apply Remark \ref{sum_form} to simplify the inner sum and insert the definition of $f$:
 \begin{align*}
@@
 \]
-So we can arrive at \ref{iep}:
+So we can arrive at Theorem \ref{iep}:
 \begin{align*}
@@
 \end{align*}
-\section{Generalizations}
+%TODO: Debrief
 
 \end{chapter}
+
 \begin{chapter}{Euler Characteristic of a Category}\label{chap_euler}
@@
 \section{M\"obius Inversion on a Category}
-
 To define M\"obius inversion on a partially ordered set, we used an ``indicator function'' which was notated as $\zeta$.
@@
 Let $C$ be the category with two objects $a$ and $b$, with exactly one morphism going each direction between $a$ and $b$, and with no other morphisms except the required identity morphisms. 
-We can draw this category:
+\begin{figure}[h]
 \[
@@
 \]
+\caption{Diagram of symmetric category with 2 points and 4 morphisms.}
+\end{figure}
 Note that whenever we draw a category, we omit the identity morphisms.
@@
 We are now ready to construct central definition of this section: the Euler-Leinster characteristic (or just Euler characteristic) of a category.
-The entire construction can be found in \cite{Lein1, Lein2, Lein4}.
+The entire construction can be found in \cite{Lein1, Lein2, Lein4}, and is due to Tom Leinster.
 
@@
 Note that even if $C$ does not admit M\"obius inversion, it might admit a weighting.
-For example, the category in example \ref{2_pt} admits the weighting $\omega(a) = \omega(b) = 0.5$, even though it does not admit M\"obius inversion.
+For example, the category in Example \ref{2_pt} admits the weighting $\omega(a) = \omega(b) = 0.5$, even though it does not admit M\"obius inversion.
 
@@
 Note that even if a category admits several weightings, they all lead to the same Euler characteristic by a simple sum rearrangement argument.
-Together with \ref{mobius_is_weighting}, this implies the following:
+Together with Lemma \ref{mobius_is_weighting}, this implies the following:
 \begin{cor}\label{euler_mu}
@@
 \begin{examp}
-Let $V=\{a,b\}, \sigma_2 = \{\{a\},\{b\}, \{a,b\}\}$. Then $\sigma_2$ is a simplicial complex over $V$. We visualize $\sigma_2$ as follows:
+Let $V=\{a,b\}, \sigma_2 = \{\{a\},\{b\}, \{a,b\}\}$. Then $\sigma_2$ is a simplicial complex over $V$. 
+\begin{figure}[h]
 \[
@@
 \end{tikzpicture}\]
+\caption{The simplicial complex $\sigma_2$.}
+\end{figure}
 Because $\{a\} \subseteq \{a,b\}$, the vertex $\{a\}$ is an endpoint of the line $\{a,b\}$.
@@
 \begin{examp}
-Let $\sigma = \{a, b, c, d, ab, ac, bc, bd, cd, abc\}$. Then we draw $\sigma$ as follows:
+Let $\sigma = \{a, b, c, d, ab, ac, bc, bd, cd, abc\}$. Then the cell $bcd$ is not in $\sigma$, even though all of its sides and vertices are.
+\begin{figure}[h]
 \[
@@
 \]
+\caption{$\sigma$ is an example of how a triangle can be outlined but not filled.}
+\end{figure}
 \end{examp}
@@
 \end{defn}
-Note that this is a distinct (although related) definition to \ref{cat_euler}, yet we use $\chi$ for both. Which we mean will be determined by what kind of object we are applying $\chi$ to.
+Note that this is a distinct (although related) definition from Definition \ref{cat_euler}, yet we use $\chi$ for both.
+Which we mean will be determined by what kind of object we are applying $\chi$ to.
 
@@
 Note that a simplicial complex can be converted into a poset, where the cells are ordered by inclusion.
-Recall that we also defined $\cat(X)$ for a poset $X$ in \ref{cat_poset}.
+Recall that we also defined $\cat(X)$ for a poset $X$ in Definition \ref{cat_poset}.
 If $\sigma$ is a simplicial complex, and $X$ is the corresponding poset, then $\cat(\sigma) = \cat(X)$.
@@
 \begin{examp}
-Let $\sigma = \{a, b, ab\}$. Then we can draw $\sigma, \cat(\sigma)$:
+Let $\sigma = \{a, b, ab\}$. Then $\cat(\sigma)$ has three objects and five morphisms, including the three identity morphisms.
+\begin{figure}[h]
 \[
@@
 \]
+\caption{$\sigma$ and $\cat(\sigma)$. Recall that we omit identity morphisms when drawing a category.}
+\end{figure}
 \end{examp}
-Recall that we omit identity morphisms when drawing a category.
 
@@
 
-Suppose that $|\beta - \alpha| = k+1$. We know by \ref{cat_mob} that, because $\alpha \neq \beta$,
+Suppose that $|\beta - \alpha| = k+1$. We know by Definition \ref{cat_mob} that, because $\alpha \neq \beta$,
  \begin{align*}
@@
 \begin{proof}
-Recall that by \ref{cat_euler}, 
+Recall that by Definition \ref{cat_euler}, 
 \[
@@
 \end{proof}
-The fact that $\chi(\cat(\sigma)) = \chi(\sigma)$ is comforting. It justifies calling using $\chi$ in \ref{cat_euler}, and calling this construction a type of Euler characteristic.
+The fact that $\chi(\cat(\sigma)) = \chi(\sigma)$ is comforting. It justifies calling using $\chi$ in Definition \ref{cat_euler}, and calling this construction a type of Euler characteristic.
 
 \section{Euler-Leinster Characteristic Examples}
+%TODO
 
@@
 
-The idea of hierarchical clustering is that instead of choosing a scale, we capture the data's structure at a variety of scales:
-
+The idea of hierarchical clustering is that instead of choosing a scale, we capture the data's structure at a variety of scales.
+\begin{figure}
 \[
@@
 
-We can see that here that as we ``zoom out'', the structure of this data changes.
+\caption{A graphical representation of hierarchical clustering.}
+\label{fig:hier}
+\end{figure}
+
+We can see in Figure \ref{fig:hier} that as we ``zoom out'', the structure of this data changes.
 First the data has first eight clusters of one point each, then four clusters of two points, and finally two clusters of four points.
@@
 In the above example, explicit clusters are formed by grouping points which are near each other.
-We will explore an alternate method of clustering, which does not actually construct clusters, but instead estimates the number of clusters using a real, rather than integer, value.
-We will use a generalization of the Euler-Leinster characteristic from chapter \ref{chap_euler}.
+Methods like this are common; see \cite{Carl1}.
+We will explore an alternate method of clustering, in which we do not explicitly group points, but instead estimates the number of clusters using a real, rather than integer, value.
+We will use a generalization of the Euler-Leinster characteristic from Chapter \ref{chap_euler}.
 We start by building some important definitions.
@@
 \section{Enriched Categories}
-In chapter \ref{chap_euler}, we defined a structure called a category.
+In Chapter \ref{chap_euler}, we defined a structure called a category.
 It turns out that this construction - which we will now call an \emph{ordinary} category - can be generalized further, to become an \emph{enriched} category.
 The idea is that we replace the sets of morphisms with objects from an ordinary category of a certain type, and adapt the definition of composition accordingly.
-
-%TODO: Fix Furthermore, the definitions and constructions we explore will be easy to apply directly to metric spaces.
-I point out that this construction is a type of category to justify dealing with them together with other categories in the next section.
-We will define the Euler characteristic of a category, and we will need to apply the definition to metric spaces by way of generalized metric spaces.
-This will make much more sense if we keep in mind that generalized metric spaces are categories.
 
@@
 
-We would like to generalize the weightings and Euler-Leinster characteristic from chapter \ref{chap_euler} so we can use them on enriched categories.
-Recall that in \ref{def_weighting}, we used the function $\zeta$ to require that for $\omega$ to be a weighting on a category $C$, for all $a \in C$,
+We would like to generalize the weightings and Euler-Leinster characteristic from Chapter \ref{chap_euler} so we can use them on enriched categories.
+Recall that in Definition \ref{def_weighting}, we used the function $\zeta$ to require that for $\omega$ to be a weighting on a category $C$, for all $a \in C$,
 \[
@@
 \begin{examp}\label{exp_norm}
-Let $D$ be the monoidal category of non-negative real numbers defined in example \ref{cat_real}. Then, for all $t \in \Rr$, the function $|\cdot|:D \rightarrow \Rr$ defined by 
+Let $D$ be the monoidal category of non-negative real numbers defined in example Example \ref{cat_real}. Then, for all $t \in \Rr$, the function $|\cdot|:D \rightarrow \Rr$ defined by 
 \[
@@
 \begin{defn}\label{gen_met}
-Let $D$ be the monoidal category of non-negative real numbers defined in example \ref{cat_real}. Let $C$ be a category enriched over $D$. Then we call $C$ a \emph{generalized metric space}.
-\end{defn}
-There is a lot of technology buried in that definition, and it can be difficult to untangle the definitions involved in enriched categories.
+Let $D$ be the monoidal category of non-negative real numbers defined in Example \ref{cat_real}. Let $C$ be a category enriched over $D$. Then we call $C$ a \emph{generalized metric space}.
+\end{defn}
+There is a lot of technology buried in that definition, and it can be difficult to untangle definitions involving enriched categories.
 Luckily, because of the simplicity of $D$, we can simplify the definition of a generalized metric space to one which does not depend on the definition of an enriched category.
@@
 \begin{proof}
-We will start with the definition from \ref{gen_met}, and argue that it is equivalent to the above.
+We will start with the definition from Definition \ref{gen_met}, and argue that it is equivalent to the above.
 As defined originally, a generalized metric space consists of a set of objects $C_0$, with a non-negative real number $C(a,b)$ between any ordered pair of elements $a,b \in C_0$.
-So what remains is to show that the composition requirements from \ref{en_cat} are equivalent to the conditions in \ref{direct_def}.
-
-Let $C$ be a generalized metric space as defined in \ref{gen_met}.
-Then \ref{en_cat} requires that there be a morphism $i_a:0 \rightarrow C(a,a)$ for any $a \in C$.
+So what remains is to show that the composition requirements from Definition \ref{en_cat} are equivalent to the conditions in Definition  \ref{direct_def}.
+
+Let $C$ be a generalized metric space as defined in Definition \ref{gen_met}.
+Then Definition \ref{en_cat} requires that there be a morphism $i_a:0 \rightarrow C(a,a)$ for any $a \in C$.
 This exists if and only if $C(a,a) \leq 0$, which is equivalent to saying that $C(a,a)=0$.
@@
 
-%TODO: Sports crowd analogy
-
-So we would like a norm on $D$, the monoidal category of real numbers, which decreases as its argument get large.
-Recall that in example \ref{exp_norm}, we observed that the function $|x|=e^{-tx}$ is a norm on $D$.
-For any positive $t$, this is a decreasing function.
-In fact, we wills see that if we use this family of norms, we can view $t$ as a ``zooming'' parameter, which allows us to consider the data at different scales.
+We would like to estimate the number of clusters in a dataset.
+To justify the rather strange way in which we'll do that, we can turn to an analogy.
+Suppose each data point represented a spectator at a sports game, some of whom are sitting in groups.
+Each group would like to attain a particular level of excitement based on the energy levels of its members.
+But each group only needs to have the same total level of excitement, and the individual energy levels of the members of group add together to determine the group's excitement.
+The question is what level of energy each fan should have so that their group has the appropriate total level of excitement.
+\begin{figure}[h]
+\[
+\includegraphics[width=.5\textwidth]{../Figures/no_weights.pdf}
+\]
+\caption{Seven sports spectators in groups}
+\label{fig:sports}
+\end{figure}
+In Figure \ref{fig:sports}, we have a group of two on the left, a group of one in the middle, and a group of three on the right.
+The goal is to assign each individual an energy level so that all three groups' excitement levels are equal to 1.
+This isn't hard to do - we give one example in Figure \ref{fig:sports_labeled}.
+\begin{figure}[h]
+\[
+\includegraphics[width=.5\textwidth]{../Figures/initial_weights.pdf}
+\]
+\caption{A possible allocation of energy}
+\label{fig:sports_labeled}
+\end{figure}
+Given these values, it's simple to count how many groups there are.
+Each group has total excitement equal to 1, so if we add the energy levels of each individual together, we will obtain the number of groups (in this case, 3).
+
+Of course, this is circular.
+We had to decide ahead of time which individuals were grouped together so that we could find the values to assign them.
+So we use a modification of this method: Each individual must have an excitement level of 1, and the excitement level of an individual is the sum of their own energy level together with a weighted sum of the levels of those around them.
+The closer two individuals are to each other, the more each of their energy levels contributes to the other's excitement.
+
+Let $M$ be the set of spectators.
+Suppose that for each spectator $a \in M, \omega(a)$ is the energy level of $a$.
+Suppose that for any $a,b \in M$, $\zeta(a,b)$ is a measure of how close together those two people are.
+So if $a$ and $b$ are very close together, $\zeta(a,b)$ approaches 1, and as they move apart it approaches zero.
+Then we are asking that the following be true for each spectator $a \in M$:
+\[
+\sum_{b \in M}\zeta(a,b)\omega(b).
+\]
+
+This looks exactly like the requirement (from Definition \ref{def_weighting}) for $\omega$ to be a weighting on a category $M$!
+So adding up values of $\omega$ is the same as finding the Euler-Leinster characteristic of $M$, assuming we can properly encode the structure of the spectators into a category.
+This is the key motivation behind the use of the Euler characteristic to count clusters.
+
+We now move from our analogy back into the realm of categories.
+We will model the situation using a generalized metric space.
+We need a norm $|\cdot|$ on $D$ such that $|x|$ will be close to 1 as $x$ gets small, and will approach zero as it gets large.
+
+Recall that in Example \ref{exp_norm}, we observed that the function $|x|=e^{-tx}$ is a norm on $D$. For any positive $t$, this is a decreasing function. 
+\begin{figure}[h]
+\[
+\includegraphics[width = 0.4\paperwidth]{../Figures/exp.pdf}
+\]
+\caption{A graph of $e^{-x}$ against $x$.}
+\end{figure}
+And the larger the value of $t$, the quicker the function decays.
+In fact, we will see that if we use this family of norms, we can view $t$ as a ``zooming'' parameter, which allows us to consider the data at different scales.
 
@@
 If it exists, let $\chi_t(M)$ be the Euler characteristic resulting from $|\cdot|$.
-Then $\chi_t(M)$ is called the \emph{$t$-magnitude} (or just \emph{magnitude} if $t=1$) of $M$, denoted $\magn_t(M)$ or just $\magn(M)$.
-\end{defn}
-%TODO: Small examples w/ graphs
+Then $\chi_t(M)$ is called the \emph{$t$-magnitude} of $M$, denoted $\magn_t(M)$.
+We will refer to the 1-magnitude as simply the magnitude of $M$, denoted $\magn(M)$.
+\end{defn}
+
+It makes sense that the magnitude of a metric space should capture the number of clusters it contains. We can consider a simple example to see how it behaves.
+\begin{examp}\label{ex:2pt}
+Consider the space $M_2$ of two points separated by distance $1$, shown in Figure \ref{fig:2pt}.
+\begin{figure}[h]
+                        \[
+\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
+
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](1) at (0,0) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](2) at (4,0) {};
+
+\draw[decoration={brace,raise=7pt},decorate] (1) -- (2) node[midway, above = 10pt] {1};
+
+\end{tikzpicture}\]
+\caption{$M_2$, a simple generalized metric space with two points.}
+\label{fig:2pt}
+\end{figure}
+If $t$ indeed behaves as a zooming parameter, then we would expect that for small values of $t$, $\chi_t(M_2)$ should have a single cluster, because we are not zoomed in.
+But for large values of $t$, the number of clusters should approach 2, as the two points fully separate from each other.
+
+In this case, for $t \in (1,\infty),$ we can let the weighting of each point equal
+\[\frac{1}{1+e^{-t}}.\]
+It is straightforward to check that this is indeed a valid weighting. So for each $t$,
+\[
+ \chi_t(M_2) = \frac{2}{1+e^{-t}}.
+\]
+
+We are varying a parameter, $t$, in the exponent of the norm definition.
+So it is reasonable to expect that the behavior of the magnitude as $t$ varies will be logarithmic.
+If we plot $\chi_t(M_2)$ against $t$, we can see that it behaves just as we expect (see Figure \ref{fig:2pt_mag}).
+\begin{figure}[H]
+\[
+\makebox[\textwidth][c]{\includegraphics[width = 0.9\paperwidth]{../Figures/2_point_.png}}
+\]
+\caption{A plot of $\chi_t(M_2)$ against $t$ on a logarithmic scale.}
+\label{fig:2pt_mag}
+\end{figure}
+\end{examp}
 \section{Product Spaces and Approximations}
-
-Consider the following set of points $A$ in two-dimensional space:
-
+In Figure \ref{fig:3+4}, we see two sets of points, $M$ and $N$. $M$ has three points while $N$ has four.
+
+\begin{figure}[h]
+\[
+\includegraphics{../Figures/4+3.pdf}
+\]
+\caption{Two sets of points.}
+\label{fig:3+4}
+\end{figure}
+In Figure \ref{fig:3x4}, we see another set of points, $A$.
+\begin{figure}[h]
 \[
@@
 \]
-
-Let $M$ be this set:
-\[
-\includegraphics{../Figures/3.pdf}
-\]
-
-and $N$ this set:
-\[
-\includegraphics{../Figures/4.pdf}
-\]
-
-The set $A$ is what you would get if you replaced each point in $M$ with the set $N$. Suppose we choose a scale, and somehow count the number of clusters in $N$ and in $M$.
-
+\caption{A set of points $A$: A copy of $N$ for each point in $M$.}
+\label{fig:3x4}
+\end{figure}
+The set $A$ is what you would get if you replaced each point in $M$ with the set $N$.
+
+Suppose we choose a scale, and somehow count the number of clusters in $N$ and in $M$.
 If the scale is very small -- if we ``zoom in'' so that points must be very close together before they are considered to be in the same cluster -- then every point will be in its own cluster.
@@
 \end{align*}
-Then, if $f \otimes g$ is the morphism required by the functoriality requirement of definition \ref{def_monoid}, we have
+Then, if $f \otimes g$ is the morphism required by the functoriality requirement of Definition \ref{def_monoid}, we have
 \[
@@
 \]
-Then definition \ref{def_monoid} tells us that the desired morphism exists.
+Then Definition \ref{def_monoid} tells us that the desired morphism exists.
 \end{proof}
@@
 Let $A$ be the following category:
+\begin{figure}[H]
 \[
@@
 \]
-Recall that we omit the identity morphisms when we draw categories. So $A$ has two points and three morphisms. Then $A \times A$ looks like this:
+\caption{A category with two points and three morphisms. Recall that we omit the identity morphisms when we draw categories.}
+\end{figure}
+Then $A \times A$ looks like this:
+\begin{figure}[H]
 \[
@@
 \]
+\caption{$A \times A$.}
+\end{figure}
 To see why, recall that the monoidal product on \catname{set} is the direct product.
@@
 \begin{examp}\label{met_prod_ex}
-We will be focusing on products of generalized metric spaces. So we consider an example of that. Let $A, B$ be the following:
+We will be focusing on products of generalized metric spaces.
+So we consider an example of that.
+Let $A, B$ each be generalized metric spaces with two points.
+Label the objects of $A$ as $a_1, a_2$, and the objects of $B$ as $b_1, b_2$.
+\begin{figure}[h]
 \[
@@
 \]
-So each space has two points, with $A(a_1, a_2) = 1, B(b_1, b_2) = 2$. Then the tensor product category $A \times B$ looks like this:
+\caption{$A$ and $B$}
+\end{figure}
+Suppose that $A(a_1, a_2) = 1, B(b_1, b_2) = 2$. Recall that the monoidal product is $+$. So the tensor product category $A \times B$ looks like this:
+\begin{figure}[H]
 \[
@@
 \]
-It is impossible to draw this product space to scale because of the way distances behave.
+\caption{$A \times B$. It is impossible to draw this product space to scale because of the way distances behave under the tensor product.. }
+\end{figure}
 
@@
 It turns out that the similarity matrix of a product category is obtained using the matrix \emph{Kronecker product}, not coincidentally (but confusingly) written using $\otimes$.
+Because this is the same notation used for the monoidal product, we will bold the operator when we are referring to the Kronecker product: $\kron$.
 \begin{defn}
 Let $A$ be an $m \times n$ matrix and $B$ be a $q \times r$ matrix.
-Then the \emph{Kronecker product} of $A$ and $B$, denoted $A \otimes B$, is the $mq \times nr$ matrix defined by the following block matrix:
-\[
-A \otimes B = 
+Then the \emph{Kronecker product} of $A$ and $B$, denoted $A \kron B$, is the $mq \times nr$ matrix defined by the following block matrix:
+\[
+A \kron B = 
 \begin{bmatrix}
@@
 \end{defn}
-We show that this definition makes sense by connecting it immediately to the tensor product of categories.
+
+\begin{rmk}\label{kron_prod}
+It is straightforward to show that, for any appropriately sized matrices $A, B, C, D$,
+\[
+(A \otimes B) \times (C \otimes D) = AC \otimes BD.
+\]
+We will use that fact soon.
+\end{rmk}
+We show that this definition is useful by connecting it immediately to the tensor product of categories.
 
 \begin{lemma}\label{tensor_kron}
-Let $A, B$ be categories both enriched over a monoidal category $M$.
+Let $A, B$ be categories both enriched over a symmetric monoidal category $M$.
 Fix some norm on $M$.
@@
 \[
-\zeta_{A \times B} = \zeta_A \otimes \zeta_B.
+\zeta_{A \times B} = \zeta_A \kron \zeta_B.
 \]
@@
 \begin{proof}
-%TODO: Prove
-\end{proof}
+Let $a_1, a_2 \in A, b_1, b_2 \in B$ be given. Recall that norms are multiplicative. Then the entry of $\zeta_{A \times B}$ corresponding with $(a_1, b_1), (a_2, b_2)$ should contain 
+\begin{align*}
+|(A \times B)((a_1, b_1), (a_2, b_2))|& = |A(a_i, a_j) \otimes B(b_k, b_l)|\\
+&= |A(a_i, a_j)| |B(b_k, b_l)|
+\end{align*}
+which is the value of the corresponding entry of $\zeta_A \kron \zeta_B$.
+\end{proof}
+
+Given this lemma, we can prove that the behavior we saw in Example \ref{met_prod_ex} occurs when we count clusters using the magnitude function.
+In fact, it turns out the for any category enriched over a symmetric monoidal category, the Euler-Leinster characteristic is multiplicative over the tensor product.
+
 \begin{thm}
@@
 \begin{proof}
-Let $\zeta_A, \zeta_B$ be the similarity matrices of $A,B$. Then, by theorem \ref{tensor_kron}, the similarity matrix of $A \times B$ is $\zeta_A \otimes \zeta_B$.
+Let $\zeta_A, \zeta_B$ be the similarity matrices of $A,B$. Then, by Theorem \ref{tensor_kron}, the similarity matrix of $A \times B$ is $\zeta_A \kron \zeta_B$.
 
@@
 Let $1^{|A|}, 1^{|B|}$ be the ones vectors of lengths $|A|$ and $|B|$.
-Then, using facts about the Kronecker product, we have
+Then, using the fact from Remark \ref{kron_prod}, we have
 \begin{align*}
@@
 1^{|B|}&= \zeta_B\omega_A \\
-1^{|A||B|} &= \zeta_A\omega_A \otimes \zeta_B\omega_B\\
-&= (\zeta_A \otimes \zeta_B)(\omega_A \otimes \omega_B)
-\end{align*}
-So the vector $\omega_A \otimes \omega_B$ is a weighting on $A \otimes B$. We have:
-\begin{align*}
-\chi(A \times B) &= \sum_{\alpha \in A \otimes B}(\omega_A \otimes \omega_B)(\alpha) \\
+1^{|A||B|} &= \zeta_A\omega_A \kron \zeta_B\omega_B\\
+&= (\zeta_A \kron \zeta_B)(\omega_A \kron \omega_B)
+\end{align*}
+So the vector $\omega_A \kron \omega_B$ is a weighting on $A \times B$. We have:
+\begin{align*}
+\chi(A \times B) &= \sum_{\alpha \in A \otimes B}(\omega_A \kron \omega_B)(\alpha) \\
 &= \sum_{a \in A, b \in B} \omega_A(a)\omega_B(b) \\
@@
 \end{proof}
-\section{Examples}
-%TODO: Necessary to be its own section?
+\begin{examp}\label{ex:4pt}
+In Example \ref{ex:2pt}, we saw the behavior of two points.
+While $t$ was small, the magnitude was close to 1, and as $t$ increased, the magnitude approached 2, the number of points.
+Now, we let $M$ be the following space of four points:
+\begin{figure}[H]
+\[
+\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](1) at (0,0) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](2) at (5,0) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](3) at (0,-.5) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](4) at (5,-.5) {};
+\draw[decoration={brace,raise=7pt},decorate] (1) -- (2) node[midway, above = 10pt] {1};
+\draw[decoration={brace, mirror, raise = 7pt},decorate] (1) -- (3) node[midway, left = 10pt] {$\frac{1}{1,000}$};
+% \draw (2) -- (4);
+% \draw (3) -- (4);
+\end{tikzpicture}\]
+\caption{$M$, a generalized metric space with four points. $M$ contains structure at two very different scales.}
+\label{fig:4pt}
+\end{figure}
+$M$ is very nearly a product space of two 2-points spaces at different scales, one separated by a distance 1, and the other by $\frac 1 {1,000}$.
+If the magnitude behaves as we expect it to, we should see the magnitude of $M$ behaving very much like the magnitude of the products of those two 2-point spaces.
+\begin{figure}[h]
+\[
+\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](1) at (0,0) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](2) at (0,-.5) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](3) at (4, -.25) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](4) at (9,-.25) {};
+\node[] at (2, -0.25) {\huge{$\times$}};
+\draw[decoration={brace,mirror, raise=7pt},decorate] (1) -- (2) node[midway, left = 10pt] {$\frac{1}{1,000}$};
+\draw[decoration={brace, raise = 7pt},decorate] (3) -- (4) node[midway, above = 10pt] {1};
+% \draw (2) -- (4);
+% \draw (3) -- (4);
+\end{tikzpicture}\]
+\caption{Two spaces whose product should be very similar to $M$.}
+\label{fig:2_2pt}
+\end{figure}
+
+In fact, we observe exactly that behavior.
+Figure \ref{fig:prod_mag} shows the magnitudes of the three spaces as we vary $t$.
+At every value of $t$, $\chi_t(M)$ is almost exactly the product of the magnitudes of the other two spaces at that $t$ value.
+\begin{figure}[H]
+\[
+\makebox[\textwidth][c]{\includegraphics[width = 0.9\paperwidth]{../Figures/prod_mag.png}}
+\]
+\caption{The magnitude of $M$ alongside the magnitudes of the factor spaces, on a logarithmic scale.}
+\label{fig:prod_mag}
+\end{figure}
+\end{examp}
+\section{Approximations}
+In Example \ref{ex:4pt}, $M$ was \emph{almost} a product space, so we expected its magnitude to be very nearly the product of the magnitudes of the two 2-point spaces.
+It would be useful to quantify how similar the magnitudes of two spaces are, given that we know something about how similar those spaces are.
+To do that, we need some simple tools from linear algebra involving vector and matrix norms.
+Note that these norms are not directly related to the norms we defined on monoidal categories - both are non-negative real-valued functions, but they operate on different structures.
+
+\begin{defn}\label{def:spec}
+Let $n$ be given. Let $|v|$ denote the Euclidean vector norm. Then the \emph{spectral norm} on real- (or complex-) valued $n \times n$ matrices, denoted $||\cdot ||$, is defined by
+\[
+||M|| = \sup_{0 \neq x \in \Rr^n}\left\{ \frac{|Ax|}{|x|} \right\}.
+\]
+\end{defn}
+\begin{rmk}
+Definition \ref{def:spec} does not tell us how to find the spectral norm of a matrix. However, it is not difficult to do so. For a given $M$, we can find $||M||$ as follows:
+
+Let $M^*$ be the adjoint, or conjugate transpose, of $M$. Let $\lambda_1$ be the largest eigenvalue of the matrix $MM^*$. Then $\lambda_1$ will be real-valued, and $||M||=\sqrt{\lambda_1}$.
+
+We will not prove or use this fact - it is simply here to assure readers that the spectral norm can be computed.
+\end{rmk}
+This norm is a common way of determining how ``large'' a matrix is. It will allow us to determine which matrices are ``small enough'' to satisfy some approximation theorems.
+
+There are some simple properties of the spectral norm which we will need.
+\begin{lemma}\label{lem:norm_prop}
+%TODO: Omit additivity if I don't need it.
+Let $A, B$ be $n \times n$ matrices. Then
+\begin{enumerate}[(a)]
+\item \[
+||A + B|| \leq ||A|| + ||B||.
+\]
+\item \[
+||AB|| \leq ||A||\times ||B||
+\]
+\end{enumerate}
+\end{lemma}
+\begin{proof}
+\begin{enumerate}[(a)]
+\item Recall that if $|\cdot|$ is the Euclidean norm on vectors in $\Rr^n$, then for all $v,w \in \Rr^n$,
+\[
+|v + w| \leq |v| + |w|.
+\]
+This is the triangle inequality. So for all $v \in \Rr^n$, we have
+\begin{align*}
+|(A + B)v| &= |Av + Bv| \\
+&\leq |Av| + |Bv|.
+\end{align*} 
+\[\sup_{0 \neq x \in \Rr^n}\left\{ \frac{|(A + B)x|}{|x|} \right\} \leq \sup_{0 \neq x \in \Rr^n}\left\{ \frac{|Ax|}{|x|} \right\} + \sup_{0 \neq x \in \Rr^n}\left\{ \frac{|Bx|}{|x|} \right\}.
+\]
+\item Let $v \in \Rr^n$ be given. Then by the definition of the spectral norm,
+\begin{align*}
+|ABv| &\leq |A(||B|| \times |v|)|\\
+&\leq (||A|| \times ||B||)|v|.
+\end{align*}
+\end{enumerate}
+\end{proof}
+
+\begin{lemma}
+Let $E$ be a real-valued $n \times n$ matrix. Suppose that $||E|| < 1$. Then:
+\[
+\lim_{i \rightarrow \infty}||(-1)^i E^i|| = 0.
+\]
+\end{lemma}
+\begin{proof}
+Let $\alpha = ||E|| <1$. We now use Lemma \ref{lem:norm_prop}:
+\begin{align*}
+\lim_{i \rightarrow \infty}||(-1)^i E^i|| &= \lim_{i \rightarrow \infty}||E||^i\\
+&= \lim_{i \rightarrow \infty}\alpha^i\\
+&= 0.
+\end{align*}
+This allows us to prove a useful fact about the inverses of matrices which are close to $I$.
+\end{proof}
+\begin{lemma}
+Let $E$ be an $n \times n$ matrix such that $||E|| < 1$. Then
+\begin{align*}
+(I + E)^{-1} &= I - E + E^2 - \cdots\\
+&= \sum_{i = 0}^\infty(-1)^i E^i.
+\end{align*}
+\end{lemma}
+\begin{proof}
+\begin{align*}
+(I + E) \sum_{i = 0}^\infty(-1)^i E^i &=  \sum_{i = 0}^\infty (-1)^i E^i  + \sum_{i = 0}^\infty(-1)^i E^{i+1}\\
+&= I + \lim_{i \rightarrow \infty}(-1)^iE^i\\
+&= I
+\end{align*}
+\end{proof}
 \end{chapter}
@@
 \iffalse
+
+A more familiar way of counting the orbits of a group is the following:
+\begin{thm}[Burnside's Lemma]\label{burnside}
+Let $G$ be a finite group acting on a finite set $\Omega$. Then:
+\[
+|\orb(\Omega, G) = \frac{1}{G}\sum_{g \in G}\fix_g(\Omega).
+\]
+\end{thm}
+Burnside's Lemma allows us to compute the number of orbits of a group action if we have access to the size of the fixed sets of each group element.
+On the other hand, Theorem \ref{orbit_count} requires that we know $f$, the size of the fixed set of each \emph{subgroup}.
+These are two different perspectives on the same question, and each might be more or less useful depending on the situation.
 

### 2017-04-10 Thesis_Comp/magnitude.py

@@ -9,3 +9,4 @@ class EuclideanSpace(object):
 
     def compute_distance_matrix(self):
         # Computes the distance matrix for the space
+        pass

### 2017-04-10 Drafts/Draft.tex
approximations

@@
 \[
-\includegraphics[width = 0.4\paperwidth]{../Figures/exp.pdf}
+\includegraphics[width = 0.5\paperwidth]{../Figures/exp.pdf}
 \]
@@
 \end{defn}
-
+\begin{examp}
+Let 
+\begin{align*}
+A &= \begin{bmatrix}
+1 & 2 \\
+3 & 1
+\end{bmatrix},\\
+B &= \begin{bmatrix}
+2  \\
+1 
+\end{bmatrix}.
+\end{align*}
+Then
+\begin{align*}
+A \otimes B &= 
+\begin{bmatrix}
+B & 2B\\
+3B & B
+\end{bmatrix}\\
+&= \begin{bmatrix}
+2 & 4 \\
+1 & 2 \\
+6 & 2\\
+3 & 1
+\end{bmatrix}.
+\end{align*}
+\end{examp}
 \begin{rmk}\label{kron_prod}
@@
 \end{examp}
-\section{Approximations}
+\section{Approximations and Error Bounding}
 In Example \ref{ex:4pt}, $M$ was \emph{almost} a product space, so we expected its magnitude to be very nearly the product of the magnitudes of the two 2-point spaces.
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:lim0}
 Let $E$ be a real-valued $n \times n$ matrix. Suppose that $||E|| < 1$. Then:
@@
 \end{align*}
-This allows us to prove a useful fact about the inverses of matrices which are close to $I$.
+This allows us to prove a useful fact which allows us to approximate the inverses of certain matrices.
 \end{proof}
-\begin{lemma}
-Let $E$ be an $n \times n$ matrix such that $||E|| < 1$. Then
-\begin{align*}
-(I + E)^{-1} &= I - E + E^2 - \cdots\\
-&= \sum_{i = 0}^\infty(-1)^i E^i.
-\end{align*}
-\end{lemma}
+\begin{thm}\label{thm:approx}
+Let $A$ be an invertible $n \times n$ matrix, and let $E$ be an $n \times n$ matrix such that $||E|| < \frac 1{||A^{-1}||}$. Then $(A-E)$ is invertible, and
+\begin{align*}
+(A - E)^{-1} &= A^{-1} + A^{-1}EA^{-1} + A^{-1}EA^{-1}EA^{-1} + \cdots\\
+&= A^{-1} + \sum_{i = 1}^\infty (EA^{-1})^i.
+\end{align*}
+\end{thm}
 \begin{proof}
-\begin{align*}
-(I + E) \sum_{i = 0}^\infty(-1)^i E^i &=  \sum_{i = 0}^\infty (-1)^i E^i  + \sum_{i = 0}^\infty(-1)^i E^{i+1}\\
-&= I + \lim_{i \rightarrow \infty}(-1)^iE^i\\
+We apply Lemma \ref{lem:lim0}
+\begin{align*}
+(A-E)  A^{-1}\sum_{i = 0}^\infty (EA^{-1})^i
+&= \left(\sum_{i = 0}^\infty (EA^{-1})^i\right) - \left( \sum_{i = 0}^\infty (EA^{-1})^{i+1}\right)\\
+&= I - \lim_{i \rightarrow \infty} (EA^{-1})^i\\
 &= I
@@
 \end{proof}
+This fact makes sense.
+The spectral norm of $A^{-1}$ is the inverse of the smallest eigenvalue of $AA^*$, and it tells us how much $A$ is capable of reducing the euclidean norm of a vector it multiplies.
+So if that value is very large, $A$ is very nearly not invertible.
+In that case, it makes sense that adding a relatively small error matrix might change the inverse significantly.
+
+We can use this result to determine how different the magnitude of a space similar to the one from Example \ref{ex:4pt} differed from that of an actual product space.
+Given matrices $A$ and $E$ which satisfy Theorem \ref{thm:approx}, we know that
+\[
+(A - E)^{-1} - A^{-1} = \sum_{i = 1}^\infty (EA^{-1})^i.
+\]
+This means that we can let $\Phi = \sum_{i = 1}^\infty (EA^{-1})^i$ be the ``error term.'' If we can bound the sum of the entries of the matrix $\Phi$, that is a bound on the difference between the magnitude of a space whose similarity matrix is $A$, and one whose similarity matrix is $A + E$.
+
+We can walk through an example:
+\begin{examp}
+Let $M$ be the following generalized metric space:
+\begin{figure}[H]
+\[
+\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](1) at (0,0) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](2) at (5,0) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](3) at (0,-.5) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](4) at (5,-.5) {};
+\draw[decoration={brace,raise=7pt},decorate] (1) -- (2) node[midway, above = 10pt] {$d$};
+\draw[decoration={brace, mirror, raise = 7pt},decorate] (1) -- (3) node[midway, left = 10pt] {1};
+% \draw (2) -- (4);
+% \draw (3) -- (4);
+\end{tikzpicture}\]
+\caption{}
+\label{fig:prod}
+\end{figure}
+And define $A,B$ as follows:
+
+\begin{figure}[H]
+\[
+\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](1) at (9,0) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](2) at (9,-.5) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](3) at (0, -.25) {};
+\node[circle, draw, fill=black,
+                        inner sep=0pt, minimum width=4pt](4) at (5,-.25) {};
+\draw[decoration={brace,mirror, raise=7pt},decorate] (1) -- (2) node[midway, left = 10pt] {1};
+\draw[decoration={brace, raise = 7pt},decorate] (3) -- (4) node[midway, above = 10pt] {d};
+% \draw (2) -- (4);
+% \draw (3) -- (4);
+\end{tikzpicture}\]
+\caption{Again, two spaces whose product should be very similar to $M$.}
+\label{fig:factors}
+\end{figure}
+Let $\zeta_A, \zeta_B, \zeta_{A \times B}, \zeta_M$ be the similarity matrices of $A, B, A \times B$, and $M$ respectively. We can write each of them down:
+\begin{align*}
+\zeta_A &= 
+\begin{bmatrix}
+1 & e^{-d} \\
+e^{-d} & 1
+\end{bmatrix}\\
+\zeta_B &= 
+\begin{bmatrix}
+1 & e^{-1} \\
+e^{-1} & 1
+\end{bmatrix}\\
+\zeta_{A \times B} = \zeta_A \otimes \zeta_B &= 
+\begin{bmatrix}
+1 & e^{-1} & e^{- d} & e^{-(1 + d)}\\
+e^{-1} & 1 & e^{-(1 + d)}& e^{- d}\\
+e^{-d} &e^{-(1 + d)} & 1 & e^{-1}\\
+e^{-(1 + d)} & e^{-d} & e^{-1} & 1
+\end{bmatrix}\\
+\zeta_M &= 
+\begin{bmatrix}
+1 & e^{-1} & e^{- d} & e^{-\sqrt{1 + d^2}}\\
+e^{-1} & 1 & e^{-\sqrt{1 + d^2}}& e^{- d}\\
+e^{-d} & e^{-\sqrt{1 + d^2}}& 1 & e^{-1}\\
+e^{-\sqrt{1 + d^2}} & e^{-d} & e^{-1} & 1
+\end{bmatrix}
+\end{align*}
+The similarity matrices of $A \times B$ and $M$ have most entries identical. We can quantify the difference between them. For any $d \in (0, \infty)$, let 
+\begin{align*}
+\ep_d = e^{-(1 + d)} - e^{-\sqrt{1 + d^2}}\\
+E_d = \begin{bmatrix}
+0 & 0 & 0 & \ep \\
+0 & 0 & \ep & 0 \\
+0 & \ep & 0 & 0 \\
+\ep & 0 & 0 & 0
+\end{bmatrix}
+\end{align*}
+Then 
+\[
+\zeta_M = \zeta_{A \times B} - E_d.
+\]
+%TODO: Plot epsilon
+If we are interested in bounding the difference in magnitude of $M$ and $A \times B$, then we can apply Theorem \ref{thm:approx}.
+We fix a $d$ to determine the relative scales of the spaces.
+Then, for any $t \in (0, \infty):$
+\[
+\mu_M = \mu_{A \times B} + \sum_{i = 1}^\infty (E_d\zeta_{A \times B}^{-1})^i.
+\]
+
+This formula gives us a way of bounding how different the magnitude of the Euclidean spaces is from the product space.
+We can numerically calculate values for $\chi_t(M), \chi_t(A \times B)$, and the error term, and plot them.
+
+If $d = 0.1$, so the scales differ by a factor of ten, then we get the following as we vary $t$:
+\begin{figure}[H]
+\[
+\makebox[\textwidth][c]{\includegraphics[width = 0.9\paperwidth]{../Figures/error_10.png}}
+\]
+\end{figure}
+We can see that the Euclidean space and the product space have very similar magnitude values, and the error bounds are quite tight.
+Note that the period where there are two clusters is much more subtle now, as the points merge together in faster succession.
+
+As we move the value of $d$ closer to 1, we expect both the error bounds and the actual error to increase.
+The product space and the Euclidean space will differ more as their scales become more similar.
+Here we see what happens when $d=1$, so our scales are identical.
+Both spaces move smoothly from having a single cluster to having four clusters, and there is much more significant error.
+In particular, $M$ now forms a square of points, and points at opposite corners have a distance equal to the diagonal of the square.
+On the other hand, in the product space, those points have a distance equal to twice the side of the square.
+This error is more significant the more similar the scales of the factor spaces.
+CLARIFY!
+%TODO: Clarify
+\begin{figure}[H]
+\[
+\makebox[\textwidth][c]{\includegraphics[width = 0.9\paperwidth]{../Figures/error_1.png}}
+\]
+\end{figure}
+\end{examp}
+
 \end{chapter}

### 2017-04-10 Thesis_Comp/matrix.py

@@ -1,0 +1,58 @@
+from matplotlib import pyplot as plt
+import numpy as np
+import math 
+
+def spec_norm(A):
+    svd = np.linalg.svd(A)
+    return svd[1][0]
+
+def calc_E(d, scale=1):
+    epsilon = math.exp(-scale*(1 + d)) - math.exp(-scale*math.sqrt(1 + d**2))
+    E = np.zeros((4,4))
+    Em = np.matrix(E)
+    for (i,j) in [(0,3), (1,2), (2,1), (3,0)]:
+        Em[i,j] = epsilon
+    return Em
+
+def inv_with_error(d, scale=1, n_terms=3):
+    """ 
+    Returns a tuple
+    (A^1, (A - E)^-1, Magnitude Error Bound)
+    """
+    # Put together A
+    A = np.empty((4,4))
+    for i in range(4):
+        A[i,i] = 1
+    for (i,j) in [(0,1), (1,0), (2,3), (3,2)]:
+        A[i,j] = math.exp(-scale)
+    for (i,j) in [(0,2), (2,0), (1,3), (3,1)]:
+        A[i,j] = math.exp(-scale*d)
+    for (i,j) in [(0,3), (1,2), (2,1), (3,0)]:
+        A[i,j] = math.exp(-scale*(1 + d))
+    A = np.matrix(A)
+    E = calc_E(d, scale)
+    ET = 0
+    for i in range(1, n_terms):
+        ET = ET + mp((E * (inv(A))),i)
+    eb = abs(np.sum(ET))
+    inv_A = inv(A)
+    inv_AE = inv(A - E)
+    # actual = np.sum(inv_A - inv_AE)
+    return (inv_A, inv_AE, eb)
+        
+def magnitudes_error(d, scale=1, n_terms=3):
+    # returns (mag(A), mag(A-E), eb)
+    (Ainv, AEInv, eb) = inv_with_error(d, scale, nterms)
+    return (np.sum(Ainv), np.sum(AEInv), eb)
+
+def mp(A,n):
+    return np.linalg.matrix_power(A,n)
+
+def inv(A):
+    return np.linalg.inv(A)
+
+def make_plot():
+    x = np.arange(0,10,.1)
+    y = map(E, x)
+    plt.plot(x,y)
+    plt.show()

### 2017-04-10 Thesis_Comp/metric.py

@@ -42,11 +42,11 @@ class MetricSpace(object):
         distance_matrix = dist.squareform(distance_matrix_compact)
         return MetricSpace(distance_matrix)
 
-    def magnitude(self, scale_factor=1):
+    def magnitude(self, t = 1):
 
         # Scale then exponentiate the distances
-        vector_inverse_exp = np.vectorize(lambda n: math.exp(-n))
-        exp_distance_matrix = vector_inverse_exp(self.distance_matrix * scale_factor)
+        vector_inverse_exp = np.vectorize(lambda n: math.exp(-(t *n)))
+        exp_distance_matrix = vector_inverse_exp(self.distance_matrix)
 
         cat_rep = cat.PartialEnrichedCategory(exp_distance_matrix)
         return np.sum(cat_rep.mobius_matrix())
@@ -55,43 +55,62 @@ class MetricSpace(object):
         magnitude_list = map(self.magnitude, scale_factor_iterable)
         return magnitude_list
 
+def euc_plots():
+    # Plot some euclidean metric space examples
+    test_arrays_euclidean = (
+        np.array(
+            [[0, 0],
+             [0, .001],
+             [1, 0],
+             [1, .001]]
+        ),
+        np.array(
+            [[0, 0],
+             [1, 0]]
+        ),
+    )
+
+    # test_distance_matrices = (
+    #     np.array(
+    #         [0,10]
+    #     ),
+    # )
+    scale_factors_low = np.arange(.1, 5, .1)
+    scale_factors_mid = np.arange(5, 1000, .5)
+    scale_factors_high = np.arange(1000, 50000, 100)
+    scale_factors = np.concatenate((scale_factors_low, scale_factors_mid, scale_factors_high))
+    scale_factors_small = scale_factors * (.001)
+    scale_factors_log = map(lambda x: math.log(x, 10), scale_factors)
+    # scale_factors_1000x_log = map(lambda x: math.log(x, 10), scale_factors_1000x)
+    
+    euclidean_space = MetricSpace.euclidean(test_arrays_euclidean[0])
+    two_space = MetricSpace.euclidean(test_arrays_euclidean[1])
+    magnitudes_euc = euclidean_space.multiscale_magnitude(scale_factors)
+    magnitudes_two = two_space.multiscale_magnitude(scale_factors)
+    magnitudes_two_small = two_space.multiscale_magnitude(scale_factors_small)
+
+    
+    #plt.subplot(211)
[…]

### 2017-04-10 Thesis_Comp/matrix.py
approximations

@@ -42,7 +42,7 @@ def inv_with_error(d, scale=1, n_terms=3):
         
 def magnitudes_error(d, scale=1, n_terms=3):
     # returns (mag(A), mag(A-E), eb)
-    (Ainv, AEInv, eb) = inv_with_error(d, scale, nterms)
+    (Ainv, AEInv, eb) = inv_with_error(d, scale, n_terms)
     return (np.sum(Ainv), np.sum(AEInv), eb)
 
 def mp(A,n):
@@ -51,8 +51,37 @@ def mp(A,n):
 def inv(A):
     return np.linalg.inv(A)
 
-def make_plot():
-    x = np.arange(0,10,.1)
-    y = map(E, x)
-    plt.plot(x,y)
+def prod_approx_plots():
+    d = 1
+    scale_factors_low = np.arange(.1, 5, .1)
+    scale_factors_mid = np.arange(5, 1000, .5)
+    scale_factors_high = np.arange(1000, 50000, 100)
+    scale_factors = np.concatenate((scale_factors_low, scale_factors_mid, scale_factors_high))
+    
+
+    scale_factors_small = scale_factors * (.001)
+    scale_factors_log = map(lambda x: math.log(x, 10), scale_factors)
+    product_magnitudes = map(
+        lambda x: magnitudes_error(d,scale=x)[0], scale_factors)
+    euc_magnitudes = map(
+        lambda x: magnitudes_error(d,scale=x)[1], scale_factors)
+    errors = map(
+        lambda x: magnitudes_error(d,scale=x)[2], scale_factors)
+    
+    plt.title("Product Space Magnitude")
+    plt.xlabel("Scale factor, log scale")
+    plt.ylabel("Magnitude")
+    #plt.plot(scale_factors_log, product_magnitudes, 'r', 
+    #         label='Product Space') 
+    plt.plot(scale_factors_log, euc_magnitudes, 'r',
+             label='Euclidean Approximation')
+    plt.errorbar(scale_factors_log, product_magnitudes, yerr=errors,fmt='b',
+                 label='Product Space Magnitude, Error Bounds')
+    font = {'family' : 'normal',
+            'size'   : 24}
+
+    plt.rc('font', **font)
+    plt.axis([-1.0,1.2,1,4.1])
+    plt.legend(loc='ul')
     plt.show()
+

### 2017-04-10 Thesis_Comp/metric.py

@@ -6,6 +6,7 @@ from scipy.spatial import distance as dist
 import math
 from matplotlib import pyplot as plt
 import category as cat
+import matrix as mat
 
 EPSILON = 10**(-5)
 
@@ -55,6 +56,8 @@ class MetricSpace(object):
         magnitude_list = map(self.magnitude, scale_factor_iterable)
         return magnitude_list
 
+    
+
 def euc_plots():
     # Plot some euclidean metric space examples
     test_arrays_euclidean = (
@@ -91,21 +94,25 @@ def euc_plots():
 
     
     #plt.subplot(211)
-    plt.title("Product Space Magnitude")
+    plt.title("Two Point Space Magnitude")
     plt.xlabel("Scale factor, log scale")
     plt.ylabel("Magnitude")
-    plt.plot(scale_factors_log, magnitudes_two, 'r', 
-             label='Two points separated by 1') 
+    plt.plot(scale_factors_log, magnitudes_two, 'b', 
+             label='Two points separated by 1')
+    ''' 
     plt.plot(scale_factors_log, magnitudes_two_small, 'b',
              label='Two points separated by 0.001')
     plt.plot(scale_factors_log, magnitudes_euc, 'm',
-             label='Four point space')
+             label='Four point space')'''
+    font = {'family' : 'normal',
+            'size'   : 24}
 
+    plt.rc('font', **font)
     
     # plt.subplot(212)
     # plt.plot(scale_factors_log, magnitudes_two)
-    plt.axis([-1.0,4.5,1,4.1])
-    plt.legend(loc='ul')
+    plt.axis([-1.0,1.5,1,2.1])
+    #plt.legend(loc='ul')
     plt.show()
 
     

### 2017-04-11 Drafts/Draft.tex
error_bounding

@@
 \advisor{Vin de Silva}
-\title{M\"obius Inversion: Construction and Applications}
-\newcommand{\kron}{\boldsymbol{\otimes}}
+\title{M\"obius Inversion: From Posets to Categories}
+\newcommand{\kron}{\odot}
 \DeclareMathOperator{\fix}{Fix}
@@
 
-\begin{abstract} %TODO: Write a better abstract.
-M\"obius inversion is a general approach to reversing certain kinds of sums.
-In many situations, we know that a value we have access to is equal to the sum over a poset interval of values we want.
-M\"obius inversion is a tool which allows us to access those summed values.
-Here, we first develop the theory of M\"obius inversion on arbitrary posets.
-Then, we investigate its application in various counting examples, including the inclusion-exclusion principle and counting orbits of group actions.
-Finally, we explore an application of M\"obius inversion to data clustering.\
+\begin{abstract}  M\"obius inversion is a general approach for reversing certain kinds of sums.
+We start by defining M\"obius inversion in its usual form, over a partially ordered set.
+We explore traditional applications in the integer divisibility lattice, including Euler's Totient.
+We then use the lattice of subgroups to count orbits under a group action.
+In the last two sections, we explore Tom Leinster's generalization of M\"obius inversion to categories and enriched categories, and investigate a data clustering algorithm.
 \end{abstract}
@@
 \section{Introduction and Motivation}
-%TODO: Capitalize "theorem, lemma,..."
 %TODO: Expand introduction with more explicit examples
+We motivate M\"obius inversion using several examples.
+\begin{examp}
 Suppose that we have the integer sequence $g$ of ones:
@@
 \]
+\end{examp}
+
 This relationship is a result of the simple structure of the positive integers.
-However, it is possible to sum up values over more subsets of more complicated structures, such that this relationship isn't so obvious.
-For example, we could add up values of $g$ over a number's divisors, instead of over all numbers less than or equal to it:
+However, it is possible to sum up values over subsets of more complicated structures, such that this relationship isn't so obvious.
+For example, we could add up values of $g$ over a number's divisors, instead of over all numbers less than or equal to it.
+\begin{examp}
+Let $h, g$ be functions on the positive integers defined as follows:
 \[
@@
 It is now much less clear how to obtain $g$ from $h$. In fact, we will see how to reverse this kind of sum soon.
+\end{examp}
 
@@
 In addition to building the necessary machinery for M\"obius inversion, we will consider several applications of it, including a somewhat surprising one in data clustering.
-\section{Initial Example and Posets}
+\section{Initial Example and Partially Ordered Sets}
 M\"obius inversion is a general construct.
@@
 Equivalently, $v_1 \leq v_2$ if $v_1$ is the projection of $v_2$ onto some subset of the axes.
-%TODO: Make sure this is true
 \end{examp}
@@
 \]
-\section{Euler's Totient} %TODO: Fix \Zz^+
+\section{Euler's Totient}
 Euler's Totient is a famous function in number theory, which counts the how many numbers are relatively prime to a particular value.
-We denote the function by $\varphi : \Nn \rightarrow \Nn$, and its definition is:
+We denote the function by $\varphi : \Zz^+ \rightarrow \Zz^+$, and its definition is:
 \[
@@
 \begin{thm}[Gauss]\label{gauss}
-Let $n \in \Nn$ be given. Then 
+Let $n \in \Zz^+$ be given. Then 
 \[
@@
 \]
-In the next example, we will walk through all the steps involved in counting the orbits of a simple action.
+In the next examples, we will walk through all the steps involved in counting the orbits of some simple actions.
+
+\section{Examples}
 \begin{examp}\label{ex:2x2}
@@
 This $\lambda$ is independent of any set $G$ might act on.
-So let's try an example.
+
+So let's try a particular action.
 Suppose we have a $2 \times 2$ chessboard, and we want to place some number of rooks on the board such that none of them attack one another.
@@
 
-Also, we define the \emph{complement} function/matrix $c$ as follows: %TODO: Change variable name
+Also, we define the \emph{complement} function/matrix $c$ as follows: %TODO: Change variable name?
 \[
@@
 \end{align*}
-%TODO: Debrief
+This is precisely the Inclusion-Exclusion principle.
+
+It makes sense that we would use M\"obius inversion to prove the Inclusion-Exclusion principle.
+The difficult aspect of counting how many elements are in the union of the sets is avoiding double-counting.
+%TODO: Finish this
 
@@
 There are several equivalent definitions, all somewhat technical, but the construct itself is quite intuitive once you get used to it.
-\begin{defn}
+\begin{defn}[\cite{Kelly1}]
 A \textit{category} $C$ consists of:
@@
 \end{examp}
-A \emph{small} category is a category whose collection of objects is a set.
 
@@
 It is not clear what kind of sum we are attempting to reverse - unlike the poset case, we don't know why we would want to reverse the operation of multiplying by $\zeta$.
-It turns out that inverting $\zeta$ (if we are able to) will allow us to calculate what is called the \emph{Euler-Leinster characteristic} of a category, which is the analog of an Euler characteristic on other structures.
+It turns out that inverting $\zeta$ (if we are able to) will allow us to calculate what is called the \emph{Euler--Leinster characteristic} of a category, which is the analog of an Euler characteristic on other structures.
 We will explore this over the next few sections.
@@
 
-\begin{defn}\label{cat_mob} 
+\begin{defn}[\cite{Lein1}]\label{cat_mob} 
 Let $C$ be a finite category. Let $\zeta$ be the similarity matrix defined above. Then the \emph{M\"obius function} $\mu$ on $C$, if it exists, is defined by 
@@
 
-\section{Euler-Leinster Characteristic of a Category}
-We are now ready to construct central definition of this section: the Euler-Leinster characteristic (or just Euler characteristic) of a category.
+\section{Euler--Leinster Characteristic of a Category}
+We are now ready to construct central definition of this section: the Euler--Leinster characteristic (or just Euler characteristic) of a category.
 The entire construction can be found in \cite{Lein1, Lein2, Lein4}, and is due to Tom Leinster.
@@
 
-The following definition is due to \cite{Lein1}.
-\begin{defn}\label{cat_euler}
-Let $\omega$ be a weighting on a finite category $A$. Then the \emph{Euler-Leinster characteristic}, or just the \emph{Euler characteristic}, of $A$, denoted by $\chi(A)$, is defined by
+\begin{defn}[Leinster, \cite{Lein1}]\label{cat_euler}
+Let $\omega$ be a weighting on a finite category $A$. Then the \emph{Euler--Leinster characteristic}, or just the \emph{Euler characteristic}, of $A$, denoted by $\chi(A)$, is defined by
 \[
@@
 It turns out that there is a straightforward way of converting a simplicial complex into a category.
-We will find that the Euler-Leinster characteristic of the resulting category will be the same as the Euler characteristic of the simplicial complex.
+We will find that the Euler--Leinster characteristic of the resulting category will be the same as the Euler characteristic of the simplicial complex.
 \begin{defn}
@@
 
-\section{Euler-Leinster Characteristic Examples}
-%TODO
+\section{Euler--Leinster Characteristic Examples}
+%TODO: Groups? Posets are boring... categories which look like other things?
 
@@
 We will explore an alternate method of clustering, in which we do not explicitly group points, but instead estimates the number of clusters using a real, rather than integer, value.
-We will use a generalization of the Euler-Leinster characteristic from Chapter \ref{chap_euler}.
+We will use a generalization of the Euler--Leinster characteristic from Chapter \ref{chap_euler}.
 We start by building some important definitions.
@@
 
-In the next section, we expand the Euler-Leinster characteristic to a generalization of categories called \emph{enriched categories}.
+In the next section, we expand the Euler--Leinster characteristic to a generalization of categories called \emph{enriched categories}.
 We will connect this back to data and metric spaces in subsequent sections.
@@
 such that
-\begin{itemize}
+\begin{enumerate}[(1)]
 \item For each ordered triple of objects $x,y,z \in A$, $(x \otimes y) \otimes z \cong x \otimes (y \otimes z)$
@@
 if $f,g$ are both isomorphisms, $f \otimes g$ also is).
-\end{itemize} 
-\end{defn}
+\item A variety of commutation/coherence conditions are satisfied.
+Here, we did not name the isomorphisms required in points (1) and (2), but in a more thorough definition they would be named.
+It would then be required that the various isomorphisms commute appropriately, along with other technical details.
+\end{enumerate} 
+\end{defn}
+
 There are a variety of commutation requirements which we are not considering in detail here. The property of being functorial is also more involved. For a full account, see \cite{Kelly1}.
@@
 The category $\catname{set}$ is the prototypical example of a monoidal category.
-In that case, the monoidal product $\otimes$ is the tensor product on sets (hence the notation $\otimes$ for the monoidal product), and $u = \{*\}$, some set with a single element.
+In that case, the monoidal product $\otimes$ is the Cartesian product on sets (hence the notation $\otimes$ for the monoidal product), and $u = \{*\}$, some set with a single element.
 
@@
 \end{examp}
-We are now ready to partially define an important generalization on ordinary categories.
+We are now ready to define an important generalization on ordinary categories.
 This definition is highly technical, and a full understanding of it is not necessary for this investigation.
 So we will not spend much time exploring examples or intuition beyond the specific applications we need.
-\begin{defn}\label{en_cat}
+\begin{defn}[\cite{Nog1}]\label{en_cat}
 Let $M$ be a monoidal category. Then a \emph{category enriched by $M$} consists of
@@
 
-\section{Norms and the Euler-Leinster Characteristic}
-The following constructions can be found in \cite{Lein4}.
-
-We would like to generalize the weightings and Euler-Leinster characteristic from Chapter \ref{chap_euler} so we can use them on enriched categories.
+\section{Norms and the Euler--Leinster Characteristic}
+The following constructions can be found in \cite{Nog1, Lein4}.
+
+We would like to generalize the weightings and Euler--Leinster characteristic from Chapter \ref{chap_euler} so we can use them on enriched categories.
 Recall that in Definition \ref{def_weighting}, we used the function $\zeta$ to require that for $\omega$ to be a weighting on a category $C$, for all $a \in C$,
@@
 We define this as follows:
-\begin{defn}
+\begin{defn}\label{def:norm}
 Let $(M,\otimes)$ be a monoidal category. Then the function $| \cdot |: M \rightarrow \Rr$ is a \emph{norm} on $M$ if, for any $a,b\in M$, and if $u$ is the unit object of $M$, it satisfies
@@
 
-It's not clear why we require that the norm function be multiplicative. %TODO: If I get into products, discuss. Add more examples of norms
+It's not clear why we require that the norm function be multiplicative.
+We will see a reason why in Section \ref{sec:prod}, where we will explore a notion of a product category.
+There, it will be necessary that norms behave in this way.
 
@@
 
-Now that we know how to replace the norm function on sets, we can redefine the $\zeta$ function, M\"obius inversion, weightings, and the Euler-Leinster characteristic on enriched categories.
+Now that we know how to replace the norm function on sets, we can redefine the $\zeta$ function, M\"obius inversion, weightings, and the Euler--Leinster characteristic on enriched categories.
 We go through these definitions, and then we will explore their ramifications.
@@
 
-\begin{defn}
+\begin{defn}[\cite{Nog1}]
 Let $C$ be a finite category enriched over a monoidal category $M$.
@@
 
-\begin{defn}
+\begin{defn}[\cite{Nog1}]
 Let $C$ be a finite category enriched over a monoidal category $M$, with a specified norm $|\cdot|$.
 Let $\omega$ be a weighting on $C$.
-Then the \emph{Euler-Leinster characteristic} of $C$, denoted $\chi_{|\cdot|}(C)$, is defined by
+Then the \emph{Euler--Leinster characteristic} of $C$, denoted $\chi_{|\cdot|}(C)$, is defined by
 \[
@@
 When $C$ is an enriched category, $\chi(C)$ is sometimes called the \emph{magnitude} of $C$ (for example, in \cite{Lein4}).
-We reserve that terminology for a particular class of enriched categories which we will soon introduce, and continue to refer to the general construction as the Euler-Leinster characteristic or the Euler characteristic of $C$.
+We reserve that terminology for a particular class of enriched categories which we will soon introduce, and continue to refer to the general construction as the Euler--Leinster characteristic or the Euler characteristic of $C$.
 \end{rmk}
@@
 This is a category enriched over a monoidal category whose objects are non-negative real numbers, allowing us to preserve a notion of distance.
-\begin{defn}\label{gen_met}
+
+\begin{defn}[Lawvere, \cite{Lawv1}]\label{gen_met}
 Let $D$ be the monoidal category of non-negative real numbers defined in Example \ref{cat_real}. Let $C$ be a category enriched over $D$. Then we call $C$ a \emph{generalized metric space}.
@@
 So we can always express a metric space as a generalized metric space.
-This allows us to find the Euler-Leinster characteristic of a finite set of data points in a metric space.
+This allows us to find the Euler--Leinster characteristic of a finite set of data points in a metric space.
 But first we must decide on the norm we will use on $D$, our monoidal category, and to do that, we take a step back and consider why we are doing this.
@@
 This looks exactly like the requirement (from Definition \ref{def_weighting}) for $\omega$ to be a weighting on a category $M$!
-So adding up values of $\omega$ is the same as finding the Euler-Leinster characteristic of $M$, assuming we can properly encode the structure of the spectators into a category.
+So adding up values of $\omega$ is the same as finding the Euler--Leinster characteristic of $M$, assuming we can properly encode the structure of the spectators into a category.
 This is the key motivation behind the use of the Euler characteristic to count clusters.
@@
 \begin{figure}[h]
+%TODO: Replace plot
 \[
@@
 We have a special name for the Euler characteristic of a generalized metric space which results from this particular norm:
-\begin{defn}
+\begin{defn}[\cite{Lein4}]
 Let $M$ be a generalized metric space. Let $|\cdot|_t:D \rightarrow \Rr$ be defined by
@@
 \]
-\caption{A plot of $\chi_t(M_2)$ against $t$ on a logarithmic scale.}
+\caption{A plot of $\chi_t(M_2)$ against $\log(t)$, where $t$ is the scale factor.}
 \label{fig:2pt_mag}
@@
 \end{examp}
-\section{Product Spaces and Approximations}
+\section{Product Spaces and Approximations}\label{sec:prod}
 In Figure \ref{fig:3+4}, we see two sets of points, $M$ and $N$. $M$ has three points while $N$ has four.
@@
 
-$A$ is an approximation of what is called a \emph{tensor product category}.
-In this section, we define the construction formally, and explore how the Euler-Leinster characteristic behaves when two categories are combined in this way.
+$A$ is an approximation of what is called a \emph{Cartesian product category}.
+In this section, we define the construction formally, and explore how the Euler--Leinster characteristic behaves when two categories are combined in this way.
 In particular, we would like for the magnitude of a product space to be the product of the magnitudes of the original spaces - this is how the number of clusters seems like it should behave when we look at examples like $A$ above.
@@
 \begin{defn}
+
 Let $A,B$ be categories both enriched over a symmetric monoidal category $M$.
 Fix a norm on $M$.
-Then the \emph{tensor product} of $A$ and $B$, denoted $A \times B$, is the category enriched over $M$ defined as follows:
+Then the \emph{Cartesian product} (or simply the \emph{product}) of $A$ and $B$, denoted $A \times B$, is the category enriched over $M$ defined as follows:
 \begin{itemize}
@@
 \begin{rmk}
-The tensor product of two categories enriched over $M$ is indeed a category enriched over $M$. There are many requirements to check, and we do not go through all of them here.
+The Cartesian product of two categories enriched over $M$ is indeed a category enriched over $M$. There are many requirements to check, and we do not go through all of them here.
 \end{rmk}
@@
 \end{figure}
-Suppose that $A(a_1, a_2) = 1, B(b_1, b_2) = 2$. Recall that the monoidal product is $+$. So the tensor product category $A \times B$ looks like this:
+Suppose that $A(a_1, a_2) = 1, B(b_1, b_2) = 2$. Recall that the monoidal product is $+$. So the product category $A \times B$ looks like this:
 \begin{figure}[H]
@@
 \]
-\caption{$A \times B$. It is impossible to draw this product space to scale because of the way distances behave under the tensor product.. }
+\caption{$A \times B$. It is impossible to draw this product space to scale because of the way distances behave under the Cartesian product.}
 \end{figure}
@@
 Suppose we used some clustering scheme where points within a threshold distance $t$ of each other were put into the same cluster.
-This is not how magnitude works, of course, but it is easier to visualize.
+This is not how magnitude works, but it is easier to visualize.
 Then we have three cases:
@@
 \end{description}
-So in all cases, the number of clusters in $A \times B$ is the product of the numbers of clusters in $A$ and $B$. We will see that this isn't a coincidence.
+So in all cases, the number of clusters in $A \times B$ is the product of the numbers of clusters in $A$ and $B$.
+We will see that if we count clusters using the magnitude of the space, the same thing happens.
 \end{examp}
@@
 Magnitude is obtained using $\zeta$, the similarity matrix.
-So we are interested in how the similarity matrix behaves under the tensor product.
+So we are interested in how the similarity matrix behaves under the Cartesian product.
 It turns out that the similarity matrix of a product category is obtained using the matrix \emph{Kronecker product}, not coincidentally (but confusingly) written using $\otimes$.
-Because this is the same notation used for the monoidal product, we will bold the operator when we are referring to the Kronecker product: $\kron$.
+Because this is the same notation used for the monoidal product, we will use non-standard notation for the Kronecker product: $\kron$.
 \begin{defn}
@@
 \[
-(A \otimes B) \times (C \otimes D) = AC \otimes BD.
+(A \otimes B) (C \otimes D) = AC \otimes BD.
 \]
@@
 \end{rmk}
-We show that this definition is useful by connecting it immediately to the tensor product of categories.
-
-\begin{lemma}\label{tensor_kron}
+We show that this definition is useful by connecting it immediately to the Cartesian product of categories.
+
+\begin{lemma}\label{prod_kron}
 Let $A, B$ be categories both enriched over a symmetric monoidal category $M$.
@@
 \begin{proof}
-Let $a_1, a_2 \in A, b_1, b_2 \in B$ be given. Recall that norms are multiplicative. Then the entry of $\zeta_{A \times B}$ corresponding with $(a_1, b_1), (a_2, b_2)$ should contain 
+Let $a_1, a_2 \in A, b_1, b_2 \in B$ be given.
+Recall that norms are multiplicative (see Definition \ref{def:norm}).
+Then the entry of $\zeta_{A \times B}$ corresponding with $(a_1, b_1), (a_2, b_2)$ should contain
 \begin{align*}
@@
 Given this lemma, we can prove that the behavior we saw in Example \ref{met_prod_ex} occurs when we count clusters using the magnitude function.
-In fact, it turns out the for any category enriched over a symmetric monoidal category, the Euler-Leinster characteristic is multiplicative over the tensor product.
+In fact, it turns out the for any category enriched over a symmetric monoidal category, the Euler--Leinster characteristic is multiplicative over the product.
 
@@
 \begin{proof}
-Let $\zeta_A, \zeta_B$ be the similarity matrices of $A,B$. Then, by Theorem \ref{tensor_kron}, the similarity matrix of $A \times B$ is $\zeta_A \kron \zeta_B$.
+Let $\zeta_A, \zeta_B$ be the similarity matrices of $A,B$. Then, by Theorem \ref{prod_kron}, the similarity matrix of $A \times B$ is $\zeta_A \kron \zeta_B$.
 
@@
 \]
-\caption{The magnitude of $M$ alongside the magnitudes of the factor spaces, on a logarithmic scale.}
+\caption{The magnitude of $M$ alongside the magnitudes of the factor spaces against $\log(t)$.}
 \label{fig:prod_mag}
@@
 \begin{defn}\label{def:spec}
-Let $n$ be given. Let $|v|$ denote the Euclidean vector norm. Then the \emph{spectral norm} on real- (or complex-) valued $n \times n$ matrices, denoted $||\cdot ||$, is defined by
-\[
-||M|| = \sup_{0 \neq x \in \Rr^n}\left\{ \frac{|Ax|}{|x|} \right\}.
+Let $n$ be given. Let $|v|$ denote the Euclidean vector norm. Then the \emph{spectral norm} on real- (or complex-) valued $n \times n$ matrices, denoted $||\cdot ||_s$, is defined by
+\[
+||M||_s = \sup_{0 \neq x \in \Rr^n}\left\{ \frac{|Ax|}{|x|} \right\}.
 \]
@@
 \begin{rmk}
-Definition \ref{def:spec} does not tell us how to find the spectral norm of a matrix. However, it is not difficult to do so. For a given $M$, we can find $||M||$ as follows:
-
-Let $M^*$ be the adjoint, or conjugate transpose, of $M$. Let $\lambda_1$ be the largest eigenvalue of the matrix $MM^*$. Then $\lambda_1$ will be real-valued, and $||M||=\sqrt{\lambda_1}$.
+Definition \ref{def:spec} does not tell us how to find the spectral norm of a matrix. However, it is not difficult to do so. For a given $M$, we can find $||M||_s$ as follows:
+
+Let $M^*$ be the adjoint, or conjugate transpose, of $M$. Let $\lambda_1$ be the largest eigenvalue of the matrix $MM^*$. Then $\lambda_1$ will be real-valued, and $||M||_s=\sqrt{\lambda_1}$.
 
@@
 
-There are some simple properties of the spectral norm which we will need.
+We also define a second matrix norm, called the $L_1$ norm.
+\begin{defn}
+Let $A$ be an $n \times n$ matrix. Then the \emph{$L_1$ norm} of $A$, denoted $||A||_2$, is the sum of the absolute values of entries of $A$. In other words,
+\[
+||A||_2 = \sum_{i = 1}^n\sum_{j = 1}^n |A_{ij}|.
+\]
+\end{defn}
+\begin{rmk}
+This is one of an infinite number of $L_p$ norms, one for each positive integer $p$. For any matrix $A$ and positive integer $p$, 
+\[
+||A||_p = \sqrt[p]{\sum_{i = 1}^n\sum_{j = 1}^n |A_{ij}|^p}.
+\]
+\end{rmk}
+
+There are three simple properties of both norms which we will need.
 \begin{lemma}\label{lem:norm_prop}
-%TODO: Omit additivity if I don't need it.
-Let $A, B$ be $n \times n$ matrices. Then
-\begin{enumerate}[(a)]
+Let $A, B$ be $n \times n$ matrices. Let $||\cdot||$ be \emph{either} the spectral norm or the $L_1$ norm. Then
+\begin{enumerate}
 \item \[
+||AB|| \leq ||A||\times ||B||,
+\]
+
+\item
+\[
 ||A + B|| \leq ||A|| + ||B||.
 \]
-\item \[
-||AB|| \leq ||A||\times ||B||
+\item 
+\[
+||A|| = 0 \iff A = 0.
 \]
@@
 \begin{proof}
-\begin{enumerate}[(a)]
-\item Recall that if $|\cdot|$ is the Euclidean norm on vectors in $\Rr^n$, then for all $v,w \in \Rr^n$,
-\[
-|v + w| \leq |v| + |w|.
-\]
-This is the triangle inequality. So for all $v \in \Rr^n$, we have
-\begin{align*}
-|(A + B)v| &= |Av + Bv| \\
-&\leq |Av| + |Bv|.
-\end{align*} 
-\[\sup_{0 \neq x \in \Rr^n}\left\{ \frac{|(A + B)x|}{|x|} \right\} \leq \sup_{0 \neq x \in \Rr^n}\left\{ \frac{|Ax|}{|x|} \right\} + \sup_{0 \neq x \in \Rr^n}\left\{ \frac{|Bx|}{|x|} \right\}.
-\]
-\item Let $v \in \Rr^n$ be given. Then by the definition of the spectral norm,
-\begin{align*}
-|ABv| &\leq |A(||B|| \times |v|)|\\
-&\leq (||A|| \times ||B||)|v|.
-\end{align*}
+\begin{description}
+\item[Spectral Norm:]
+\begin{enumerate}
+\item By the definition of the spectral norm, for any $v \in \Rr^n$,
+\begin{align*}
+|ABv| &\leq |A(||B||_s \times |v|)|\\
+&\leq (||A||_s \times ||B||_s)|v|.
+\end{align*}
+It follows that 
+ \[
+||AB|| \leq ||A||_s\times ||B||.
+\]
+\item For any $v \in \Rr^n$,
+\begin{align*}
+|(A + B)v| &= |Av + Bv|\\
+ &\leq |Av| + |Bv|\\
+ &\leq ||A||_s + ||B||_s)v.
+\end{align*}
+\item It is clear that if $A=0$ then $||A||_s=0$.
+Now suppose that $A$ is not zero.
+Then the column space of $A$ has nonzero dimension, so there exists a $v$ such that $Av \neq 0$.
+So $||A||_s \geq \frac{|Av|}{|v|} > 0$.
 \end{enumerate}
+\item[$L_1$ Norm:]
+\begin{enumerate}
+\item We have
+\begin{align*}
+|AB_ij| &= \left| \sum_{k = 1}^nA_{ik}B{kj}\right|\\
+&\leq \sum_{k = 1}^n|A_{ik}||B{kj}|. \text{ Therefore}\\
+||AB||_1 &\leq \sum_{i = 1}^n\sum_{j=1}^n\sum_{k=1}^n|A_{ik}||B{kj}|\\
+&\leq \sum_{i = 1}^n\sum_{j=1}^n\sum_{k=1}^n\sum_{l=1}^n|A_{ik}||B_{lj}|\\
+&= ||A||_1||B||.
+\end{align*}
+\item For each $i,j$, $|(A + B)_{ij}| = |A_{ij} + B_{ij}| \leq |A_{ij}| + |B_{ij}|$. The result follows.
+\item If $A=0$ then $||A||_1=0$. On the other hand, if any entry of $A$ is nonzero, then $||A||_1 > 0$ by definition.
+\end{enumerate}
+\end{description}
 \end{proof}
 
+We would like to show some results about limits and series convergence of matrices. To do that, we need to establish some notation. 
+\begin{defn}\label{def:mat_conv}
+Let $A_i$ be an infinite sequence of $m \times n$ matrices, and let $||\cdot||$ be some matrix norm (the spectral norm, the $L_1$ norm, or another matrix norm).
+Suppose we have an $m \times n$ matrix $L$ such that
+\[
+\lim_{i \rightarrow \infty} ||A_i - L|| = 0.
+\]
+Then we say that 
+\[
+\lim_{i \rightarrow \infty} A_i = L.
+\]
+\end{defn}
+It turns out that if the matrices involved are finite-dimensional, the choice of norm does not matter - a sequence will either always converge or always diverge.
+So there is no need to specify the norm when stating a fact about matrix convergence.
+
+This is an instance of the general definition of a convergent sequence in a metric space, where our chosen norm induces a metric.
+Furthermore, for this discussion, we will be concerned primarily with norms of matrices, so this definition of convergence makes sense for us to use.
+
 \begin{lemma}\label{lem:lim0}
-Let $E$ be a real-valued $n \times n$ matrix. Suppose that $||E|| < 1$. Then:
-\[
-\lim_{i \rightarrow \infty}||(-1)^i E^i|| = 0.
+Let $E$ be a real-valued $n \times n$ matrix.  Suppose that $||E||_s < 1$. Then:
+\[
+\lim_{i \rightarrow \infty}E^i = 0.
 \]
@@
 \begin{proof}
-Let $\alpha = ||E|| <1$. We now use Lemma \ref{lem:norm_prop}:
-\begin{align*}
-\lim_{i \rightarrow \infty}||(-1)^i E^i|| &= \lim_{i \rightarrow \infty}||E||^i\\
-&= \lim_{i \rightarrow \infty}\alpha^i\\
+Recall that the meaning of this statement is determined by Definition \ref{def:mat_conv}.
+
+Let $||E|| < 1$. Let $\vec{0}$ represent be the zero matrix. We now use Lemma \ref{lem:norm_prop}:
+\begin{align*}
+\lim_{i \rightarrow \infty}|| E^i - \vec{0}|| &\leq \lim_{i \rightarrow \infty}|| E^i|| - ||\vec{0}|| \\
+&\leq \lim_{i \rightarrow \infty}|| E||^i\\
 &= 0.
 \end{align*}
+Then, by Definition \ref{def:mat_conv},
+\[
+\lim_{i \rightarrow \infty} E^i = 0.
+\]
+\end{proof}
+We actually could have used any norm instead of the spectral norm.
+But the spectral norm is always less than or equal to the $L_1$ norm, as well as most other matrix norms, so the more general result is implied.
+
 This allows us to prove a useful fact which allows us to approximate the inverses of certain matrices.
-\end{proof}
 \begin{thm}\label{thm:approx}
@@
 (A - E)^{-1} &= A^{-1} + A^{-1}EA^{-1} + A^{-1}EA^{-1}EA^{-1} + \cdots\\
-&= A^{-1} + \sum_{i = 1}^\infty (EA^{-1})^i.
+&= A^{-1} + A^{-1}\sum_{i = 1}^\infty (EA^{-1})^i.
 \end{align*}
@@
 \end{proof}
+\begin{rmk}
+Recall that, because we rely on Lemma \ref{lem:lim0}, the meaning of this theorem is governed by Definition \ref{def:mat_conv}. That is what the equals sign really means. 
+\end{rmk}
 This fact makes sense.
@@
 \[
-(A - E)^{-1} - A^{-1} = \sum_{i = 1}^\infty (EA^{-1})^i.
-\]
-This means that we can let $\Phi = \sum_{i = 1}^\infty (EA^{-1})^i$ be the ``error term.'' If we can bound the sum of the entries of the matrix $\Phi$, that is a bound on the difference between the magnitude of a space whose similarity matrix is $A$, and one whose similarity matrix is $A + E$.
-
-We can walk through an example:
+(A - E)^{-1} - A^{-1} = A^{-1}\sum_{i = 1}^\infty (EA^{-1})^i.
+\]
+This means that we can let $\Phi = A^{-1}\sum_{i = 1}^\infty (EA^{-1})^i$ be the ``error term.'' If we can bound the sum of the entries of the matrix $\Phi$, that is a bound on the difference between the magnitude of a space whose similarity matrix is $A$, and one whose similarity matrix is $A + E$.
+Of course, this approximation scheme only works if both spaces admit M\"obius inversion.
+
+Let $A$ be a generalized metric space which admits M\"obius inversion.
+Suppose we know $\chi(A)$, the magnitude of $A$, and we would like to know how much adding $E$, a perturbation matrix, to $\zeta_A$, will change the magnitude.
+Suppose that $E$ satisfies the condition of Theorem \ref{thm:approx}.
+
+The magnitude of $A$ is equal to $||\mu_A||_1 = ||\zeta_A^{-1}||_1$, where $||\cdot||_1$ is the $L_1$ matrix norm.
+
+We demonstrate this approximation of magnitude through an example:
 \begin{examp}
-Let $M$ be the following generalized metric space:
+We will consider a situation quite similar to Example \ref{ex:4pt}. Let $M$ be the following generalized metric space:
 \begin{figure}[H]
@@
 \end{figure}
-Let $\zeta_A, \zeta_B, \zeta_{A \times B}, \zeta_M$ be the similarity matrices of $A, B, A \times B$, and $M$ respectively. We can write each of them down:
+Suppose that we are trying to approximate $M$ using a product space of $A$ and $B$. We are interested in finding a bound on the error of our estimate.
+
+Let $\zeta_A, \zeta_B, \zeta_{A \times B}, \zeta_M$ be the similarity matrices of $A, B, A \times B$, and $M$ respectively.
+Recall that we are using the norm $|x| = e^{-tx}$, where we will vary $t$.
+So the matrices are as follows:
 \begin{align*}
@@
 \begin{bmatrix}
-1 & e^{-d} \\
-e^{-d} & 1
+1 & e^{-td} \\
+e^{-td} & 1
 \end{bmatrix}\\
@@
 \begin{bmatrix}
-1 & e^{-1} \\
-e^{-1} & 1
+1 & e^{-t} \\
+e^{-t} & 1
 \end{bmatrix}\\
@@
 \begin{bmatrix}
-1 & e^{-1} & e^{- d} & e^{-(1 + d)}\\
-e^{-1} & 1 & e^{-(1 + d)}& e^{- d}\\
-e^{-d} &e^{-(1 + d)} & 1 & e^{-1}\\
-e^{-(1 + d)} & e^{-d} & e^{-1} & 1
+1 & e^{-t} & e^{- td} & e^{-t(1 + d)}\\
+e^{-t} & 1 & e^{-t(1 + d)}& e^{- td}\\
+e^{-td} & e^{-t(1 + d)} & 1 & e^{-t}\\
+e^{-t(1 + d)} & e^{-td} & e^{-t} & 1
 \end{bmatrix}\\
@@
 \begin{bmatrix}
-1 & e^{-1} & e^{- d} & e^{-\sqrt{1 + d^2}}\\
-e^{-1} & 1 & e^{-\sqrt{1 + d^2}}& e^{- d}\\
-e^{-d} & e^{-\sqrt{1 + d^2}}& 1 & e^{-1}\\
-e^{-\sqrt{1 + d^2}} & e^{-d} & e^{-1} & 1
+1 & e^{-t} & e^{- td} & e^{-t\sqrt{1 + d^2}}\\
+e^{-t} & 1 &  e^{-t\sqrt{1 + d^2}}& e^{- td}\\
+e^{-td} &  e^{-t\sqrt{1 + d^2}} & 1 & e^{-t}\\
+ e^{-t\sqrt{1 + d^2}}& e^{-td} & e^{-t} & 1
 \end{bmatrix}
 \end{align*}
-The similarity matrices of $A \times B$ and $M$ have most entries identical. We can quantify the difference between them. For any $d \in (0, \infty)$, let 
-\begin{align*}
-\ep_d = e^{-(1 + d)} - e^{-\sqrt{1 + d^2}}\\
-E_d = \begin{bmatrix}
-0 & 0 & 0 & \ep \\
-0 & 0 & \ep & 0 \\
-0 & \ep & 0 & 0 \\
-\ep & 0 & 0 & 0
+The similarity matrices of $A \times B$ and $M$ have most entries identical. We can quantify the difference between them. For any $d, t \in (0, \infty)$, let 
+\begin{align*}
+\ep_{dt} = e^{-t(1 + d)} - e^{-t\sqrt{1 + d^2}}\\
+E_{dt} = \begin{bmatrix}
+0 & 0 & 0 & \ep_{dt} \\
+0 & 0 & \ep_{dt} & 0 \\
+0 & \ep_{dt} & 0 & 0 \\
+\ep_{dt} & 0 & 0 & 0
 \end{bmatrix}
 \end{align*}
-Then 
-\[
-\zeta_M = \zeta_{A \times B} - E_d.
-\]
-%TODO: Plot epsilon
+Then for each $d,t$,
+\[
+\zeta_M = \zeta_{A \times B} - E_{dt}.
+\]
+Note that I am omitting the $d,t$ subscripts from the similarity matrices to avoid clutter, but they do depend on $d$ and $t$.
+
 If we are interested in bounding the difference in magnitude of $M$ and $A \times B$, then we can apply Theorem \ref{thm:approx}.
@@
 \[
-\mu_M = \mu_{A \times B} + \sum_{i = 1}^\infty (E_d\zeta_{A \times B}^{-1})^i.
+\mu_M = \mu_{A \times B} + \mu_{A \times B}\sum_{i = 1}^\infty (E_{dt}\zeta_{A \times B}^{-1})^i.
 \]
@@
 \]
+\caption{Magnitudes and error bounds, $d = 0.1$, error calculated to third term, against $\log(t)$ where $t$ is the scale factor.}
+\label{fig:approx10}
 \end{figure}
@@
 
+If we were trying to approximate $M$ with $A \times B$, then we would not have access to the orange line in Figure \ref{fig:approx10}.
+But in this case, we can see that we could determine the line with good accuracy using only $A \times B$ and the error bounds.
+
 As we move the value of $d$ closer to 1, we expect both the error bounds and the actual error to increase.
 The product space and the Euclidean space will differ more as their scales become more similar.
-Here we see what happens when $d=1$, so our scales are identical.
-Both spaces move smoothly from having a single cluster to having four clusters, and there is much more significant error.
-In particular, $M$ now forms a square of points, and points at opposite corners have a distance equal to the diagonal of the square.
-On the other hand, in the product space, those points have a distance equal to twice the side of the square.
-This error is more significant the more similar the scales of the factor spaces.
-CLARIFY!
-%TODO: Clarify
+Recall that the only pairs of points which differ at all in distance between $A \times B$ and $M$ are points at opposite corners (see Figure \ref{fig:4pt}).
+When one dimension is extremely small, that diagonal distance is very close to the length of the longer side.
+On the other hand, in the product space the distance is the sum of the dimensions.
+When the small dimension is small enough, that, too, is essentially the distance of the longer side.
+
+On the other hand, as $d$ approaches 1, the space becomes square.
+If $d=1$, then the distance of opposite points in $M$ will be $\sqrt{2}$, while in the product space the distance will be 2.
+This is quite a significant difference.
+In the next example, we look at exactly this case.
+
+Here we see what happens when $d=1$, so our dimensions are identical. Both spaces move smoothly from having a single cluster to having four clusters, and there is more error. 
 \begin{figure}[H]
@@
 \]
+\caption{Magnitudes and error bounds, $d = 1$, error calculated to third term, against $\log(t)$ where $t$ is the scale factor.}
 \end{figure}
 \end{examp}
+However, even if the orange line were removed, we would still have a good idea of the cluster structure of $M$.
+We would know that $M$ starts with one cluster, and then at a scale factor of approximately $10^{-\frac12} \approx 3$, the points begin to move apart.
+They smoothly separate until four clusters form.
+Because of the error bounds, we know that given the behavior of $A \times B$, the magnitude of $M$ can't differ too much from that behavior.
 

### 2017-04-12 Drafts/Draft.tex
editing error bounding

@@
 \end{examp}
+
 \section{Approximations and Error Bounding}
@@
 Note that these norms are not directly related to the norms we defined on monoidal categories - both are non-negative real-valued functions, but they operate on different structures.
+
+There are many norms on matrices. Formally, a matrix norm is simply a function from matrices to the non-negative real numbers which satisfies certain properties.
 
@@
 \end{proof}
-
-We would like to show some results about limits and series convergence of matrices. To do that, we need to establish some notation. 
+Again, there are many other matrix norms. For our purposes, when a theorem uses an arbitrary matrix norm, we will assume that it satisfies Lemma \ref{lem:norm_prop}.
+
+Now that we have some basic technology for working with matrix norms, we would like to show some results about limits and series convergence of matrices.
+To do that, we need to establish some notation.
 \begin{defn}\label{def:mat_conv}
@@
 \begin{lemma}\label{lem:lim0}
-Let $E$ be a real-valued $n \times n$ matrix.  Suppose that $||E||_s < 1$. Then:
+Let $E$ be a real-valued $n \times n$ matrix.  Suppose that for some matrix norm $||\cdot||$, $||E|| < 1$. Then:
 \[
@@
 \begin{proof}
-Recall that the meaning of this statement is determined by Definition \ref{def:mat_conv}.
+Recall that we are supposing that any norm we use satisfies Lemma \ref{lem:norm_prop}.
 
@@
 \end{proof}
-We actually could have used any norm instead of the spectral norm.
-But the spectral norm is always less than or equal to the $L_1$ norm, as well as most other matrix norms, so the more general result is implied.
 
@@
 \begin{thm}\label{thm:approx}
-Let $A$ be an invertible $n \times n$ matrix, and let $E$ be an $n \times n$ matrix such that $||E|| < \frac 1{||A^{-1}||}$. Then $(A-E)$ is invertible, and
+Let $A$ be an invertible $n \times n$ matrix, let $||\cdot||$ be some matrix norm, and let $E$ be an $n \times n$ matrix such that $||E|| < \frac 1{||A^{-1}||}$. Then $(A-E)$ is invertible, and
 \begin{align*}
@@
 \end{rmk}
-This fact makes sense.
-The spectral norm of $A^{-1}$ is the inverse of the smallest eigenvalue of $AA^*$, and it tells us how much $A$ is capable of reducing the euclidean norm of a vector it multiplies.
+This fact makes sense, in particular if we consider the spectral norm.
+$||A^{-1}||_s$ is the inverse of the smallest eigenvalue of $AA^*$, and it tells us how much $A$ is capable of reducing the euclidean norm of a vector it multiplies.
 So if that value is very large, $A$ is very nearly not invertible.
@@
 
-We can use this result to determine how different the magnitude of a space similar to the one from Example \ref{ex:4pt} differed from that of an actual product space.
-Given matrices $A$ and $E$ which satisfy Theorem \ref{thm:approx}, we know that
-\[
-(A - E)^{-1} - A^{-1} = A^{-1}\sum_{i = 1}^\infty (EA^{-1})^i.
-\]
-This means that we can let $\Phi = A^{-1}\sum_{i = 1}^\infty (EA^{-1})^i$ be the ``error term.'' If we can bound the sum of the entries of the matrix $\Phi$, that is a bound on the difference between the magnitude of a space whose similarity matrix is $A$, and one whose similarity matrix is $A + E$.
-Of course, this approximation scheme only works if both spaces admit M\"obius inversion.
+Next, we use Theorem \ref{thm:approx} to find a closed-form bound on how much a perturbation matrix changes the magnitude of a generalized metric space.
 
@@
 Suppose we know $\chi(A)$, the magnitude of $A$, and we would like to know how much adding $E$, a perturbation matrix, to $\zeta_A$, will change the magnitude.
-Suppose that $E$ satisfies the condition of Theorem \ref{thm:approx}.
-
-The magnitude of $A$ is equal to $||\mu_A||_1 = ||\zeta_A^{-1}||_1$, where $||\cdot||_1$ is the $L_1$ matrix norm.
+Suppose that $||EA^{-1}|| < 1$ for some matrix norm, so we can use Theorem \ref{thm:approx}.
+
+The magnitude of $A$ is equal to the sum of the entries of $\zeta_A^{-1}$.
+So the $L_1$ norm of the difference between $\zeta_A$ and $\zeta_A + E$ will be an upper bound on how much adding $E$ changes the magnitude of $A$.
+We can repeatedly use Lemma \ref{lem:norm_prop} to isolate the error term:
+\begin{align}
+\left|\left|\zeta_A^{-1} - \zeta_A^{-1} - \zeta_A^{-1}\sum_{i = 1}^\infty (EA^{-1})^i\right|\right|_1 \nonumber 
+&= \left|\left|\zeta_A^{-1}\sum_{i = 1}^\infty (EA^{-1})^i\right|\right|_1 \nonumber \\
+&\leq ||\zeta_A^{-1}||_1\sum_{i = 1}^\infty ||(EA^{-1})^i||_1. \label{eq:series}
+\end{align}
+
+Suppose that $||EA^{-1}||_1 <1$. Then we can convert \eqref{eq:series} to a closed form. 
+\begin{align*}
+||\zeta_A^{-1}||_1\sum_{i = 1}^\infty ||EA^{-1}||_1^i &\leq
+||\zeta_A^{-1}||_1 \sum_{i = 1}^\infty||(\zeta_A + E)^{-1}||_1^i\\
+ &\leq ||\zeta_A^{-1}||\frac{||EA^{-1}||_1}{1-||EA^{-1}||_1}.
+\end{align*}
+
+However, as we mentioned earlier, all matrix norms are equivalent when it comes to convergence.
+So if $||EA^{-1}||_1 \geq 1$ but, for example, $||EA^{-1}||_s <1$, the above would no longer work, but we would still expect \eqref{eq:series} to converge.
+This might be useful, because the spectral norm is often smaller than the $L_1$ norm.
+To make this work, we will need some way of replacing the $L_2$ norm with a spectral norm.
+It turns out we can do that:
+\begin{lemma}\label{lem:norm_switch}
+Let $A$ be an $n \times n$ matrix. Then
+\[
+||A||_1 \leq n^2||A||_s.
+\]
+\end{lemma}
+\begin{proof}
+Let $m$ be the absolute value of the largest element of $A$.
+Suppose that for some $i,j, |A_{ij}| > ||A||_s$.
+Let $e_j$ be the column vector with a one in index $j$ and zeros everywhere else.
+Then $Ae_j$ will have $A_{ij}$ in its $i$'th index, so $|Ae_j| \geq |A_{ij}| >||A||_s$.
+Because $|e_j|=1$, this is a contradiction.
+So $m \leq ||A||_1$.
+$||A||_1 \leq n^2m$, so $||A||_1 \leq n^2||A||_s$.
+\end{proof}
+
+This means that we can rewrite \eqref{eq:series} in the following way:
+\begin{align*}
+||\zeta_A^{-1}||_1\sum_{i = 1}^\infty ||EA^{-1}||_1^i &\leq n^2||\zeta_A^{-1}||_1\sum_{i = 1}^\infty ||(EA^{-1})^i||_s^i\\
+&\leq n^2||\zeta_A^{-1}||_1\sum_{i = 1}^\infty ||(EA^{-1})||_s^i\\
+&\leq n^2||\zeta_A^{-1}||\frac{||EA^{-1}||_s}{1-||EA^{-1}||_s}.
+\end{align*}
+
+We have (possibly) reduced the value of the norm, at the price of a factor of $n^2$. We can exchange the $L_1$ norm for other matrix norms in a similar fashion, using different constants.
 

### 2017-04-12 Thesis_Comp/matrix.py

@@ -1,3 +1,4 @@
+from __future__ import division
 from matplotlib import pyplot as plt
 import numpy as np
 import math 
@@ -14,10 +15,33 @@ def calc_E(d, scale=1):
         Em[i,j] = epsilon
     return Em
 
+def l2(A):
+    # L_2 norm of a matrix
+    total = 0
+    for row in A:
+        for el in row:
+            total += abs(el)
+    return total
+
+def error_bounds(A, E):
+    # returns (bounded 1-norm of phi, 1-norm of phi). 1-norm of EA^-1
+    # must be less than one.
+    ET = 0
+    inv_A = inv(A)
+    l2_EAinv = l2(E*inv_A)
+    assert l2_EAinv < 1, "L2 norm is too large"
+    for i in range(1, n_terms):
+        ET = ET + inv_A*mp((E *  inv_A ),i)
+    actual = abs(np.sum(ET))
+    limit = l2_EAinv / (1 - l2_EAinv)
+    return l2(inv_A) * limit
+    
+    
+
 def inv_with_error(d, scale=1, n_terms=3):
     """ 
     Returns a tuple
-    (A^1, (A - E)^-1, Magnitude Error Bound)
+    (A^1, (A - E)^-1, Magnitude Error Bound, Actual Error)
     """
     # Put together A
     A = np.empty((4,4))
@@ -31,14 +55,10 @@ def inv_with_error(d, scale=1, n_terms=3):
         A[i,j] = math.exp(-scale*(1 + d))
     A = np.matrix(A)
     E = calc_E(d, scale)
-    ET = 0
-    for i in range(1, n_terms):
-        ET = ET + mp((E * (inv(A))),i)
-    eb = abs(np.sum(ET))
-    inv_A = inv(A)
+    eb, actual = error_bounds(A, E)
     inv_AE = inv(A - E)
     # actual = np.sum(inv_A - inv_AE)
-    return (inv_A, inv_AE, eb)
+    return (inv_A, inv_AE, eb, actual)
         
 def magnitudes_error(d, scale=1, n_terms=3):
     # returns (mag(A), mag(A-E), eb)
@@ -77,11 +97,10 @@ def prod_approx_plots():
              label='Euclidean Approximation')
     plt.errorbar(scale_factors_log, product_magnitudes, yerr=errors,fmt='b',
                  label='Product Space Magnitude, Error Bounds')
-    font = {'family' : 'normal',
[…]

### 2017-04-12 Drafts/Draft.tex
with approximation

@@
 \section{Introduction and Motivation}
-%TODO: Expand introduction with more explicit examples
 We motivate M\"obius inversion using several examples.
@@
 \section{Initial Example and Partially Ordered Sets}
-M\"obius inversion is a general construct.
-The classical definition of a M\"obius function is a function $\mu$ on the positive integers which satisfies the following for functions $f,g$ on the positive integers:
+M\"obius inversion is a general construction.
+It refers to the process of using what is called a \emph{M\"obius function} to access individual terms of a sum over some structure.
+We would like the M\"obius function to depend only on that structure, and not on the specific values being added up.
+
+The classical definition of a M\"obius function is a real-valued function $\mu$ on the positive integers which satisfies the following for any functions $f,g$:
 \begin{equation}\label{init_mob} 
-f(n) = \sum_{d | n} g(d) \iff g(n) = \sum_{d | n}  f(d)\mu\left(\frac dn\right)
+f(n) = \sum_{d | n} g(d) \iff g(n) = \sum_{d | n}  f(d)\mu\left(\frac dn\right).
 \end{equation}
 
-Our first goal is to prove the existence of, and find, this function $\mu$. We will do this using by developing M\"obius inversion in general and then applying it. We start with several definitions.
+Then M\"obius inversion is simply the process of using $\mu$ to obtain values of $g$ from values of $f$.
+Without knowing anything about either function other than how they relate to each other, we are able to write down $g$ in terms of $f$.
+
+In fact, this function $\mu$ does exist. We will prove that, and find $\mu$, by developing M\"obius inversion in general and then applying it. We start with several definitions.
 
@@
 \item Totally order $X$ such that the partial order is respected;
-\item Write $g$ as a row vector which contains the values $g$ takes on elements of $X$, with respect to the total ordering;
-\item Write $\zeta$ as a matrix whose $i,j$ entry is equal to $\zeta(a_i, a_j)$, where $a_i, a_j$ are the $i$'th and $j$'th elements of $X$ under the total ordering.
+\item Write $g$ as a (possibly infinite) row vector which contains the values $g$ takes on elements of $X$, with respect to the total ordering;
+\item Write $\zeta$ as a (possibly infinite) matrix whose $i,j$ entry is equal to $\zeta(a_i, a_j)$, where $a_i, a_j$ are the $i$'th and $j$'th elements of $X$ under the total ordering.
 \end{itemize}
+
+The matrices and vectors we construct in this way might be infinite, so we have to be careful.
+In this chapter, all possibly infinite matrices we consider will be upper triangular (it is clear from the definition of $\zeta$ that this is the case here).
+Each term of the product of two upper triangular matrices is can be calculated from a finite number of matrix elements, even if the factor matrices are infinite.
+The same is true when an upper triangular matrix is left-multiplied by a row vector.
+Finally, because our matrices will be upper triangular and have ones on the diagonal, they will automatically be invertible (see Lemma \ref{inv_ex}), and can be inverted even if infinite.
+In subsequent chapters, we will restrict our attention to M\"obius inversion which uses only finite matrices.
+
+We now are able to define our desired function (or vector) $f$ more succinctly:
+\[
+f = g \zeta
+\]
+
+If the matrix multiplication is explicitly written out, what we get is identical to \eqref{sum_form_intro}.
 
@@
 Going forward, $g\zeta$ will refer to the vector/matrix product of $g$ and $\zeta$ rather than function composition, and $\zeta^{-1}$ will refer to the matrix inverse of $\zeta$ rather than the inverse function under composition.
-
-We now are able to define our desired function (or vector) $f$ more succinctly:
-\[
-f = g \zeta
-\]
-
-If the matrix multiplication is explicitly written out, what we get is identical to \eqref{sum_form_intro}.
 
@@
 \]
-\section{Euler's Totient}
-Euler's Totient is a famous function in number theory, which counts the how many numbers are relatively prime to a particular value.
+This is a powerful, versatile result in number theory. As an example, we will walk through how this application of M\"obius inversion is related to Euler's Totient function.
+\begin{examp}[Euler's Totient]
+One of the most fundamental functions of number theory is Euler's Totient, which counts the how many numbers are relatively prime to a particular value.
 We denote the function by $\varphi : \Zz^+ \rightarrow \Zz^+$, and its definition is:
@@
 This is a straightforward example of how M\"obius inversion's ability to reverse a sum can be useful.
+\end{examp}
 \end{chapter}
 
-\begin{chapter}{Groups and Orbits} \label{chap_groups}
-\section{Background}
-For this chapter, it is necessary to be familiar with a simple structure called a \emph{group}.
+\begin{chapter}{Groups and Orbits} \label{chap:groups}
+\section{Motivation and Definitions}
+A \emph{group} is one of the simplest possible algebraic structures.
+It is a set with a binary operation, analogous to addition or multiplication.
+Groups are useful for encoding symmetries and permutations, using a construction called a \emph{group action}, which we will define shortly.
+After we build some machinery, we can consider a motivating problem, which this chapter will give us the tools to solve.
+
+For this chapter, it is necessary to be familiar with groups, including some basic facts about them.
 In this section, we will define it and briefly establish the machinery we need without going into too much detail, omitting proofs.
 More detail on elementary group theory can be found in an abstract algebra textbook.
-Knowledge of groups is not needed for any other chapters in this investigation.
+Knowledge of groups is not needed for any other subsequent chapters.
 
@@
 \end{defn}
+
+This is enough terminology for a motivating problem.
+
+\begin{examp}\label{ex:coloring_init}
+Suppose we have a $4 \times 4$ board, and we would like to color each of the 16 squares using one of $k$ possible colors.
+We want to count the possible colorings.
+However, the board is symmetric, and we would like to consider colorings equivalent if the board can be rotated to obtain one coloring from the other.
+So our goal is to count how many \emph{distinct} colorings there are, where two colorings are distinct if they never coincide even if the board is rotated.
+
+Our first guess is $k^{16}$, the number of ways of coloring the board without regard for rotations.
+But we will end up counting some colorings multiple times.
+Dividing by 4 is no good, because some colorings are not counted four times but two times or once.
+
+One solution is to let a particular group act on the set of $k^{16}$ initial colorings, and count the number of orbits.
+If the group properly captures the symmetry of the board, colorings will be in the same group if and only if they are equivalent.
+So we need to develop the technology to count the orbits of a group action.
+This will occupy the next several sections, and we will use the tools we develop to solve this particular problem in Example \ref{ex:coloring}.
+\end{examp}
 
@@
 \end{align*}
-This $\lambda$ is independent of any set $G$ might act on.
-
-So let's try a particular action.
+We determined $\lambda$ before even deciding what set $G$ might act on. So all the work we have done so far can be reused for a variety of actions.
+
+Let's try a particular action.
 Suppose we have a $2 \times 2$ chessboard, and we want to place some number of rooks on the board such that none of them attack one another.
@@
 
-We can first solve this problem by inspection, or by "brute force," by just enumerating the possibilities:
+We can first solve this problem by inspection, or by "brute force," by just enumerating the possibilities.
+This way, when we solve it with $\lambda$, we can determine whether we found the right answer.
 \begin{description}
@@
 &= \frac 14 12\\
-&=3
-\end{align*}
-So we indeed find the correct answer. 
+&=3.
+\end{align*}
+So we indeed get the correct answer. 
 \end{examp}
@@
 But if we were to increase $n$, we could still determine the number of distinct arrangements relatively easily, because $\lambda$ wouldn't change.
-Furthermore, in many situations (including this one) it is much easier to determine how many \emph{total} arrangements are fixed by a subgroup that it is to find the number of \emph{distinct} arrangements.
-As an example of that, we can look at another example, which is more difficult to solve by hand.
-\begin{examp}
-Suppose we have a $4 \times 4$ board, and we would like to color each square one of $k$ colors.
+Furthermore, in many situations (including this one) it is much easier to determine how many \emph{total} arrangements are fixed by a subgroup that it is to count the number of \emph{distinct} arrangements.
+We can look at another example, which is more difficult to solve by enumeration.
+\begin{examp}[Example \ref{ex:coloring_init}, cont]\label{ex:coloring}
+We now have the tools to solve the problem from Example \ref{ex:coloring_init}.
+We briefly restate the setup: Suppose we have a $4 \times 4$ board, and we would like to color each square one of $k$ colors.
 We would like to consider colorings identical if one can be obtained from the other by rotating the board.
@@
 
-\begin{chapter}{Inclusion-Exclusion}
+\begin{chapter}{Inclusion-Exclusion}\label{chap:iep}
 \section{Introduction}
@@
 There are many ways of proving the Inclusion-Exclusion Principle.
-%TODO: Explain why proving it with Mobius inversion is worthwhile
+We will prove it using M\"obius inversion.
+What is important here is not the result itself -- Theorem \ref{iep} is not hard to prove -- but establishing a connection.
+In fact, the Inclusion-Exclusion principle is in some sense a special case of M\"obius inversion, and the proof we walk through in this chapter is one way of looking at that connection.
 
@@
 
-The goal of the inclusion-exclusion principle is, given a subset $K$ of $I$, to find the size of the union of the sets $A_i$ for $i \in K$.
+The goal of the Inclusion-Exclusion Principle is, given a subset $K$ of $I$, to find the size of the union of the sets $A_i$ for $i \in K$.
 The difficulty arises from counting elements multiple times.
@@
 
-Also, we define the \emph{complement} function/matrix $c$ as follows: %TODO: Change variable name?
+Also, we define the \emph{complement} function/matrix $c$ as follows: 
 \[
@@
 It makes sense that we would use M\"obius inversion to prove the Inclusion-Exclusion principle.
-The difficult aspect of counting how many elements are in the union of the sets is avoiding double-counting.
-%TODO: Finish this
+The difficult aspect of counting how many elements were in the union of the sets was avoiding counting elements multiple times.
+Given a particular set of subsets of $S$, it was easy to determine how many elements were in all of them, because we had access to intersections of the subsets.
+But what we really needed to know was how many elements were in those subsets and \emph{only} those subsets.
+
+This was a similar problem to what we confronted in Chapter \ref{chap:groups}.
+There, we were easily able to find elements of the set which were fixed by at \emph{least} some subgroup, but we needed M\"obius inversion to find the precise subgroup that fixed each element, so we could properly count orbits.
+
+In this chapter, we used M\"obius inversion to determine precisely which subsets of $S$ the various set elements were in.
+This allowed us to determine exactly how many times each element was being counted, and then use facts about binomial coefficients to cancel those extra counts.
+That was what we did when we found $g$ using $f$ -- the step involving M\"obius inversion.
+The rest of the proof was simply rearranging terms to arrive at precisely the Inclusion-Exclusion Principle.
 
@@
 
-\begin{chapter}{Euler Characteristic of a Category}\label{chap_euler}
+\begin{chapter}{Categories and Euler Characteristics}\label{chap:euler}
 \section{Introduction to Categories} \label{cat_defs}
@@
 We present several examples.
-\begin{examp}
-Let $G$ be a group. Then we can represent $G$ as a category $C$ as follows: 
+\begin{examp}\label{ex:grp_cat}
+Let $G$ be a group. Then we can represent $G$ as a category, which we write as $\star^G$:
 \begin{itemize}
-\item Let $C_0 = \{*\}$, a single object
-\item Let $C(*, *) = G$. In other words, let the set of morphisms from $*$ to $*$ be equal to the set of group elements. 
-\item Use the group operation for multiplication. In other words, if $g,h \in C(*,*)$, then, because $g,h \in G$, we can write $gh$. So let $g \circ h = gh$. 
+\item Let $(\star^G)_0 = \{\star\}$, a single object
+\item Let $C(\star, \star) = G$. In other words, let the set of morphisms from $\star$ to $\star$ be equal to the set of group elements.
+\item Use the group operation for composition. In other words, if $g,h \in C(\star,\star)$, then, because $g,h \in G$, we can write $gh$. So let $g \circ h = gh$. 
 \end{itemize}
-It is straightforward to check that $C$ is indeed a category. 
+It is straightforward to check that $\star^G$ is indeed a category. 
 \end{examp}
@@
 \begin{defn}\label{def_weighting}
-A \emph{weighting} on a category $\Aa$ is a function $\omega$ on $\obj(\Aa)$ such that for all $a \in \Aa$,
+A \emph{weighting} on a category $C$ is a function $\omega$ on $C_0$, the objects of $C$ such that for all $a \in C$,
 \[
@@
 \]
-\end{defn}
-
-One of the first questions we ask when we see this definition is how we can write find valid weightings.
+A \emph{coweighting} on $C$ is a function $\kappa$ on $C_0$ such that for all $b \in C$, 
+\[
+\sum_{a \in C}\kappa(a)|C(a,b)| = 1,
+\]
+or, equivalently, if
+\[
+\sum_{a \in C}\kappa(a)\zeta(a, b) = 1.
+\]
+\end{defn}
+
+One of the first questions we ask when we see this definition is how we can write find valid weightings/coweightings.
 Luckily, this definition looks familiar.
@@
 \label{mobius_is_weighting}
-If $C$ has M\"obius inversion, then the weighting $\omega_\mu$ defined by $\omega_\mu(a) = \sum_b \mu(a,b)$ is a weighting on $C$.
+If $C$ has M\"obius inversion, then the function $\omega_\mu$ defined by $\omega_\mu(a) = \sum_b \mu(a,b)$ is a weighting on $C$.
+The function $\kappa_\mu$ defined by $\kappa_\mu(b) = \sum_a \mu(a,b)$ is a coweighting on $C$.
 \end{lemma}
@@
 \end{align*}
-\end{proof}
-
-Note that even if $C$ does not admit M\"obius inversion, it might admit a weighting.
-For example, the category in Example \ref{2_pt} admits the weighting $\omega(a) = \omega(b) = 0.5$, even though it does not admit M\"obius inversion.
+The proof is almost identical for $\kappa_\mu$.
+\end{proof}
 
@@
 
+Note that even if $C$ does not admit M\"obius inversion, it might admit a weighting and/or a coweighting.
+For example, the category in Example \ref{2_pt} admits the weighting and coweighting $\omega(a) =\kappa(a)= \omega(b) = 0.5$, even though it does not admit M\"obius inversion.
+
+\begin{lemma}\label{lem:weight_eq}
+Let $C$ be a finite category. Suppose that $\omega$ and $\kappa$ are a weighting and a coweighting respectively on $C$. Then 
+\[\sum_{b \in C} \omega(b) = \sum_{a \in C} \kappa(a).
+\]
+\end{lemma}
+\begin{proof}
+\begin{align*}
+\sum_{b \in C} \omega(b) &= \sum_{b \in C}\left( \sum_{a \in C} \kappa(a)\zeta(a,b)\right)\omega(b) \\
+&= \sum_{a \in C}\left(\sum_{b \in C} \zeta(a,b)\omega(b)\right)  \kappa(a) \\
+&= \sum_{a \in C}\kappa(a).
+\end{align*}
+\end{proof}
+
 \begin{defn}[Leinster, \cite{Lein1}]\label{cat_euler}
-Let $\omega$ be a weighting on a finite category $A$. Then the \emph{Euler--Leinster characteristic}, or just the \emph{Euler characteristic}, of $A$, denoted by $\chi(A)$, is defined by
-\[
-\chi(A) = \sum_{a \in A} \omega(a)
-\]
-\end{defn}
-Note that even if a category admits several weightings, they all lead to the same Euler characteristic by a simple sum rearrangement argument.
-Together with Lemma \ref{mobius_is_weighting}, this implies the following:
+$C$ be a category with a weighting $\omega$ and a coweighting $\kappa$.
+Then the \emph{Euler--Leinster characteristic}, or just the \emph{Euler characteristic}, of $C$, denoted by $\chi(C)$, is defined by
+\[
+\chi(A) = \sum_{b \in C} \omega(b) = \sum_{a \in C} \kappa(a).
+\]
+\end{defn}
+Lemma \ref{lem:weight_eq} tells us that which weighting or coweighting we choose does not change the value of the Euler characteristic.
+
+Together with Lemma \ref{mobius_is_weighting}, we have the following:
 \begin{cor}\label{euler_mu}
@@
 \end{cor}
-%TODO: Think of category w/ no euler char
+%TODO: Think of category w/ no euler char?
 \section{Simplicial Complexes}
@@
 \begin{examp}
-Let $\sigma = \{a, b, ab\}$. Then $\cat(\sigma)$ has three objects and five morphisms, including the three identity morphisms.
+Let $\sigma = \{a, b, ab\}$. Then $\cat(\sigma)$ has three objects and five morphisms, including the three identity morphisms. See Figure \ref{fig:catsigma}.
 \begin{figure}[h]
@@
 \caption{$\sigma$ and $\cat(\sigma)$. Recall that we omit identity morphisms when drawing a category.}
+\label{fig:catsigma}
 \end{figure}
@@
 &= (-1)^{|\beta - \alpha|} -  \sum_{i = 0}^{|\beta - \alpha|}(-1)^i{|\beta- \alpha| \choose i}\\ 
-&= (-1)^{|\beta - \alpha|} \\ 
+&= (-1)^{|\beta - \alpha|} .\\ 
 \end{align*}
@@
 \begin{proof}
-Recall that by Definition \ref{cat_euler}, 
+Recall that by Corrolary \ref{euler_mu}, 
 \[
@@
 
-\section{Euler--Leinster Characteristic Examples}
-%TODO: Groups? Posets are boring... categories which look like other things?
+\begin{examp}
+In Example \ref{ex:grp_cat}, we saw how a group can be represented in a category.
+Let $G$ be a group, and let $\star^G$ be the corresponding category.
+Then $\zeta_{\star^G} = \begin{bmatrix}|G|\end{bmatrix}$.
+So $\mu_{\star^G} = \begin{bmatrix} \frac 1{|G|}\end{bmatrix}$, meaning that $\chi(\star^G)=\frac 1{|G|}$.
+\end{examp}
 
@@
 We will explore an alternate method of clustering, in which we do not explicitly group points, but instead estimates the number of clusters using a real, rather than integer, value.
-We will use a generalization of the Euler--Leinster characteristic from Chapter \ref{chap_euler}.
+We will use a generalization of the Euler--Leinster characteristic from Chapter \ref{chap:euler}.
 We start by building some important definitions.
@@
 \section{Enriched Categories}
-In Chapter \ref{chap_euler}, we defined a structure called a category.
+In Chapter \ref{chap:euler}, we defined a structure called a category.
 It turns out that this construction - which we will now call an \emph{ordinary} category - can be generalized further, to become an \emph{enriched} category.
@@
 The category $\catname{set}$ is the prototypical example of a monoidal category.
-In that case, the monoidal product $\otimes$ is the Cartesian product on sets (hence the notation $\otimes$ for the monoidal product), and $u = \{*\}$, some set with a single element.
+In that case, the monoidal product $\otimes$ is the Cartesian product on sets (hence the notation $\otimes$ for the monoidal product), and $u = \{\star\}$, some set with a single element.
 
 Here, we can consider what the required isomorphisms look like.
-It's required that for any set $X \in \catname{set}, \{*\} \otimes X \cong X$.
-Elements of $\{*\} \otimes X$ are of the form $(*, x)$ for $x \in X$.
+It's required that for any set $X \in \catname{set}, \{\star\} \otimes X \cong X$.
+Elements of $\{\star\} \otimes X$ are of the form $(\star, x)$ for $x \in X$.
 Also recall that an isomorphism is an invertible morphism, and that in \catname{set}, morphisms are just maps.
-So, because $|X| = |\{*\} \otimes X|$, the two sets are isomorphic in \catname{set}.
+So, because $|X| = |\{\star\} \otimes X|$, the two sets are isomorphic in \catname{set}.
 The associativity isomorphisms are similar.
@@
 
-We would like to generalize the weightings and Euler--Leinster characteristic from Chapter \ref{chap_euler} so we can use them on enriched categories.
+We would like to generalize the weightings and Euler--Leinster characteristic from Chapter \ref{chap:euler} so we can use them on enriched categories.
 Recall that in Definition \ref{def_weighting}, we used the function $\zeta$ to require that for $\omega$ to be a weighting on a category $C$, for all $a \in C$,
@@
 
+If we raise a norm to a power, it is still a norm. This will be a useful fact.
+\begin{lemma}\label{lem:exp_norm}
+Let $M$ be a monoidal category. Let $|\cdot|$ be some norm on $M$. Then, for any real number $t$,  $|\cdot|^t$ is a norm on $M$.
+\end{lemma}
+\begin{proof}
+We can check the two requirements. Let $a,b \in M$ be given, and let $u$ be the unit in $M$.
+\[|M|^t = 1^t = 1
+\]
+\begin{align*}
+|a|^t|b|^t &= (|a||b|)^t\\
+&= |ab|^t.
+\end{align*}
+\end{proof}
+
 We can consider some examples of norms.
-\begin{examp}\label{exp_norm}
-Let $D$ be the monoidal category of non-negative real numbers defined in example Example \ref{cat_real}. Then, for all $t \in \Rr$, the function $|\cdot|:D \rightarrow \Rr$ defined by 
-\[
-|x| = e^{-tx}
+\begin{examp}
+Let \catname{set} be the category of finite sets.
+Then the usual norm, cardinality, is a norm under this definition.
+This is the norm we use when we view ordinary categories as categories enriched over \catname{set}.
+Interestingly, Lemma \ref{lem:exp_norm} tells us that we can raise set cardinality to any power, and we still have a norm.
+It might be interesting to explore the effect this has on the Euler characteristic of a category over \catname{set}, although we do not explore that here.
+\end{examp}
+\begin{examp}\label{ex:exp_norm}
+Let $D$ be the monoidal category of non-negative real numbers defined in example Example \ref{cat_real}. Then he function $|\cdot|:D \rightarrow \Rr$ defined by 
+\[
+|x| = e^{-x}
 \]
@@
 \]
-\[|x + y| = e^{-tx + ty} = |x||y|.
-\]
-We will explore this norm in detail shortly.
+\[|x + y| = e^{-x + y} = |x||y|.
+\]
+Note that by \ref{lem:exp_norm}, this implies that $e^{-tx}$ is a norm on $D$ for any real number $t$. We will explore this family of norms in detail shortly.
 \end{examp}
@@
 \begin{defn}
-Let $C$ be a finite category enriched over a monoidal category $M$, with a specificed norm $|\cdot|$. Then $\omega$ is a \emph{weighting} on $C$ if, for all $a \in C$, 
+Let $C$ be a finite category enriched over a monoidal category $M$, with a specified norm $|\cdot|$. Then $\omega$ is a \emph{weighting} on $C$ if, for all $a \in C$, 
 \[
@@
 When $C$ is an enriched category, $\chi(C)$ is sometimes called the \emph{magnitude} of $C$ (for example, in \cite{Lein4}).
-We reserve that terminology for a particular class of enriched categories which we will soon introduce, and continue to refer to the general construction as the Euler--Leinster characteristic or the Euler characteristic of $C$.
+We reserve that terminology for a particular class of enriched categories which we introduce in Definition \ref{def:magn}, and continue to refer to the general construction as the Euler--Leinster characteristic or the Euler characteristic of $C$.
 \end{rmk}
@@
 \end{rmk}
-%TODO: Examples of euler characteristics of non-metric space enriched categories
+%TODO: Examples of euler characteristics of non-metric space enriched categories?
 
@@
 \begin{defn}[Lawvere, \cite{Lawv1}]\label{gen_met}
-Let $D$ be the monoidal category of non-negative real numbers defined in Example \ref{cat_real}. Let $C$ be a category enriched over $D$. Then we call $C$ a \emph{generalized metric space}.
+Let $D$ be the monoidal category of non-negative real numbers defined in Example \ref{cat_real}.
+Let $C$ be a category enriched over $D$.
+Then we call $C$ a \emph{generalized metric space} (or sometimes a \emph{Lawvere megric space}).
 \end{defn}
@@
 
-Recall that in Example \ref{exp_norm}, we observed that the function $|x|=e^{-tx}$ is a norm on $D$. For any positive $t$, this is a decreasing function. 
-\begin{figure}[h]
-%TODO: Replace plot
-\[
-\includegraphics[width = 0.5\paperwidth]{../Figures/exp.pdf}
-\]
-\caption{A graph of $e^{-x}$ against $x$.}
-\end{figure}
-And the larger the value of $t$, the quicker the function decays.
+Recall that in Example \ref{ex:exp_norm}, we observed that the function $|x|=e^{-tx}$ is a norm on $D$.
+For any positive $t$, this is a decreasing function in $x$.
+The larger the value of $t$, the quicker the function decays.
 In fact, we will see that if we use this family of norms, we can view $t$ as a ``zooming'' parameter, which allows us to consider the data at different scales.
@@
 We have a special name for the Euler characteristic of a generalized metric space which results from this particular norm:
-\begin{defn}[\cite{Lein4}]
+\begin{defn}[\cite{Lein4, Lein2}]\label{def:magn}
 Let $M$ be a generalized metric space. Let $|\cdot|_t:D \rightarrow \Rr$ be defined by
@@
 \end{figure}
-If $t$ indeed behaves as a zooming parameter, then we would expect that for small values of $t$, $\chi_t(M_2)$ should have a single cluster, because we are not zoomed in.
+If $t$ indeed behaves as a zooming parameter, then we would expect that for small values of $t$, $\magn_t(M_2)$ should have a single cluster, because we are not zoomed in.
 But for large values of $t$, the number of clusters should approach 2, as the two points fully separate from each other.
@@
 \[
- \chi_t(M_2) = \frac{2}{1+e^{-t}}.
+ \magn_t(M_2) = \frac{2}{1+e^{-t}}.
 \]
@@
 So it is reasonable to expect that the behavior of the magnitude as $t$ varies will be logarithmic.
-If we plot $\chi_t(M_2)$ against $t$, we can see that it behaves just as we expect (see Figure \ref{fig:2pt_mag}).
+If we plot $\magn_t(M_2)$ against $t$, we can see that it behaves just as we expect (see Figure \ref{fig:2pt_mag}).
 \begin{figure}[H]
@@
 \]
-\caption{A plot of $\chi_t(M_2)$ against $\log(t)$, where $t$ is the scale factor.}
+\caption{A plot of $\magn_t(M_2)$ against $\log(t)$, where $t$ is the scale factor.}
 \label{fig:2pt_mag}
@@
 \begin{rmk}
-The Cartesian product of two categories enriched over $M$ is indeed a category enriched over $M$. There are many requirements to check, and we do not go through all of them here.
+The Cartesian product of two categories enriched over $M$ is indeed a category enriched over $M$. There are many requirements to check, and we do not go through them here.
 \end{rmk}
@@
 Figure \ref{fig:prod_mag} shows the magnitudes of the three spaces as we vary $t$.
-At every value of $t$, $\chi_t(M)$ is almost exactly the product of the magnitudes of the other two spaces at that $t$ value.
+At every value of $t$, $\magn_t(M)$ is almost exactly the product of the magnitudes of the other two spaces at that $t$ value.
 \begin{figure}[H]
@@
 Let $A$ be a generalized metric space which admits M\"obius inversion.
-Suppose we know $\chi(A)$, the magnitude of $A$, and we would like to know how much adding $E$, a perturbation matrix, to $\zeta_A$, will change the magnitude.
+Suppose we know $\magn(A)$, the magnitude of $A$, and we would like to know how much adding $E$, a perturbation matrix, to $\zeta_A$, will change the magnitude.
 Suppose that $||EA^{-1}|| < 1$ for some matrix norm, so we can use Theorem \ref{thm:approx}.
@@
 We demonstrate this approximation of magnitude through an example:
-\begin{examp}
+\begin{examp} %TODO Rework 
 We will consider a situation quite similar to Example \ref{ex:4pt}. Let $M$ be the following generalized metric space:
@@
 This formula gives us a way of bounding how different the magnitude of the Euclidean spaces is from the product space.
-We can numerically calculate values for $\chi_t(M), \chi_t(A \times B)$, and the error term, and plot them.
+We can numerically calculate values for $\magn_t(M), \magn_t(A \times B)$, and the error term, and plot them.
 

### 2017-04-12 Drafts/Draft.tex
complete draft

@@
 \end{examp}
-\section{Product Spaces and Approximations}\label{sec:prod}
+\section{Product Spaces}\label{sec:prod}
 In Figure \ref{fig:3+4}, we see two sets of points, $M$ and $N$. $M$ has three points while $N$ has four.
@@
 
-\section{Approximations and Error Bounding}
 In Example \ref{ex:4pt}, $M$ was \emph{almost} a product space, so we expected its magnitude to be very nearly the product of the magnitudes of the two 2-point spaces.
 It would be useful to quantify how similar the magnitudes of two spaces are, given that we know something about how similar those spaces are.
-To do that, we need some simple tools from linear algebra involving vector and matrix norms.
+In the next section, we explore one idea for bounding error, but see that it has an important flaw.
+We then propose a possible route for a more useful error bounding method.
+
+\section{Approximation Attempts and Questions}
+First, we work through an approach to error bounding which has promise, but does not seem to be effective.
+We need some simple tools from linear algebra involving vector and matrix norms.
 Note that these norms are not directly related to the norms we defined on monoidal categories - both are non-negative real-valued functions, but they operate on different structures.
@@
 There are many norms on matrices. Formally, a matrix norm is simply a function from matrices to the non-negative real numbers which satisfies certain properties.
-
-\begin{defn}\label{def:spec}
-Let $n$ be given. Let $|v|$ denote the Euclidean vector norm. Then the \emph{spectral norm} on real- (or complex-) valued $n \times n$ matrices, denoted $||\cdot ||_s$, is defined by
-\[
-||M||_s = \sup_{0 \neq x \in \Rr^n}\left\{ \frac{|Ax|}{|x|} \right\}.
-\]
-\end{defn}
-\begin{rmk}
-Definition \ref{def:spec} does not tell us how to find the spectral norm of a matrix. However, it is not difficult to do so. For a given $M$, we can find $||M||_s$ as follows:
-
-Let $M^*$ be the adjoint, or conjugate transpose, of $M$. Let $\lambda_1$ be the largest eigenvalue of the matrix $MM^*$. Then $\lambda_1$ will be real-valued, and $||M||_s=\sqrt{\lambda_1}$.
-
-We will not prove or use this fact - it is simply here to assure readers that the spectral norm can be computed.
-\end{rmk}
-This norm is a common way of determining how ``large'' a matrix is. It will allow us to determine which matrices are ``small enough'' to satisfy some approximation theorems.
-
-We also define a second matrix norm, called the $L_1$ norm.
+We define one called the $L_1$ norm.
 \begin{defn}
-Let $A$ be an $n \times n$ matrix. Then the \emph{$L_1$ norm} of $A$, denoted $||A||_2$, is the sum of the absolute values of entries of $A$. In other words,
-\[
-||A||_2 = \sum_{i = 1}^n\sum_{j = 1}^n |A_{ij}|.
+Let $A$ be an $n \times n$ matrix. Then the \emph{$L_1$ norm} of $A$, denoted $||A||_1$, is the sum of the absolute values of entries of $A$. In other words,
+\[
+||A||_1 = \sum_{i = 1}^n\sum_{j = 1}^n |A_{ij}|.
 \]
@@
 
-There are three simple properties of both norms which we will need.
+There are three simple properties of this norm which we will need.
 \begin{lemma}\label{lem:norm_prop}
-Let $A, B$ be $n \times n$ matrices. Let $||\cdot||$ be \emph{either} the spectral norm or the $L_1$ norm. Then
+Let $A, B$ be $n \times n$ matrices. Let $||\cdot||_1$ be the $L_1$ norm. Then
 \begin{enumerate}
 \item \[
-||AB|| \leq ||A||\times ||B||,
+||AB||_1 \leq ||A||_1\times ||B||_1,
 \]
@@
 \[
-||A + B|| \leq ||A|| + ||B||.
+||A + B||_1 \leq ||A||_1 + ||B||_1.
 \]
@@
 \[
-||A|| = 0 \iff A = 0.
+||A||_1 = 0 \iff A = 0.
 \]
@@
 \begin{proof}
-\begin{description}
-\item[Spectral Norm:]
-\begin{enumerate}
-\item By the definition of the spectral norm, for any $v \in \Rr^n$,
-\begin{align*}
-|ABv| &\leq |A(||B||_s \times |v|)|\\
-&\leq (||A||_s \times ||B||_s)|v|.
-\end{align*}
-It follows that 
- \[
-||AB|| \leq ||A||_s\times ||B||.
-\]
-\item For any $v \in \Rr^n$,
-\begin{align*}
-|(A + B)v| &= |Av + Bv|\\
- &\leq |Av| + |Bv|\\
- &\leq ||A||_s + ||B||_s)v.
-\end{align*}
-\item It is clear that if $A=0$ then $||A||_s=0$.
-Now suppose that $A$ is not zero.
-Then the column space of $A$ has nonzero dimension, so there exists a $v$ such that $Av \neq 0$.
-So $||A||_s \geq \frac{|Av|}{|v|} > 0$.
-\end{enumerate}
-\item[$L_1$ Norm:]
 \begin{enumerate}
@@
 \end{enumerate}
-\end{description}
+
 \end{proof}
-Again, there are many other matrix norms. For our purposes, when a theorem uses an arbitrary matrix norm, we will assume that it satisfies Lemma \ref{lem:norm_prop}.
 
@@
 \begin{defn}\label{def:mat_conv}
-Let $A_i$ be an infinite sequence of $m \times n$ matrices, and let $||\cdot||$ be some matrix norm (the spectral norm, the $L_1$ norm, or another matrix norm).
-Suppose we have an $m \times n$ matrix $L$ such that
-\[
-\lim_{i \rightarrow \infty} ||A_i - L|| = 0.
+Let $A_i$ be an infinite sequence of $m \times n$ matrices, and let $||\cdot||_1$ be the $L_1$ matrix norm. Suppose we have an $m \times n$ matrix $L$ such that 
+\[
+\lim_{i \rightarrow \infty} ||A_i - L||_1 = 0.
 \]
@@
 \begin{lemma}\label{lem:lim0}
-Let $E$ be a real-valued $n \times n$ matrix.  Suppose that for some matrix norm $||\cdot||$, $||E|| < 1$. Then:
+Let $E$ be a real-valued $n \times n$ matrix. Suppose that $||\cdot||_1$, $||E|| < 1$. Then:
 \[
@@
 
-Let $||E|| < 1$. Let $\vec{0}$ represent be the zero matrix. We now use Lemma \ref{lem:norm_prop}:
-\begin{align*}
-\lim_{i \rightarrow \infty}|| E^i - \vec{0}|| &\leq \lim_{i \rightarrow \infty}|| E^i|| - ||\vec{0}|| \\
-&\leq \lim_{i \rightarrow \infty}|| E||^i\\
+Let $||E||_1 < 1$. Let $\vec{0}$ represent be the zero matrix. We now use Lemma \ref{lem:norm_prop}:
+\begin{align*}
+\lim_{i \rightarrow \infty}|| E^i - \vec{0}||_1 &\leq \lim_{i \rightarrow \infty}|| E^i||_1 - ||\vec{0}||_1 \\
+&\leq \lim_{i \rightarrow \infty}|| E||_1^i\\
 &= 0.
@@
 \begin{thm}\label{thm:approx}
-Let $A$ be an invertible $n \times n$ matrix, let $||\cdot||$ be some matrix norm, and let $E$ be an $n \times n$ matrix such that $||E|| < \frac 1{||A^{-1}||}$. Then $(A-E)$ is invertible, and
+Let $A$ be an invertible $n \times n$ matrix, and let $E$ be an $n \times n$ matrix such that $||E||_1 < \frac 1{||A^{-1}||_1}$. Then $(A-E)$ is invertible, and
 \begin{align*}
@@
 \end{rmk}
-This fact makes sense, in particular if we consider the spectral norm.
-$||A^{-1}||_s$ is the inverse of the smallest eigenvalue of $AA^*$, and it tells us how much $A$ is capable of reducing the euclidean norm of a vector it multiplies.
-So if that value is very large, $A$ is very nearly not invertible.
-In that case, it makes sense that adding a relatively small error matrix might change the inverse significantly.
 
@@
 Suppose we know $\magn(A)$, the magnitude of $A$, and we would like to know how much adding $E$, a perturbation matrix, to $\zeta_A$, will change the magnitude.
-Suppose that $||EA^{-1}|| < 1$ for some matrix norm, so we can use Theorem \ref{thm:approx}.
+Suppose that $||EA^{-1}||_1 < 1$, so we can use Theorem \ref{thm:approx}.
 
@@
 \end{align*}
-
-However, as we mentioned earlier, all matrix norms are equivalent when it comes to convergence.
-So if $||EA^{-1}||_1 \geq 1$ but, for example, $||EA^{-1}||_s <1$, the above would no longer work, but we would still expect \eqref{eq:series} to converge.
-This might be useful, because the spectral norm is often smaller than the $L_1$ norm.
-To make this work, we will need some way of replacing the $L_2$ norm with a spectral norm.
-It turns out we can do that:
-\begin{lemma}\label{lem:norm_switch}
-Let $A$ be an $n \times n$ matrix. Then
-\[
-||A||_1 \leq n^2||A||_s.
-\]
-\end{lemma}
-\begin{proof}
-Let $m$ be the absolute value of the largest element of $A$.
-Suppose that for some $i,j, |A_{ij}| > ||A||_s$.
-Let $e_j$ be the column vector with a one in index $j$ and zeros everywhere else.
-Then $Ae_j$ will have $A_{ij}$ in its $i$'th index, so $|Ae_j| \geq |A_{ij}| >||A||_s$.
-Because $|e_j|=1$, this is a contradiction.
-So $m \leq ||A||_1$.
-$||A||_1 \leq n^2m$, so $||A||_1 \leq n^2||A||_s$.
-\end{proof}
-
-This means that we can rewrite \eqref{eq:series} in the following way:
-\begin{align*}
-||\zeta_A^{-1}||_1\sum_{i = 1}^\infty ||EA^{-1}||_1^i &\leq n^2||\zeta_A^{-1}||_1\sum_{i = 1}^\infty ||(EA^{-1})^i||_s^i\\
-&\leq n^2||\zeta_A^{-1}||_1\sum_{i = 1}^\infty ||(EA^{-1})||_s^i\\
-&\leq n^2||\zeta_A^{-1}||\frac{||EA^{-1}||_s}{1-||EA^{-1}||_s}.
-\end{align*}
-
-We have (possibly) reduced the value of the norm, at the price of a factor of $n^2$. We can exchange the $L_1$ norm for other matrix norms in a similar fashion, using different constants.
-
-We demonstrate this approximation of magnitude through an example:
+Unfortunately, this approach often does not work.
+The problem is that we are interested in considering spaces and scales such that some groups of points form clusters, meaning that they are very near each other.
+This will lead to $\zeta_A$ being very nearly not invertible, which has the effect of causing $\zeta_A^{-1}$ to have very large positive and negative values.
+These might mostly cancel to give us the magnitude we expect, but when we take the $L_1$ norm, the values no longer cancel.
+This causes our error bounds to get quite large when the points are not all separated (see Figure \ref{fig:failed_bound}).
+
+\begin{figure}[h]
+\[
+\makebox[\textwidth][c]{\includegraphics[width = 0.9\paperwidth]{../Figures/error_1_correct.png}}
+\]
+\caption{A plot of the magnitude of a four-point square space, approximated by the product of two identical two-point spaces, with error bars calculated using the above technique when possible.
+Until all four points separate, the bounds are not useful or the limit diverges.}
+\label{fig:failed_bound}
+\end{figure}
+One possible solution would be to bound the error on the magnitude without relying on inverting $\zeta_A$: By using weightings or coweightings directly.
+In particular, we can pose the problem like this: The magnitude of $A$ is the sum of entries of some vector $\omega$ where $\zeta_A\omega = \vec{1}$ (here $\omega$ is a weighting on $A$).
+Suppose that $E$ is a perturbation matrix, which is small enough that $(\zeta_A + E)\omega' = \vec{1}$ can still be solved for $\omega'$.
+Can we bound the sum of entries of $\omega' - \omega$?
+It would be interesting to know how this might be done, depending on what restrictions we put on $E$.
+
+\iffalse
 \begin{examp} %TODO Rework 
@@
 Because of the error bounds, we know that given the behavior of $A \times B$, the magnitude of $M$ can't differ too much from that behavior.
-
+\fi
 \end{chapter}

### 2017-04-13 Drafts/Draft.tex
submitted version

@@
 We explore traditional applications in the integer divisibility lattice, including Euler's Totient.
-We then use the lattice of subgroups to count orbits under a group action.
+We then use the lattice of subgroups to count orbits under a group action, and use the lattice of subsets to prove the Inclusion-Exclusion Principle.
 In the last two sections, we explore Tom Leinster's generalization of M\"obius inversion to categories and enriched categories, and investigate a data clustering algorithm.
@@
 \]
-Replacing one of the square brackets with a parenthesis means we are omitting that element. So
+Replacing one of the square brackets with a parenthesis means we are omitting the bound on that end. So
 \begin{align*}
@@
 The same is true when an upper triangular matrix is left-multiplied by a row vector.
-Finally, because our matrices will be upper triangular and have ones on the diagonal, they will automatically be invertible (see Lemma \ref{inv_ex}), and can be inverted even if infinite.
+Finally, because our matrices will be upper triangular and have ones on the diagonal, they will automatically be invertible (see Lemma \ref{inv_ex}), have upper triangular inverses, and can be inverted even if infinite.
 In subsequent chapters, we will restrict our attention to M\"obius inversion which uses only finite matrices.
@@
 \begin{proof}
-The poset axioms are easily checked. We also observe that for any $x \in (\Nn^n, \leq)$,
+The poset axioms are easily checked. To see why the poset is lower finite, we observe that for any $x \in (\Nn^n, \leq)$,
 \[
@@
 \begin{rmk}
-Note that the piecewise form is actually not necessary, because if $a \nleq b$ then the sum will be empty. So it is correct - albeit less clear- to just write
+Note that the piecewise form is actually not necessary, because if $a \nleq b$ then the sum will be empty. So it is also correct to just write
 \[
@@
 \begin{proof}
-We induct on $\#[x_1, x_2]$.
+We induct on $\#[x_1, x_2]$, starting with the base case.
 Because $x_1 \leq x_2$, if $[x_1, x_2] = 1$, then $x_1 = x_2$.
 So by Lemma \ref{recurse}, $\mu_X(x_1, x_2) = 1$.
-Because $\phi(x_1) = \phi(x_2), \mu_Y(\phi(x_1), \phi(x)2) = 1$ also.
+Because $\phi(x_1) = \phi(x_2)$, we know that $\mu_Y(\phi(x_1), \phi(x)2) = 1$.
+So the M\"obius functions take the same value.
 
@@
 \[
-\mu_Y(\phi(x_1), \phi(x_2)) = -\sum_{y \in [\phi(x_1), \phi(x_2)]}\mu_Y(\phi(x_1), y)
+\mu_Y(\phi(x_1), \phi(x_2)) = -\sum_{y \in [\phi(x_1), \phi(x_2))}\mu_Y(\phi(x_1), y)
 \]
@@
 \[
-\mu_Y(\phi(x_1), \phi(x_2)) = -\sum_{x \in [x_1, x_2]}\mu_Y(\phi(x_1), \phi(x))
-\]
-We can restrict $\phi$ to $[\phi(x_1), \phi(x)]$ to satisfy the hypotheses for all intermediate elements $x$. So we can apply the inductive hypothesis to all the terms of this sum:
-\begin{align*}
-\mu_Y(\phi(x_1), \phi(x_2)) &= -\sum_{x \in [x_1, x_2]}\mu_X(x_1, x)\\
+\mu_Y(\phi(x_1), \phi(x_2)) = -\sum_{x \in [x_1, x_2)}\mu_Y(\phi(x_1), \phi(x))
+\]
+We can restrict $\phi$ to $[x_1, x]$ to satisfy the hypotheses for all intermediate elements $x$. So we can apply the inductive hypothesis to all the terms of this sum:
+\begin{align*}
+\mu_Y(\phi(x_1), \phi(x_2)) &= -\sum_{x \in [x_1, x_2)}\mu_X(x_1, x)\\
 &= \mu_X(x_1, x_2)
@@
 
-So $\phi:[d,n] \leftrightarrow [\phi(d), \phi(n)]$ is a bijection.
-
-This allows us to use Theorem \ref{mapping}, and the result immediately follows.
+So $\phi:[d,n] \leftrightarrow [\phi(d), \phi(n)]$ is a bijection. This allows us to use Theorem \ref{mapping}, and the result immediately follows.
 \end{proof}
@@
 \end{examp}
-\begin{rmk}
-We are ordering the poset this way for reasons that will soon become clear.
-But to reduce confusion, we will continue to use inclusion notation to define $\zeta$, and so $\mu$, rather than using $\leq$.
-I will be using $\subseteq$ rather than $\leq$ to denote subgroups, also to reduce confusion with the poset relation.
-\end{rmk}
+
 This puts us in the position to apply M\"obius inversion. We first define the usual functions on $\sub(G) \times \sub(G)$:
@@
 
-Now, Theorem \ref{mob_inv} tells us that, for any row vectors $f,g$ of length $|\sub{G}|$, 
+Theorem \ref{mob_inv} tells us that, for any row vectors $f,g$ of length $|\sub{G}|$, 
 \[
@@
 \]
-Now, of course, the challenge is to determine how to formulate the problem such that inverting $\zeta$ will be useful.
+Now, of course, the challenge is to determine how to formulate the problem of counting orbits such that inverting $\zeta$ will be useful.
 \section{Counting Orbits}
-Throughout this section, let $G$ be a finite group acting on a set $\Omega$.
+Throughout this section, let $G$ be a finite group acting on a finite set $\Omega$.
 
@@
 The same is true of all the orbits in $\Omega$.
-So our final total will be the size of $G/X$.
+So our final total will be the size of $\Omega/G$.
 
@@
 \begin{equation}\label{eq_counting}
-|G/X| = \sum_{x \in \Omega}\frac 1 {|\orb_G(x)|}.
+|\Omega/G| = \sum_{x \in \Omega}\frac 1 {|\orb_G(x)|}.
 \end{equation}
@@
 
-\[|G| = |G(x)||\stab(x, G)|.\]
-
-Because $G$ is finite, this implies that \[|G(x)| = \frac{|G|}{|\stab(x, G)|}.\]
-
-Starting from a trivial fact, we have:
-\begin{align*}
-|\orb(\Omega, G)| &= \sum_{O \in \orb(\Omega, G)}1\\
-&= \sum_{O \in \orb(\Omega, G)}\left(\sum_{x \in O}\frac{1}{|O|}\right)\\
-&= \sum_{x \in \Omega}\frac{1}{|G(x)|}
-\end{align*}
-
-Substituting, we now have the relationship:
-\[
-|\orb(\Omega, G)| = \frac{1}{|G|}\sum_{x \in \Omega}|\stab(x, G)|
+\[|G| = |\orb_G(x)||\stab(x, G)|.\]
+
+Because $G$ is finite, this implies that \begin{equation}|\orb_G(x)| = \frac{|G|}{|\stab(x, G)|}.\end{equation} \label{eq:orb_stab}
+
+Starting from a trivial fact, we can recover \eqref{eq_counting}:
+\begin{align*}
+|\Omega/G| &= \sum_{O \in \Omega/G}1\\
+&= \sum_{O \in \Omega/G}\left(\sum_{x \in O}\frac{1}{|O|}\right)\\
+&= \sum_{x \in \Omega}\frac{1}{|\orb_G(x)|}
+\end{align*}
+
+Substituting \eqref{eq:orb_stab}, we now have the relationship:
+\[
+|\Omega/G| = \frac{1}{|G|}\sum_{x \in \Omega}|\stab(x, G)|
 \]
@@
 \[
-|\orb(\Omega, G)| = \frac{1}{|G|}\sum_{A \in \sub(G)}\left(\sum_{x \in \Omega: \stab(x) = A}|A|\right)
+|\Omega/G| = \frac{1}{|G|}\sum_{A \in \sub(G)}\left(\sum_{x \in \Omega: \stab(x) = A}|A|\right)
 \]
@@
 \begin{align*}
-|\orb(\Omega, G)| &= \frac{1}{|G|}\sum_{A \in \sub(G)}g(A)|A|\\
+|\Omega/G| &= \frac{1}{|G|}\sum_{A \in \sub(G)}g(A)|A|\\
 &= \frac {1}{|G|}g \cdot \sigma
@@
 On to Step 2.
-It is clear that $f_A = \sum_{B \supseteq A} g_A$.
-Another way of putting that is that $f = g\zeta$.
+It is clear from our definitions that \[f_A = \sum_{B \supseteq A} g_A.\] Another way of putting it is that $f = g\zeta$.
 As usual, this implies that $g = f\mu$.
@@
 
-\[|\orb(\Omega, G)| = \frac {1}{|G|}f\mu \cdot \sigma.\]
+\[|\Omega/G| = \frac {1}{|G|}f\mu \cdot \sigma.\]
 
@@
 \[
-|\orb(\Omega, G)| = \frac {1}{|G|}(\mu \cdot \sigma)^Tf^T
+|\Omega/G| = \frac {1}{|G|}(\mu \cdot \sigma)^Tf^T
 \]
@@
 \begin{bmatrix} 4 \\ 2 \\ 1 \end{bmatrix}\\
-&= \frac 14 \begin{bmatrix} 2 \\ 1 \\ 1\end{bmatrix}
+&= \frac 14 \begin{bmatrix} 2 \\ 1 \\ 1\end{bmatrix}.
 \end{align*}
@@
 
-We can first solve this problem by inspection, or by "brute force," by just enumerating the possibilities.
+We can first solve this problem by inspection, or by ``brute force,'' by just enumerating the possibilities.
 This way, when we solve it with $\lambda$, we can determine whether we found the right answer.
@@
 \lambda f^T &= \frac 14 [2, 1, 1] \begin{bmatrix} 1 \\ 3 \\ 7\end{bmatrix} \\
-&= \frac 14 12\\
+&= \frac 14\cdot 12\\
 &=3.
@@
 
-In this example, it's not clear that using $\lambda$ actually saved work - in fact, it seemed to take longer.
+In this example, it's not clear that using $\lambda$ actually saved work.
 But if we were to increase $n$, we could still determine the number of distinct arrangements relatively easily, because $\lambda$ wouldn't change.
@@
 Let $\mu$ denote the M\"obius function on $\cat(\sigma)$.
-Then $\mu(\cat(\alpha), \cat(\beta)) =(-1)^{|\beta - \alpha|} = (-1)^{|\alpha|} (-1)^{|\beta|}$ (note that $|\alpha|$ simply denotes the size of $\alpha$ as a set).
+Then $\mu(\cat(\alpha), \cat(\beta)) =(-1)^{|\beta - \alpha|} = (-1)^{|\alpha|} (-1)^{|\beta|}$ (note that $|\alpha|$ denotes the size of $\alpha$ as a set).
 \end{lemma}
 \begin{proof}
-We use induction. Base case: $\alpha = \beta$, and $\mu(\alpha, \beta)=1$.
+We use induction. The base case is trivial: If $\alpha \subseteq \beta$ and $|\beta - \alpha| =0$, then $\alpha = \beta$, and so $\mu(\alpha, \beta)=1$.
 
@@
 \end{chapter}
-\begin{chapter}{Metric Space Magnitude}\label{chap_magnitude}
+\begin{chapter}{Enriched Categories and Magnitude}\label{chap_magnitude}
 \section{Motivation: Hierarchical Clustering}
@@
 
-We can see in Figure \ref{fig:hier} that as we ``zoom out'', the structure of this data changes.
+We can see in Figure \ref{fig:hier} that as we ``zoom out,'' the structure of this data changes.
 First the data has first eight clusters of one point each, then four clusters of two points, and finally two clusters of four points.
@@
 \[
-\sum_{b \in C}\zeta_{|\cdot|}(a,b)\omega(b) = 1.
-\]
-\end{defn}
-
+\sum_{b \in C}\zeta_{|\cdot|}(a,b)\omega(b) = 1,
+\]
+and $\kappa$ is a \emph{coweighting} on $C$ if, for all $b \in C$,
+
+\[
+\sum_{a \in C}\kappa(a)|C(a,b)|= 1,
+\]
+or, equivalently, if
+\[
+\sum_{b \in C}\kappa(a)\zeta_{|\cdot|}(a,b) = 1.
+\]
+\end{defn}
+As before, the sum of different weightings or coweightings of the same category will always be the same. The proof is identical as in Lemma \ref{lem:weight_eq}.
 \begin{defn}[\cite{Nog1}]
 Let $C$ be a finite category enriched over a monoidal category $M$, with a specified norm $|\cdot|$.
-Let $\omega$ be a weighting on $C$.
+Let $\omega$ be a weighting on $C$ and $\kappa$ a coweighting.
 Then the \emph{Euler--Leinster characteristic} of $C$, denoted $\chi_{|\cdot|}(C)$, is defined by
 \[
-\chi_{|\cdot|}(C) = \sum_{a \in c} \omega(a).
-\]
-\end{defn}
+\chi_{|\cdot|}(C) = \sum_{a \in c} \omega(a) = \sum_{b \in c} \kappa(b).
+\]
+\end{defn}
+
 In the notation just introduced, we will sometimes omit the subscripts specifying the norm, if the norm is implied.
@@
 
-This looks exactly like the requirement (from Definition \ref{def_weighting}) for $\omega$ to be a weighting on a category $M$!
+This looks exactly like the requirement (from Definition \ref{def_weighting}) for $\omega$ to be a weighting on a category $M$.
 So adding up values of $\omega$ is the same as finding the Euler--Leinster characteristic of $M$, assuming we can properly encode the structure of the spectators into a category.
@@
 So it is reasonable to expect that the behavior of the magnitude as $t$ varies will be logarithmic.
-If we plot $\magn_t(M_2)$ against $t$, we can see that it behaves just as we expect (see Figure \ref{fig:2pt_mag}).
+If we plot $\magn_t(M_2)$ against $\log(t)$, we can see that it behaves just as we expect (see Figure \ref{fig:2pt_mag}).
 \begin{figure}[H]
@@
 \end{examp}
+
+In this figure, we can see a good example of what happens in a simple generalized metric space when we vary $t$, the exponent on the norm function.
+But Lemma \ref{lem:exp_norm} tells us that any norm on a monoidal category can be scaled in this way.
+Although we don't go into that here, we wonder what effects this scaling might have on other instances of the Euler characteristic, including on ordinary categories.
 \section{Product Spaces}\label{sec:prod}
@@
 In the next section, we explore one idea for bounding error, but see that it has an important flaw.
-We then propose a possible route for a more useful error bounding method.
+We then propose a possible route for a more useful error bounding method which could be pursued in the future.
 
@@
 \end{defn}
-It turns out that if the matrices involved are finite-dimensional, the choice of norm does not matter - a sequence will either always converge or always diverge.
-So there is no need to specify the norm when stating a fact about matrix convergence.
-
-This is an instance of the general definition of a convergent sequence in a metric space, where our chosen norm induces a metric.
-Furthermore, for this discussion, we will be concerned primarily with norms of matrices, so this definition of convergence makes sense for us to use.
-
 \begin{lemma}\label{lem:lim0}
@@
 \begin{align}
-\left|\left|\zeta_A^{-1} - \zeta_A^{-1} - \zeta_A^{-1}\sum_{i = 1}^\infty (EA^{-1})^i\right|\right|_1 \nonumber 
-&= \left|\left|\zeta_A^{-1}\sum_{i = 1}^\infty (EA^{-1})^i\right|\right|_1 \nonumber \\
-&\leq ||\zeta_A^{-1}||_1\sum_{i = 1}^\infty ||(EA^{-1})^i||_1. \label{eq:series}
+\left|\left|\zeta_A^{-1} - \zeta_A^{-1} - \zeta_A^{-1}\sum_{i = 1}^\infty (E\zeta_A^{-1})^i\right|\right|_1 \nonumber 
+&= \left|\left|\zeta_A^{-1}\sum_{i = 1}^\infty (E\zeta_A^{-1})^i\right|\right|_1 \nonumber \\
+&\leq ||\zeta_A^{-1}||_1\sum_{i = 1}^\infty ||(E\zeta_A^{-1})^i||_1. \label{eq:series}
 \end{align}
 
-Suppose that $||EA^{-1}||_1 <1$. Then we can convert \eqref{eq:series} to a closed form. 
-\begin{align*}
-||\zeta_A^{-1}||_1\sum_{i = 1}^\infty ||EA^{-1}||_1^i &\leq
-||\zeta_A^{-1}||_1 \sum_{i = 1}^\infty||(\zeta_A + E)^{-1}||_1^i\\
- &\leq ||\zeta_A^{-1}||\frac{||EA^{-1}||_1}{1-||EA^{-1}||_1}.
-\end{align*}
-Unfortunately, this approach often does not work.
-The problem is that we are interested in considering spaces and scales such that some groups of points form clusters, meaning that they are very near each other.
+Suppose that $||E\zeta_A^{-1}||_1 <1$. Then we can convert \eqref{eq:series} to a closed form. 
+\begin{align*}
+||\zeta_A^{-1}||_1\sum_{i = 1}^\infty ||(E\zeta_A^{-1})^i||_1 &\leq
+||\zeta_A^{-1}||_1 \sum_{i = 1}^\infty||E\zeta_A^{-1}||_1^i\\
+ &= ||\zeta_A^{-1}||\frac{||E\zeta_A^{-1}||_1}{1-||EA^{-1}||_1}.
+\end{align*}
+This is a closed form bound on the error in magnitude of using $\zeta_A + E$ instead of $\zeta_A$, which is what we are looking for.
+
+Unfortunately, this approach has a problem.
+We are interested in considering spaces and scales such that some groups of points form clusters, meaning that they are very near each other.
 This will lead to $\zeta_A$ being very nearly not invertible, which has the effect of causing $\zeta_A^{-1}$ to have very large positive and negative values.
 These might mostly cancel to give us the magnitude we expect, but when we take the $L_1$ norm, the values no longer cancel.
-This causes our error bounds to get quite large when the points are not all separated (see Figure \ref{fig:failed_bound}).
+This causes our error bounds to get quite large when the points are not all separated (see Figure \ref{fig:failed_bound} for an example).
 
@@
 \]
-\caption{A plot of the magnitude of a four-point square space, approximated by the product of two identical two-point spaces, with error bars calculated using the above technique when possible.
-Until all four points separate, the bounds are not useful or the limit diverges.}
+\caption{A plot of the magnitude of a four-point square space against the log of the scale factor $t$, approximated by the product of two identical two-point spaces, with error bars calculated using the above technique when possible.
+Until all four points separate, the bounds are not useful.}
 \label{fig:failed_bound}
@@
 It would be interesting to know how this might be done, depending on what restrictions we put on $E$.
-
-\iffalse
-\begin{examp} %TODO Rework 
-We will consider a situation quite similar to Example \ref{ex:4pt}. Let $M$ be the following generalized metric space:
-\begin{figure}[H]
-\[
-\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
-\node[circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](1) at (0,0) {};
-\node[circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](2) at (5,0) {};
-\node[circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](3) at (0,-.5) {};
-\node[circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](4) at (5,-.5) {};
-\draw[decoration={brace,raise=7pt},decorate] (1) -- (2) node[midway, above = 10pt] {$d$};
-\draw[decoration={brace, mirror, raise = 7pt},decorate] (1) -- (3) node[midway, left = 10pt] {1};
-% \draw (2) -- (4);
-% \draw (3) -- (4);
-\end{tikzpicture}\]
-\caption{}
-\label{fig:prod}
-\end{figure}
-And define $A,B$ as follows:
-
-\begin{figure}[H]
-\[
-\begin{tikzpicture}[auto, node distance = 3cm, main node/.style={dot}]
-\node[circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](1) at (9,0) {};
-\node[circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](2) at (9,-.5) {};
-\node[circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](3) at (0, -.25) {};
-\node[circle, draw, fill=black,
-                        inner sep=0pt, minimum width=4pt](4) at (5,-.25) {};
-\draw[decoration={brace,mirror, raise=7pt},decorate] (1) -- (2) node[midway, left = 10pt] {1};
-\draw[decoration={brace, raise = 7pt},decorate] (3) -- (4) node[midway, above = 10pt] {d};
-% \draw (2) -- (4);
-% \draw (3) -- (4);
-\end{tikzpicture}\]
-\caption{Again, two spaces whose product should be very similar to $M$.}
-\label{fig:factors}
-\end{figure}
-Suppose that we are trying to approximate $M$ using a product space of $A$ and $B$. We are interested in finding a bound on the error of our estimate.
-
-Let $\zeta_A, \zeta_B, \zeta_{A \times B}, \zeta_M$ be the similarity matrices of $A, B, A \times B$, and $M$ respectively.
-Recall that we are using the norm $|x| = e^{-tx}$, where we will vary $t$.
-So the matrices are as follows:
-\begin{align*}
-\zeta_A &= 
-\begin{bmatrix}
-1 & e^{-td} \\
-e^{-td} & 1
-\end{bmatrix}\\
-\zeta_B &= 
-\begin{bmatrix}
-1 & e^{-t} \\
-e^{-t} & 1
-\end{bmatrix}\\
-\zeta_{A \times B} = \zeta_A \otimes \zeta_B &= 
-\begin{bmatrix}
-1 & e^{-t} & e^{- td} & e^{-t(1 + d)}\\
-e^{-t} & 1 & e^{-t(1 + d)}& e^{- td}\\
-e^{-td} & e^{-t(1 + d)} & 1 & e^{-t}\\
-e^{-t(1 + d)} & e^{-td} & e^{-t} & 1
-\end{bmatrix}\\
-\zeta_M &= 
-\begin{bmatrix}
-1 & e^{-t} & e^{- td} & e^{-t\sqrt{1 + d^2}}\\
-e^{-t} & 1 &  e^{-t\sqrt{1 + d^2}}& e^{- td}\\
-e^{-td} &  e^{-t\sqrt{1 + d^2}} & 1 & e^{-t}\\
-e^{-t\sqrt{1 + d^2}}& e^{-td} & e^{-t} & 1
-\end{bmatrix}
-\end{align*}
-The similarity matrices of $A \times B$ and $M$ have most entries identical. We can quantify the difference between them. For any $d, t \in (0, \infty)$, let 
-\begin{align*}
-\ep_{dt} = e^{-t(1 + d)} - e^{-t\sqrt{1 + d^2}}\\
-E_{dt} = \begin{bmatrix}
-0 & 0 & 0 & \ep_{dt} \\
-0 & 0 & \ep_{dt} & 0 \\
-0 & \ep_{dt} & 0 & 0 \\
-\ep_{dt} & 0 & 0 & 0
-\end{bmatrix}
-\end{align*}
-Then for each $d,t$,
-\[
-\zeta_M = \zeta_{A \times B} - E_{dt}.
-\]
-Note that I am omitting the $d,t$ subscripts from the similarity matrices to avoid clutter, but they do depend on $d$ and $t$.
-
-If we are interested in bounding the difference in magnitude of $M$ and $A \times B$, then we can apply Theorem \ref{thm:approx}.
-We fix a $d$ to determine the relative scales of the spaces.
-Then, for any $t \in (0, \infty):$
-\[
-\mu_M = \mu_{A \times B} + \mu_{A \times B}\sum_{i = 1}^\infty (E_{dt}\zeta_{A \times B}^{-1})^i.
-\]
-
-This formula gives us a way of bounding how different the magnitude of the Euclidean spaces is from the product space.
-We can numerically calculate values for $\magn_t(M), \magn_t(A \times B)$, and the error term, and plot them.
-
-If $d = 0.1$, so the scales differ by a factor of ten, then we get the following as we vary $t$:
-\begin{figure}[H]
-\[
-\makebox[\textwidth][c]{\includegraphics[width = 0.9\paperwidth]{../Figures/error_10.png}}
-\]
-\caption{Magnitudes and error bounds, $d = 0.1$, error calculated to third term, against $\log(t)$ where $t$ is the scale factor.}
-\label{fig:approx10}
-\end{figure}
-We can see that the Euclidean space and the product space have very similar magnitude values, and the error bounds are quite tight.
-Note that the period where there are two clusters is much more subtle now, as the points merge together in faster succession.
-
-If we were trying to approximate $M$ with $A \times B$, then we would not have access to the orange line in Figure \ref{fig:approx10}.
-But in this case, we can see that we could determine the line with good accuracy using only $A \times B$ and the error bounds.
-
-As we move the value of $d$ closer to 1, we expect both the error bounds and the actual error to increase.
-The product space and the Euclidean space will differ more as their scales become more similar.
-Recall that the only pairs of points which differ at all in distance between $A \times B$ and $M$ are points at opposite corners (see Figure \ref{fig:4pt}).
-When one dimension is extremely small, that diagonal distance is very close to the length of the longer side.
-On the other hand, in the product space the distance is the sum of the dimensions.
-When the small dimension is small enough, that, too, is essentially the distance of the longer side.
-
-On the other hand, as $d$ approaches 1, the space becomes square.
-If $d=1$, then the distance of opposite points in $M$ will be $\sqrt{2}$, while in the product space the distance will be 2.
-This is quite a significant difference.
-In the next example, we look at exactly this case.
-
-Here we see what happens when $d=1$, so our dimensions are identical. Both spaces move smoothly from having a single cluster to having four clusters, and there is more error. 
-\begin{figure}[H]
-\[
-\makebox[\textwidth][c]{\includegraphics[width = 0.9\paperwidth]{../Figures/error_1.png}}
-\]
-\caption{Magnitudes and error bounds, $d = 1$, error calculated to third term, against $\log(t)$ where $t$ is the scale factor.}
-\end{figure}
-\end{examp}
-However, even if the orange line were removed, we would still have a good idea of the cluster structure of $M$.
-We would know that $M$ starts with one cluster, and then at a scale factor of approximately $10^{-\frac12} \approx 3$, the points begin to move apart.
-They smoothly separate until four clusters form.
-Because of the error bounds, we know that given the behavior of $A \times B$, the magnitude of $M$ can't differ too much from that behavior.
-\fi
 \end{chapter}
